### 2022-08-11 manuscript-figures.Rmd
first commit

---
title: "Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission"
author: |
    | Kyle J.-M. Dahlin, Suzanne M. O'Regan, Barbara A. Han, 
    | John Paul Schmidt, John M. Drake
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    keep_tex: yes
    extra_dependencies: ["float"]
    includes:
      in_header: header.tex
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "doc") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp) #nec
library(reshape2) #nec
library(cowplot)
library(viridis)
library(RColorBrewer) #nec
library(MetBrewer)
library(here)
library(lemon)  #nec
library(zplyr) # only needed for placing text using absolute coordinates in contact comparison figure

# Tell R where the manuscript lives
here::i_am("manuscript-figures.Rmd")

# Load in necessary functions and files---------------------------------------------------
# Functions for computing equilibrium quantities:
#  mosquito abundance (compute.V0), basic reproduction number (compute.R0)
source("code/output-functions.R")
```

```{r load-data, include=FALSE}
# Run analysis scripts to obtain data for plotting------------------------------
source("code/get-mosquito-traits.R")
source("code/get-analysis-dfs.R")

# Load data files and configure for plotting------------------------------------

## Vector trait thermal performance curves
VecParms <- read_csv("results/VectorTraits.csv", show_col_types = FALSE)

## Compute mosquito thermal tolerance range (minimum and maximum)
MosqThermRange_df <- VecParms %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()

## All outputs
  AllOutputs <- read_csv("results/AllOutputs.csv", show_col_types = FALSE)

  # Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
  AllOutputs <- AllOutputs %>%
    mutate(system_label = case_when(
      system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
      system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
      system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
      system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
      system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
    ))

  ## Add a "point at infinity" for sigmaH
  # Value of sigmaH to replace 'Inf' with for plotting
  infinite_skew <- 10^3 + 2500

  # Get the largest value of log10(sigmaH)
  max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
    select(sigmaH) %>%
    max() %>%
    log10()

  # Used to create a gap dividing finite and infinite sigmaH
  infinite_divide <- 10^mean(c(3, log10(infinite_skew)))

  # add a second proxy sigmaH point at infinity to make the values easier to see there
  temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
  AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
    sigmaH, infinite_skew
  ))
  AllOutputs <- add_row(AllOutputs, temp) %>% distinct()

  # Define sigmaH tick breaks and labels
  sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
  sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

## Parasite thermal characteristics
  ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)

  # Title names for each mosquito+pathogen combination
  ThermPathChars <- ThermPathChars %>%
    mutate(system_label = case_when(
      system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
      system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
      system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
      system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
      system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
    ))
  ## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
  # Value of sigmaH to replace 'Inf' with for plotting
  infinite_skew <- 10^3 + 2500

  # Get the largest value of log10(sigmaH)
  max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
    select(sigmaH) %>%
    max() %>%
    log10()

  # Used to create a gap dividing finite and infinite sigmaH
  infinite_divide <- 10^mean(c(3, log10(infinite_skew)))

  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
  ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
    sigmaH, infinite_skew
  ))
  # add a second proxy sigmaH point at infinity to make the values easier to see there
  temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))

  ThermPathChars <- add_row(ThermPathChars, temp) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  ## Options
  # Define sigmaH tick breaks and labels
  sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
  sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

```

```{r plot-settings, include = FALSE}
# Set theme
theme_set(theme_minimal(11))

# Helper function to place legends in empty facets of plot grids
# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
shift_legend <- function(p) {
  pnls <- cowplot::plot_to_gtable(p) %>%
    gtable::gtable_filter("panel") %>%
    with(setNames(grobs, layout$name)) %>%
    purrr::keep(~ identical(.x, zeroGrob()))

  if (length(pnls) == 0) stop("No empty facets in the plot")

  lemon::reposition_legend(p, "center", panel = names(pnls))
}
```

# Figures

```{r fig-1_contact_comparison, dev = c('pdf','svg', 'tiff'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}

# resolution setting
resolution <- 1E2

## Define different contact models
# For each model, there is a vector-to-host and host-to-vector term

# Bites per mosquito per day
vector_host_contact_func <- function(df) {
  with(as.list(df), {
    ret <- case_when(
      # Ross-Macdonald aka Reservoir frequency dependence
      model == "RM" ~ sigma_V,
      # Chitnis dynamic
      model == "CD" ~ sigma_V * sigma_H * H / (sigma_H * H + sigma_V * V)
    )
  })
}

# Bites per host per day
host_vector_contact_func <- function(df) {
  with(as.list(df), {
    ret <- case_when(
      # Ross-Macdonald aka Reservoir frequency dependence
      model == "RM" ~ sigma_V * V / H,
      # Chitnis dynamic
      model == "CD" ~ sigma_H * sigma_V * V / (sigma_H * H + sigma_V * V)
    )
  })
}

## Set up density ranges
host_density_range <- c(1E-1, 1E2)
host_fixed_value <- 50
host_density_vec <- sort(c(seq(host_density_range[1], host_density_range[2],
  length.out = resolution
), host_fixed_value))

vector_density_range <- c(0, 1E3)
vector_fixed_value <- 500
vector_density_vec <- sort(c(seq(vector_density_range[1], vector_density_range[2],
  length.out = resolution
), vector_fixed_value))

## Set other parameters
max_biting_rate <- 0.45
sigma_V <- max_biting_rate

host_annoyance_threshold <- 50
sigma_H <- host_annoyance_threshold

## Create contact dynamics dataframe
models <- c("RM", "CD")
names(models) <- c("Ross-Macdonald", "Chitnis dynamic")

contact_df <- expand.grid(
  H = host_density_vec,
  V = vector_density_vec,
  sigma_V = sigma_V,
  sigma_H = sigma_H,
  model = models
) %>%
  mutate("Transmission model" = names(model)) %>%
  mutate(bites_mosquito_time = vector_host_contact_func(.)) %>%
  mutate(bites_host_time = host_vector_contact_func(.)) %>%
  rename("Host population density" = H) %>%
  rename("Mosquito population density" = V) %>%
  rename("Bites per mosquito per day" = bites_mosquito_time) %>%
  rename("Bites per host per day" = bites_host_time)

## Put plots together:
new_df <- contact_df %>%
  filter(`Mosquito population density` == vector_fixed_value |
    `Host population density` == host_fixed_value) %>%
  filter(`Bites per host per day` < 1E3) %>%
  select(-sigma_V, -sigma_H, -model) %>%
  melt(
    id = c(
      "Transmission model", "Bites per mosquito per day",
      "Bites per host per day"
    ),
    value.name = "x_vals"
  ) %>%
  rename(x_vars = variable) %>%
  melt(id = c("Transmission model", "x_vars", "x_vals"), value.name = "y_vals") %>%
  rename(y_vars = variable) %>%
  filter(x_vals != host_fixed_value & x_vals != vector_fixed_value) %>%
  mutate(y_max = 1.05 * y_vals) %>%
  mutate(label = case_when(
    x_vars == "Host population density" & y_vars == "Bites per mosquito per day" ~ "(a)",
    x_vars == "Mosquito population density" & y_vars == "Bites per mosquito per day" ~ "(b)",
    x_vars == "Host population density" & y_vars == "Bites per host per day" ~ "(c)",
    x_vars == "Mosquito population density" & y_vars == "Bites per host per day" ~ "(d)"
  )) %>%
  distinct()

# x = Host population density, y = Bites per mosquito per day
plot_HD_MC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +

  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +

  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
    color = "black", show.legend = FALSE
  ) +

  # x-axis:
  scale_x_continuous(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per mosquito per day",
    expand = c(0, 0),
    limits = c(0, NA)
  )

# x = Mosquito population density, y = Bites per mosquito per day
plot_MD_MC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +

  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +

  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
    color = "black", show.legend = FALSE
  ) +

  # x-axis:
  scale_x_continuous(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

# x = Mosquito population density, y = Bites per host per day
plot_MD_HC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +

  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +

  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
    color = "black", show.legend = FALSE
  ) +

  # x-axis:
  scale_x_continuous(
    name = "Mosquito population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    limits = c(0, NA)
  )

# x = Host population density, y = Bites per host per day
plot_HD_HC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +

  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +

  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
    color = "black", show.legend = FALSE
  ) +

  # x-axis:
  scale_x_continuous(
    name = "Host population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per host per day",
    expand = c(0, 0),
    limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

contact_plot <- plot_grid(
  plot_HD_MC + theme(legend.position = "none"),
  plot_MD_MC + theme(legend.position = "none"),
  plot_HD_HC + theme(legend.position = "none"),
  plot_MD_HC + theme(legend.position = "none")
)

legend <- get_legend(
  plot_HD_MC +
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

contact_plot <- plot_grid(contact_plot, legend, ncol = 1, rel_heights = c(1, .05))

contact_plot
```

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'tiff'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model. '}

## Set up plot dataframe
MosqThermTraits_df <- VecParms %>%
  ## Set up plot dataframe
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Select relevant traits and parameters
  select(
    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
  ) %>%
  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
  # 'variables'
  melt(id = c("Temperature", "system_ID")) %>%
  group_by(Temperature, system_ID)

# Assign nice labels for each variable
levels(MosqThermTraits_df$variable) <- c(
  lambdaV = TeX("(a) Recruitment rate: $\\lambda_V$ (ind. day$^{-1}$)"),
  sigmaV = TeX("(b) Maximum biting frequency: $\\sigma_V$ (day$^{-1}$)"),
  betaV = TeX("(c) Vector competence: $\\beta_V$"),
  lf = TeX("(d) Average adult lifespan: $1/\\mu_V$ (days)"),
  P_EIP = TeX("(e) Prob. of surviving EIP: $\\theta_V$")
)

MosqThermTraits_plot <- MosqThermTraits_df %>%
  # Set up plotting variables and theme
  # x = Temperature, y = trait value
  ggplot(mapping = aes(x = Temperature, y = value, group = system_ID)) +

  # Plot trait values:
  geom_line(aes(colour = system_ID), size = 1) +

  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(10, 35),
    breaks = seq(10, 36, 2)
  ) +

  # y-axis:
  scale_y_continuous(expand = c(0.05, 0)) +

  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti+ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes aegypti+DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes albopictus+DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles spp.+P.fal." ~ "*Anopheles* spp. and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus+WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  ) +

  # faceting:
  facet_wrap(~variable, nrow = 3, scales = "free", labeller = labeller(variable = label_parsed)) +

  # legend:
  guides(color = guide_legend(override.aes = list(size = 4))) +

  # theme options:
  theme_minimal_vgrid(11) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(),
    legend.text = ggtext::element_markdown(),
    legend.direction = "vertical",
    legend.justification = "center",
    axis.title.x = element_text(hjust = 0.2),
    strip.text = element_text(
      face = "bold",
      hjust = 0
    )
  )

shift_legend(MosqThermTraits_plot)
```

```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'tiff'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}

# Plot R0 vs. temperature curves. One plot for each mosquito+pathogen pair.
# One curve for Ross-Macdonald, a few for Chitnis

# x-axes = temperature
# y-axes = R0 (normalized so that max(R0) = 1)
# plots = one for each mosquito+pathogen combination, "system_ID"
# curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
# curves  = Chitnis dynamic R0,
#   - colour = value of KH. place it on a color scale in the bottom right corner

  R0_df <- AllOutputs %>%
    # To set num. of curves, change "length.out" to be the number of curves you want
    filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)]) %>%
    # Just consider one finite value of sigmaH and the Ross-Macdonald model
    filter(sigmaH == 100 | is.infinite(sigmaH)) %>%
    # Group by curve_ID and system_ID
    group_by(Model, KH, system_ID) %>%
    # Normalize R0 for each curve_ID x system_ID combination, so that the maximum is always at one
    mutate(norm_R0 = R0 / max(R0)) %>%
    # Restrict temperatures to where R0 is positive
    filter(norm_R0 > 0) %>%
    arrange(system_ID, sigmaH, Temperature)

  ## PLOTTING ##
  R0_plot <- R0_df %>%
    # x = Temperature, y = normalized R0
    # grouped by K_H value
    ggplot(mapping = aes(
      x = Temperature,
      y = norm_R0,
      group = KH
    )) +

    # path of R0 as a function of temperature (finite sigmaH):
    geom_path(
      data = filter(R0_df, sigmaH == 100),
      aes(colour = KH, linetype = "finite")
    ) +
    # path of R0 as a function of temperature (infinite sigmaH):
    geom_path(
      data = filter(R0_df, sigmaH == Inf),
      aes(linetype = "infinite", colour = "black"),
      colour = "black",
      lwd = 1.5
    ) +

    # x-axis:
    scale_x_continuous(
      name = "Temperature (°C)",
      expand = c(0, 0),
      limits = c(15, 35)
    ) +
    # y-axis:
    scale_y_continuous(
      name = TeX("Normalized $R_0$"),
      expand = c(0, .05)
    ) +

    # color: scaled log10, color-blind friendly
    scale_color_viridis(
      name = "Vertebrate host population\ndensity (ind/ha)",
      trans = "log10",
      breaks = 10^seq(-2, 4),
      labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
      option = "plasma"
    ) +

    # linetype:
    scale_linetype_manual(
      name = "Biting tolerance\n(bites per host per day)",
      breaks = c("finite", "infinite"),
      labels = unname(c(TeX("100 (Chitnis)"), TeX("$\\infty$ (Ross-Macdonald)"))),
      values = c("solid", "22")
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # legend
    guides(
      color = guide_colourbar(
        title.position = "top",
        nrow = 1,
        barwidth = 12,
        show.limits = TRUE,
        direction = "horizontal"
      ),
      linetype = guide_legend(
        title.position = "top",
        nrow = 2,
        keywidth = 4,
        direction = "vertical"
      )
    ) +

    # theme options:
    theme_minimal_vgrid(11) +
    theme(
      legend.box = "vertical",
      legend.margin = margin(),
      legend.title = element_text(size = 10),
      legend.text = element_text(
        size = 10,
        hjust = 0
      ),
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # move legend into lower right-hand corner
  shift_legend(R0_plot)
```

```{r fig-5_Topt, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = width of parasite thermal niche (CTmax - CTmin)
# Facets = systems

  Toptalt_df <- ThermPathChars %>%
    ungroup() %>%
    distinct() %>%
    # Arrange along the plotting variables
    arrange(system_label, sigmaH_proxy, KH, Topt)

  # add many proxy sigmaH points at infinity to make the values easier to see there
  temp <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.25 * infinite_divide, infinite_skew))
    ))
  temp2 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.15 * infinite_divide, infinite_skew))
    ))
  temp3 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.05 * infinite_divide, infinite_skew))
    ))
  temp4 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.3 * infinite_divide, infinite_skew))
    ))
  temp5 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.2 * infinite_divide, infinite_skew))
    ))
  temp6 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.1 * infinite_divide, infinite_skew))
    ))
  temp7 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(infinite_divide, infinite_skew))
    ))

  Toptalt_df <- add_row(Toptalt_df, temp)
  Toptalt_df <- add_row(Toptalt_df, temp2)
  Toptalt_df <- add_row(Toptalt_df, temp3)
  Toptalt_df <- add_row(Toptalt_df, temp4)
  Toptalt_df <- add_row(Toptalt_df, temp5)
  Toptalt_df <- add_row(Toptalt_df, temp6)
  Toptalt_df <- add_row(Toptalt_df, temp7) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  Topt_breaks <- seq(21, 31, by = 1)

  Toptalt_plots <- Toptalt_df %>%
    ## Set up plot ##
    # x = biting tolerance (with a point at infinity),
    # y = vertebrate host population density,
    # color = transmission thermal optimum
    ggplot(aes(x = KH, y = sigmaH_proxy)) +

    # Topt for FINITE sigmaH:
    geom_contour_filled(
      data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.98),
      aes(z = Topt),
      breaks = Topt_breaks
    ) +

    # Topt for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.02),
      aes(z = Topt),
      size = 1,
      breaks = Topt_breaks
    ) +

    # R0 = 1 contour:
    geom_contour(aes(z = R0opt, colour = "R0=1"), breaks = c(1), size = 1) +

    # x-axis: log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(0.05, 1E4),
      breaks = 10^seq(-1, 4, 1),
      labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
    ) +
    # y-axis: log10-scale y axis, with no buffer space
    scale_y_log10(
      name = TeX("Biting tolerance (bites per host per day)"),
      expand = c(0, 0),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels
    ) +

    # fill:
    scale_fill_manual(
      name = "Transmission thermal optimum (°C)",
      values = met.brewer("Johnson",
        n = length(Topt_breaks),
        direction = -1
      )
    ) +

    # color:
    scale_colour_manual(
      name = "",
      labels = c("R0=1" = unname(TeX("$R_0=1$"))),
      values = c("black"),
      guide = guide_legend(
        order = 1,
        keyheight = unit(1, "cm"),
        override.aes = list(size = 6)
      )
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # legend:
    guides(fill = guide_coloursteps(
      title.position = "top", title.hjust = 0.5,
      barwidth = unit(5, "cm"),
      show.limits = TRUE
    )) +

    # theme options:
    theme_minimal(11) +
    theme(
      legend.box = "vertical",
      legend.position = "bottom",
      legend.margin = margin(0, 0, 0, 0),
      legend.title = element_text(size = 10),
      legend.direction = "horizontal",
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(Toptalt_plots)
```

```{r fig-6_CT_Width, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = width of parasite thermal niche (CTmax - CTmin)
# Facets = systems

  CTWidth_df <- ThermPathChars %>%
    ungroup() %>%
    # Calculate thermal niche width
    mutate(CTwidth = CTmax - CTmin) %>%
    mutate(CTwidth = replace(CTwidth, is.na(CTwidth), 0)) %>%
    distinct() %>%
    select(system_label, sigmaH, sigmaH_proxy, KH, CTwidth) %>%
    # Arrange along the plotting variables
    arrange(system_label, sigmaH_proxy, KH, CTwidth)

  # add many third proxy sigmaH points at infinity to make the values easier to see there
  temp <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.25 * infinite_divide, infinite_skew))
    ))
  temp2 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.15 * infinite_divide, infinite_skew))
    ))
  temp3 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.05 * infinite_divide, infinite_skew))
    ))
  temp4 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.3 * infinite_divide, infinite_skew))
    ))
  temp5 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.2 * infinite_divide, infinite_skew))
    ))
  temp6 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.1 * infinite_divide, infinite_skew))
    ))
  temp7 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(infinite_divide, infinite_skew))
    ))

  CTWidth_df <- add_row(CTWidth_df, temp)
  CTWidth_df <- add_row(CTWidth_df, temp2)
  CTWidth_df <- add_row(CTWidth_df, temp3)
  CTWidth_df <- add_row(CTWidth_df, temp4)
  CTWidth_df <- add_row(CTWidth_df, temp5)
  CTWidth_df <- add_row(CTWidth_df, temp6)
  CTWidth_df <- add_row(CTWidth_df, temp7) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  CTWidth_heat_plots <- CTWidth_df %>%
    ## Set up plot ##
    # x = biting tolerance (with a point at infinity),
    # y = vertebrate host population density,
    # color = width of parasite thermal niche
    ggplot(aes(x = KH, y = sigmaH_proxy)) +

    # CTwidth for FINITE sigmaH:
    geom_contour_filled(
      data = filter(CTWidth_df, sigmaH_proxy < infinite_divide**0.98),
      aes(z = CTwidth)
    ) +

    # CTwidth for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(CTWidth_df, sigmaH_proxy > infinite_divide**1.02),
      aes(z = CTwidth)
    ) +

    # x-axis: log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(0.05, 1E4),
      breaks = 10^seq(-1, 4, 1),
      labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
    ) +
    # y-axis: log10-scale y axis, with no buffer space
    scale_y_log10(
      name = TeX("Biting tolerance (bites per host per day)"),
      expand = c(0, 0),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels
    ) +
    # color:
    scale_fill_viridis_d(
      name = "Parasite thermal tolerance\nrange width (°C)",
      option = "plasma"
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # legend:
    guides(fill = guide_coloursteps(
      title.position = "top", title.hjust = 0.5,
      barwidth = unit(5, "cm"),
      show.limits = TRUE
    )) +

    # theme options:
    theme_minimal(11) +
    theme(
      legend.box = "horizontal",
      legend.position = "bottom",
      legend.margin = margin(0, 0, 0, 0),
      legend.title = element_text(size = 10),
      legend.direction = "horizontal",
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(CTWidth_heat_plots)
```

# Supplementary Figures

```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.

# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
# y = Temperature
# color = R0
# curves:
#   R0 = 1 contour (black curve)
#   Topt (red curve)

# Facets:
# Rows = levels of vertebrate host population density
# Columns = two MBPT systems
# Total = 6 plots

  ## Set up plot data frame
  # We re-create the output data frame so that we can vary sigmaH correctly.
  # We also drop the resolution of KH down to just three values
  # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"

  ## Configure data frame for plotting
  R0_df <- AllOutputs %>%
    select(system_ID, system_label, Temperature, sigmaH, KH, R0) %>%
    # Consider only 3 values of KH (on a log10-scale)
    filter(KH %in% c(1E-1, 1E0, 1E1)) %>%
    # Choose a limited range of sigmaH values
    filter(sigmaH > 10^0.5) %>%
    # Group by plotting variables
    group_by(system_ID, KH, sigmaH) %>%
    # Calculate Topt (which.max requires grouping)
    mutate(Topt = `Temperature`[which.max(R0)]) %>%
    as_tibble() %>%
    arrange(system_ID, sigmaH, Temperature)

  ## Add a "point at infinity" for sigmaH
  # Value of sigmaH to replace 'Inf' with for plotting
  infinite_skew <- 10^3 + 2500

  # Get the largest value of log10(sigmaH)
  max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
    select(sigmaH) %>%
    max() %>%
    log10()

  # Used to create a gap dividing finite and infinite sigmaH
  infinite_divide <- 10^mean(c(3, log10(infinite_skew)))

  # add a second proxy sigmaH point at infinity to make the values easier to see there
  temp <- filter(R0_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
  R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
    sigmaH, infinite_skew
  ))
  R0_df <- add_row(R0_df, temp) %>% distinct()

  ## Compute mosquito thermal tolerance range (minimum and maximum)
  temp_MosqThermRange_df <- MosqThermRange_df %>%
    select(system_label, CTmin_V0, CTmax_V0)

  ## PLOTTING ##

  ## Options
  # Define sigmaH tick breaks and labels
  sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
  sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

  # Labels for facet rows
  R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
  mylabels <- as_labeller(c(
    `0.1` = "0.1 vertebrate hosts / ha",
    `1` = "1 vertebrate host / ha",
    `10` = "10 vertebrate hosts / ha"
  ))

  # Breaks used to decide fill for the heat map
  fill_breaks <- c(1, seq(5, 20, by = 5), Inf)

  # Define colors for heat map so that values of R0>1 go from yellow to red
  my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))

  ## PLOT ##
  R0_plot <- R0_df %>%
    ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +

    # Mosquito thermal tolerance range lines
    geom_hline(
      data = temp_MosqThermRange_df,
      aes(yintercept = CTmin_V0, colour = "VTTR"),
      lwd = 1.275
    ) +
    geom_hline(
      data = temp_MosqThermRange_df,
      aes(yintercept = CTmax_V0, colour = "VTTR"),
      lwd = 1.275
    ) +

    # R0 contours for FINITE sigmaH:
    geom_contour_filled(
      data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
      breaks = fill_breaks
    ) +

    # R0 contours for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
      breaks = fill_breaks
    ) +

    # R0 = 1 contour:
    geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +

    # Topt curve:
    geom_line(
      # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
      mapping = aes(
        x = sigmaH_proxy,
        y = Topt,
        colour = "Topt"
      ),
      lwd = 1,
      linetype = 1
    ) +

    # white lines breaking up finite/infinite sigmaH values
    geom_vline(
      aes(xintercept = 0.85 * infinite_divide),
      colour = "white",
      lwd = .8,
      show.legend = FALSE
    ) +
    geom_vline(
      aes(xintercept = infinite_divide),
      colour = "white",
      lwd = .8,
      show.legend = FALSE
    ) +
    geom_vline(
      aes(xintercept = 1.2 * infinite_divide),
      colour = "white",
      lwd = .8,
      show.legend = FALSE
    ) +

    # x-axis:
    scale_x_log10(
      name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels,
      expand = c(0, 0)
    ) +

    # y-axis:
    scale_y_continuous(
      name = expression("Temperature "(degree * C)),
      expand = c(0, 0),
      limits = c(14, 36),
      breaks = seq(10, 36, by = 2)
    ) +

    # color:
    scale_colour_manual(
      name = "",
      labels = c(
        "R0=1" = unname(TeX("$R_0=1$")),
        "Topt" = "Transmission\nthermal\noptimum",
        "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
      ),
      values = c("black", "purple", "grey"),
      guide = guide_legend(
        order = 1,
        keyheight = unit(2, "cm"),
        override.aes = list(size = 6)
      )
    ) +

    # fill:
    scale_fill_manual(
      name = TeX("$R_0$"),
      values = my.cols,
      guide = guide_colorsteps(
        order = 2,
        breaks = fill_breaks,
        barheight = unit(8, "cm")
      )
    ) +

    # faceting:
    facet_rep_grid(
      rows = vars(system_label),
      cols = vars(KH),
      scales = "free_y",
      labeller = labeller(.cols = mylabels),
      repeat.tick.labels = "left"
    ) +

    # theme options:
    theme_minimal_hgrid(11) +
    theme(
      axis.line = element_line(),
      panel.spacing = unit(1, "lines"),
      legend.text = element_text(size = 11),
      legend.text.align = 0,
      strip.text = ggtext::element_markdown(
        size = 8,
        hjust = 0
      )
    )

  # Plot it
  R0_plot
```

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}

  Topt_df <- ThermPathChars %>%
    filter(KH > 0.01) %>%
    filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
    group_by(KH) %>%
    # Arrange along the plotting variables
    arrange(system_ID, KH, Topt) %>%
    arrange(sigmaH) %>%
    ungroup()

  Topt_plots <- Topt_df %>%
    ## Set up plot ##
    # x = blood meal supply, y = thermal optimum,
    # color = sigmaH
    ggplot(aes(
      x = KH, y = Topt,
      colour = as.factor(sigmaH)
    )) +

    # Topt curves:
    geom_path(lwd = 1) +

    # x-axis: log10 scale, no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(0.01, 2E4),
      breaks = 10^seq(-2, 4),
      labels = TeX(c(
        "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
      ))
    ) +

    # y-axis
    scale_y_continuous(
      name = expression("Thermal optimum "(degree * C)),
      expand = c(0.05, 0.05),
      limits = range(ThermPathChars$Topt),
      breaks = seq(floor(range(ThermPathChars$Topt)[1]),
        floor(range(ThermPathChars$Topt)[2]),
        by = 1
      )
    ) +
    # color:
    scale_colour_manual(
      name = "Vertebrate host biting tolerance\n(bites per host per day)",
      values = c(met.brewer("VanGogh3", 3, direction = 1), "black"),
      # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
      breaks = c(1, 10, 100, Inf),
      labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
    ) +

    # faceting:
    facet_wrap(~system_label,
      scales = "free",
      nrow = 2,
      labeller = labeller()
    ) +

    # theme options:
    theme_minimal_hgrid(11) +
    guides(color = guide_legend(override.aes = list(size = 4))) +
    theme(
      legend.position = "bottom",
      legend.margin = margin(),
      legend.direction = "vertical",
      legend.title = element_text(size = 10),
      legend.text = element_text(
        size = 10,
        hjust = 0
      ),
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(Topt_plots)

```

```{r fig-S3_Topt_plots, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}

  # x-axis = vertebrate host biting tolerance
  # y-axis = thermal optimum
  # color = vertebrate host population density

  Topt_df <- ThermPathChars %>%
    # Choose appropriate pop. dens. values and group
    filter(KH %in% 10^seq(0, 4)) %>%
    group_by(KH) %>%
    # Arrange along the plotting variables
    arrange(system_ID, sigmaH, Topt) %>%
    arrange(KH) %>%
    ungroup()

  Topt_plots <- Topt_df %>%
    ## Set up plot ##
    # x-axis = vertebrate host biting tolerance, y-axis = thermal optimum,
    # color = vertebrate host population density
    ggplot(aes(x = sigmaH_proxy, y = Topt, colour = as.factor(KH))) +

    # Topt curves:
    geom_path(lwd = 2) +

    # white lines breaking up finite/infinite sigmaH values:
    geom_vline(
      aes(xintercept = 0.95 * infinite_divide),
      colour = "white",
      lwd = .9,
      show.legend = FALSE
    ) +
    geom_vline(
      aes(xintercept = 1.05 * infinite_divide),
      colour = "white",
      lwd = .9,
      show.legend = FALSE
    ) +
    geom_vline(
      aes(xintercept = 1.15 * infinite_divide),
      colour = "white",
      lwd = .9,
      show.legend = FALSE
    ) +

    # x-axis: Use a log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
      expand = c(0, 0),
      limits = c(5, 3500),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels
    ) +

    # y-axis: Set limits and breaks and add some buffer space
    scale_y_continuous(
      name = expression("Thermal optimum "(degree * C)),
      expand = c(0.05, 0.05),
      limits = range(ThermPathChars$Topt),
      breaks = seq(floor(range(ThermPathChars$Topt)[1]),
        floor(range(ThermPathChars$Topt)[2]),
        by = 1
      )
    ) +

    # color:
    scale_colour_manual(
      name = "Vertebrate host population\ndensity (ind/ha)",
      values = met.brewer("Hokusai3", 5),
      # option = "plasma"
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # theme options:
    theme_minimal_hgrid(11) +
    guides(color = guide_legend(override.aes = list(size = 4))) +
    theme(
      legend.position = "bottom",
      legend.margin = margin(),
      legend.direction = "vertical",
      legend.justification = "center",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(Topt_plots)
```

```{r fig-S4_CTmin, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = CTmin
# Facets = systems

  CTmin_df <- ThermPathChars %>%
    ungroup() %>%
    distinct() %>%
    # Arrange along the plotting variables
    arrange(system_label, sigmaH_proxy, KH, CTmin)

  # add many proxy sigmaH points at infinity to make the values easier to see there
  temp <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.25 * infinite_divide, infinite_skew))
    ))
  temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.15 * infinite_divide, infinite_skew))
    ))
  temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.05 * infinite_divide, infinite_skew))
    ))
  temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.3 * infinite_divide, infinite_skew))
    ))
  temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.2 * infinite_divide, infinite_skew))
    ))
  temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.1 * infinite_divide, infinite_skew))
    ))
  temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(infinite_divide, infinite_skew))
    ))

  CTmin_df <- add_row(CTmin_df, temp)
  CTmin_df <- add_row(CTmin_df, temp2)
  CTmin_df <- add_row(CTmin_df, temp3)
  CTmin_df <- add_row(CTmin_df, temp4)
  CTmin_df <- add_row(CTmin_df, temp5)
  CTmin_df <- add_row(CTmin_df, temp6)
  CTmin_df <- add_row(CTmin_df, temp7) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  CTmin_breaks <- seq(15, 31, by = 1)

  CTmin_plots <- CTmin_df %>%
    ## Set up plot ##
    # x = biting tolerance (with a point at infinity),
    # y = vertebrate host population density,
    # color = transmission thermal optimum
    ggplot(aes(x = KH, y = sigmaH_proxy)) +

    # CTmin for FINITE sigmaH:
    geom_contour_filled(
      data = filter(CTmin_df, sigmaH_proxy < infinite_divide**0.98),
      aes(z = CTmin),
      breaks = CTmin_breaks
    ) +

    # CTmin for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(CTmin_df, sigmaH_proxy > infinite_divide**1.02),
      aes(z = CTmin),
      size = 1,
      breaks = CTmin_breaks
    ) +

    # x-axis: log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(0.05, 1E4),
      breaks = 10^seq(-1, 4, 1),
      labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
    ) +
    # y-axis: log10-scale y axis, with no buffer space
    scale_y_log10(
      name = TeX("Biting tolerance (bites per host per day)"),
      expand = c(0, 0),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels
    ) +

    # fill:
    scale_fill_viridis_d(
      name = "Critical thermal minimum (°C)"
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # legend:
    guides(fill = guide_coloursteps(
      title.position = "top",
      title.hjust = 0.5,
      direction = "vertical",
      barheight = unit(6, "cm"),
      show.limits = TRUE
    )) +

    # theme options:
    theme_minimal(11) +
    theme(
      plot.title = ggtext::element_markdown(),
      legend.position = "right",
      legend.margin = margin(0, 0, 0, 0),
      legend.text = element_text(size = 11),
      legend.title = element_text(size = 11, hjust = 0),
      legend.direction = "horizontal",
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0)
      )
    )

  # Plot
  shift_legend(CTmin_plots)
```

```{r fig-S5_CTmax, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'}

# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = CTmax
# Facets = systems

  CTmax_df <- ThermPathChars %>%
    ungroup() %>%
    distinct() %>%
    # Arrange along the plotting variables
    arrange(system_label, sigmaH_proxy, KH, CTmin)

  # add many proxy sigmaH points at infinity to make the values easier to see there
  temp <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.25 * infinite_divide, infinite_skew))
    ))
  temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.15 * infinite_divide, infinite_skew))
    ))
  temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.05 * infinite_divide, infinite_skew))
    ))
  temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.3 * infinite_divide, infinite_skew))
    ))
  temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.2 * infinite_divide, infinite_skew))
    ))
  temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.1 * infinite_divide, infinite_skew))
    ))
  temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(infinite_divide, infinite_skew))
    ))

  CTmax_df <- add_row(CTmax_df, temp)
  CTmax_df <- add_row(CTmax_df, temp2)
  CTmax_df <- add_row(CTmax_df, temp3)
  CTmax_df <- add_row(CTmax_df, temp4)
  CTmax_df <- add_row(CTmax_df, temp5)
  CTmax_df <- add_row(CTmax_df, temp6)
  CTmax_df <- add_row(CTmax_df, temp7) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  CTmax_breaks <- seq(23, 35, by = 1)

  CTmax_plots <- CTmax_df %>%
    ## Set up plot ##
    # x = biting tolerance (with a point at infinity),
    # y = vertebrate host population density,
    # color = transmission thermal optimum
    ggplot(aes(x = KH, y = sigmaH_proxy)) +

    # CTmin for FINITE sigmaH:
    geom_contour_filled(
      data = filter(CTmax_df, sigmaH_proxy < infinite_divide**0.98),
      aes(z = CTmax),
      breaks = CTmax_breaks
    ) +

    # CTmin for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(CTmax_df, sigmaH_proxy > infinite_divide**1.02),
      aes(z = CTmax),
      size = 1,
      breaks = CTmax_breaks
    ) +

    # x-axis: log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(0.05, 1E4),
      breaks = 10^seq(-1, 4, 1),
      labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
    ) +
    # y-axis: log10-scale y axis, with no buffer space
    scale_y_log10(
      name = TeX("Biting tolerance (bites per host per day)"),
      expand = c(0, 0),
      breaks = sigmaH_breaks,
      labels = sigmaH_labels
    ) +

    # fill:
    scale_fill_manual(
      name = "Critical thermal maximum (°C)",
      values = met.brewer("Tam",
        n = length(CTmax_breaks),
        direction = -1
      )
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

    # legend:
    guides(fill = guide_coloursteps(
      title.position = "top",
      title.hjust = 0.5,
      direction = "vertical",
      barheight = unit(6, "cm"),
      show.limits = TRUE
    )) +

    # theme options:
    theme_minimal(11) +
    theme(
      plot.title = ggtext::element_markdown(),
      legend.position = "right",
      legend.margin = margin(0, 0, 0, 0),
      legend.text = element_text(size = 11),
      legend.title = element_text(size = 11, hjust = 0),
      legend.direction = "horizontal",
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0)
      )
    )

  # Plot
  shift_legend(CTmax_plots)
```

```{r fig-S6_CT_Range, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'}
# x-axis = vertebrate host population density
# y-axis = Temperature
# linetype = biting tolerance
# colour = CT_min (blue), CT_max (red)

  CTRange_df <- ThermPathChars %>%
    # Arrange along the plotting variables
    select(system_label, sigmaH, KH, CTmax, CTmin) %>%
    # Choose a few sigmaH values to plot, including Inf
    filter(sigmaH %in% c(10, 50, Inf)) %>%
    group_by(KH) %>%
    # Arrange along the plotting variables
    arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
    ungroup() %>%
    melt(id = c("system_label", "KH", "sigmaH")) %>%
    arrange(KH, sigmaH)

  CTRange_plots <- CTRange_df %>%
    ## Set up plot ##
    # x-axis = population density, y-axis = temperature,
    # color = thermal extrema, linetype = sigmaH
    ggplot(aes(
      x = KH, y = value,
      linetype = as.factor(sigmaH), color = variable
    )) +

    # Mosquito thermal tolerance range lines
    geom_hline(
      data = MosqThermRange_df,
      aes(yintercept = CTmin_V0, colour = "VTTR"),
      lwd = 1.275
    ) +
    geom_hline(
      data = MosqThermRange_df,
      aes(yintercept = CTmax_V0, colour = "VTTR"),
      lwd = 1.275
    ) +

    # Curves showing CTmin and CTmax
    geom_path(
      data = filter(CTRange_df, variable == "CTmin"),
      lwd = 1
    ) +
    geom_path(
      data = filter(CTRange_df, variable == "CTmax"),
      lwd = 1
    ) +

    # x-axis: log10-scale with no buffer space
    scale_x_log10(
      name = TeX("Vertebrate host population density (ind/ha)"),
      expand = c(0, 0),
      limits = c(1E-2, 1E5),
      breaks = 10^seq(-1, 4),
      labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
    ) +
    # y-axis: small buffer space
    scale_y_continuous(
      name = expression("Temperature "(degree * C)),
      expand = c(0.05, 0.05),
      limits = range(CTRange_df$value, na.rm = TRUE),
      breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
        floor(range(CTRange_df$value, na.rm = TRUE)[2]),
        by = 2
      )
    ) +
    # linetype:
    scale_linetype_manual(
      name = "Vertebrate host biting tolerance\n(bites per host per day)",
      values = c("solid", "longdash", "dotted"),
      breaks = c(10, 50, Inf),
      labels = unname(c("10 (Chitnis)", "50 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
    ) +
    # color:
    scale_colour_manual(
      name = "Thermal extrema",
      breaks = c("CTmax", "CTmin", "VTTR"),
      labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"),
      values = c("red", "blue", "grey"),
      guide = guide_legend(keyheight = unit(40, "cm"))
    ) +

    # faceting:
    facet_wrap(~system_label,
      scales = "free",
      nrow = 2,
      labeller = labeller()
    ) +

    # legend:
    guides(
      color = guide_legend(
        override.aes = list(size = 4),
        order = 1
      ),
      linetype = guide_legend(
        keywidth = 4,
        order = 2
      ),
    ) +

    # theme options:
    theme_minimal_hgrid(11) +
    theme(
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0
      )
    )

  # Plot
  shift_legend(CTRange_plots)
```

```{r fig-S7_CH_Range, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CH_Range} Critical community sizes as a function of temperature and biting tolerance.'}

# x = vertebrate host population density
# y = Temperature
# linetype = vertebrate host biting tolerance (needs to vary from "zero to infinity")
# curves:
#   CH_min - blue
#   CH_max - red
#   VTTR - black

  # build data frame for plotting
  CHRange_df <- AllOutputs %>%
    ungroup() %>%
    # Arrange along the plotting variables
    select(system_label, Temperature, sigmaH, CHmax, CHmin) %>%
    filter(sigmaH %in% c(10, 50, 100)) %>%
    filter(is.finite(CHmax)) %>%
    filter(CHmin > 0) %>%
    distinct() %>%
    # Arrange along the plotting variables
    arrange(system_label, Temperature, sigmaH, CHmax, CHmin) %>%
    melt(id = c("system_label", "Temperature", "sigmaH")) %>%
    arrange(Temperature, sigmaH)

  CHRange_plots <- CHRange_df %>%
    ## Set up plot ##
    # x = threshold values, y = temperature,
    # color = threshold type, line type = sigmaH
    ggplot(aes(
      x = value, y = Temperature,
      color = variable, linetype = as.factor(sigmaH)
    )) +

    # mosquito thermal tolerance range curves:
    geom_hline(
      data = MosqThermRange_df,
      aes(yintercept = CTmin_V0, colour = "VTTR"),
      lwd = 1
    ) +
    geom_hline(
      data = MosqThermRange_df,
      aes(yintercept = CTmax_V0, colour = "VTTR"),
      lwd = 1
    ) +

    # CH threshold curves:
    geom_path(
      data = filter(CHRange_df, variable == "CHmin" & is.finite(sigmaH)),
      lwd = 1
    ) +
    geom_path(
      data = filter(CHRange_df, variable == "CHmax"),
      lwd = 1
    ) +

    # x-axis: log10-scaled with no buffer-space
    scale_x_log10(
      name = TeX("Vertebrate host population density"),
      expand = c(0, 0),
      limits = c(0.01, 2E5),
      breaks = 10^seq(-2, 5),
      labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$", "$10^5$"))
    ) +
    # y-axis:
    scale_y_continuous(
      name = expression("Temperature "(degree * C)),
      expand = c(0.05, 0.05),
      limits = range(CHRange_df$Temperature),
      breaks = seq(floor(range(CHRange_df$Temperature)[1]),
        floor(range(CHRange_df$Temperature)[2]),
        by = 2
      )
    ) +
    # linetype:
    scale_linetype_manual(
      name = "Biting tolerance\n(bites per host per day)",
      values = c("solid", "longdash", "dotdash"),
      breaks = c(10, 50, 100)
    ) +

    # color:
    scale_colour_manual(
      name = "Threshold type",
      values = c("red", "blue", "grey"),
      breaks = c("CHmax", "CHmin", "VTTR"),
      labels = c("Maximum community size", "Minimum community size", "Mosquito thermal niche")
    ) +

    # faceting:
    facet_wrap(~system_label, scales = "free", nrow = 2) +

    # legend:
    guides(
      color = guide_legend(
        override.aes = list(size = 4),
        order = 1
      ),
      linetype = guide_legend(
        keywidth = 4,
        order = 2
      ),
    ) +
    # theme options:
    theme_minimal_vgrid(11) +
    theme(
      legend.box = "vertical",
      legend.position = "bottom",
      legend.margin = margin(0, 0, 0, 0),
      legend.text = ggtext::element_markdown(),
      legend.title = element_text(size = 11),
      legend.direction = "vertical",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(CHRange_plots)
```

```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}

# Estimating the difference between Topt and Topt_RM numerically using our previous data
Toptdiff_df1 <- ThermPathChars %>%
  select(system_ID, sigmaH, KH, Topt) %>%
  filter(is.finite(sigmaH)) %>%
  distinct()

Toptdiff_df2 <- ThermPathChars %>%
  filter(is.infinite(sigmaH)) %>%
  select(system_ID, KH, Topt) %>%
  rename(Topt_RM = Topt) %>%
  distinct()

Toptdiff_df <- left_join(Toptdiff_df1, Toptdiff_df2) %>%
  mutate(Toptdiff = Topt_RM - Topt) %>%
  mutate(absToptdiff = abs(Toptdiff)) %>%
  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
  mutate(sigmaHKH = sigmaH * KH) %>%
  group_by(system_ID) %>%
  filter(absToptdiff == max(absToptdiff)) %>%
  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
  distinct()

# Calculating Topt0 using the "simplified" equation
Topt0_df <- VecParms %>%
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
  filter(is.finite(proxy_0)) %>%
  select(system_ID, Temperature, proxy_0) %>%
  group_by(system_ID)

Topt0_base_estimates <- Topt0_df %>%
  group_by(system_ID) %>%
  # Calculate Topt_0
  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
  rename(Topt_0 = Temperature)
# check with above: Topt_0 matches with Topt when sigmaH*KH is minimized
# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)

# Calculating Topt0 using the "simplified" equation
ToptRM_df <- VecParms %>%
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
  select(system_ID, Temperature, proxy_RM) %>%
  group_by(system_ID)

ToptRM_base_estimates <- ToptRM_df %>%
  group_by(system_ID) %>%
  # Calculate Topt_RM
  filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>%
  rename(Topt_RM = Temperature)
# check with above: Topt_RM matches with Topt when sigmaH*KH is maximized
# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)

Topt_estimates <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
  select(system_ID, Topt_RM, Topt_0) %>%
  mutate(Topt_diff = Topt_RM - Topt_0) %>%
  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)

# Investigating Topt_RM and Topt_0 further

test_df <- VecParms %>%
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(sigmaVV0 = sigmaV * V0) %>%
  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0
  filter(is.finite(proxy_0)) %>%
  select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0)
```

### 2022-08-11 code/get-analysis-dfs.R

@@ -1,0 +1,215 @@
+## For questions, contact Kyle Dahlin, kydahlin@gmail.com
+## Originated September 2021
+##
+## Title: Analysis code for "Thermal optima" manuscript ########################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Build data frames for: 1) vector traits, 2) all traits and model
+##          outputs, and 3) thermal characteristics of transmission
+##
+## Contents: 0) Load in necessary packages, functions, settings
+##           1) Build vector trait data frame
+##           2) Build all traits and model outputs data frame
+##           3) Build thermal characteristics data frame
+##
+##
+## Settings:  Options for reducing the resolution of variables for memory
+##            allocation and figure plotting purposes
+##
+##
+## Outputs: (in ./results)
+##          1) VectorTraits.csv - vector trait data frame
+##          2) AllOutputs.csv - all traits and model outputs data frame
+##          3) ThermalCharacteristics.csv - thermal characteristics data frame
+##
+
+# 0) Load in necessary packages, functions, settings ###########################
+# Packages
+require(tidyverse)
+
+# Functions for computing transmission measures
+source("code/output-functions.R")
+
+## Settings---------------------------------------------------------------------
+
+# Resolution settings: (set these to Inf to keep original resolution)
+# Temperature: Factor by which to reduce resolution
+Temp_vec_length <- 500
+
+# Host density vector: Number of values to include to consider for vertebrate host density
+KH_vec_length <- 100
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 100
+
+# 1) Build vector trait data frame #############################################
+## Assign names to mosquitoes and pathogens
+# Define mosquito species names and codes:
+mosquito_names <- c(
+  "Aedes aegypti", "Aedes albopictus",
+  "Culex quinquefasciatus", "Anopheles spp."
+)
+
+# Define pathogen names and codes
+pathogen_names <- c("DENV", "ZIKV", "WNV", "P.fal.")
+
+## Build table of mosquito parameters-------------------------------------------
[…]

### 2022-08-11 code/get-mosquito-traits.R

@@ -1,0 +1,224 @@
+## Kyle Dahlin, University of Georgia, kydahlin@gmail.com
+## Started September 2021
+##
+## Title: Mosquito trait functions #############################################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Functions for determining mosquito traits as parameters for the 
+##          transmission model. Traits may vary by mosquito species, pathogen
+##          of interest, and temperature.
+##
+## Contents: 1) Set-up, load in necessary packages and data-sets
+##           2) Define accessory functions
+##           3) Build parameter table-generating function for mosquito-pathogen pairs
+##
+##
+## Inputs:  (currently not implemented but code can be modified to take 
+##           different values for temperature)
+##        temp_seq: a sequence of temperature values at which to evaluate
+##          mosquito-pathogen traits
+##             
+##
+## Outputs: MosquitoThermalResponse.csv
+##          a table of vector+pathogen traits with columns of 
+##          Species (= mosquito species), Pathogen (= name of pathogen), 
+##          Temperature (in Celsius) and all mosquito-pathogen traits: 
+##          maximum biting frequency (sigma_V), fecundity (f),
+##          probability of egg survival to adulthood (delta_L),
+##          immature mosquito development rate (rho_L), and adult mosquito 
+##          mortality rate (mu_V) 
+
+# 1) Set-up,load packages, get data, etc.#######################################
+
+  ## Load Libraries---------------------------------------------------------------
+library(tidyverse)
+
+## Get data---------------------------------------------------------------------
+
+# Read in mosquito-specific traits
+MosqThermParms <- read_csv("./data/clean/MosquitoThermalParameters.csv",
+                           col_types = cols())
+
+
+# Define mosquito species names and codes:
+sp_names <- c('Aedes aegypti', 'Aedes albopictus','Culex quinquefasciatus', 
+              'Anopheles spp.')
+sp_code <- c('AE','AL','CQ', 'AN')
+names(sp_names) <- sp_code
+
+# Define pathogen names
+path_names <- c('DENV', 'ZIKV', 'WNV', 'P.fal.')
+
[…]

### 2022-08-11 code/output-functions.R

@@ -1,0 +1,110 @@
+## For questions, contact Kyle Dahlin, kydahlin@gmail.com
+## Initialized Oct 2020
+##
+## Title: Functions for getting model outputs like R0 #############
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Provide functions for evaluating several model properties and equilibrium values
+##
+## Contents: A set of functions listed below
+##
+##          compute.RH: Evaluates the host type reproduction number
+##
+##          compute.RV: Evaluates the mosquito type reproduction number
+##
+##          compute.R0: Evaluates the basic reproduction number (actually just sqrt(RH*RV))
+##
+##          compute.CHmin: Evaluates the critical minimum host density for pathogen persistence
+##
+##          compute.CHmax: Evaluates the critical maximum host density for pathogen persistence
+
+
+# Helper function: Reduces resolution of a vector by sub-sampling to length new_length
+res_reduce <- function(df, new_length) {
+  old_length <- length(unique(df))
+  if (old_length < new_length) {
+    warning("new_length is larger than old length. Vector will be unchanged")
+    new_length <- old_length
+  }
+  ret <- unique(df)[seq(1, length(unique(df)), length.out = new_length)]
+}
+
+## 1) Functions for computing outputs ##########################################
+
+### Equilibrium total vector population-----------------------------------------
+compute.V0 <- function(input) {
+  with(input, {
+    temp <- sigmaV * fecundity * deltaL
+    # check if reproduction rate exceeds mortality
+    temp_bool <- temp > (1 / lf)
+    ifelse(temp_bool,
+           V0 <- KL * rhoL * (1 - 1 / (lf * temp)) * lf,
+           V0 <- 0 # if mortality exceeds reproduction, set to zero
+    )
+  })
+}
+
+### Host-to-mosquito reproduction number----------------------------------------
+compute.RH <- function(input) {
+  with(input, {
+    # Derive intermediate quantities
+    # V0 = compute.V0(input)
+    bV <- ifelse(is.infinite(sigmaH),
+                 sigmaV, # Ross-Macdonald model
+                 sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0)
+    )
[…]

### 2023-02-17 manuscript-figures.Rmd
preliminary figures for R0, Topt with uncertainty

@@
 library(reshape2) #nec
-library(cowplot)
-library(viridis)
+library(cowplot) #nec
+library(viridis) #nec
 library(RColorBrewer) #nec
-library(MetBrewer)
+library(MetBrewer) #nec
 library(here)

### 2023-02-17 code/TEMP_R0_uncertainty.R

@@ -14,7 +14,7 @@
 ##
 ##
 ## Inputs:  data - data/clean/ThermalTraitSamples.csv
-##                 
+##
 ##
 ##          code - code/Mordecai2017/mcmc_utils_all.R
 ##                 code/Mordecai2017/temp_functions_all.R
@@ -31,9 +31,21 @@
 ### Load Libraries ----
 library(tidyverse)
 
+# Helper function to thin vectors
+res_reduce <- function(df, new_length) {
+  old_length <- length(unique(df))
+  if (old_length < new_length) {
+    warning("new_length is larger than old length. Vector will be unchanged")
+    new_length <- old_length
+  }
+  ret <- unique(df)[seq(1, length(unique(df)), length.out = new_length)]
+}
+
 ### Load in data and functions ----
 # Load samples of thermal trait parameters
-samples.All <- read.csv("data/clean/ThermalTraitSamples.csv")
+samples.All <- read.csv("data/clean/ThermalTraitSamples.csv") %>% 
+  # thin samples for analyses
+  filter(sample_num %in% res_reduce(sample_num, 200))
 
 # Load functions from Mordecai et al., 2017
 # This file contains tools for analysis and visualization.
@@ -44,15 +56,6 @@ source("code/Mordecai2017/temp_functions_all.R")
 
 # This file contains functions to compute model outputs like R0 and sensitivities
 source("code/output-functions.R")
-
-res_reduce <- function(df, new_length) {
-  old_length <- length(unique(df))
-  if (old_length < new_length) {
-    warning("new_length is larger than old length. Vector will be unchanged")
-    new_length <- old_length
-  }
-  ret <- unique(df)[seq(1, length(unique(df)), length.out = new_length)]
-}
 
 
 # Keep track of list of trait names
@@ -79,12 +82,8 @@ sample_vec <- unique(samples.All$sample_num)
 # Temperature
 min_Temp <- 10
 max_Temp <- 40
-res_Temp <- 0.5
+res_Temp <- 0.1
 Temp_vec <- seq(min_Temp, max_Temp, by = res_Temp)
-
-# Model type (Ross-Macdonald or Chitnis)
-Models <- c("RM", "Chitnis")
-
 
[…]

### 2023-05-09 manuscript-figures.Rmd
update manuscript figures
so far only finished the first 3*. need to fix figure 5 (Topt heatmap). there's an issue where the contours are extending to the infinite sigmaH band when they're not supposed to. likely caused by choosing the wrong value for sigmaH proxies

--- 2022-08-11 manuscript-figures.Rmd
@@
 library(reshape2) #nec
-library(cowplot)
-library(viridis)
+library(cowplot) #nec
+library(viridis) #nec
 library(RColorBrewer) #nec
-library(MetBrewer)
+library(MetBrewer) #nec
 library(here)
 library(lemon)  #nec
-library(zplyr) # only needed for placing text using absolute coordinates in contact comparison figure
+library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure
 
@@
 
-# Load in necessary functions and files---------------------------------------------------
+# Load in necessary functions and files ----------------------------------------
 # Functions for computing equilibrium quantities:
 #  mosquito abundance (compute.V0), basic reproduction number (compute.R0)
-source("code/output-functions.R")
+# source("code/output-functions.R")
+
+# Helper function: add a "point at infinity" for plotting when sigmaH is infinite
+inf_skew_func <- function(df, n_rows_to_add) {
+  # Value of sigmaH to replace 'Inf' with for plotting
+  infinite_skew <- 10^3 + 2500
+
+  # Get the largest value of log10(sigmaH)
+  max_log10sigmaH <- filter(df, is.finite(sigmaH)) %>%
+    select(sigmaH) %>%
+    max() %>%
+    log10()
+
+  # Used to create a gap dividing finite and infinite sigmaH
+  infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+
+  # add a second proxy sigmaH point at infinity to make the values easier to see there
+  temp <- filter(df, is.infinite(sigmaH)) %>%
+    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
+  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
+  df <- mutate(df, sigmaH_proxy = ifelse(is.finite(sigmaH),
+                                         sigmaH, infinite_skew
+  ))
+
+  for (i in 1:n_rows_to_add) {
+    bump_val <- 1+0.05*(i-1)
+    temp <- filter(df, is.infinite(sigmaH)) %>%
+      mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
+                                   mean(c(bump_val * infinite_divide, infinite_skew))
+      ))
+    df <- add_row(df, temp) %>% distinct()
+    }
+
+  return(df)
+
+}
+
 ```
@@
 ```{r load-data, include=FALSE}
-# Run analysis scripts to obtain data for plotting------------------------------
-source("code/get-mosquito-traits.R")
-source("code/get-analysis-dfs.R")
-
-# Load data files and configure for plotting------------------------------------
-
-## Vector trait thermal performance curves
-VecParms <- read_csv("results/VectorTraits.csv", show_col_types = FALSE)
+# Run analysis scripts to obtain data for plotting -----------------------------
+
+data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
+# Define temperature range of study
+Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
+
+# Thin sample size
+thin_size <- 1000 # full = 1000, thin = 100
+
+plot_bool = FALSE
+source("code/trait-transform.R")
+# Host density vector: Number of values to include to consider for vertebrate host density
+KH_vec_length <- 300 # full = 300, thin = 20
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 300 # full = 300, thin = 20
+
+source("code/trait-variation.R")
+
+# Load output data -------------------------------------------------------------
+
+# R0 data
+data.R0 <- read_rds("results/R0_vals.rds")
+# Topt data
+data.Topt <- read_rds("results/Topt_vals.rds")
+# Critical thermal extrema data
+data.CT <- read_rds("results/CT_vals.rds")
+
+# Configure data sets for plotting ---------------------------------------------
+
+## Get mean values of vector traits across samples
+mean.Vec <- data.Vec %>% 
+  select(-c(mosquito_species, pathogen, muL, etaL)) %>% 
+  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
+  group_by(system_ID, Temperature, variable) %>% 
+  summarise(mean = mean(value), .groups = "keep") %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = "variable", values_from = "mean") %>% 
+  mutate(etaL = rhoL / (deltaL + eps)) %>%
+  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
+  mutate(muL = etaL - rhoL) %>%
+  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
+                      0,
+                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))
 
 ## Compute mosquito thermal tolerance range (minimum and maximum)
-MosqThermRange_df <- VecParms %>%
+MosqThermRange_df <- mean.Vec %>%
   mutate(system_label = case_when(
-    system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
   )) %>%
@@
 
-## All outputs
-  AllOutputs <- read_csv("results/AllOutputs.csv", show_col_types = FALSE)
-
 # Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
-  AllOutputs <- AllOutputs %>%
+data.R0 <- data.R0 %>%
+  ungroup() %>% 
   mutate(system_label = case_when(
-      system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
-      system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-      system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
-      system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
-      system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
   ))
@@
 ## Set up plot dataframe
-MosqThermTraits_df <- VecParms %>%
+MosqThermTraits_df <- mean.Vec %>%
   ## Set up plot dataframe
+  # Mortality rate
+  mutate(muV = 1/lf) %>% 
   # Recruitment rate
@@
       case_when(
-        x == "Aedes aegypti+ZIKV" ~ "*Ae. aegypti* and ZIKV",
-        x == "Aedes aegypti+DENV" ~ "*Aedes aegypti* and DENV",
-        x == "Aedes albopictus+DENV" ~ "*Aedes albopictus* and DENV",
-        x == "Anopheles spp.+P.fal." ~ "*Anopheles* spp. and *Plasmodium falciparum*",
-        x == "Culex quinquefasciatus+WNV" ~ "*Culex quinquefasciatus* and WNV"
+        x == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
+        x == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+        x == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
+        x == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+        x == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
       )
@@
 
-  R0_df <- AllOutputs %>%
-    # To set num. of curves, change "length.out" to be the number of curves you want
-    filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)]) %>%
-    # Just consider one finite value of sigmaH and the Ross-Macdonald model
-    filter(sigmaH == 100 | is.infinite(sigmaH)) %>%
-    # Group by curve_ID and system_ID
-    group_by(Model, KH, system_ID) %>%
-    # Normalize R0 for each curve_ID x system_ID combination, so that the maximum is always at one
-    mutate(norm_R0 = R0 / max(R0)) %>%
-    # Restrict temperatures to where R0 is positive
-    filter(norm_R0 > 0) %>%
-    arrange(system_ID, sigmaH, Temperature)
-
-  ## PLOTTING ##
-  R0_plot <- R0_df %>%
-    # x = Temperature, y = normalized R0
-    # grouped by K_H value
-    ggplot(mapping = aes(
-      x = Temperature,
-      y = norm_R0,
-      group = KH
-    )) +
-
-    # path of R0 as a function of temperature (finite sigmaH):
+# R0 as a function of temperature, seperate curves across values of KH and sigmaH
+
+# Plot R0 vs. temperature curves. One plot for each system
+# One curve for Ross-Macdonald, a few for Chitnis
+
+# x-axes = temperature
+# y-axes = R0 (normalized so that max(R0) = 1)
+# plots = one for each mosquito+pathogen combination, "system_ID"
+# curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
+# curves  = Chitnis dynamic R0,
+#   - colour = value of KH. place it on a color scale in the bottom right corner
+newKH_vals <- unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]
+
+data.R0_norm <- data.R0 %>% 
+  filter(KH %in% newKH_vals) %>% 
+  filter(variable == "R0") %>%
+  select(-variable) %>%
+  # normalize variables to have a maximum of 1
+  group_by(system_ID, Model, sigmaH, KH) %>% 
+  # mutate(mean_norm = mean / max(mean)) %>% 
+  mutate(median_norm = median / max(median)) %>%
+  # mutate(highHCI_norm = highHCI / max(median)) %>% 
+  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
+  arrange(system_ID, sigmaH, KH, Temperature, mean_norm)
+
+R0_plot <- ggplot(mapping = aes(x = Temperature, group = KH)) +
+  # path of mean, normalized R0 as a function of temperature (finite sigmaH):
   geom_path(
-      data = filter(R0_df, sigmaH == 100),
-      aes(colour = KH, linetype = "finite")
-    ) +
-    # path of R0 as a function of temperature (infinite sigmaH):
+    data = filter(data.R0_norm, sigmaH == 100),
+    aes(y = median_norm, colour = KH, linetype = "finite"),
+    lwd = 1
+  ) +
+  # path of mean, normalized R0 as a function of temperature (infinite sigmaH):
   geom_path(
-      data = filter(R0_df, sigmaH == Inf),
-      aes(linetype = "infinite", colour = "black"),
+    data = filter(data.R0_norm, sigmaH == Inf),
+    aes(y = median_norm, linetype = "infinite", colour = "black"),
     colour = "black",
@@
   ) +
-
+  # # 89% HCI of R0 TPC curves
+  # geom_ribbon(
+  #   data = filter(data.R0_norm, sigmaH == 100),
+  #   aes(ymin = lowHCI_norm, ymax = highHCI_norm, fill = KH),
+  #   alpha = 0.1
+  # ) +
   # x-axis:
   scale_x_continuous(
-      name = "Temperature (°C)",
+    name = "Temperature (C)",
     expand = c(0, 0),
-      limits = c(15, 35)
+    limits = c(14, 34)
   ) +
@@
   ) +
-
   # color: scaled log10, color-blind friendly
@@
   ) +
-
+  # fill: scaled log10, color-blind friendly
+  scale_fill_viridis(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    trans = "log10",
+    breaks = 10^seq(-2, 4),
+    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
+    option = "plasma"
+  ) +
   # linetype:
@@
   ) +
-
   # faceting:
-    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
   # legend
@@
   ) +
-
   # theme options:
-    theme_minimal_vgrid(11) +
+  theme_minimal_vgrid(16) +
   theme(
@@
 
-  # move legend into lower right-hand corner
-  shift_legend(R0_plot)
+# Plot
+R0_plot <- shift_legend(R0_plot)
+
 ```
@@
 
-  Toptalt_df <- ThermPathChars %>%
+Toptalt_df <- data.Topt %>%
   ungroup() %>%
@@
   # Arrange along the plotting variables
-    arrange(system_label, sigmaH_proxy, KH, Topt)
+  arrange(system_ID, sigmaH, KH, mean) %>% 
+  mutate(sigmaH_proxy = sigmaH)
 
 # add many proxy sigmaH points at infinity to make the values easier to see there
-  temp <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.25 * infinite_divide, infinite_skew))
-    ))
-  temp2 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.15 * infinite_divide, infinite_skew))
-    ))
-  temp3 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.05 * infinite_divide, infinite_skew))
-    ))
-  temp4 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.3 * infinite_divide, infinite_skew))
-    ))
-  temp5 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.2 * infinite_divide, infinite_skew))
-    ))
-  temp6 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(1.1 * infinite_divide, infinite_skew))
-    ))
-  temp7 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-      mean(c(infinite_divide, infinite_skew))
-    ))
-
-  Toptalt_df <- add_row(Toptalt_df, temp)
-  Toptalt_df <- add_row(Toptalt_df, temp2)
-  Toptalt_df <- add_row(Toptalt_df, temp3)
-  Toptalt_df <- add_row(Toptalt_df, temp4)
-  Toptalt_df <- add_row(Toptalt_df, temp5)
-  Toptalt_df <- add_row(Toptalt_df, temp6)
-  Toptalt_df <- add_row(Toptalt_df, temp7) %>%
-    arrange(sigmaH_proxy) %>%
-    distinct()
-
-  Topt_breaks <- seq(21, 31, by = 1)
-
-  Toptalt_plots <- Toptalt_df %>%
+Toptalt_df <- inf_skew_func(Toptalt_df, 6)
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, 10^log10(mean(c(infinite_divide,infinite_skew))))
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+min_Topt <- floor(min(min(Toptalt_df$mean),min(Toptalt_df$median)))
+max_Topt <- ceiling(max(max(Toptalt_df$mean),max(Toptalt_df$median)))
+Topt_breaks <- seq(min_Topt, max_Topt, by = 1)
+
+# Plot mean of Topt heat map
+Toptalt_plots <- Toptalt_df2 %>%
   ## Set up plot ##
@@
   # color = transmission thermal optimum
-    ggplot(aes(x = KH, y = sigmaH_proxy)) +
-
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
   # Topt for FINITE sigmaH:
   geom_contour_filled(
-      data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.98),
-      aes(z = Topt),
+    data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.99),
     breaks = Topt_breaks
   ) +
-
   # Topt for INFINITE sigmaH:
+  # take mean of mean to hide variation from artifacts of uncertainty 
   geom_contour_filled(
-      data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.02),
-      aes(z = Topt),
+    data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.01) %>% 
+      group_by(system_ID) %>% 
+      mutate(mean = mean(mean), .groups = "keep"),
     size = 1,
@@
   ) +
-
-    # R0 = 1 contour:
-    geom_contour(aes(z = R0opt, colour = "R0=1"), breaks = c(1), size = 1) +
-
+  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
+  geom_contour(data = filter(data.CT, variable == "CTwidth"),
+               aes(y = sigmaH, z = mean, colour = "R0 = 1"), 
+               breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
+               size = 1) +
+  # geom_contour(data = data.R0_norm,
+  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
   # x-axis: log10-scale with no buffer space
@@
   scale_fill_manual(
-      name = "Transmission thermal optimum (°C)",
+    name = "Transmission\nthermal optimum (°C)",
     values = met.brewer("Johnson",
@@
   ) +
-
   # color:
@@
   ) +
-
   # faceting:
-    facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
   guides(fill = guide_coloursteps(
-      title.position = "top", title.hjust = 0.5,
-      barwidth = unit(5, "cm"),
+    title.position = "top", title.hjust = 0,
+    barheight = unit(5, "cm"),
     show.limits = TRUE
   )) +
-
   # theme options:
-    theme_minimal(11) +
+  theme_minimal(16) +
   theme(
     legend.box = "vertical",
-      legend.position = "bottom",
+    legend.position = "right",
     legend.margin = margin(0, 0, 0, 0),
     legend.title = element_text(size = 10),
-      legend.direction = "horizontal",
+    legend.direction = "vertical",
     legend.justification = "left",
@@
 # Plot
-  shift_legend(Toptalt_plots)
+Toptalt_plots <- shift_legend(Toptalt_plots)
+
 ```

### 2023-05-09 code/main-analysis.R

@@ -61,16 +61,13 @@ source("code/get-thermal-trait-priors.R")
 Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
 
 # Thin sample size
-thin_size <- 1000 # full = 600, thin = 100
+thin_size <- 1000 # full = 1000, thin = 100
 
 plot_bool = FALSE
 source("code/trait-transform.R")
 
 # write_rds(data.in.params, "data/clean/parameter_TPCs.rds", compress = "gz")
 # write_rds(data.in.params, "data/clean/parameter_TPCs_thin.rds", compress = "gz")
-
-# remove work sets
-rm("combined_df", "Infection_df", "noInfection_df", "TPC_df", "missing_traits_df")#, "data.in.transform")
 
 # 4) Build data set incorporating all axes of variation -------------------
 
@@ -91,6 +88,9 @@ source("code/trait-variation.R")
 # 5) Calculate model outputs ----------------------------------------------
 
 # data.in.analysis <- read_rds("data/clean/full_traitset.rds")
+
+data.Vec <- read_rds("data/clean/data_vector.rds")
+data.Host <- read_rds("data/clean/data_host.rds")
 
 # Thin sample size
 thin_size <- 600 # full = 600, thin = 100

### 2023-05-09 code/trait-transform.R

@@ -244,3 +244,6 @@ ggsave("figures/imputed_traits/param_TPC_plot.svg",
        device = "svg",
        width = 16, height = 9, units = "in")
 }
+
+# remove work sets
+rm("combined_df", "Infection_df", "noInfection_df", "TPC_df", "data.in.transform")

### 2023-05-09 code/trait-variation.R

@@ -76,6 +76,7 @@ data.Host <- expand_grid(
 ) %>% as.data.frame() %>%
   mutate(Model = ifelse(is.infinite(sigmaH), "Ross-Macdonald model", "Chitnis model"))
 
+
 # 2) Set non-TPC *mosquito* parameters ------------------------------------
 
 ## Carrying capacity for larval mosquitoes
@@ -89,6 +90,7 @@ data.Vec <- data.in.params %>%
   mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
                       0,
                       KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))
+
 
 # Remove the parameter data frame to free up memory
 rm(data.in.params)

### 2023-05-10 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 # Helper function: add a "point at infinity" for plotting when sigmaH is infinite
-inf_skew_func <- function(df, n_rows_to_add) {
-  # Value of sigmaH to replace 'Inf' with for plotting
-  infinite_skew <- 10^3 + 2500
-
+inf_skew_func <- function(df, skew, divide, n_rows_to_add) {
   # Get the largest value of log10(sigmaH)
@@
   # Used to create a gap dividing finite and infinite sigmaH
-  infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-
-  # add a second proxy sigmaH point at infinity to make the values easier to see there
-  temp <- filter(df, is.infinite(sigmaH)) %>%
-    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
+  infinite_divide <- 10^mean(log10(c(divide, skew)))
+
+  # Create a proxy sigmaH variable that replaces Inf with skew
   df <- mutate(df, sigmaH_proxy = ifelse(is.finite(sigmaH),
-                                         sigmaH, infinite_skew
+                                         sigmaH, skew
   ))
+
+  added_sigma_vals <- seq(divide, skew, length.out = n_rows_to_add)
 
@@
       mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                                   mean(c(bump_val * infinite_divide, infinite_skew))
-      ))
+                                   added_sigma_vals[i]))
+
     df <- add_row(df, temp) %>% distinct()
@@
 
-## Add a "point at infinity" for sigmaH
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^3 + 2500
-
-# Get the largest value of log10(sigmaH)
-max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
-  select(sigmaH) %>%
-  max() %>%
-  log10()
-
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-
-# add a second proxy sigmaH point at infinity to make the values easier to see there
-temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-# Create a proxy sigmaH variable that replaces Inf with infinite_skew
-AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
-                                                       sigmaH, infinite_skew
-))
-AllOutputs <- add_row(AllOutputs, temp) %>% distinct()
-
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
-sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-## Parasite thermal characteristics
-ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)
-
-# Title names for each mosquito+pathogen combination
-ThermPathChars <- ThermPathChars %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
-  ))
-## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^3 + 2500
-
-# Get the largest value of log10(sigmaH)
-max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
-  select(sigmaH) %>%
-  max() %>%
-  log10()
-
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-
-# Create a proxy sigmaH variable that replaces Inf with infinite_skew
-ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
-                                                               sigmaH, infinite_skew
-))
-# add a second proxy sigmaH point at infinity to make the values easier to see there
-temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-
-ThermPathChars <- add_row(ThermPathChars, temp) %>%
-  arrange(sigmaH_proxy) %>%
-  distinct()
-
-## Options
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+# ## Add a "point at infinity" for sigmaH
+# # Value of sigmaH to replace 'Inf' with for plotting
+# infinite_skew <- 10^3 + 2500
+# 
+# # Get the largest value of log10(sigmaH)
+# max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
+#   select(sigmaH) %>%
+#   max() %>%
+#   log10()
+# 
+# # Used to create a gap dividing finite and infinite sigmaH
+# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+# 
+# # add a second proxy sigmaH point at infinity to make the values easier to see there
+# temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
+#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
+# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
+# AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
+#                                                        sigmaH, infinite_skew
+# ))
+# AllOutputs <- add_row(AllOutputs, temp) %>% distinct()
+# 
+# # Define sigmaH tick breaks and labels
+# sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
+# sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+# 
+# ## Parasite thermal characteristics
+# ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)
+# 
+# # Title names for each mosquito+pathogen combination
+# ThermPathChars <- ThermPathChars %>%
+#   mutate(system_label = case_when(
+#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
+#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+#     system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
+#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
+#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+#   ))
+# ## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
+# # Value of sigmaH to replace 'Inf' with for plotting
+# infinite_skew <- 10^3 + 2500
+# 
+# # Get the largest value of log10(sigmaH)
+# max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
+#   select(sigmaH) %>%
+#   max() %>%
+#   log10()
+# 
+# # Used to create a gap dividing finite and infinite sigmaH
+# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+# 
+# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
+# ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
+#                                                                sigmaH, infinite_skew
+# ))
+# # add a second proxy sigmaH point at infinity to make the values easier to see there
+# temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
+#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
+# 
+# ThermPathChars <- add_row(ThermPathChars, temp) %>%
+#   arrange(sigmaH_proxy) %>%
+#   distinct()
+# 
+# ## Options
+# # Define sigmaH tick breaks and labels
+# sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
+# sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
 
@@
 # add many proxy sigmaH points at infinity to make the values easier to see there
-Toptalt_df <- inf_skew_func(Toptalt_df, 6)
+max_sigmaH <- max(filter(Toptalt_df, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^log10(max_sigmaH*1)
+
+# infinite_skew <- 10^2 + 150
+Toptalt_df <- inf_skew_func(Toptalt_df, infinite_skew, infinite_divide, 8)
+
+# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
 
 # Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, 10^log10(mean(c(infinite_divide,infinite_skew))))
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), mean(c(infinite_divide, infinite_skew)), max(Toptalt_df$sigmaH_proxy))
 sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
@@
 # Plot mean of Topt heat map
-Toptalt_plots <- Toptalt_df2 %>%
+Toptalt_plots <- Toptalt_df %>%
   ## Set up plot ##
@@
   geom_contour_filled(
-    data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.01) %>% 
+    data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.02) %>% 
       group_by(system_ID) %>% 
@@
 ```{r fig-6_CT_Width, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
-# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
+# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
+# depends on vertebrate host availability (density and biting tolerance) in each
+# of the focal systems.
 
@@
 
-CTWidth_df <- ThermPathChars %>%
-  ungroup() %>%
-  # Calculate thermal niche width
-  mutate(CTwidth = CTmax - CTmin) %>%
-  mutate(CTwidth = replace(CTwidth, is.na(CTwidth), 0)) %>%
-  distinct() %>%
-  select(system_label, sigmaH, sigmaH_proxy, KH, CTwidth) %>%
+CTwidth_df <- data.CT %>%
+  filter(variable == "CTwidth") %>% 
+  mutate(sigmaH_proxy = sigmaH) %>% 
   # Arrange along the plotting variables
-  arrange(system_label, sigmaH_proxy, KH, CTwidth)
-
-# add many third proxy sigmaH points at infinity to make the values easier to see there
-temp <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.25 * infinite_divide, infinite_skew))
-  ))
-temp2 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.15 * infinite_divide, infinite_skew))
-  ))
-temp3 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.05 * infinite_divide, infinite_skew))
-  ))
-temp4 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.3 * infinite_divide, infinite_skew))
-  ))
-temp5 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.2 * infinite_divide, infinite_skew))
-  ))
-temp6 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.1 * infinite_divide, infinite_skew))
-  ))
-temp7 <- filter(CTWidth_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(infinite_divide, infinite_skew))
-  ))
-
-CTWidth_df <- add_row(CTWidth_df, temp)
-CTWidth_df <- add_row(CTWidth_df, temp2)
-CTWidth_df <- add_row(CTWidth_df, temp3)
-CTWidth_df <- add_row(CTWidth_df, temp4)
-CTWidth_df <- add_row(CTWidth_df, temp5)
-CTWidth_df <- add_row(CTWidth_df, temp6)
-CTWidth_df <- add_row(CTWidth_df, temp7) %>%
-  arrange(sigmaH_proxy) %>%
-  distinct()
-
-CTWidth_heat_plots <- CTWidth_df %>%
+  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
+  ungroup()
+
+infinite_skew <- 10^3 + 250
+CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, divide_order = 3, 8)
+
+infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
+CTWidth_heat_plots <- CTwidth_df %>%
   ## Set up plot ##
@@
   # y = vertebrate host population density,
-  # color = width of parasite thermal niche
-  ggplot(aes(x = KH, y = sigmaH_proxy)) +
-
+  # color = width of parasite thermal mean_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
   # CTwidth for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTWidth_df, sigmaH_proxy < infinite_divide**0.98),
-    aes(z = CTwidth)
-  ) +
-
+  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < infinite_divide**0.99)) +
   # CTwidth for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTWidth_df, sigmaH_proxy > infinite_divide**1.02),
-    aes(z = CTwidth)
-  ) +
-
+  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy > infinite_divide**1.01)) +
   # x-axis: log10-scale with no buffer space
@@
   scale_fill_viridis_d(
-    name = "Parasite thermal tolerance\nrange width (°C)",
+    name = "Mean parasite\nthermal tolerance\nrange width (°C)",
     option = "plasma"
   ) +
-
   # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
@@
   )) +
-
   # theme options:
-  theme_minimal(11) +
+  theme_minimal(16) +
   theme(
@@
 # Plot
-shift_legend(CTWidth_heat_plots)
+CTWidth_heat_plots <- shift_legend(CTWidth_heat_plots)
+
 ```

### 2023-05-11 manuscript-figures.Rmd
add updated figure code to Rmd
remains to:
* re-calculate R0 values with enough resolution to plot heatmap
* re-create persistence threshold figures (CTmin/max vs. CHmin/max)

@@
 
+# Plot settings ----
+
+# Set theme
+theme_set(theme_minimal(11))
+
+# Helper function to place legends in empty facets of plot grids
+# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
+shift_legend <- function(p) {
+  pnls <- cowplot::plot_to_gtable(p) %>%
+    gtable::gtable_filter("panel") %>%
+    with(setNames(grobs, layout$name)) %>%
+    purrr::keep(~ identical(.x, zeroGrob()))
+
+  if (length(pnls) == 0) stop("No empty facets in the plot")
+
+  lemon::reposition_legend(p, "center", panel = names(pnls))
+}
+
 ```
@@
 # R0 data
-data.R0 <- read_rds("results/R0_vals.rds")
+data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
 # Topt data
@@
 
-```{r plot-settings, include = FALSE}
-# Set theme
-theme_set(theme_minimal(11))
-
-# Helper function to place legends in empty facets of plot grids
-# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
-shift_legend <- function(p) {
-  pnls <- cowplot::plot_to_gtable(p) %>%
-    gtable::gtable_filter("panel") %>%
-    with(setNames(grobs, layout$name)) %>%
-    purrr::keep(~ identical(.x, zeroGrob()))
-
-  if (length(pnls) == 0) stop("No empty facets in the plot")
-
-  lemon::reposition_legend(p, "center", panel = names(pnls))
-}
-```
-
 # Figures
@@
 ## Configure data frame for plotting
-R0_df <- AllOutputs %>%
-  select(system_ID, system_label, Temperature, sigmaH, KH, R0) %>%
+R0_df <- data.R0 %>%
+  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
+  rename(R0 = median) %>% 
   # Consider only 3 values of KH (on a log10-scale)
-  filter(KH %in% c(1E-1, 1E0, 1E1)) %>%
+  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
   # Choose a limited range of sigmaH values
@@
 ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
-
-Topt_df <- ThermPathChars %>%
-  filter(KH > 0.01) %>%
-  filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
+Topt_df <- data.Topt %>% 
+  pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"), 
+              names_from = variable,
+              values_from = c("mean", "median", "lowHCI", "highHCI"))  %>% 
+  right_join(read_rds("results/CT_vals.rds") %>% 
+               filter(variable == "CTwidth") %>% 
+               pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"), 
+                           names_from = "variable",
+                           values_from = c("mean", "median", "lowHCI", "highHCI"))) %>% 
+  filter(sigmaH %in% c(1, 10, 100, Inf)) %>% 
+  # filter(mean_CTwidth>0) %>% 
+  select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>%
+  rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt, 
+         highHCI = highHCI_Topt) %>% 
+  # filter(KH > 0.01) %>%
+  # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
   group_by(KH) %>%
   # Arrange along the plotting variables
-  arrange(system_ID, KH, Topt) %>%
+  arrange(system_ID, KH, mean) %>%
   arrange(sigmaH) %>%
@@
 
-Topt_plots <- Topt_df %>%
+# PLOTTING
+Topt_plot <- Topt_df %>%
   ## Set up plot ##
-  # x = blood meal supply, y = thermal optimum,
   # color = sigmaH
-  ggplot(aes(
-    x = KH, y = Topt,
-    colour = as.factor(sigmaH)
-  )) +
-
+  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
   # Topt curves:
-  geom_path(lwd = 1) +
-
+  geom_path(aes(y = median), lwd = 1) +
+  # # Add dotted lines showing 89% HCI limits
+  # geom_path(aes(y = lowHCI), linetype = "dashed") +
+  # geom_path(aes(y = highHCI), linetype = "dashed") +
   # x-axis: log10 scale, no buffer space
@@
   ) +
-
   # y-axis
@@
     expand = c(0.05, 0.05),
-    limits = range(ThermPathChars$Topt),
-    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
-                 floor(range(ThermPathChars$Topt)[2]),
-                 by = 1
-    )
+    limits = c(21,30.5), # mean: 21-31, median: 21-32
+    breaks = seq(21,32, by = 1)
   ) +
@@
     name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c(met.brewer("VanGogh3", 3, direction = 1), "black"),
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
     # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
@@
   ) +
-
+  scale_fill_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
+    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
   # faceting:
-  facet_wrap(~system_label,
-             scales = "free",
-             nrow = 2,
-             labeller = labeller()
-  ) +
-
+  facet_wrap(~system_ID, nrow = 2, labeller = labeller()) +
   # theme options:
-  theme_minimal_hgrid(11) +
+  theme_minimal(16) +
   guides(color = guide_legend(override.aes = list(size = 4))) +
@@
 # Plot
-shift_legend(Topt_plots)
-
+Topt_plot <- shift_legend(Topt_plot)
 ```
@@
 
-Topt_df <- ThermPathChars %>%
+Topt_plot <- data.Topt %>% 
+  # filter(sigmaH %in% c(1, 10, 100, Inf)) %>% 
   # Choose appropriate pop. dens. values and group
-  filter(KH %in% 10^seq(0, 4)) %>%
-  group_by(KH) %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, sigmaH, Topt) %>%
-  arrange(KH) %>%
-  ungroup()
-
-Topt_plots <- Topt_df %>%
+  filter(KH %in% 10^seq(0, 3)) %>%
+  arrange(system_ID, KH, sigmaH, median) %>% 
   ## Set up plot ##
-  # x-axis = vertebrate host biting tolerance, y-axis = thermal optimum,
-  # color = vertebrate host population density
-  ggplot(aes(x = sigmaH_proxy, y = Topt, colour = as.factor(KH))) +
-
+  # color = sigmaH
+  ggplot(aes(x = sigmaH, colour = as.factor(KH))) +
   # Topt curves:
-  geom_path(lwd = 2) +
-
+  geom_path(aes(y = mean), lwd = 1) +
+  # # Dotted lines showing limits of 89% HCI
+  # geom_path(aes(y = lowHCI),linetype = "dashed") +
+  # geom_path(aes(y = highHCI),linetype = "dashed") +
   # white lines breaking up finite/infinite sigmaH values:
@@
   ) +
-
   # x-axis: Use a log10-scale with no buffer space
@@
     expand = c(0, 0),
-    limits = c(5, 3500),
+    limits = c(0.5, 150),
     breaks = sigmaH_breaks,
@@
   ) +
-
-  # y-axis: Set limits and breaks and add some buffer space
+  # y-axis
   scale_y_continuous(
@@
     expand = c(0.05, 0.05),
-    limits = range(ThermPathChars$Topt),
-    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
-                 floor(range(ThermPathChars$Topt)[2]),
-                 by = 1
-    )
-  ) +
-
+    limits = c(21,31), # mean: 21-31, median: 21-32
+    breaks = seq(21,32, by = 1)
+  ) +
   # color:
@@
     name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 5),
+    values = met.brewer("Hokusai3", 4,
                         # option = "plasma"
-  ) +
-
+    )) +
+  scale_fill_manual(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    values = met.brewer("Hokusai3", 4,
+                        # option = "plasma"
+    )) +
   # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID,
+             scales = "free",
+             nrow = 2,
+             labeller = labeller()  ) +
   # theme options:
-  theme_minimal_hgrid(11) +
+  theme_minimal(16) +
   guides(color = guide_legend(override.aes = list(size = 4))) +
@@
     legend.direction = "vertical",
-    legend.justification = "center",
+    legend.title = element_text(size = 10),
+    legend.text = element_text(
+      size = 10,
+      hjust = 0
+    ),
+    legend.justification = "left",
     axis.title.x = element_text(hjust = 0.5),
@@
 # Plot
-shift_legend(Topt_plots)
+Topt_plot <- shift_legend(Topt_plot)
 ```
@@
 
-CTmin_df <- ThermPathChars %>%
-  ungroup() %>%
-  distinct() %>%
+CTmin_df <- data.CT %>%
+  filter(variable == "CTmin") %>% 
+  filter(is.finite(mean)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>% 
   # Arrange along the plotting variables
-  arrange(system_label, sigmaH_proxy, KH, CTmin)
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
+  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
+  ungroup()
+
+# add many third proxy sigmaH points at infinity to make the values easier to see there
 temp <- filter(CTmin_df, is.infinite(sigmaH)) %>%
@@
 
-CTmin_breaks <- seq(15, 31, by = 1)
-
-CTmin_plots <- CTmin_df %>%
+CTmin_heat_plots <- CTmin_df %>%
   ## Set up plot ##
@@
   # y = vertebrate host population density,
-  # color = transmission thermal optimum
-  ggplot(aes(x = KH, y = sigmaH_proxy)) +
+  # color = width of parasite thermal mean_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
 
@@
   geom_contour_filled(
-    data = filter(CTmin_df, sigmaH_proxy < infinite_divide**0.98),
-    aes(z = CTmin),
-    breaks = CTmin_breaks
+    data = filter(CTmin_df, sigmaH_proxy < 100)
   ) +
@@
   geom_contour_filled(
-    data = filter(CTmin_df, sigmaH_proxy > infinite_divide**1.02),
-    aes(z = CTmin),
-    size = 1,
-    breaks = CTmin_breaks
+    data = filter(CTmin_df, is.infinite(sigmaH))
   ) +
@@
   ) +
-
-  # fill:
+  # color:
   scale_fill_viridis_d(
-    name = "Critical thermal minimum (°C)"
-  ) +
-
+    name = "Mean critical thermal minimum (°C)",
+    option = "plasma"
+  ) +
   # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
   guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    direction = "vertical",
-    barheight = unit(6, "cm"),
+    title.position = "top", title.hjust = 0.5,
+    barwidth = unit(10, "cm"),
     show.limits = TRUE
   )) +
-
   # theme options:
-  theme_minimal(11) +
+  theme_minimal(16) +
   theme(
-    plot.title = ggtext::element_markdown(),
-    legend.position = "right",
+    legend.box = "horizontal",
+    legend.position = "bottom",
     legend.margin = margin(0, 0, 0, 0),
-    legend.text = element_text(size = 11),
-    legend.title = element_text(size = 11, hjust = 0),
+    legend.title = element_text(size = 10),
     legend.direction = "horizontal",
@@
       hjust = 0,
-      padding = margin(0, 0, 0, 0)
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
     )
@@
 # Plot
-shift_legend(CTmin_plots)
+CTmin_heat_plots <- shift_legend(CTmin_heat_plots)
 ```
@@
 
-CTmax_df <- ThermPathChars %>%
-  ungroup() %>%
-  distinct() %>%
+CTmax_df <- read_rds("results/CT_vals.rds") %>%
+  filter(variable == "CTmax") %>% 
+  filter(is.finite(mean)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>% 
   # Arrange along the plotting variables
-  arrange(system_label, sigmaH_proxy, KH, CTmin)
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
+  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
+  ungroup()
+
+# add many third proxy sigmaH points at infinity to make the values easier to see there
 temp <- filter(CTmax_df, is.infinite(sigmaH)) %>%
@@
 
-CTmax_breaks <- seq(23, 35, by = 1)
-
-CTmax_plots <- CTmax_df %>%
+min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median)))
+max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median)))
+CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1)
+
+CTmax_heat_plots <- CTmax_df %>%
   ## Set up plot ##
@@
   # y = vertebrate host population density,
-  # color = transmission thermal optimum
-  ggplot(aes(x = KH, y = sigmaH_proxy)) +
-
-  # CTmin for FINITE sigmaH:
+  # color = CTmax
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
+  # CTmax for FINITE sigmaH:
   geom_contour_filled(
-    data = filter(CTmax_df, sigmaH_proxy < infinite_divide**0.98),
-    aes(z = CTmax),
-    breaks = CTmax_breaks
-  ) +
-
-  # CTmin for INFINITE sigmaH:
+    data = filter(CTmax_df, sigmaH_proxy < 100)
+  ) +
+
+  # CTmax for INFINITE sigmaH:
   geom_contour_filled(
-    data = filter(CTmax_df, sigmaH_proxy > infinite_divide**1.02),
-    aes(z = CTmax),
-    size = 1,
-    breaks = CTmax_breaks
-  ) +
-
+    data = filter(CTmax_df, is.infinite(sigmaH))
+  ) +
   # x-axis: log10-scale with no buffer space
@@
   ) +
-
-  # fill:
-  scale_fill_manual(
-    name = "Critical thermal maximum (°C)",
-    values = met.brewer("Tam",
-                        n = length(CTmax_breaks),
-                        direction = -1
-    )
-  ) +
-
+  # color:
+  scale_fill_viridis_d(
+    name = "Mean critical thermal maximum (°C)",
+    option = "plasma"
+  ) +
   # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
+  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
   guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    direction = "vertical",
-    barheight = unit(6, "cm"),
+    title.position = "top", title.hjust = 0.5,
+    barwidth = unit(10, "cm"),
     show.limits = TRUE
   )) +
-
   # theme options:
-  theme_minimal(11) +
+  theme_minimal(16) +
   theme(
-    plot.title = ggtext::element_markdown(),
-    legend.position = "right",
+    legend.box = "horizontal",
+    legend.position = "bottom",
     legend.margin = margin(0, 0, 0, 0),
-    legend.text = element_text(size = 11),
-    legend.title = element_text(size = 11, hjust = 0),
+    legend.title = element_text(size = 10),
     legend.direction = "horizontal",
@@
 # Plot
-shift_legend(CTmax_plots)
+CTmax_heat_plots <- shift_legend(CTmax_heat_plots)
 ```

### 2023-05-11 manuscript-figures.Rmd
Update manuscript-figures.Rmd

--- 2023-05-10 manuscript-figures.Rmd
@@
   # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
-  arrange(system_ID, sigmaH, KH, Temperature, mean_norm)
+  arrange(system_ID, sigmaH, KH, Temperature, median_norm)
 

### 2023-05-12 manuscript-figures.Rmd
little fixes

@@
 # Tell R where the manuscript lives
-here::i_am("manuscript-figures.Rmd")
+# here::i_am("manuscript-figures.Rmd")
+
+data.in.transform <- read_rds(here::here("data/clean/TPC_param_samples.rds"))
 
@@
 
-data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
 # Define temperature range of study
@@
 plot_bool = FALSE
-source("code/trait-transform.R")
+source("code/trait-transform.R", local = TRUE)
 # Host density vector: Number of values to include to consider for vertebrate host density
@@
 
-source("code/trait-variation.R")
+# Get data for plotting thermal performance curves (data.Vec)
+source("code/trait-variation.R", local = TRUE)
 
 # Load output data -------------------------------------------------------------
+# These data are produced by the code in code/get-outputs.R
 
 # R0 data
-data.R0 <- read_rds("results/R0_vals.rds")
+data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
 # Topt data
@@
   pivot_wider(names_from = "variable", values_from = "mean") %>% 
+  mutate(etaL = rhoL / (deltaL + eps)) %>%
+  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
+  mutate(muL = etaL - rhoL) %>%
+  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
+                      0,
+                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))
+
+median.Vec <- data.Vec %>% 
+  select(-c(mosquito_species, pathogen, muL, etaL)) %>% 
+  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
+  group_by(system_ID, Temperature, variable) %>% 
+  summarise(median = median(value), .groups = "keep") %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = "variable", values_from = "median") %>% 
   mutate(etaL = rhoL / (deltaL + eps)) %>%
@@
 
-```{r plot-settings, include = FALSE}
-# Set theme
-theme_set(theme_minimal(11))
-
-# Helper function to place legends in empty facets of plot grids
-# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
-shift_legend <- function(p) {
-  pnls <- cowplot::plot_to_gtable(p) %>%
-    gtable::gtable_filter("panel") %>%
-    with(setNames(grobs, layout$name)) %>%
-    purrr::keep(~ identical(.x, zeroGrob()))
-
-  if (length(pnls) == 0) stop("No empty facets in the plot")
-
-  lemon::reposition_legend(p, "center", panel = names(pnls))
-}
-```
-
 # Figures
 
-```{r fig-1_contact_comparison, dev = c('pdf','svg', 'tiff'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}
+```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}
 
@@
 
-```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'tiff'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model.
+```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model.
 '}
@@
 ## Set up plot dataframe
-MosqThermTraits_df <- mean.Vec %>%
+MosqThermTraits_df <- median.Vec %>%
   ## Set up plot dataframe
@@
 
-```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'tiff'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}
+```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}
 
@@
 
-```{r fig-5_Topt, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
+```{r fig-5_Topt, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
 # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
@@
 
-```{r fig-6_CT_Width, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
+```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
 # Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
@@
   # Arrange along the plotting variables
-  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
+  arrange(system_ID, KH, sigmaH_proxy, median) %>% 
   ungroup()
 
-infinite_skew <- 10^3 + 250
-CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, divide_order = 3, 8)
-
-infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
+CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, infinite_divide, 8)
+
 CTWidth_heat_plots <- CTwidth_df %>%
@@
   scale_fill_viridis_d(
-    name = "Mean parasite\nthermal tolerance\nrange width (°C)",
+    name = "Median parasite\nthermal tolerance\nrange width (°C)",
     option = "plasma"
@@
 
-# Supplementary Figures
-
-```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
-# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
-
-# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
-# y = Temperature
-# color = R0
-# curves:
-#   R0 = 1 contour (black curve)
-#   Topt (red curve)
-
-# Facets:
-# Rows = levels of vertebrate host population density
-# Columns = two MBPT systems
-# Total = 6 plots
-
-## Set up plot data frame
-# We re-create the output data frame so that we can vary sigmaH correctly.
-# We also drop the resolution of KH down to just three values
-# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"
-
-## Configure data frame for plotting
-R0_df <- AllOutputs %>%
-  select(system_ID, system_label, Temperature, sigmaH, KH, R0) %>%
-  # Consider only 3 values of KH (on a log10-scale)
-  filter(KH %in% c(1E-1, 1E0, 1E1)) %>%
-  # Choose a limited range of sigmaH values
-  filter(sigmaH > 10^0.5) %>%
-  # Group by plotting variables
-  group_by(system_ID, KH, sigmaH) %>%
-  # Calculate Topt (which.max requires grouping)
-  mutate(Topt = `Temperature`[which.max(R0)]) %>%
-  as_tibble() %>%
-  arrange(system_ID, sigmaH, Temperature)
-
-## Add a "point at infinity" for sigmaH
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^3 + 2500
-
-# Get the largest value of log10(sigmaH)
-max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
-  select(sigmaH) %>%
-  max() %>%
-  log10()
-
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-
-# add a second proxy sigmaH point at infinity to make the values easier to see there
-temp <- filter(R0_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-# Create a proxy sigmaH variable that replaces Inf with infinite_skew
-R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
-                                             sigmaH, infinite_skew
-))
-R0_df <- add_row(R0_df, temp) %>% distinct()
-
-## Compute mosquito thermal tolerance range (minimum and maximum)
-temp_MosqThermRange_df <- MosqThermRange_df %>%
-  select(system_label, CTmin_V0, CTmax_V0)
-
-## PLOTTING ##
-
-## Options
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-# Labels for facet rows
-R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
-mylabels <- as_labeller(c(
-  `0.1` = "0.1 vertebrate hosts / ha",
-  `1` = "1 vertebrate host / ha",
-  `10` = "10 vertebrate hosts / ha"
-))
-
-# Breaks used to decide fill for the heat map
-fill_breaks <- c(1, seq(5, 20, by = 5), Inf)
-
-# Define colors for heat map so that values of R0>1 go from yellow to red
-my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))
-
-## PLOT ##
-R0_plot <- R0_df %>%
-  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
-
-  # Mosquito thermal tolerance range lines
-  geom_hline(
-    data = temp_MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  geom_hline(
-    data = temp_MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-
-  # R0 contours for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
-    breaks = fill_breaks
-  ) +
-
-  # R0 contours for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
-    breaks = fill_breaks
-  ) +
-
-  # R0 = 1 contour:
-  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
-
-  # Topt curve:
-  geom_line(
-    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
-    mapping = aes(
-      x = sigmaH_proxy,
-      y = Topt,
-      colour = "Topt"
-    ),
-    lwd = 1,
-    linetype = 1
-  ) +
-
-  # white lines breaking up finite/infinite sigmaH values
-  geom_vline(
-    aes(xintercept = 0.85 * infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.2 * infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-
-  # x-axis:
-  scale_x_log10(
-    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels,
-    expand = c(0, 0)
-  ) +
-
-  # y-axis:
-  scale_y_continuous(
-    name = expression("Temperature "(degree * C)),
-    expand = c(0, 0),
-    limits = c(14, 36),
-    breaks = seq(10, 36, by = 2)
-  ) +
-
-  # color:
-  scale_colour_manual(
-    name = "",
-    labels = c(
-      "R0=1" = unname(TeX("$R_0=1$")),
-      "Topt" = "Transmission\nthermal\noptimum",
-      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
-    ),
-    values = c("black", "purple", "grey"),
-    guide = guide_legend(
-      order = 1,
-      keyheight = unit(2, "cm"),
-      override.aes = list(size = 6)
-    )
-  ) +
-
-  # fill:
-  scale_fill_manual(
-    name = TeX("$R_0$"),
-    values = my.cols,
-    guide = guide_colorsteps(
-      order = 2,
-      breaks = fill_breaks,
-      barheight = unit(8, "cm")
-    )
-  ) +
-
-  # faceting:
-  facet_rep_grid(
-    rows = vars(system_label),
-    cols = vars(KH),
-    scales = "free_y",
-    labeller = labeller(.cols = mylabels),
-    repeat.tick.labels = "left"
-  ) +
-
-  # theme options:
-  theme_minimal_hgrid(11) +
-  theme(
-    axis.line = element_line(),
-    panel.spacing = unit(1, "lines"),
-    legend.text = element_text(size = 11),
-    legend.text.align = 0,
-    strip.text = ggtext::element_markdown(
-      size = 8,
-      hjust = 0
-    )
-  )
-
-# Plot it
-R0_plot
-```
-
-```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
-
-Topt_df <- ThermPathChars %>%
-  filter(KH > 0.01) %>%
-  filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
-  group_by(KH) %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, KH, Topt) %>%
-  arrange(sigmaH) %>%
-  ungroup()
-
-Topt_plots <- Topt_df %>%
-  ## Set up plot ##
-  # x = blood meal supply, y = thermal optimum,
-  # color = sigmaH
-  ggplot(aes(
-    x = KH, y = Topt,
-    colour = as.factor(sigmaH)
-  )) +
-
-  # Topt curves:
-  geom_path(lwd = 1) +
-
-  # x-axis: log10 scale, no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.01, 2E4),
-    breaks = 10^seq(-2, 4),
-    labels = TeX(c(
-      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
-    ))
-  ) +
-
-  # y-axis
-  scale_y_continuous(
-    name = expression("Thermal optimum "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = range(ThermPathChars$Topt),
-    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
-                 floor(range(ThermPathChars$Topt)[2]),
-                 by = 1
-    )
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c(met.brewer("VanGogh3", 3, direction = 1), "black"),
-    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
-    breaks = c(1, 10, 100, Inf),
-    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label,
-             scales = "free",
-             nrow = 2,
-             labeller = labeller()
-  ) +
-
-  # theme options:
-  theme_minimal_hgrid(11) +
-  guides(color = guide_legend(override.aes = list(size = 4))) +
-  theme(
-    legend.position = "bottom",
-    legend.margin = margin(),
-    legend.direction = "vertical",
-    legend.title = element_text(size = 10),
-    legend.text = element_text(
-      size = 10,
-      hjust = 0
-    ),
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(Topt_plots)
-
-```
-
-```{r fig-S3_Topt_plots, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}
-
-# x-axis = vertebrate host biting tolerance
-# y-axis = thermal optimum
-# color = vertebrate host population density
-
-Topt_df <- ThermPathChars %>%
-  # Choose appropriate pop. dens. values and group
-  filter(KH %in% 10^seq(0, 4)) %>%
-  group_by(KH) %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, sigmaH, Topt) %>%
-  arrange(KH) %>%
-  ungroup()
-
-Topt_plots <- Topt_df %>%
-  ## Set up plot ##
-  # x-axis = vertebrate host biting tolerance, y-axis = thermal optimum,
-  # color = vertebrate host population density
-  ggplot(aes(x = sigmaH_proxy, y = Topt, colour = as.factor(KH))) +
-
-  # Topt curves:
-  geom_path(lwd = 2) +
-
-  # white lines breaking up finite/infinite sigmaH values:
-  geom_vline(
-    aes(xintercept = 0.95 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.05 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.15 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-
-  # x-axis: Use a log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    limits = c(5, 3500),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-
-  # y-axis: Set limits and breaks and add some buffer space
-  scale_y_continuous(
-    name = expression("Thermal optimum "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = range(ThermPathChars$Topt),
-    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
-                 floor(range(ThermPathChars$Topt)[2]),
-                 by = 1
-    )
-  ) +
-
-  # color:
-  scale_colour_manual(
-    name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 5),
-    # option = "plasma"
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
-  # theme options:
-  theme_minimal_hgrid(11) +
-  guides(color = guide_legend(override.aes = list(size = 4))) +
-  theme(
-    legend.position = "bottom",
-    legend.margin = margin(),
-    legend.direction = "vertical",
-    legend.justification = "center",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(Topt_plots)
-```
-
-```{r fig-S4_CTmin, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'}
-# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
-
-#   x    = biting tolerance (with a point at infinity)
-#   y    = vertebrate host population density
-# colour = CTmin
-# Facets = systems
-
-CTmin_df <- ThermPathChars %>%
-  ungroup() %>%
-  distinct() %>%
-  # Arrange along the plotting variables
-  arrange(system_label, sigmaH_proxy, KH, CTmin)
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-temp <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.25 * infinite_divide, infinite_skew))
-  ))
-temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.15 * infinite_divide, infinite_skew))
-  ))
-temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.05 * infinite_divide, infinite_skew))
-  ))
-temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.3 * infinite_divide, infinite_skew))
-  ))
-temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.2 * infinite_divide, infinite_skew))
-  ))
-temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.1 * infinite_divide, infinite_skew))
-  ))
-temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(infinite_divide, infinite_skew))
-  ))
-
-CTmin_df <- add_row(CTmin_df, temp)
-CTmin_df <- add_row(CTmin_df, temp2)
-CTmin_df <- add_row(CTmin_df, temp3)
-CTmin_df <- add_row(CTmin_df, temp4)
-CTmin_df <- add_row(CTmin_df, temp5)
-CTmin_df <- add_row(CTmin_df, temp6)
-CTmin_df <- add_row(CTmin_df, temp7) %>%
-  arrange(sigmaH_proxy) %>%
-  distinct()
-
-CTmin_breaks <- seq(15, 31, by = 1)
-
-CTmin_plots <- CTmin_df %>%
-  ## Set up plot ##
-  # x = biting tolerance (with a point at infinity),
-  # y = vertebrate host population density,
-  # color = transmission thermal optimum
-  ggplot(aes(x = KH, y = sigmaH_proxy)) +
-
-  # CTmin for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTmin_df, sigmaH_proxy < infinite_divide**0.98),
-    aes(z = CTmin),
-    breaks = CTmin_breaks
-  ) +
-
-  # CTmin for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTmin_df, sigmaH_proxy > infinite_divide**1.02),
-    aes(z = CTmin),
-    size = 1,
-    breaks = CTmin_breaks
-  ) +
-
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.05, 1E4),
-    breaks = 10^seq(-1, 4, 1),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: log10-scale y axis, with no buffer space
-  scale_y_log10(
-    name = TeX("Biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-
-  # fill:
-  scale_fill_viridis_d(
-    name = "Critical thermal minimum (°C)"
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
-  # legend:
-  guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    direction = "vertical",
-    barheight = unit(6, "cm"),
-    show.limits = TRUE
-  )) +
-
-  # theme options:
-  theme_minimal(11) +
-  theme(
-    plot.title = ggtext::element_markdown(),
-    legend.position = "right",
-    legend.margin = margin(0, 0, 0, 0),
-    legend.text = element_text(size = 11),
-    legend.title = element_text(size = 11, hjust = 0),
-    legend.direction = "horizontal",
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0)
-    )
-  )
-
-# Plot
-shift_legend(CTmin_plots)
-```
-
-```{r fig-S5_CTmax, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'}
-
-# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
-
-#   x    = biting tolerance (with a point at infinity)
-#   y    = vertebrate host population density
-# colour = CTmax
-# Facets = systems
-
-CTmax_df <- ThermPathChars %>%
-  ungroup() %>%
-  distinct() %>%
-  # Arrange along the plotting variables
-  arrange(system_label, sigmaH_proxy, KH, CTmin)
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-temp <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.25 * infinite_divide, infinite_skew))
-  ))
-temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.15 * infinite_divide, infinite_skew))
-  ))
-temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.05 * infinite_divide, infinite_skew))
-  ))
-temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.3 * infinite_divide, infinite_skew))
-  ))
-temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.2 * infinite_divide, infinite_skew))
-  ))
-temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(1.1 * infinite_divide, infinite_skew))
-  ))
-temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                               mean(c(infinite_divide, infinite_skew))
-  ))
-
-CTmax_df <- add_row(CTmax_df, temp)
-CTmax_df <- add_row(CTmax_df, temp2)
-CTmax_df <- add_row(CTmax_df, temp3)
-CTmax_df <- add_row(CTmax_df, temp4)
-CTmax_df <- add_row(CTmax_df, temp5)
-CTmax_df <- add_row(CTmax_df, temp6)
-CTmax_df <- add_row(CTmax_df, temp7) %>%
-  arrange(sigmaH_proxy) %>%
-  distinct()
-
-CTmax_breaks <- seq(23, 35, by = 1)
-
-CTmax_plots <- CTmax_df %>%
-  ## Set up plot ##
-  # x = biting tolerance (with a point at infinity),
-  # y = vertebrate host population density,
-  # color = transmission thermal optimum
-  ggplot(aes(x = KH, y = sigmaH_proxy)) +
-
-  # CTmin for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTmax_df, sigmaH_proxy < infinite_divide**0.98),
-    aes(z = CTmax),
-    breaks = CTmax_breaks
-  ) +
-
-  # CTmin for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(CTmax_df, sigmaH_proxy > infinite_divide**1.02),
-    aes(z = CTmax),
-    size = 1,
-    breaks = CTmax_breaks
-  ) +
-
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.05, 1E4),
-    breaks = 10^seq(-1, 4, 1),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: log10-scale y axis, with no buffer space
-  scale_y_log10(
-    name = TeX("Biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-
-  # fill:
-  scale_fill_manual(
-    name = "Critical thermal maximum (°C)",
-    values = met.brewer("Tam",
-                        n = length(CTmax_breaks),
-                        direction = -1
-    )
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-
-  # legend:
-  guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    direction = "vertical",
-    barheight = unit(6, "cm"),
-    show.limits = TRUE
-  )) +
-
-  # theme options:
-  theme_minimal(11) +
-  theme(
-    plot.title = ggtext::element_markdown(),
-    legend.position = "right",
-    legend.margin = margin(0, 0, 0, 0),
-    legend.text = element_text(size = 11),
-    legend.title = element_text(size = 11, hjust = 0),
-    legend.direction = "horizontal",
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0)
-    )
-  )
-
-# Plot
-shift_legend(CTmax_plots)
-```
-
-```{r fig-S6_CT_Range, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'}
-# x-axis = vertebrate host population density
-# y-axis = Temperature
-# linetype = biting tolerance
-# colour = CT_min (blue), CT_max (red)
-
-CTRange_df <- ThermPathChars %>%
-  # Arrange along the plotting variables
-  select(system_label, sigmaH, KH, CTmax, CTmin) %>%
-  # Choose a few sigmaH values to plot, including Inf
-  filter(sigmaH %in% c(10, 50, Inf)) %>%
-  group_by(KH) %>%
-  # Arrange along the plotting variables
-  arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
-  ungroup() %>%
-  melt(id = c("system_label", "KH", "sigmaH")) %>%
-  arrange(KH, sigmaH)
-
-CTRange_plots <- CTRange_df %>%
-  ## Set up plot ##
-  # x-axis = population density, y-axis = temperature,
-  # color = thermal extrema, linetype = sigmaH
-  ggplot(aes(
-    x = KH, y = value,
-    linetype = as.factor(sigmaH), color = variable
-  )) +
-
-  # Mosquito thermal tolerance range lines
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-
-  # Curves showing CTmin and CTmax
-  geom_path(
-    data = filter(CTRange_df, variable == "CTmin"),
-    lwd = 1
-  ) +
-  geom_path(
-    data = filter(CTRange_df, variable == "CTmax"),
-    lwd = 1
-  ) +
-
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(1E-2, 1E5),
-    breaks = 10^seq(-1, 4),
-    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: small buffer space
-  scale_y_continuous(
-    name = expression("Temperature "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = range(CTRange_df$value, na.rm = TRUE),
-    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
-                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
-                 by = 2
-    )
-  ) +
-  # linetype:
-  scale_linetype_manual(
-    name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c("solid", "longdash", "dotted"),
-    breaks = c(10, 50, Inf),
-    labels = unname(c("10 (Chitnis)", "50 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "Thermal extrema",
-    breaks = c("CTmax", "CTmin", "VTTR"),
-    labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"),
-    values = c("red", "blue", "grey"),
-    guide = guide_legend(keyheight = unit(40, "cm"))
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label,
-             scales = "free",
-             nrow = 2,
-             labeller = labeller()
-  ) +
-
-  # legend:
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 4),
-      order = 1
-    ),
-    linetype = guide_legend(
-      keywidth = 4,
-      order = 2
-    ),
-  ) +
-
-  # theme options:
-  theme_minimal_hgrid(11) +
-  theme(
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0
-    )
-  )
-
-# Plot
-shift_legend(CTRange_plots)
-```
-
-```{r fig-S7_CH_Range, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CH_Range} Critical community sizes as a function of temperature and biting tolerance.'}
-
-# x = vertebrate host population density
-# y = Temperature
-# linetype = vertebrate host biting tolerance (needs to vary from "zero to infinity")
-# curves:
-#   CH_min - blue
-#   CH_max - red
-#   VTTR - black
-
-# build data frame for plotting
-CHRange_df <- AllOutputs %>%
-  ungroup() %>%
-  # Arrange along the plotting variables
-  select(system_label, Temperature, sigmaH, CHmax, CHmin) %>%
-  filter(sigmaH %in% c(10, 50, 100)) %>%
-  filter(is.finite(CHmax)) %>%
-  filter(CHmin > 0) %>%
-  distinct() %>%
-  # Arrange along the plotting variables
-  arrange(system_label, Temperature, sigmaH, CHmax, CHmin) %>%
-  melt(id = c("system_label", "Temperature", "sigmaH")) %>%
-  arrange(Temperature, sigmaH)
-
-CHRange_plots <- CHRange_df %>%
-  ## Set up plot ##
-  # x = threshold values, y = temperature,
-  # color = threshold type, line type = sigmaH
-  ggplot(aes(
-    x = value, y = Temperature,
-    color = variable, linetype = as.factor(sigmaH)
-  )) +
-
-  # mosquito thermal tolerance range curves:
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
-    lwd = 1
-  ) +
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
-    lwd = 1
-  ) +
-
-  # CH threshold curves:
-  geom_path(
-    data = filter(CHRange_df, variable == "CHmin" & is.finite(sigmaH)),
-    lwd = 1
-  ) +
-  geom_path(
-    data = filter(CHRange_df, variable == "CHmax"),
-    lwd = 1
-  ) +
-
-  # x-axis: log10-scaled with no buffer-space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density"),
-    expand = c(0, 0),
-    limits = c(0.01, 2E5),
-    breaks = 10^seq(-2, 5),
-    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$", "$10^5$"))
-  ) +
-  # y-axis:
-  scale_y_continuous(
-    name = expression("Temperature "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = range(CHRange_df$Temperature),
-    breaks = seq(floor(range(CHRange_df$Temperature)[1]),
-                 floor(range(CHRange_df$Temperature)[2]),
-                 by = 2
-    )
-  ) +
-  # linetype:
-  scale_linetype_manual(
-    name = "Biting tolerance\n(bites per host per day)",
-    values = c("solid", "longdash", "dotdash"),
-    breaks = c(10, 50, 100)
-  ) +
-
-  # color:
-  scale_colour_manual(
-    name = "Threshold type",
-    values = c("red", "blue", "grey"),
-    breaks = c("CHmax", "CHmin", "VTTR"),
-    labels = c("Maximum community size", "Minimum community size", "Mosquito thermal niche")
-  ) +
-
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2) +
-
-  # legend:
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 4),
-      order = 1
-    ),
-    linetype = guide_legend(
-      keywidth = 4,
-      order = 2
-    ),
-  ) +
-  # theme options:
-  theme_minimal_vgrid(11) +
-  theme(
-    legend.box = "vertical",
-    legend.position = "bottom",
-    legend.margin = margin(0, 0, 0, 0),
-    legend.text = ggtext::element_markdown(),
-    legend.title = element_text(size = 11),
-    legend.direction = "vertical",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(CHRange_plots)
-```
-
-```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
-
-# Estimating the difference between Topt and Topt_RM numerically using our previous data
-Toptdiff_df1 <- ThermPathChars %>%
-  select(system_ID, sigmaH, KH, Topt) %>%
-  filter(is.finite(sigmaH)) %>%
-  distinct()
-
-Toptdiff_df2 <- ThermPathChars %>%
-  filter(is.infinite(sigmaH)) %>%
-  select(system_ID, KH, Topt) %>%
-  rename(Topt_RM = Topt) %>%
-  distinct()
-
-Toptdiff_df <- left_join(Toptdiff_df1, Toptdiff_df2) %>%
-  mutate(Toptdiff = Topt_RM - Topt) %>%
-  mutate(absToptdiff = abs(Toptdiff)) %>%
-  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
-  mutate(sigmaHKH = sigmaH * KH) %>%
-  group_by(system_ID) %>%
-  filter(absToptdiff == max(absToptdiff)) %>%
-  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
-  distinct()
-
-# Calculating Topt0 using the "simplified" equation
-Topt0_df <- VecParms %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
-  filter(is.finite(proxy_0)) %>%
-  select(system_ID, Temperature, proxy_0) %>%
-  group_by(system_ID)
-
-Topt0_base_estimates <- Topt0_df %>%
-  group_by(system_ID) %>%
-  # Calculate Topt_0
-  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
-  rename(Topt_0 = Temperature)
-# check with above: Topt_0 matches with Topt when sigmaH*KH is minimized
-# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
-
-# Calculating Topt0 using the "simplified" equation
-ToptRM_df <- VecParms %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
-  select(system_ID, Temperature, proxy_RM) %>%
-  group_by(system_ID)
-
-ToptRM_base_estimates <- ToptRM_df %>%
-  group_by(system_ID) %>%
-  # Calculate Topt_RM
-  filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>%
-  rename(Topt_RM = Temperature)
-# check with above: Topt_RM matches with Topt when sigmaH*KH is maximized
-# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
-
-Topt_estimates <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
-  select(system_ID, Topt_RM, Topt_0) %>%
-  mutate(Topt_diff = Topt_RM - Topt_0) %>%
-  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
-
-# Investigating Topt_RM and Topt_0 further
-
-test_df <- VecParms %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(sigmaVV0 = sigmaV * V0) %>%
-  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
-  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0
-  filter(is.finite(proxy_0)) %>%
-  select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0)
-```
+<!-- # Supplementary Figures -->
+
+<!-- ```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'} -->
+<!-- # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density. -->
+
+<!-- # x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity") -->
+<!-- # y = Temperature -->
+<!-- # color = R0 -->
+<!-- # curves: -->
+<!-- #   R0 = 1 contour (black curve) -->
+<!-- #   Topt (red curve) -->
+
+<!-- # Facets: -->
+<!-- # Rows = levels of vertebrate host population density -->
+<!-- # Columns = two MBPT systems -->
+<!-- # Total = 6 plots -->
+
+<!-- ## Set up plot data frame -->
+<!-- # We re-create the output data frame so that we can vary sigmaH correctly. -->
+<!-- # We also drop the resolution of KH down to just three values -->
+<!-- # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald" -->
+
+<!-- ## Configure data frame for plotting -->
+<!-- R0_df <- data.R0 %>% -->
+<!--   select(system_ID, system_label, Temperature, sigmaH, KH, median) %>% -->
+<!--   rename(R0 = median) %>%  -->
+<!--   # Consider only 3 values of KH (on a log10-scale) -->
+<!--   filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1 -->
+<!--   # Choose a limited range of sigmaH values -->
+<!--   filter(sigmaH > 10^0.5) %>% -->
+<!--   # Group by plotting variables -->
+<!--   group_by(system_ID, KH, sigmaH) %>% -->
+<!--   # Calculate Topt (which.max requires grouping) -->
+<!--   mutate(Topt = `Temperature`[which.max(R0)]) %>% -->
+<!--   as_tibble() %>% -->
+<!--   arrange(system_ID, sigmaH, Temperature) -->
+
+<!-- ## Add a "point at infinity" for sigmaH -->
+<!-- # Value of sigmaH to replace 'Inf' with for plotting -->
+<!-- infinite_skew <- 10^3 + 2500 -->
+
+<!-- # Get the largest value of log10(sigmaH) -->
+<!-- max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>% -->
+<!--   select(sigmaH) %>% -->
+<!--   max() %>% -->
+<!--   log10() -->
+
+<!-- # Used to create a gap dividing finite and infinite sigmaH -->
+<!-- infinite_divide <- 10^mean(c(3, log10(infinite_skew))) -->
+
+<!-- # add a second proxy sigmaH point at infinity to make the values easier to see there -->
+<!-- temp <- filter(R0_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide)) -->
+<!-- # Create a proxy sigmaH variable that replaces Inf with infinite_skew -->
+<!-- R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH), -->
+<!--                                              sigmaH, infinite_skew -->
+<!-- )) -->
+<!-- R0_df <- add_row(R0_df, temp) %>% distinct() -->
+
+<!-- ## Compute mosquito thermal tolerance range (minimum and maximum) -->
+<!-- temp_MosqThermRange_df <- MosqThermRange_df %>% -->
+<!--   select(system_label, CTmin_V0, CTmax_V0) -->
+
+<!-- ## PLOTTING ## -->
+
+<!-- ## Options -->
+<!-- # Define sigmaH tick breaks and labels -->
+<!-- sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew) -->
+<!-- sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$")) -->
+
+<!-- # Labels for facet rows -->
+<!-- R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10)) -->
+<!-- mylabels <- as_labeller(c( -->
+<!--   `0.1` = "0.1 vertebrate hosts / ha", -->
+<!--   `1` = "1 vertebrate host / ha", -->
+<!--   `10` = "10 vertebrate hosts / ha" -->
+<!-- )) -->
+
+<!-- # Breaks used to decide fill for the heat map -->
+<!-- fill_breaks <- c(1, seq(5, 20, by = 5), Inf) -->
+
+<!-- # Define colors for heat map so that values of R0>1 go from yellow to red -->
+<!-- my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd")))) -->
+
+<!-- ## PLOT ## -->
+<!-- R0_plot <- R0_df %>% -->
+<!--   ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) + -->
+
+<!--   # Mosquito thermal tolerance range lines -->
+<!--   geom_hline( -->
+<!--     data = temp_MosqThermRange_df, -->
+<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
+<!--     lwd = 1.275 -->
+<!--   ) + -->
+<!--   geom_hline( -->
+<!--     data = temp_MosqThermRange_df, -->
+<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
+<!--     lwd = 1.275 -->
+<!--   ) + -->
+
+<!--   # R0 contours for FINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98), -->
+<!--     breaks = fill_breaks -->
+<!--   ) + -->
+
+<!--   # R0 contours for INFINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02), -->
+<!--     breaks = fill_breaks -->
+<!--   ) + -->
+
+<!--   # R0 = 1 contour: -->
+<!--   geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) + -->
+
+<!--   # Topt curve: -->
+<!--   geom_line( -->
+<!--     # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one -->
+<!--     mapping = aes( -->
+<!--       x = sigmaH_proxy, -->
+<!--       y = Topt, -->
+<!--       colour = "Topt" -->
+<!--     ), -->
+<!--     lwd = 1, -->
+<!--     linetype = 1 -->
+<!--   ) + -->
+
+<!--   # white lines breaking up finite/infinite sigmaH values -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = 0.85 * infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .8, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .8, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = 1.2 * infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .8, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+
+<!--   # x-axis: -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
+<!--     breaks = sigmaH_breaks, -->
+<!--     labels = sigmaH_labels, -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+
+<!--   # y-axis: -->
+<!--   scale_y_continuous( -->
+<!--     name = expression("Temperature "(degree * C)), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(14, 36), -->
+<!--     breaks = seq(10, 36, by = 2) -->
+<!--   ) + -->
+
+<!--   # color: -->
+<!--   scale_colour_manual( -->
+<!--     name = "", -->
+<!--     labels = c( -->
+<!--       "R0=1" = unname(TeX("$R_0=1$")), -->
+<!--       "Topt" = "Transmission\nthermal\noptimum", -->
+<!--       "VTTR" = "Mosquito\nthermal\ntolerance\nlimit" -->
+<!--     ), -->
+<!--     values = c("black", "purple", "grey"), -->
+<!--     guide = guide_legend( -->
+<!--       order = 1, -->
+<!--       keyheight = unit(2, "cm"), -->
+<!--       override.aes = list(size = 6) -->
+<!--     ) -->
+<!--   ) + -->
+
+<!--   # fill: -->
+<!--   scale_fill_manual( -->
+<!--     name = TeX("$R_0$"), -->
+<!--     values = my.cols, -->
+<!--     guide = guide_colorsteps( -->
+<!--       order = 2, -->
+<!--       breaks = fill_breaks, -->
+<!--       barheight = unit(8, "cm") -->
+<!--     ) -->
+<!--   ) + -->
+
+<!--   # faceting: -->
+<!--   facet_rep_grid( -->
+<!--     rows = vars(system_label), -->
+<!--     cols = vars(KH), -->
+<!--     scales = "free_y", -->
+<!--     labeller = labeller(.cols = mylabels), -->
+<!--     repeat.tick.labels = "left" -->
+<!--   ) + -->
+
+<!--   # theme options: -->
+<!--   theme_minimal_hgrid(11) + -->
+<!--   theme( -->
+<!--     axis.line = element_line(), -->
+<!--     panel.spacing = unit(1, "lines"), -->
+<!--     legend.text = element_text(size = 11), -->
+<!--     legend.text.align = 0, -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 8, -->
+<!--       hjust = 0 -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot it -->
+<!-- R0_plot -->
+<!-- ``` -->
+
+<!-- ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'} -->
+<!-- Topt_df <- data.Topt %>%  -->
+<!--   pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
+<!--               names_from = variable, -->
+<!--               values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%  -->
+<!--   right_join(read_rds("results/CT_vals.rds") %>%  -->
+<!--                filter(variable == "CTwidth") %>%  -->
+<!--                pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
+<!--                            names_from = "variable", -->
+<!--                            values_from = c("mean", "median", "lowHCI", "highHCI"))) %>%  -->
+<!--   filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
+<!--   # filter(mean_CTwidth>0) %>%  -->
+<!--   select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>% -->
+<!--   rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,  -->
+<!--          highHCI = highHCI_Topt) %>%  -->
+<!--   # filter(KH > 0.01) %>% -->
+<!--   # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>% -->
+<!--   group_by(KH) %>% -->
+<!--   # Arrange along the plotting variables -->
+<!--   arrange(system_ID, KH, mean) %>% -->
+<!--   arrange(sigmaH) %>% -->
+<!--   ungroup() -->
+
+<!-- # PLOTTING -->
+<!-- Topt_plot <- Topt_df %>% -->
+<!--   ## Set up plot ## -->
+<!--   # color = sigmaH -->
+<!--   ggplot(aes(x = KH, colour = as.factor(sigmaH))) + -->
+<!--   # Topt curves: -->
+<!--   geom_path(aes(y = median), lwd = 1) + -->
+<!--   # # Add dotted lines showing 89% HCI limits -->
+<!--   # geom_path(aes(y = lowHCI), linetype = "dashed") + -->
+<!--   # geom_path(aes(y = highHCI), linetype = "dashed") + -->
+<!--   # x-axis: log10 scale, no buffer space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(0.01, 2E4), -->
+<!--     breaks = 10^seq(-2, 4), -->
+<!--     labels = TeX(c( -->
+<!--       "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$" -->
+<!--     )) -->
+<!--   ) + -->
+<!--   # y-axis -->
+<!--   scale_y_continuous( -->
+<!--     name = expression("Thermal optimum "(degree * C)), -->
+<!--     expand = c(0.05, 0.05), -->
+<!--     limits = c(21,30.5), # mean: 21-31, median: 21-32 -->
+<!--     breaks = seq(21,32, by = 1) -->
+<!--   ) + -->
+<!--   # color: -->
+<!--   scale_colour_manual( -->
+<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
+<!--     values = c(met.brewer("VanGogh3", 4, direction = 1), "black"), -->
+<!--     # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"), -->
+<!--     breaks = c(1, 10, 100, Inf), -->
+<!--     labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
+<!--   ) + -->
+<!--   scale_fill_manual( -->
+<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
+<!--     values = c(met.brewer("VanGogh3", 4, direction = 1), "black"), -->
+<!--     # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"), -->
+<!--     breaks = c(1, 10, 100, Inf), -->
+<!--     labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
+<!--   ) + -->
+<!--   # faceting: -->
+<!--   facet_wrap(~system_ID, nrow = 2, labeller = labeller()) + -->
+<!--   # theme options: -->
+<!--   theme_minimal(16) + -->
+<!--   guides(color = guide_legend(override.aes = list(size = 4))) + -->
+<!--   theme( -->
+<!--     legend.position = "bottom", -->
+<!--     legend.margin = margin(), -->
+<!--     legend.direction = "vertical", -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     legend.text = element_text( -->
+<!--       size = 10, -->
+<!--       hjust = 0 -->
+<!--     ), -->
+<!--     legend.justification = "left", -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- Topt_plot <- shift_legend(Topt_plot) -->
+<!-- ``` -->
+
+<!-- ```{r fig-S3_Topt_plots, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'} -->
+
+<!-- # x-axis = vertebrate host biting tolerance -->
+<!-- # y-axis = thermal optimum -->
+<!-- # color = vertebrate host population density -->
+
+<!-- Topt_plot <- data.Topt %>%  -->
+<!--   # filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
+<!--   # Choose appropriate pop. dens. values and group -->
+<!--   filter(KH %in% 10^seq(0, 3)) %>% -->
+<!--   arrange(system_ID, KH, sigmaH, median) %>%  -->
+<!--   ## Set up plot ## -->
+<!--   # color = sigmaH -->
+<!--   ggplot(aes(x = sigmaH, colour = as.factor(KH))) + -->
+<!--   # Topt curves: -->
+<!--   geom_path(aes(y = mean), lwd = 1) + -->
+<!--   # # Dotted lines showing limits of 89% HCI -->
+<!--   # geom_path(aes(y = lowHCI),linetype = "dashed") + -->
+<!--   # geom_path(aes(y = highHCI),linetype = "dashed") + -->
+<!--   # white lines breaking up finite/infinite sigmaH values: -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = 0.95 * infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .9, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = 1.05 * infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .9, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+<!--   geom_vline( -->
+<!--     aes(xintercept = 1.15 * infinite_divide), -->
+<!--     colour = "white", -->
+<!--     lwd = .9, -->
+<!--     show.legend = FALSE -->
+<!--   ) + -->
+<!--   # x-axis: Use a log10-scale with no buffer space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(0.5, 150), -->
+<!--     breaks = sigmaH_breaks, -->
+<!--     labels = sigmaH_labels -->
+<!--   ) + -->
+<!--   # y-axis -->
+<!--   scale_y_continuous( -->
+<!--     name = expression("Thermal optimum "(degree * C)), -->
+<!--     expand = c(0.05, 0.05), -->
+<!--     limits = c(21,31), # mean: 21-31, median: 21-32 -->
+<!--     breaks = seq(21,32, by = 1) -->
+<!--   ) + -->
+<!--   # color: -->
+<!--   scale_colour_manual( -->
+<!--     name = "Vertebrate host population\ndensity (ind/ha)", -->
+<!--     values = met.brewer("Hokusai3", 4, -->
+<!--                         # option = "plasma" -->
+<!--     )) + -->
+<!--   scale_fill_manual( -->
+<!--     name = "Vertebrate host population\ndensity (ind/ha)", -->
+<!--     values = met.brewer("Hokusai3", 4, -->
+<!--                         # option = "plasma" -->
+<!--     )) + -->
+<!--   # faceting: -->
+<!--   facet_wrap(~system_ID, -->
+<!--              scales = "free", -->
+<!--              nrow = 2, -->
+<!--              labeller = labeller()  ) + -->
+<!--   # theme options: -->
+<!--   theme_minimal(16) + -->
+<!--   guides(color = guide_legend(override.aes = list(size = 4))) + -->
+<!--   theme( -->
+<!--     legend.position = "bottom", -->
+<!--     legend.margin = margin(), -->
+<!--     legend.direction = "vertical", -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     legend.text = element_text( -->
+<!--       size = 10, -->
+<!--       hjust = 0 -->
+<!--     ), -->
+<!--     legend.justification = "left", -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- Topt_plot <- shift_legend(Topt_plot) -->
+<!-- ``` -->
+
+<!-- ```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'} -->
+<!-- # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider. -->
+
+<!-- #   x    = biting tolerance (with a point at infinity) -->
+<!-- #   y    = vertebrate host population density -->
+<!-- # colour = CTmin -->
+<!-- # Facets = systems -->
+
+<!-- CTmin_df <- data.CT %>% -->
+<!--   filter(variable == "CTmin") %>%  -->
+<!--   filter(is.finite(mean)) %>% -->
+<!--   mutate(sigmaH_proxy = sigmaH) %>%  -->
+<!--   # Arrange along the plotting variables -->
+<!--   arrange(system_ID, KH, sigmaH_proxy, mean) %>%  -->
+<!--   ungroup() -->
+
+<!-- # add many third proxy sigmaH points at infinity to make the values easier to see there -->
+<!-- temp <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.25 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.15 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.05 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.3 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.2 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.1 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(infinite_divide, infinite_skew)) -->
+<!--   )) -->
+
+<!-- CTmin_df <- add_row(CTmin_df, temp) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp2) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp3) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp4) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp5) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp6) -->
+<!-- CTmin_df <- add_row(CTmin_df, temp7) %>% -->
+<!--   arrange(sigmaH_proxy) %>% -->
+<!--   distinct() -->
+
+<!-- CTmin_heat_plots <- CTmin_df %>% -->
+<!--   ## Set up plot ## -->
+<!--   # x = biting tolerance (with a point at infinity), -->
+<!--   # y = vertebrate host population density, -->
+<!--   # color = width of parasite thermal mean_CTwidth -->
+<!--   ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) + -->
+
+<!--   # CTmin for FINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(CTmin_df, sigmaH_proxy < 100) -->
+<!--   ) + -->
+
+<!--   # CTmin for INFINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(CTmin_df, is.infinite(sigmaH)) -->
+<!--   ) + -->
+
+<!--   # x-axis: log10-scale with no buffer space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(0.05, 1E4), -->
+<!--     breaks = 10^seq(-1, 4, 1), -->
+<!--     labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$")) -->
+<!--   ) + -->
+<!--   # y-axis: log10-scale y axis, with no buffer space -->
+<!--   scale_y_log10( -->
+<!--     name = TeX("Biting tolerance (bites per host per day)"), -->
+<!--     expand = c(0, 0), -->
+<!--     breaks = sigmaH_breaks, -->
+<!--     labels = sigmaH_labels -->
+<!--   ) + -->
+<!--   # color: -->
+<!--   scale_fill_viridis_d( -->
+<!--     name = "Mean critical thermal minimum (°C)", -->
+<!--     option = "plasma" -->
+<!--   ) + -->
+<!--   # faceting: -->
+<!--   facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) + -->
+<!--   # legend: -->
+<!--   guides(fill = guide_coloursteps( -->
+<!--     title.position = "top", title.hjust = 0.5, -->
+<!--     barwidth = unit(10, "cm"), -->
+<!--     show.limits = TRUE -->
+<!--   )) + -->
+<!--   # theme options: -->
+<!--   theme_minimal(16) + -->
+<!--   theme( -->
+<!--     legend.box = "horizontal", -->
+<!--     legend.position = "bottom", -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     legend.direction = "horizontal", -->
+<!--     legend.justification = "left", -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- CTmin_heat_plots <- shift_legend(CTmin_heat_plots) -->
+<!-- ``` -->
+
+<!-- ```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'} -->
+
+<!-- # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider. -->
+
+<!-- #   x    = biting tolerance (with a point at infinity) -->
+<!-- #   y    = vertebrate host population density -->
+<!-- # colour = CTmax -->
+<!-- # Facets = systems -->
+
+<!-- CTmax_df <- read_rds("results/CT_vals.rds") %>% -->
+<!--   filter(variable == "CTmax") %>%  -->
+<!--   filter(is.finite(mean)) %>% -->
+<!--   mutate(sigmaH_proxy = sigmaH) %>%  -->
+<!--   # Arrange along the plotting variables -->
+<!--   arrange(system_ID, KH, sigmaH_proxy, mean) %>%  -->
+<!--   ungroup() -->
+
+<!-- # add many third proxy sigmaH points at infinity to make the values easier to see there -->
+<!-- temp <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.25 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.15 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.05 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.3 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.2 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(1.1 * infinite_divide, infinite_skew)) -->
+<!--   )) -->
+<!-- temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
+<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
+<!--                                mean(c(infinite_divide, infinite_skew)) -->
+<!--   )) -->
+
+<!-- CTmax_df <- add_row(CTmax_df, temp) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp2) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp3) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp4) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp5) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp6) -->
+<!-- CTmax_df <- add_row(CTmax_df, temp7) %>% -->
+<!--   arrange(sigmaH_proxy) %>% -->
+<!--   distinct() -->
+
+<!-- min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median))) -->
+<!-- max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median))) -->
+<!-- CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1) -->
+
+<!-- CTmax_heat_plots <- CTmax_df %>% -->
+<!--   ## Set up plot ## -->
+<!--   # x = biting tolerance (with a point at infinity), -->
+<!--   # y = vertebrate host population density, -->
+<!--   # color = CTmax -->
+<!--   ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) + -->
+<!--   # CTmax for FINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(CTmax_df, sigmaH_proxy < 100) -->
+<!--   ) + -->
+
+<!--   # CTmax for INFINITE sigmaH: -->
+<!--   geom_contour_filled( -->
+<!--     data = filter(CTmax_df, is.infinite(sigmaH)) -->
+<!--   ) + -->
+<!--   # x-axis: log10-scale with no buffer space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(0.05, 1E4), -->
+<!--     breaks = 10^seq(-1, 4, 1), -->
+<!--     labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$")) -->
+<!--   ) + -->
+<!--   # y-axis: log10-scale y axis, with no buffer space -->
+<!--   scale_y_log10( -->
+<!--     name = TeX("Biting tolerance (bites per host per day)"), -->
+<!--     expand = c(0, 0), -->
+<!--     breaks = sigmaH_breaks, -->
+<!--     labels = sigmaH_labels -->
+<!--   ) + -->
+<!--   # color: -->
+<!--   scale_fill_viridis_d( -->
+<!--     name = "Mean critical thermal maximum (°C)", -->
+<!--     option = "plasma" -->
+<!--   ) + -->
+<!--   # faceting: -->
+<!--   facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) + -->
+<!--   # legend: -->
+<!--   guides(fill = guide_coloursteps( -->
+<!--     title.position = "top", title.hjust = 0.5, -->
+<!--     barwidth = unit(10, "cm"), -->
+<!--     show.limits = TRUE -->
+<!--   )) + -->
+<!--   # theme options: -->
+<!--   theme_minimal(16) + -->
+<!--   theme( -->
+<!--     legend.box = "horizontal", -->
+<!--     legend.position = "bottom", -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     legend.direction = "horizontal", -->
+<!--     legend.justification = "left", -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- CTmax_heat_plots <- shift_legend(CTmax_heat_plots) -->
+<!-- ``` -->
+
+<!-- ```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'} -->
+<!-- # x-axis = vertebrate host population density -->
+<!-- # y-axis = Temperature -->
+<!-- # linetype = biting tolerance -->
+<!-- # colour = CT_min (blue), CT_max (red) -->
+
+<!-- CTRange_df <- ThermPathChars %>% -->
+<!--   # Arrange along the plotting variables -->
+<!--   select(system_label, sigmaH, KH, CTmax, CTmin) %>% -->
+<!--   # Choose a few sigmaH values to plot, including Inf -->
+<!--   filter(sigmaH %in% c(10, 50, Inf)) %>% -->
+<!--   group_by(KH) %>% -->
+<!--   # Arrange along the plotting variables -->
+<!--   arrange(system_label, KH, sigmaH, CTmax, CTmin) %>% -->
+<!--   ungroup() %>% -->
+<!--   melt(id = c("system_label", "KH", "sigmaH")) %>% -->
+<!--   arrange(KH, sigmaH) -->
+
+<!-- CTRange_plots <- CTRange_df %>% -->
+<!--   ## Set up plot ## -->
+<!--   # x-axis = population density, y-axis = temperature, -->
+<!--   # color = thermal extrema, linetype = sigmaH -->
+<!--   ggplot(aes( -->
+<!--     x = KH, y = value, -->
+<!--     linetype = as.factor(sigmaH), color = variable -->
+<!--   )) + -->
+
+<!--   # Mosquito thermal tolerance range lines -->
+<!--   geom_hline( -->
+<!--     data = MosqThermRange_df, -->
+<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
+<!--     lwd = 1.275 -->
+<!--   ) + -->
+<!--   geom_hline( -->
+<!--     data = MosqThermRange_df, -->
+<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
+<!--     lwd = 1.275 -->
+<!--   ) + -->
+
+<!--   # Curves showing CTmin and CTmax -->
+<!--   geom_path( -->
+<!--     data = filter(CTRange_df, variable == "CTmin"), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+<!--   geom_path( -->
+<!--     data = filter(CTRange_df, variable == "CTmax"), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+
+<!--   # x-axis: log10-scale with no buffer space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(1E-2, 1E5), -->
+<!--     breaks = 10^seq(-1, 4), -->
+<!--     labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$")) -->
+<!--   ) + -->
+<!--   # y-axis: small buffer space -->
+<!--   scale_y_continuous( -->
+<!--     name = expression("Temperature "(degree * C)), -->
+<!--     expand = c(0.05, 0.05), -->
+<!--     limits = range(CTRange_df$value, na.rm = TRUE), -->
+<!--     breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]), -->
+<!--                  floor(range(CTRange_df$value, na.rm = TRUE)[2]), -->
+<!--                  by = 2 -->
+<!--     ) -->
+<!--   ) + -->
+<!--   # linetype: -->
+<!--   scale_linetype_manual( -->
+<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
+<!--     values = c("solid", "longdash", "dotted"), -->
+<!--     breaks = c(10, 50, Inf), -->
+<!--     labels = unname(c("10 (Chitnis)", "50 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
+<!--   ) + -->
+<!--   # color: -->
+<!--   scale_colour_manual( -->
+<!--     name = "Thermal extrema", -->
+<!--     breaks = c("CTmax", "CTmin", "VTTR"), -->
+<!--     labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"), -->
+<!--     values = c("red", "blue", "grey"), -->
+<!--     guide = guide_legend(keyheight = unit(40, "cm")) -->
+<!--   ) + -->
+
+<!--   # faceting: -->
+<!--   facet_wrap(~system_label, -->
+<!--              scales = "free", -->
+<!--              nrow = 2, -->
+<!--              labeller = labeller() -->
+<!--   ) + -->
+
+<!--   # legend: -->
+<!--   guides( -->
+<!--     color = guide_legend( -->
+<!--       override.aes = list(size = 4), -->
+<!--       order = 1 -->
+<!--     ), -->
+<!--     linetype = guide_legend( -->
+<!--       keywidth = 4, -->
+<!--       order = 2 -->
+<!--     ), -->
+<!--   ) + -->
+
+<!--   # theme options: -->
+<!--   theme_minimal_hgrid(11) + -->
+<!--   theme( -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0 -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- shift_legend(CTRange_plots) -->
+<!-- ``` -->
+
+<!-- ```{r fig-S7_CH_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CH_Range} Critical community sizes as a function of temperature and biting tolerance.'} -->
+
+<!-- # x = vertebrate host population density -->
+<!-- # y = Temperature -->
+<!-- # linetype = vertebrate host biting tolerance (needs to vary from "zero to infinity") -->
+<!-- # curves: -->
+<!-- #   CH_min - blue -->
+<!-- #   CH_max - red -->
+<!-- #   VTTR - black -->
+
+<!-- # build data frame for plotting -->
+<!-- CHRange_df <- AllOutputs %>% -->
+<!--   ungroup() %>% -->
+<!--   # Arrange along the plotting variables -->
+<!--   select(system_label, Temperature, sigmaH, CHmax, CHmin) %>% -->
+<!--   filter(sigmaH %in% c(10, 50, 100)) %>% -->
+<!--   filter(is.finite(CHmax)) %>% -->
+<!--   filter(CHmin > 0) %>% -->
+<!--   distinct() %>% -->
+<!--   # Arrange along the plotting variables -->
+<!--   arrange(system_label, Temperature, sigmaH, CHmax, CHmin) %>% -->
+<!--   melt(id = c("system_label", "Temperature", "sigmaH")) %>% -->
+<!--   arrange(Temperature, sigmaH) -->
+
+<!-- CHRange_plots <- CHRange_df %>% -->
+<!--   ## Set up plot ## -->
+<!--   # x = threshold values, y = temperature, -->
+<!--   # color = threshold type, line type = sigmaH -->
+<!--   ggplot(aes( -->
+<!--     x = value, y = Temperature, -->
+<!--     color = variable, linetype = as.factor(sigmaH) -->
+<!--   )) + -->
+
+<!--   # mosquito thermal tolerance range curves: -->
+<!--   geom_hline( -->
+<!--     data = MosqThermRange_df, -->
+<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+<!--   geom_hline( -->
+<!--     data = MosqThermRange_df, -->
+<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+
+<!--   # CH threshold curves: -->
+<!--   geom_path( -->
+<!--     data = filter(CHRange_df, variable == "CHmin" & is.finite(sigmaH)), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+<!--   geom_path( -->
+<!--     data = filter(CHRange_df, variable == "CHmax"), -->
+<!--     lwd = 1 -->
+<!--   ) + -->
+
+<!--   # x-axis: log10-scaled with no buffer-space -->
+<!--   scale_x_log10( -->
+<!--     name = TeX("Vertebrate host population density"), -->
+<!--     expand = c(0, 0), -->
+<!--     limits = c(0.01, 2E5), -->
+<!--     breaks = 10^seq(-2, 5), -->
+<!--     labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$", "$10^5$")) -->
+<!--   ) + -->
+<!--   # y-axis: -->
+<!--   scale_y_continuous( -->
+<!--     name = expression("Temperature "(degree * C)), -->
+<!--     expand = c(0.05, 0.05), -->
+<!--     limits = range(CHRange_df$Temperature), -->
+<!--     breaks = seq(floor(range(CHRange_df$Temperature)[1]), -->
+<!--                  floor(range(CHRange_df$Temperature)[2]), -->
+<!--                  by = 2 -->
+<!--     ) -->
+<!--   ) + -->
+<!--   # linetype: -->
+<!--   scale_linetype_manual( -->
+<!--     name = "Biting tolerance\n(bites per host per day)", -->
+<!--     values = c("solid", "longdash", "dotdash"), -->
+<!--     breaks = c(10, 50, 100) -->
+<!--   ) + -->
+
+<!--   # color: -->
+<!--   scale_colour_manual( -->
+<!--     name = "Threshold type", -->
+<!--     values = c("red", "blue", "grey"), -->
+<!--     breaks = c("CHmax", "CHmin", "VTTR"), -->
+<!--     labels = c("Maximum community size", "Minimum community size", "Mosquito thermal niche") -->
+<!--   ) + -->
+
+<!--   # faceting: -->
+<!--   facet_wrap(~system_label, scales = "free", nrow = 2) + -->
+
+<!--   # legend: -->
+<!--   guides( -->
+<!--     color = guide_legend( -->
+<!--       override.aes = list(size = 4), -->
+<!--       order = 1 -->
+<!--     ), -->
+<!--     linetype = guide_legend( -->
+<!--       keywidth = 4, -->
+<!--       order = 2 -->
+<!--     ), -->
+<!--   ) + -->
+<!--   # theme options: -->
+<!--   theme_minimal_vgrid(11) + -->
+<!--   theme( -->
+<!--     legend.box = "vertical", -->
+<!--     legend.position = "bottom", -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.text = ggtext::element_markdown(), -->
+<!--     legend.title = element_text(size = 11), -->
+<!--     legend.direction = "vertical", -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- # Plot -->
+<!-- shift_legend(CHRange_plots) -->
+<!-- ``` -->
+
+<!-- ```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'} -->
+
+<!-- # Estimating the difference between Topt and Topt_RM numerically using our previous data -->
+<!-- Toptdiff_df1 <- ThermPathChars %>% -->
+<!--   select(system_ID, sigmaH, KH, Topt) %>% -->
+<!--   filter(is.finite(sigmaH)) %>% -->
+<!--   distinct() -->
+
+<!-- Toptdiff_df2 <- ThermPathChars %>% -->
+<!--   filter(is.infinite(sigmaH)) %>% -->
+<!--   select(system_ID, KH, Topt) %>% -->
+<!--   rename(Topt_RM = Topt) %>% -->
+<!--   distinct() -->
+
+<!-- Toptdiff_df <- left_join(Toptdiff_df1, Toptdiff_df2) %>% -->
+<!--   mutate(Toptdiff = Topt_RM - Topt) %>% -->
+<!--   mutate(absToptdiff = abs(Toptdiff)) %>% -->
+<!--   mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>% -->
+<!--   mutate(sigmaHKH = sigmaH * KH) %>% -->
+<!--   group_by(system_ID) %>% -->
+<!--   filter(absToptdiff == max(absToptdiff)) %>% -->
+<!--   select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>% -->
+<!--   distinct() -->
+
+<!-- # Calculating Topt0 using the "simplified" equation -->
+<!-- Topt0_df <- VecParms %>% -->
+<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
+<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
+<!--   filter(is.finite(proxy_0)) %>% -->
+<!--   select(system_ID, Temperature, proxy_0) %>% -->
+<!--   group_by(system_ID) -->
+
+<!-- Topt0_base_estimates <- Topt0_df %>% -->
+<!--   group_by(system_ID) %>% -->
+<!--   # Calculate Topt_0 -->
+<!--   filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>% -->
+<!--   rename(Topt_0 = Temperature) -->
+<!-- # check with above: Topt_0 matches with Topt when sigmaH*KH is minimized -->
+<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->
+
+<!-- # Calculating Topt0 using the "simplified" equation -->
+<!-- ToptRM_df <- VecParms %>% -->
+<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
+<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% -->
+<!--   select(system_ID, Temperature, proxy_RM) %>% -->
+<!--   group_by(system_ID) -->
+
+<!-- ToptRM_base_estimates <- ToptRM_df %>% -->
+<!--   group_by(system_ID) %>% -->
+<!--   # Calculate Topt_RM -->
+<!--   filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>% -->
+<!--   rename(Topt_RM = Temperature) -->
+<!-- # check with above: Topt_RM matches with Topt when sigmaH*KH is maximized -->
+<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->
+
+<!-- Topt_estimates <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>% -->
+<!--   select(system_ID, Topt_RM, Topt_0) %>% -->
+<!--   mutate(Topt_diff = Topt_RM - Topt_0) %>% -->
+<!--   mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM) -->
+
+<!-- # Investigating Topt_RM and Topt_0 further -->
+
+<!-- test_df <- VecParms %>% -->
+<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
+<!--   mutate(sigmaVV0 = sigmaV * V0) %>% -->
+<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
+<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0 -->
+<!--   filter(is.finite(proxy_0)) %>% -->
+<!--   select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0) -->
+<!-- ``` -->

### 2023-05-12 code/main-analysis.R

@@ -89,9 +89,6 @@ source("code/trait-variation.R")
 
 # data.in.analysis <- read_rds("data/clean/full_traitset.rds")
 
-data.Vec <- read_rds("data/clean/data_vector.rds")
-data.Host <- read_rds("data/clean/data_host.rds")
-
 # Thin sample size
 thin_size <- 600 # full = 600, thin = 100
 

### 2023-05-12 code/trait-variation.R

@@ -43,8 +43,8 @@ lambdaH_baseline <- .005
 muH_baseline <- 1 / (365 * 20)
 
 # Host maximum biting tolerance (mosquitoes bites per day)
-sigmaH_vec <- 10^seq(-0.25,2.25, length.out = sigmaH_vec_length - 6) %>%
-  c(1, 10, 20, 50, 100, Inf) %>%
+sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
+  c(1, 10, 20, 50, 100, 1000, Inf) %>%
   unique() %>% sort()
 sigmaH_baseline <- 100
 

### 2023-05-15 manuscript-figures.Rmd
add figures

@@
 
-```{r fig-5_Topt, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
+```{r fig-5_Topt, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
 # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
@@
 
-```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
+```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
 # Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 

### 2023-05-15 code/sensitivity.R

@@ -53,6 +53,21 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                   sigmaH = c(), KH = c(), variable = c(),
                   lowHCI = c(), highHCI = c(), mean = c(), median = c())
 
+# Load needed datasets
+# R0 data
+data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
+# Topt data
+data.Topt <- read_rds("results/Topt_vals.rds")
+# Critical thermal extrema data
+data.CT <- read_rds("results/CT_vals.rds")
+
+
+KH_vec_length <- 300 # full = 300, thin = 20
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 300 # full = 300, thin = 20
+
+source("code/trait-variation.R")
 
 # 1) Define accessory functions -------------------------------------------
 
@@ -62,176 +77,12 @@ slice<-function(x,n) {
   lapply(seq(1,N,n),function(i) x[i:min(i+n-1,N)])
 }
 
-# Function: evaluate R0 (as a function of temperature), its mean, median, and 
-#           highest prob. intervals across samples
-R0_TPC_func <- function(in_df, system_name) {
-  out_df <- in_df %>%
-    expand_grid(dplyr::filter(data.Vec, system_ID == system_name)) %>%
-    data.table::data.table() %>%
-    mutate(RV = ifelse(is.infinite(sigmaH),
-                       sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
-                       sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
-    mutate(bV = ifelse(is.infinite(sigmaH),
-                       sigmaV, # Ross-Macdonald model
-                       sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
-    mutate(RH = ifelse(V0 == 0,
-                       0,
-                       bV * betaV * V0 * exp(-1 / (lf * etaV)) / (KH * (gammaH + muH) + eps))) %>%
-    # Basic reproduction number
-    mutate(R0 = sqrt(RV*RH))%>%
-    dplyr::select(system_ID, sample_num, Temperature, Model, sigmaH, KH, R0) %>%
-    # Normalize R0 across temperature
[…]

### 2023-05-15 code/sensitivity.R
update Topt uncertainty figure

@@ -688,18 +688,18 @@ for (var_name in temp_vars) {
 }
 
 # Save Topt relative highest posterior density data
-write_rds(Topt.HPD, "results/Topt_HPD_sens.rds")
-# Topt.HPD <- read_rds("results/Topt_HPD_sens.rds")
+# write_rds(Topt.HPD, "results/Topt_HPD_sens.rds")
+Topt.HPD <- read_rds("results/Topt_HPD_sens.rds")
 
 ## Plot Topt uncertainty 
 var_name_table <- list(
-  betaV = c(TeX("$\\beta_V$")),
-  deltaL = c(TeX("$\\delta_L$")),
-  etaV = c(TeX("$\\eta_V$")),
-  muV = c(TeX("$\\mu_V$")),
-  rhoL = c(TeX("$\\rho_L$")),
-  sigmaV = c(TeX("$\\sigma_V$")),
-  sigmaV_f = c(TeX("$\\sigma_v f$"))
+  betaV = "Vector competence",
+  deltaL = "Pr(larval survival)",
+  etaV = "Parasite development rate",
+  muV = "Mortality rate",
+  rhoL = "Immature development rate",
+  sigmaV = "Max. biting rate",
+  sigmaV_f = "Eggs per female per day"
 )
 
 Topt.uncertainty.plot <- Topt.HPD %>% 
@@ -717,22 +717,24 @@ Topt.uncertainty.plot <- Topt.HPD %>%
   dplyr::filter(rel_HPD_width < 1.01) %>%
   # arrange(system_ID, sigmaH, focal_var, Temperature) %>%
   ggplot(aes(x = KH, y = rel_HPD_width, color = focal_var)) +
-  geom_path(linewidth = 1) +
+  geom_point(linewidth = 1) +
   scale_color_discrete(
     name = "Focal parameter",
     breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
-    labels =  unname(TeX(c("$\\beta_V$", "$\\delta_L$", "$\\eta_V$", 
-                           "$\\mu_V$", "$\\rho_L$", "$\\sigma_V$",
-                           "$\\sigma_v f$")))
-  ) +
+    labels =  c("Vector competence", "Pr(larval survival)", 
+                "Parasite development rate", "Mortality rate", 
+                "Immature development rate", "Max. biting rate", 
+                "Eggs per female per day")
+  )  +
   scale_x_continuous(
[…]

### 2023-05-22 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 
-# Define temperature range of study
-Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
-
-# Thin sample size
-thin_size <- 1000 # full = 1000, thin = 100
-
-plot_bool = FALSE
-source("code/trait-transform.R", local = TRUE)
-# Host density vector: Number of values to include to consider for vertebrate host density
-KH_vec_length <- 300 # full = 300, thin = 20
-
-# Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 300 # full = 300, thin = 20
-
-# Get data for plotting thermal performance curves (data.Vec)
-source("code/trait-variation.R", local = TRUE)
+# # Define temperature range of study
+# Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
+# 
+# # Thin sample size
+# thin_size <- 1000 # full = 1000, thin = 100
+# 
+# plot_bool = FALSE
+# source("code/trait-transform.R", local = TRUE)
+# # Host density vector: Number of values to include to consider for vertebrate host density
+# KH_vec_length <- 300 # full = 300, thin = 20
+# 
+# # Biting tolerance vector: Number of values to consider for biting tolerance
+# sigmaH_vec_length <- 300 # full = 300, thin = 20
+# 
+# # Get data for plotting thermal performance curves (data.Vec)
+# !!! save a specific dataset to use for plotting trait TPCs
+# source("code/trait-variation.R", local = TRUE)
 
@@
 
-# R0 data
-data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
+# R0 data # !!! needs to be updated to include 1e-1, 1e0, 1e1
+data.R0 <- read_rds("results/R0_vals.rds")
 # Topt data
@@
 data.R0_norm <- data.R0 %>% 
+  ungroup() %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+  )) %>% 
   filter(KH %in% newKH_vals) %>% 
@@
   scale_x_continuous(
-    name = "Temperature (C)",
+    name = "Temperature (°C)",
     expand = c(0, 0),
@@
   # faceting:
-  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
   # legend
@@
   ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+  )) %>% 
   distinct() %>%
@@
     name = "",
-    labels = c("R0=1" = unname(TeX("$R_0=1$"))),
+    labels = c("R0=1" = unname(TeX("$\\mathcal{R}_0=1$"))),
     values = c("black"),
@@
   # faceting:
-  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
@@
     legend.title = element_text(size = 10),
-    legend.direction = "vertical",
+    legend.direction = "horizontal",
     legend.justification = "left",

### 2023-05-22 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
     title.position = "top", title.hjust = 0,
-    barheight = unit(5, "cm"),
+    barwidth = unit(5, "cm"),
     show.limits = TRUE

### 2023-05-22 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
     title.position = "top", title.hjust = 0,
-    barwidth = unit(5, "cm"),
+    barwidth = unit(7, "cm"),
     show.limits = TRUE

### 2023-05-22 manuscript-figures.Rmd
add vector trait TPC dataset

--- 2023-05-22 manuscript-figures.Rmd
@@
 
-data.in.transform <- read_rds(here::here("data/clean/TPC_param_samples.rds"))
-
 # Load in necessary functions and files ----------------------------------------
@@
 ```{r load-data, include=FALSE}
-# Run analysis scripts to obtain data for plotting -----------------------------
-
-# # Define temperature range of study
-# Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
-# 
-# # Thin sample size
-# thin_size <- 1000 # full = 1000, thin = 100
-# 
-# plot_bool = FALSE
-# source("code/trait-transform.R", local = TRUE)
-# # Host density vector: Number of values to include to consider for vertebrate host density
-# KH_vec_length <- 300 # full = 300, thin = 20
-# 
-# # Biting tolerance vector: Number of values to consider for biting tolerance
-# sigmaH_vec_length <- 300 # full = 300, thin = 20
-# 
-# # Get data for plotting thermal performance curves (data.Vec)
-# !!! save a specific dataset to use for plotting trait TPCs
-# source("code/trait-variation.R", local = TRUE)
-
-# Load output data -------------------------------------------------------------
-# These data are produced by the code in code/get-outputs.R
-
+# Load results data -------------------------------------------------------------
+# Vector trait TPC data
+data.Vec <- read_rds("results/VecTPC_vals.rds")
 # R0 data # !!! needs to be updated to include 1e-1, 1e0, 1e1

### 2023-05-22 code/get-outputs.R
update R0 values to cover a wider range of sigmah values

@@ -238,7 +238,7 @@ if (!exists("cluster")) {
 
 # Set up host trait data frame (for future visualization)
 data.R0 <- data.Host %>%
-  filter(sigmaH %in% c(100, Inf)) %>% 
+  filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>% 
   filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)])
 
 # Slice host trait data

### 2023-05-23 code/sensitivity.R
Update sensitivity.R

@@ -62,12 +62,12 @@ data.Topt <- read_rds("results/Topt_vals.rds")
 data.CT <- read_rds("results/CT_vals.rds")
 
 
-KH_vec_length <- 300 # full = 300, thin = 20
-
-# Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 300 # full = 300, thin = 20
-
-source("code/trait-variation.R")
+# KH_vec_length <- 300 # full = 300, thin = 20
+# 
+# # Biting tolerance vector: Number of values to consider for biting tolerance
+# sigmaH_vec_length <- 300 # full = 300, thin = 20
+# 
+# source("code/trait-variation.R")
 
 # 1) Define accessory functions -------------------------------------------
 
@@ -89,6 +89,8 @@ appender_KH <- function(string) {
 ###* Mean traits data frame ----
 
 # Get mean values of uncertain traits
+
+data.Vec <- read_rds("results/VecTPC_vals.rds")
 
 mean.Vec <- data.Vec %>% 
   select(-c(KL, mosquito_species, pathogen, muL, etaL)) %>% 
@@ -294,13 +296,13 @@ for (var_name in temp_vars) {
 }
 
 # Save R0 relative highest posterior density data
-write_rds(R0.HPD, "results/R0_HPD_sens.rds")
-# R0.HPD <- read_rds("results/R0_HPD_sens.rds")
+# write_rds(R0.HPD, "results/R0_HPD_sens.rds")
+R0.HPD <- read_rds("results/R0_HPD_sens.rds")
 
 ## Plot R0 uncertainty 
-plot_Temp_range <- R0.HPD %>% ungroup() %>% 
-  dplyr::filter(HPD_width > eps) %>% 
-  # dplyr::filter(KH == KH_select) %>% 
+plot_Temp_range <- R0.HPD %>% ungroup() %>%
+  dplyr::filter(HPD_width > eps) %>%
+  # dplyr::filter(KH == KH_select) %>%
   select(Temperature) %>% range()
 
 # var_name_table <- list(
@@ -339,7 +341,7 @@ R0.uncertainty.plot <- R0.HPD %>%
   dplyr::filter(KH %in% c(1, 100)) %>%
   dplyr::filter(rel_HPD_width < 1.01) %>%
   # arrange(system_ID, sigmaH, focal_var, Temperature) %>%
-  ggplot(aes(x = Temperature, y = rel_HPD_width, color = focal_var)) +
[…]

### 2023-05-23 manuscript-figures.Rmd
fixing figures

@@
 # Load results data -------------------------------------------------------------
+eps <- .Machine$double.eps
+
 # Vector trait TPC data
@@
       case_when(
-        x == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
-        x == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-        x == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-        x == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
-        x == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
+        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
+        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
+        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
+        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
       )
@@
     system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* & *P. falciparum*",
     system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+infinite_skew <- 10^2.35#10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^log10(max_sigmaH*1)
-
-# infinite_skew <- 10^2 + 150
+infinite_divide <- 10^2.7 #10^log10(max_sigmaH*1)
+
 Toptalt_df <- inf_skew_func(Toptalt_df, infinite_skew, infinite_divide, 8)
@@
 # Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), mean(c(infinite_divide, infinite_skew)), max(Toptalt_df$sigmaH_proxy))
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
 sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
@@
   geom_contour_filled(
-    data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.99),
+    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
     breaks = Topt_breaks
@@
   geom_contour_filled(
-    data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.02) %>% 
+    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>% 
       group_by(system_ID) %>% 
@@
   scale_fill_manual(
-    name = "Transmission\nthermal optimum (°C)",
+    name = "Transmission thermal optimum (°C)",
     values = met.brewer("Johnson",
@@
   scale_fill_viridis_d(
-    name = "Median parasite\nthermal tolerance\nrange width (°C)",
+    name = "Parasite thermal tolerance\nrange width (°C)",
     option = "plasma"

### 2023-05-23 code/get-outputs.R

@@ -373,6 +373,36 @@ if (exists("Topt_alt.df") & dim(Topt_alt.df)[1] == proper_dim)
 
 
 # 5) Calculate CTmin, CTmax, and CTwidth ----------------------------------
+# Set up new cluster
+# Close old cluster connections
+rm(cluster)
+gc()
+# Start new cluster for doParallel
+cluster_size <- parallel::detectCores()-1
+
+my.cluster <- parallel::makeCluster(
+  cluster_size, 
+  type = "PSOCK"
+)
+# Register cluster for doParallel
+doSNOW::registerDoSNOW(cl = my.cluster)
+
+# Set up iteration grid
+iter_grid <- expand_grid(system_ID = unique(data.Vec$system_ID),
+                         tibble(KH = data.Host$KH,
+                                sigmaH = data.Host$sigmaH))
+# Set up progress bar
+iterations <- dim(iter_grid)[1]
+
+pb <- progress_bar$new(
+  format = ":spin :system progress = :percent [:bar] :elapsed | eta: :eta",
+  total = iterations,
+  width = 120)                                                                                                         
+
+progress <- function(n){
+  pb$tick(tokens = list(system = iter_grid$system_ID[n]))
+}
+opts <- list(progress = progress)
 
 CT.df <- foreach(
   system_name = iter_grid$system_ID,

### 2023-05-23 code/main-analysis.R

@@ -53,7 +53,7 @@ source("code/get-thermal-trait-priors.R")
 # write_rds(data.in.transform, "data/clean/TPC_param_samples.rds")
 
 # # Run this to load pre-processed data set
-# data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
+data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
 
 # 3) Translate traits into model parameters -------------------------------
 

### 2023-05-25 manuscript-figures.Rmd
figure edits

@@
   mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
   )) %>%
@@
   mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
   ))
@@
 #   mutate(system_label = case_when(
-#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
-#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-#     system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
-#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
-#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* and DENV",
+#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+#     system_ID == "Aedes albopictus+DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *An. gambiae* and *P. falciparum*",
+#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
 #   ))
@@
   mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
   )) %>%
@@
   mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
   )) %>% 
@@
   # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
-  geom_contour(data = filter(data.CT, variable == "CTwidth"),
+  geom_contour(data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
                aes(y = sigmaH, z = mean, colour = "R0 = 1"), 
@@
 CTwidth_df <- data.CT %>%  
+  ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  )) %>% 
   filter(variable == "CTwidth") %>% 
+  # filter(sigmaH < 10^2.2) %>% 
   mutate(sigmaH_proxy = sigmaH) %>% 
@@
   # CTwidth for FINITE sigmaH:
-  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < infinite_divide**0.99)) +
+  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < 10^2.2)) +
   # CTwidth for INFINITE sigmaH:
-  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy > infinite_divide**1.01)) +
+  geom_contour_filled(data = filter(CTwidth_df, 
+                                    sigmaH_proxy > 10^2.4, 
+                                    sigmaH_proxy < infinite_divide)) +
   # x-axis: log10-scale with no buffer space

### 2023-05-26 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 
-<!-- ```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'} -->
-
-<!-- # Estimating the difference between Topt and Topt_RM numerically using our previous data -->
-<!-- Toptdiff_df1 <- ThermPathChars %>% -->
-<!--   select(system_ID, sigmaH, KH, Topt) %>% -->
-<!--   filter(is.finite(sigmaH)) %>% -->
-<!--   distinct() -->
-
-<!-- Toptdiff_df2 <- ThermPathChars %>% -->
-<!--   filter(is.infinite(sigmaH)) %>% -->
-<!--   select(system_ID, KH, Topt) %>% -->
-<!--   rename(Topt_RM = Topt) %>% -->
-<!--   distinct() -->
-
-<!-- Toptdiff_df <- left_join(Toptdiff_df1, Toptdiff_df2) %>% -->
-<!--   mutate(Toptdiff = Topt_RM - Topt) %>% -->
-<!--   mutate(absToptdiff = abs(Toptdiff)) %>% -->
-<!--   mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>% -->
-<!--   mutate(sigmaHKH = sigmaH * KH) %>% -->
-<!--   group_by(system_ID) %>% -->
-<!--   filter(absToptdiff == max(absToptdiff)) %>% -->
-<!--   select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>% -->
-<!--   distinct() -->
-
-<!-- # Calculating Topt0 using the "simplified" equation -->
-<!-- Topt0_df <- VecParms %>% -->
-<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
-<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
-<!--   filter(is.finite(proxy_0)) %>% -->
-<!--   select(system_ID, Temperature, proxy_0) %>% -->
-<!--   group_by(system_ID) -->
-
-<!-- Topt0_base_estimates <- Topt0_df %>% -->
-<!--   group_by(system_ID) %>% -->
-<!--   # Calculate Topt_0 -->
-<!--   filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>% -->
-<!--   rename(Topt_0 = Temperature) -->
-<!-- # check with above: Topt_0 matches with Topt when sigmaH*KH is minimized -->
-<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->
-
-<!-- # Calculating Topt0 using the "simplified" equation -->
-<!-- ToptRM_df <- VecParms %>% -->
-<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
-<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% -->
-<!--   select(system_ID, Temperature, proxy_RM) %>% -->
-<!--   group_by(system_ID) -->
-
-<!-- ToptRM_base_estimates <- ToptRM_df %>% -->
-<!--   group_by(system_ID) %>% -->
-<!--   # Calculate Topt_RM -->
-<!--   filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>% -->
-<!--   rename(Topt_RM = Temperature) -->
-<!-- # check with above: Topt_RM matches with Topt when sigmaH*KH is maximized -->
-<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->
-
-<!-- Topt_estimates <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>% -->
-<!--   select(system_ID, Topt_RM, Topt_0) %>% -->
-<!--   mutate(Topt_diff = Topt_RM - Topt_0) %>% -->
-<!--   mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM) -->
-
-<!-- # Investigating Topt_RM and Topt_0 further -->
-
-<!-- test_df <- VecParms %>% -->
-<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
-<!--   mutate(sigmaVV0 = sigmaV * V0) %>% -->
-<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
-<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0 -->
-<!--   filter(is.finite(proxy_0)) %>% -->
-<!--   select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0) -->
-<!-- ``` -->
+```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
+
+# Estimating the difference between Topt and Topt_RM numerically using our previous data
+Toptdiff_CCH <- data.Topt %>%
+  ungroup() %>% 
+  select(system_ID, sigmaH, KH, median) %>%
+  rename(Topt = median) %>%
+  filter(is.finite(sigmaH)) %>%
+  distinct()
+
+Toptdiff_RM <- data.Topt %>%
+  ungroup() %>% 
+  filter(is.infinite(sigmaH)) %>%
+  select(system_ID, KH, median) %>%
+  rename(Topt_RM = median) %>%
+  distinct()
+
+Toptdiff_df <- left_join(Toptdiff_CCH, Toptdiff_RM) %>%
+  mutate(Toptdiff = Topt_RM - Topt) %>%
+  mutate(absToptdiff = abs(Toptdiff)) %>%
+  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
+  mutate(sigmaHKH = sigmaH * KH) %>%
+  group_by(system_ID) %>%
+  filter(absToptdiff == max(absToptdiff)) %>%
+  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
+  distinct()
+
+# Calculating Topt0 using the "simplified" equation
+Topt0_df <- median.Vec %>%
+  filter(V0 > 1) %>% 
+  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(P_EIP = exp(-muV / etaV)) %>%
+  mutate(proxy_0 = lf * betaV * P_EIP / (KL * rhoL * (lf - 1 / (sigmaV_f * deltaL)))) %>%
+  select(system_ID, Temperature, proxy_0) %>%
+  group_by(system_ID)
+
+test_plot <- Topt0_df %>% 
+  ggplot(aes(x = Temperature, y = proxy_0)) +
+  geom_point() +
+  facet_wrap(~system_ID, scales = "free")
+test_plot
+
+Topt0_base_estimates <- Topt0_df %>%
+  group_by(system_ID) %>%
+  # Calculate Topt_0
+  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
+  rename(Topt_0 = Temperature)
+# check with above: Topt_0 matches with Topt when sigmaH*KH is minimized
+# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
+
+# Calculating Topt0 using the "simplified" equation
+ToptRM_df <- median.Vec %>%
+  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(P_EIP = exp(-muV / etaV)) %>%
+  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
+  select(system_ID, Temperature, proxy_RM) %>%
+  group_by(system_ID)
+
+ToptRM_base_estimates <- data.Topt %>%
+  group_by(system_ID) %>%
+  filter(is.infinite(sigmaH)) %>% 
+  select(system_ID, median) %>% 
+  rename(Topt_RM = median) %>% 
+  distinct()
+  # Calculate Topt_RM
+  # filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>%
+  # rename(Topt_RM = Temperature)
+# check with above: Topt_RM matches with Topt when sigmaH*KH is maximized
+# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
+
+Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
+  select(system_ID, Topt_RM, Topt_0) %>%
+  mutate(Topt_diff = Topt_RM - Topt_0) %>%
+  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
+
+# Investigating Topt_RM and Topt_0 further
+
+test_df <- median.Vec %>%
+  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(P_EIP = exp(-muV / etaV)) %>%
+  mutate(sigmaVV0 = sigmaV * V0) %>%
+  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
+  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0
+  filter(is.finite(proxy_0)) %>%
+  select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0)
+```

### 2023-06-02 manuscript-figures.Rmd
add sensitivity figures

@@
 ```
+
+```{r fig-SX_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum, critical thermal maximum, and thermal optimum vary with vertebrate host availability.'}
+all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%  
+  ungroup() %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+### Option 1: inline violin plots ----
+plot.densities_violin_inline <- ggplot() +
+  geom_violin(data = filter(all.density.df, variable == "Thermal optimum"),
+              aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
+  ) +
+  geom_violin(data = filter(all.density.df, variable == "Critical thermal minimum"),
+              aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
+  ) +
+  geom_violin(data = filter(all.density.df, variable == "Critical thermal maximum"),
+              aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0,0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = "",
+    breaks = c("CTmin", "Topt", "CTmax"),
+    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_violin_inline)
+
+### Option 2: inline box and whisker plots ----
+plot.densities_boxwhisker_inline <- ggplot() +
+  geom_boxplot(data = filter(all.density.df, variable == "Thermal optimum"),
+               aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
+  ) +
+  geom_boxplot(data = filter(all.density.df, variable == "Critical thermal minimum"),
+               aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
+  ) +
+  geom_boxplot(data = filter(all.density.df, variable == "Critical thermal maximum"),
+               aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0,0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = "",
+    breaks = c("CTmin", "Topt", "CTmax"),
+    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_boxwhisker_inline)
+
+### Option 3: stacked violin plots ----
+plot.densities_violin_stacked <- ggplot() +
+  geom_violin(data = all.density.df,
+              aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0,0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = ""
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_violin_stacked)
+
+### Option 4: stacked box and whisker plots ----
+plot.densities_boxwhisker_stacked <- ggplot() +
+  geom_boxplot(data = all.density.df,
+              aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0,0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = ""
+  ) +  
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_boxwhisker_stacked)
+
+```
+
+```{r fig-SX_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+
+R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%  
+  ungroup() %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+# Label functions: 
+appender_sigmaH <- function(string) {
+  unname(TeX(paste("$\\sigma_H = $", string)))}
+appender_KH <- function(string) {
+  unname(TeX(paste("$K_H = $", string)))}
+
+Temp_range_for_plot <- R0.HPD %>% 
+  ungroup() %>%
+  dplyr::filter(rel_HPD_width > eps) %>%
+  select(Temperature) %>% range()
+
+plot.R0.rel.sens <- R0.HPD %>% 
+  filter(KH %in% c(1,100) & sigmaH %in% c(50, Inf)) %>% 
+  filter(!(KH == 100 & sigmaH == Inf)) %>% 
+  filter(rel_HPD_width != 0) %>% 
+  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  group_by(system_ID, sigmaH, KH, Temperature) %>% 
+  mutate(sens_total = sum(rel_HPD_width)) %>% 
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  arrange(sens_rel) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels =  c("Vector competence", "Pr(larval survival)", 
+                "Parasite development rate", "Mortality rate", 
+                "Immature development rate", "Max. biting rate", 
+                "Eggs per female per day")
+  ) +
+  scale_x_continuous(
+    limits = Temp_range_for_plot,
+    expand = c(0,0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
+  ) +
+  facet_grid(cols = vars(system_label),
+             rows = vars(KH, sigmaH), 
+             labeller = labeller(
+               system_label = label_wrap_gen(width = 10),
+               sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+               KH = as_labeller(appender_KH, default = label_parsed)),
+             scales = "free_y") +
+  theme_minimal_hgrid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.R0.rel.sens
+# shift_legend(plot.R0.rel.sens)
+
+```
+
+```{r fig-SX_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+
+ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%  
+  ungroup() %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+## Plot R0 uncertainty 
+Temp_range_for_plot <- ddTR0.HPD %>% ungroup() %>% 
+  dplyr::filter(HPD_width > eps) %>% 
+  select(Temperature) %>%  range()
+
+var_name_table <- list(
+  betaV = c(TeX("$\\beta_V$")),
+  deltaL = c(TeX("$\\delta_L$")),
+  etaV = c(TeX("$\\eta_V$")),
+  muV = c(TeX("$\\mu_V$")),
+  rhoL = c(TeX("$\\rho_L$")),
+  sigmaV = c(TeX("$\\sigma_V$")),
+  sigmaV_f = c(TeX("$\\sigma_v f$"))
+)
+
+plot.ddTR0.rel.sens <- ddTR0.HPD %>% 
+  filter(KH %in% c(1,100) & sigmaH %in% c(50, Inf)) %>% 
+  filter(!(KH == 100 & sigmaH == Inf)) %>% 
+  filter(rel_HPD_width != 0) %>% 
+  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  group_by(system_ID, sigmaH, KH, Temperature) %>% 
+  mutate(sens_total = sum(rel_HPD_width)) %>% 
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  arrange(sens_rel) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels =  c("Vector competence", "Pr(larval survival)", 
+                "Parasite development rate", "Mortality rate", 
+                "Immature development rate", "Max. biting rate", 
+                "Eggs per female per day")
+  ) +
+  scale_x_continuous(
+    limits = Temp_range_for_plot,
+    expand = c(0,0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $\\frac{d}{dT}R_0$ HPD width"))
+  ) +
+  facet_grid(cols = vars(system_label),
+             rows = vars(KH, sigmaH), 
+             labeller = labeller(
+               system_label = label_wrap_gen(width = 10),
+               sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+               KH = as_labeller(appender_KH, default = label_parsed)),
+             scales = "free_y") +
+  theme_minimal_hgrid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.ddTR0.rel.sens
+
+```
+```{r fig-SX_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%  
+  ungroup() %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  )) %>%
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>% 
+  mutate(sens_total = sum(rel_HPD_width)) %>% 
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) #%>% 
+  # arrange(sens_rel)
+
+# !!! mention the value of sigmaH
+
+plot.Topt.rel.sens <- Topt.HPD %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels =  c("Vector competence", "Pr(larval survival)", 
+                "Parasite development rate", "Mortality rate", 
+                "Immature development rate", "Max. biting rate", 
+                "Eggs per female per day")
+  )  +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
+  ) +
+  # scale_y_continuous(
+  #   limits = c(0,1)
+  # ) +
+  facet_wrap(~system_label, scales = "free") +
+  theme_minimal_hgrid(16) +
+    theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.Topt.rel.sens)
+
+```

### 2023-06-02 code/sensitivity.R

@@ -1512,6 +1512,8 @@ all.density.df$variable <- factor(all.density.df$variable,
 all.density.df$sigmaH <- factor(all.density.df$sigmaH, 
                                 levels = c(100, Inf))
 
+write_rds(all.density.df, "results/CTminmaxTopt_densities.rds")
+
 # !!! [] clean up code
 # !!! [] make y label nice
 # !!! [] make system labels nice (decrease font size)

### 2023-06-02 manuscript-figures.Rmd
clean up manuscript figures (up to trait TPC plot)

--- 2023-05-26 manuscript-figures.Rmd
@@
 library(tidyverse)
-library(latex2exp) #nec
-library(reshape2) #nec
-library(cowplot) #nec
-library(viridis) #nec
-library(RColorBrewer) #nec
-library(MetBrewer) #nec
+library(latex2exp)
+library(reshape2)
+library(cowplot)
+library(viridis)
+library(RColorBrewer)
+library(MetBrewer)
 library(here)
-library(lemon)  #nec
+library(lemon)
 library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure
 
-# Tell R where the manuscript lives
-# here::i_am("manuscript-figures.Rmd")
-
-# Load in necessary functions and files ----------------------------------------
-# Functions for computing equilibrium quantities:
-#  mosquito abundance (compute.V0), basic reproduction number (compute.R0)
-# source("code/output-functions.R")
-
-# Helper function: add a "point at infinity" for plotting when sigmaH is infinite
+# Plot settings ----
+
+# !!! [] make sure all plots have font size set at 11 max, unless necessary
+
+# Set theme
+theme_set(theme_minimal(11))
+
+# Helper function: adds a "point at infinity" for plots with infinite sigmaH
 inf_skew_func <- function(df, skew, divide, n_rows_to_add) {
-  # Get the largest value of log10(sigmaH)
+  # Get the largest value of log10(sigmaH) in the data frame
   max_log10sigmaH <- filter(df, is.finite(sigmaH)) %>%
@@
 
-  # Used to create a gap dividing finite and infinite sigmaH
+  # Define the gap dividing finite and infinite sigmaH
   infinite_divide <- 10^mean(log10(c(divide, skew)))
 
-  # Create a proxy sigmaH variable that replaces Inf with skew
+  # Create a proxy sigmaH variable that replaces Inf with the value of "skew"
   df <- mutate(df, sigmaH_proxy = ifelse(is.finite(sigmaH),
@@
 
+  # add more proxy sigmaH values to make a "spread" at Inf
   added_sigma_vals <- seq(divide, skew, length.out = n_rows_to_add)
-
   for (i in 1:n_rows_to_add) {
-    bump_val <- 1+0.05*(i-1)
+    bump_val <- 1 + 0.05 * (i - 1)
     temp <- filter(df, is.infinite(sigmaH)) %>%
       mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
-                                   added_sigma_vals[i]))
-
+        added_sigma_vals[i]
+      ))
     df <- add_row(df, temp) %>% distinct()
   }
-
   return(df)
-
 }
 
-# Plot settings ----
-
-# Set theme
-theme_set(theme_minimal(11))
-
-# Helper function to place legends in empty facets of plot grids
+# Helper function: place legends in empty facets of plot grids
 # Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
@@
 
-```
-
-```{r load-data, include=FALSE}
-# Load results data -------------------------------------------------------------
+# Helper function: apply nice labels for pathosystems
+pathosystem_labeller <- function(df) {
+  df <- df %>%
+    ungroup() %>%
+    mutate(system_label = case_when(
+      system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+      system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+      system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+      system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+      system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+    ))
+  return(df)
+}
+
+# Load required data ----
+
+# !!! [] make sure all data is getting loaded here
+
 eps <- .Machine$double.eps
@@
 # Vector trait TPC data
-data.Vec <- read_rds("results/VecTPC_vals.rds")
-# R0 data # !!! needs to be updated to include 1e-1, 1e0, 1e1
-data.R0 <- read_rds("results/R0_vals.rds")
+data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
+  #
+  pathosystem_labeller()
+# R0 data
+# !!! [] needs to be updated to include 1e-1, 1e0, 1e1
+data.R0 <- read_rds("results/R0_vals.rds") %>%
+  pathosystem_labeller()
 # Topt data
-data.Topt <- read_rds("results/Topt_vals.rds")
+data.Topt <- read_rds("results/Topt_vals.rds") %>%
+  pathosystem_labeller()
 # Critical thermal extrema data
-data.CT <- read_rds("results/CT_vals.rds")
-
-# Configure data sets for plotting ---------------------------------------------
-
-## Get mean values of vector traits across samples
+data.CT <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller()
+
+# Configure data sets for plotting ----
+
+## Get values of vector traits across samples
+# Mean values
 mean.Vec <- data.Vec %>%
@@
   mutate(etaL = rhoL / (deltaL + eps)) %>%
-  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
   mutate(muL = etaL - rhoL) %>%
-  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
+  mutate(V0 = ifelse(sigmaV_f * deltaL < (1 / lf),
     0,
-                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))
-
+    KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))
+  ))
+# Median values (this one is used more frequently)
 median.Vec <- data.Vec %>%
@@
   mutate(muL = etaL - rhoL) %>%
-  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
+  mutate(V0 = ifelse(sigmaV_f * deltaL < (1 / lf),
     0,
-                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))
-
-## Compute mosquito thermal tolerance range (minimum and maximum)
-MosqThermRange_df <- mean.Vec %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
+    KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))
+  ))
+
+# Compute *mosquito* thermal tolerance range (minimum and maximum)
+MosqThermRange_df <- median.Vec %>%
+  pathosystem_labeller() %>%
   group_by(system_label) %>%
@@
   distinct()
-
-# Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
-data.R0 <- data.R0 %>%
-  ungroup() %>% 
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  ))
-
-# ## Add a "point at infinity" for sigmaH
-# # Value of sigmaH to replace 'Inf' with for plotting
-# infinite_skew <- 10^3 + 2500
-# 
-# # Get the largest value of log10(sigmaH)
-# max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
-#   select(sigmaH) %>%
-#   max() %>%
-#   log10()
-# 
-# # Used to create a gap dividing finite and infinite sigmaH
-# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-# 
-# # add a second proxy sigmaH point at infinity to make the values easier to see there
-# temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
-#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
-# AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
-#                                                        sigmaH, infinite_skew
-# ))
-# AllOutputs <- add_row(AllOutputs, temp) %>% distinct()
-# 
-# # Define sigmaH tick breaks and labels
-# sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
-# sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-# 
-# ## Parasite thermal characteristics
-# ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)
-# 
-# # Title names for each mosquito+pathogen combination
-# ThermPathChars <- ThermPathChars %>%
-#   mutate(system_label = case_when(
-#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* and DENV",
-#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-#     system_ID == "Aedes albopictus+DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *An. gambiae* and *P. falciparum*",
-#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-#   ))
-# ## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
-# # Value of sigmaH to replace 'Inf' with for plotting
-# infinite_skew <- 10^3 + 2500
-# 
-# # Get the largest value of log10(sigmaH)
-# max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
-#   select(sigmaH) %>%
-#   max() %>%
-#   log10()
-# 
-# # Used to create a gap dividing finite and infinite sigmaH
-# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
-# 
-# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
-# ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
-#                                                                sigmaH, infinite_skew
-# ))
-# # add a second proxy sigmaH point at infinity to make the values easier to see there
-# temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
-#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-# 
-# ThermPathChars <- add_row(ThermPathChars, temp) %>%
-#   arrange(sigmaH_proxy) %>%
-#   distinct()
-# 
-# ## Options
-# # Define sigmaH tick breaks and labels
-# sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
-# sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
 ```
@@
 ```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}
-
 # resolution setting
@@
 
-## Define different contact models
+## Define the contact models
 # For each model, there is a vector-to-host and host-to-vector term
@@
   ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
-
   # curves:
@@
   geom_blank(aes(y = y_max)) +
-
   # plot labels
@@
   ) +
-
   # x-axis:
@@
 
+# Combine plots into a grid and remove legends
 contact_plot <- plot_grid(
@@
 
+# Set legend to bottom of grid
 legend <- get_legend(
@@
 
+# Put together grid and legend
 contact_plot <- plot_grid(contact_plot, legend, ncol = 1, rel_heights = c(1, .05))
 
+# Plot
 contact_plot
@@
 ```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model.
-'}
-
+The range of temperatures is restricted to values where the immature development rate is positive.
+For traits that do not involve a parasite, *Aedes aegypti* with DENV and *Ae.
+aegypti* with ZIKV curves overlap.'}
 ## Set up plot dataframe
 MosqThermTraits_df <- median.Vec %>%
-  ## Set up plot dataframe
   # Mortality rate
-  mutate(muV = 1/lf) %>% 
+  mutate(muV = 1 / lf) %>%
   # Recruitment rate
@@
   mutate(P_EIP = exp(-muV / etaV)) %>%
+  # Prob. of larval survival
   # Select relevant traits and parameters
-  select(
-    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
-  ) %>%
-  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
-  # 'variables'
+  select(Temperature, system_ID, sigmaV, sigmaV_f, rhoL, lf, deltaL, P_EIP, betaV) %>%
+  # select(Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP) %>%
+  # Turn all columns except Temperature and system_ID into variables
   melt(id = c("Temperature", "system_ID")) %>%
+  mutate(variable = factor(variable,
+    levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "P_EIP", "betaV"),
+    labels = c(
+      TeX("(a) Adult lifespan: $1/\\mu_V$ (days)"),
+      TeX("(b) Biting frequency: $\\sigma_V$ (day$^{-1}$)"),
+      TeX("(c) Eggs per female per day: $\\sigma_V f$"),
+      TeX("(d) Immature development rate: $\\rho_L$"),
+      TeX("(e) Prob. of immature survival: $\\delta_L$"),
+      TeX("(f) Prob. of surviving EIP: $\\theta_V$"),
+      TeX("(g) Vector competence: $\\beta_V$")
+    )
+  )) %>%
   group_by(Temperature, system_ID)
 
-# Assign nice labels for each variable
-levels(MosqThermTraits_df$variable) <- c(
-  lambdaV = TeX("(a) Recruitment rate: $\\lambda_V$ (ind. day$^{-1}$)"),
-  sigmaV = TeX("(b) Maximum biting frequency: $\\sigma_V$ (day$^{-1}$)"),
-  betaV = TeX("(c) Vector competence: $\\beta_V$"),
-  lf = TeX("(d) Average adult lifespan: $1/\\mu_V$ (days)"),
-  P_EIP = TeX("(e) Prob. of surviving EIP: $\\theta_V$")
-)
+# !!! [] be sure to use a consistent order for mosquito life history traits
+# !!! [] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
 
@@
   ggplot(mapping = aes(x = Temperature, y = value, group = system_ID)) +
-
   # Plot trait values:
   geom_line(aes(colour = system_ID), size = 1) +
-
   # x-axis:
@@
   ) +
-
   # y-axis:
   scale_y_continuous(expand = c(0.05, 0)) +
-
   # color:
@@
   ) +
-
   # faceting:
-  facet_wrap(~variable, nrow = 3, scales = "free", labeller = labeller(variable = label_parsed)) +
-
+  facet_wrap(~variable,
+    nrow = 3, scales = "free",
+    labeller = labeller(variable = label_parsed)
+  ) +
   # legend:
   guides(color = guide_legend(override.aes = list(size = 4))) +
-
   # theme options:
@@
 ```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}
-
 # Plot R0 vs. temperature curves. One plot for each mosquito+pathogen pair.
@@
 R0_plot <- shift_legend(R0_plot)
-
 ```
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35#10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7 #10^log10(max_sigmaH*1)
+infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
 
@@
 
-min_Topt <- floor(min(min(Toptalt_df$mean),min(Toptalt_df$median)))
-max_Topt <- ceiling(max(max(Toptalt_df$mean),max(Toptalt_df$median)))
+min_Topt <- floor(min(min(Toptalt_df$mean), min(Toptalt_df$median)))
+max_Topt <- ceiling(max(max(Toptalt_df$mean), max(Toptalt_df$median)))
 Topt_breaks <- seq(min_Topt, max_Topt, by = 1)
@@
   # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
-  geom_contour(data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
+  geom_contour(
+    data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
     aes(y = sigmaH, z = mean, colour = "R0 = 1"),
     breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
-               size = 1) +
+    size = 1
+  ) +
   # geom_contour(data = data.R0_norm,
@@
 Toptalt_plots <- shift_legend(Toptalt_plots)
-
 ```
@@
   # CTwidth for INFINITE sigmaH:
-  geom_contour_filled(data = filter(CTwidth_df, 
+  geom_contour_filled(data = filter(
+    CTwidth_df,
     sigmaH_proxy > 10^2.4,
-                                    sigmaH_proxy < infinite_divide)) +
+    sigmaH_proxy < infinite_divide
+  )) +
   # x-axis: log10-scale with no buffer space
@@
 CTWidth_heat_plots <- shift_legend(CTWidth_heat_plots)
-
 ```
@@
 ```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
-
 # Estimating the difference between Topt and Topt_RM numerically using our previous data
@@
   filter(V0 > 1) %>%
-  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(muV = 1 / (lf + eps)) %>%
   mutate(P_EIP = exp(-muV / etaV)) %>%
@@
 ToptRM_df <- median.Vec %>%
-  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(muV = 1 / (lf + eps)) %>%
   mutate(P_EIP = exp(-muV / etaV)) %>%
@@
 test_df <- median.Vec %>%
-  mutate(muV = 1/(lf + eps)) %>% 
+  mutate(muV = 1 / (lf + eps)) %>%
   mutate(P_EIP = exp(-muV / etaV)) %>%
@@
 ```
+
+```{r fig-SX_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum, critical thermal maximum, and thermal optimum vary with vertebrate host availability.'}
+all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%
+  ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+### Option 1: inline violin plots ----
+plot.densities_violin_inline <- ggplot() +
+  geom_violin(
+    data = filter(all.density.df, variable == "Thermal optimum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
+  ) +
+  geom_violin(
+    data = filter(all.density.df, variable == "Critical thermal minimum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
+  ) +
+  geom_violin(
+    data = filter(all.density.df, variable == "Critical thermal maximum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = "",
+    breaks = c("CTmin", "Topt", "CTmax"),
+    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_violin_inline)
+
+### Option 2: inline box and whisker plots ----
+plot.densities_boxwhisker_inline <- ggplot() +
+  geom_boxplot(
+    data = filter(all.density.df, variable == "Thermal optimum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
+  ) +
+  geom_boxplot(
+    data = filter(all.density.df, variable == "Critical thermal minimum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
+  ) +
+  geom_boxplot(
+    data = filter(all.density.df, variable == "Critical thermal maximum"),
+    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = "",
+    breaks = c("CTmin", "Topt", "CTmax"),
+    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_boxwhisker_inline)
+
+### Option 3: stacked violin plots ----
+plot.densities_violin_stacked <- ggplot() +
+  geom_violin(
+    data = all.density.df,
+    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = ""
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_violin_stacked)
+
+### Option 4: stacked box and whisker plots ----
+plot.densities_boxwhisker_stacked <- ggplot() +
+  geom_boxplot(
+    data = all.density.df,
+    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
+  ) +
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0)
+  ) +
+  scale_y_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = ""
+  ) +
+  facet_wrap(~system_label, labeller = labeller()) +
+  theme_minimal_grid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.densities_boxwhisker_stacked)
+```
+
+```{r fig-SX_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
+  ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+# Label functions:
+appender_sigmaH <- function(string) {
+  unname(TeX(paste("$\\sigma_H = $", string)))
+}
+appender_KH <- function(string) {
+  unname(TeX(paste("$K_H = $", string)))
+}
+
+Temp_range_for_plot <- R0.HPD %>%
+  ungroup() %>%
+  dplyr::filter(rel_HPD_width > eps) %>%
+  select(Temperature) %>%
+  range()
+
+plot.R0.rel.sens <- R0.HPD %>%
+  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
+  filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(rel_HPD_width != 0) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  group_by(system_ID, sigmaH, KH, Temperature) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>%
+  arrange(sens_rel) %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels = c(
+      "Vector competence", "Pr(larval survival)",
+      "Parasite development rate", "Mortality rate",
+      "Immature development rate", "Max. biting rate",
+      "Eggs per female per day"
+    )
+  ) +
+  scale_x_continuous(
+    limits = Temp_range_for_plot,
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
+  ) +
+  facet_grid(
+    cols = vars(system_label),
+    rows = vars(KH, sigmaH),
+    labeller = labeller(
+      system_label = label_wrap_gen(width = 10),
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free_y"
+  ) +
+  theme_minimal_hgrid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.R0.rel.sens
+# shift_legend(plot.R0.rel.sens)
+```
+
+```{r fig-SX_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
+  ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  ))
+
+## Plot R0 uncertainty
+Temp_range_for_plot <- ddTR0.HPD %>%
+  ungroup() %>%
+  dplyr::filter(HPD_width > eps) %>%
+  select(Temperature) %>%
+  range()
+
+var_name_table <- list(
+  betaV = c(TeX("$\\beta_V$")),
+  deltaL = c(TeX("$\\delta_L$")),
+  etaV = c(TeX("$\\eta_V$")),
+  muV = c(TeX("$\\mu_V$")),
+  rhoL = c(TeX("$\\rho_L$")),
+  sigmaV = c(TeX("$\\sigma_V$")),
+  sigmaV_f = c(TeX("$\\sigma_v f$"))
+)
+
+plot.ddTR0.rel.sens <- ddTR0.HPD %>%
+  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
+  filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(rel_HPD_width != 0) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  group_by(system_ID, sigmaH, KH, Temperature) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>%
+  arrange(sens_rel) %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels = c(
+      "Vector competence", "Pr(larval survival)",
+      "Parasite development rate", "Mortality rate",
+      "Immature development rate", "Max. biting rate",
+      "Eggs per female per day"
+    )
+  ) +
+  scale_x_continuous(
+    limits = Temp_range_for_plot,
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $dR_0/dT$ HPD width"))
+  ) +
+  facet_grid(
+    cols = vars(system_label),
+    rows = vars(KH, sigmaH),
+    labeller = labeller(
+      system_label = label_wrap_gen(width = 10),
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free_y"
+  ) +
+  theme_minimal_hgrid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.ddTR0.rel.sens
+```
+```{r fig-SX_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
+  ungroup() %>%
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  )) %>%
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
+# arrange(sens_rel)
+
+# !!! mention the value of sigmaH
+
+plot.Topt.rel.sens <- Topt.HPD %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels = c(
+      "Vector competence", "Pr(larval survival)",
+      "Parasite development rate", "Mortality rate",
+      "Immature development rate", "Max. biting rate",
+      "Eggs per female per day"
+    )
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
+  ) +
+  # scale_y_continuous(
+  #   limits = c(0,1)
+  # ) +
+  facet_wrap(~system_label, scales = "free") +
+  theme_minimal_hgrid(16) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.Topt.rel.sens)
+```

### 2023-06-03 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 
-# !!! [] be sure to use a consistent order for mosquito life history traits
-# !!! [] be sure to use a consistent list of mosquito life history traits:
-#         - adult lifespan (1/mu_V)
-#         - biting frequency (sigma_V)
-#         - eggs per female per day (sigma_V * f)
-#         - immature development rate
-#         - Pr(larval survival) (deltaL)
-#         - Pr(surviving EIP) (theta_V)
-#         - vector competence (beta_V)
-
 MosqThermTraits_plot <- MosqThermTraits_df %>%
@@
     expand = c(0, 0),
-    limits = c(10, 35),
-    breaks = seq(10, 36, 2)
+    limits = c(10, 40),
+    breaks = seq(10, 40, 2)
   ) +
@@
 ```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}
-# Plot R0 vs. temperature curves. One plot for each mosquito+pathogen pair.
-# One curve for Ross-Macdonald, a few for Chitnis
+# Plot R0 vs. temperature curves. One plot for each pathosysten
+# One curve for Ross-Macdonald and a few illustrative examples for Chitnis
 
@@
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
+  pathosystem_labeller() %>% 
   filter(KH %in% newKH_vals) %>%
@@
   scale_x_continuous(
-    name = "Temperature (°C)",
+    name = "Temperature (C)",
     expand = c(0, 0),
@@
 # Plot
-R0_plot <- shift_legend(R0_plot)
+shift_legend(R0_plot)
 ```
@@
 ```{r fig-SX_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+
+# !!! [x] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
@@
 ```{r fig-SX_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+
+# !!! [x] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
@@
 ```
+
 ```{r fig-SX_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+# !!! [x] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%

### 2023-06-05 manuscript-figures.Rmd
update supplementary figures

--- 2023-06-02 manuscript-figures.Rmd
@@
 data.R0_norm <- data.R0 %>%
-  ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
   filter(KH %in% newKH_vals) %>%
@@
 Toptalt_df <- data.Topt %>%
-  ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
-  distinct() %>%
   # Arrange along the plotting variables
-  arrange(system_ID, sigmaH, KH, mean) %>%
+  arrange(system_ID, sigmaH, KH, median) %>%
   mutate(sigmaH_proxy = sigmaH)
@@
 
-# Plot mean of Topt heat map
+# Plot median of Topt heat map
 Toptalt_plots <- Toptalt_df %>%
@@
   # Topt for INFINITE sigmaH:
-  # take mean of mean to hide variation from artifacts of uncertainty
+  # take median of median to hide variation from artifacts of uncertainty
   geom_contour_filled(
@@
       group_by(system_ID) %>%
-      mutate(mean = mean(mean), .groups = "keep"),
+      mutate(median = median(median), .groups = "keep"),
     size = 1,
@@
     data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
-    aes(y = sigmaH, z = mean, colour = "R0 = 1"),
-    breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
+    aes(y = sigmaH, z = median, colour = "R0 = 1"),
+    breaks = min(filter(data.CT, variable == "CTwidth", median > 0)$median),
     size = 1
@@
   # geom_contour(data = data.R0_norm,
-  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
+  #              aes(y = sigmaH, z = median, colour = "R0=1"), breaks = c(1), size = 1) +
   # x-axis: log10-scale with no buffer space
@@
 CTwidth_df <- data.CT %>%
-  ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
   filter(variable == "CTwidth") %>%
@@
   # y = vertebrate host population density,
-  # color = width of parasite thermal mean_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
+  # color = width of parasite thermal median_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
   # CTwidth for FINITE sigmaH:
@@
 
-<!-- # Supplementary Figures -->
-
-<!-- ```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'} -->
-<!-- # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density. -->
-
-<!-- # x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity") -->
-<!-- # y = Temperature -->
-<!-- # color = R0 -->
-<!-- # curves: -->
-<!-- #   R0 = 1 contour (black curve) -->
-<!-- #   Topt (red curve) -->
-
-<!-- # Facets: -->
-<!-- # Rows = levels of vertebrate host population density -->
-<!-- # Columns = two MBPT systems -->
-<!-- # Total = 6 plots -->
-
-<!-- ## Set up plot data frame -->
-<!-- # We re-create the output data frame so that we can vary sigmaH correctly. -->
-<!-- # We also drop the resolution of KH down to just three values -->
-<!-- # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald" -->
-
-<!-- ## Configure data frame for plotting -->
-<!-- R0_df <- data.R0 %>% -->
-<!--   select(system_ID, system_label, Temperature, sigmaH, KH, median) %>% -->
-<!--   rename(R0 = median) %>%  -->
-<!--   # Consider only 3 values of KH (on a log10-scale) -->
-<!--   filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1 -->
-<!--   # Choose a limited range of sigmaH values -->
-<!--   filter(sigmaH > 10^0.5) %>% -->
-<!--   # Group by plotting variables -->
-<!--   group_by(system_ID, KH, sigmaH) %>% -->
-<!--   # Calculate Topt (which.max requires grouping) -->
-<!--   mutate(Topt = `Temperature`[which.max(R0)]) %>% -->
-<!--   as_tibble() %>% -->
-<!--   arrange(system_ID, sigmaH, Temperature) -->
-
-<!-- ## Add a "point at infinity" for sigmaH -->
-<!-- # Value of sigmaH to replace 'Inf' with for plotting -->
-<!-- infinite_skew <- 10^3 + 2500 -->
-
-<!-- # Get the largest value of log10(sigmaH) -->
-<!-- max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>% -->
-<!--   select(sigmaH) %>% -->
-<!--   max() %>% -->
-<!--   log10() -->
-
-<!-- # Used to create a gap dividing finite and infinite sigmaH -->
-<!-- infinite_divide <- 10^mean(c(3, log10(infinite_skew))) -->
-
-<!-- # add a second proxy sigmaH point at infinity to make the values easier to see there -->
-<!-- temp <- filter(R0_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide)) -->
-<!-- # Create a proxy sigmaH variable that replaces Inf with infinite_skew -->
-<!-- R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH), -->
-<!--                                              sigmaH, infinite_skew -->
-<!-- )) -->
-<!-- R0_df <- add_row(R0_df, temp) %>% distinct() -->
-
-<!-- ## Compute mosquito thermal tolerance range (minimum and maximum) -->
-<!-- temp_MosqThermRange_df <- MosqThermRange_df %>% -->
-<!--   select(system_label, CTmin_V0, CTmax_V0) -->
-
-<!-- ## PLOTTING ## -->
-
-<!-- ## Options -->
-<!-- # Define sigmaH tick breaks and labels -->
-<!-- sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew) -->
-<!-- sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$")) -->
-
-<!-- # Labels for facet rows -->
-<!-- R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10)) -->
-<!-- mylabels <- as_labeller(c( -->
-<!--   `0.1` = "0.1 vertebrate hosts / ha", -->
-<!--   `1` = "1 vertebrate host / ha", -->
-<!--   `10` = "10 vertebrate hosts / ha" -->
-<!-- )) -->
-
-<!-- # Breaks used to decide fill for the heat map -->
-<!-- fill_breaks <- c(1, seq(5, 20, by = 5), Inf) -->
-
-<!-- # Define colors for heat map so that values of R0>1 go from yellow to red -->
-<!-- my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd")))) -->
-
-<!-- ## PLOT ## -->
-<!-- R0_plot <- R0_df %>% -->
-<!--   ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) + -->
-
-<!--   # Mosquito thermal tolerance range lines -->
-<!--   geom_hline( -->
-<!--     data = temp_MosqThermRange_df, -->
-<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-<!--   geom_hline( -->
-<!--     data = temp_MosqThermRange_df, -->
-<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-
-<!--   # R0 contours for FINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98), -->
-<!--     breaks = fill_breaks -->
-<!--   ) + -->
-
-<!--   # R0 contours for INFINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02), -->
-<!--     breaks = fill_breaks -->
-<!--   ) + -->
-
-<!--   # R0 = 1 contour: -->
-<!--   geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) + -->
-
-<!--   # Topt curve: -->
-<!--   geom_line( -->
-<!--     # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one -->
-<!--     mapping = aes( -->
-<!--       x = sigmaH_proxy, -->
-<!--       y = Topt, -->
-<!--       colour = "Topt" -->
-<!--     ), -->
-<!--     lwd = 1, -->
-<!--     linetype = 1 -->
-<!--   ) + -->
-
-<!--   # white lines breaking up finite/infinite sigmaH values -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 0.85 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 1.2 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-
-<!--   # x-axis: -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
-<!--     breaks = sigmaH_breaks, -->
-<!--     labels = sigmaH_labels, -->
-<!--     expand = c(0, 0) -->
-<!--   ) + -->
-
-<!--   # y-axis: -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Temperature "(degree * C)), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(14, 36), -->
-<!--     breaks = seq(10, 36, by = 2) -->
-<!--   ) + -->
-
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "", -->
-<!--     labels = c( -->
-<!--       "R0=1" = unname(TeX("$R_0=1$")), -->
-<!--       "Topt" = "Transmission\nthermal\noptimum", -->
-<!--       "VTTR" = "Mosquito\nthermal\ntolerance\nlimit" -->
-<!--     ), -->
-<!--     values = c("black", "purple", "grey"), -->
-<!--     guide = guide_legend( -->
-<!--       order = 1, -->
-<!--       keyheight = unit(2, "cm"), -->
-<!--       override.aes = list(size = 6) -->
-<!--     ) -->
-<!--   ) + -->
-
-<!--   # fill: -->
-<!--   scale_fill_manual( -->
-<!--     name = TeX("$R_0$"), -->
-<!--     values = my.cols, -->
-<!--     guide = guide_colorsteps( -->
-<!--       order = 2, -->
-<!--       breaks = fill_breaks, -->
-<!--       barheight = unit(8, "cm") -->
-<!--     ) -->
-<!--   ) + -->
-
-<!--   # faceting: -->
-<!--   facet_rep_grid( -->
-<!--     rows = vars(system_label), -->
-<!--     cols = vars(KH), -->
-<!--     scales = "free_y", -->
-<!--     labeller = labeller(.cols = mylabels), -->
-<!--     repeat.tick.labels = "left" -->
-<!--   ) + -->
-
-<!--   # theme options: -->
-<!--   theme_minimal_hgrid(11) + -->
-<!--   theme( -->
-<!--     axis.line = element_line(), -->
-<!--     panel.spacing = unit(1, "lines"), -->
-<!--     legend.text = element_text(size = 11), -->
-<!--     legend.text.align = 0, -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 8, -->
-<!--       hjust = 0 -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot it -->
-<!-- R0_plot -->
-<!-- ``` -->
-
-<!-- ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'} -->
-<!-- Topt_df <- data.Topt %>%  -->
-<!--   pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
-<!--               names_from = variable, -->
-<!--               values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%  -->
-<!--   right_join(read_rds("results/CT_vals.rds") %>%  -->
-<!--                filter(variable == "CTwidth") %>%  -->
-<!--                pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
-<!--                            names_from = "variable", -->
-<!--                            values_from = c("mean", "median", "lowHCI", "highHCI"))) %>%  -->
-<!--   filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
-<!--   # filter(mean_CTwidth>0) %>%  -->
-<!--   select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>% -->
-<!--   rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,  -->
-<!--          highHCI = highHCI_Topt) %>%  -->
-<!--   # filter(KH > 0.01) %>% -->
-<!--   # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>% -->
-<!--   group_by(KH) %>% -->
-<!--   # Arrange along the plotting variables -->
-<!--   arrange(system_ID, KH, mean) %>% -->
-<!--   arrange(sigmaH) %>% -->
-<!--   ungroup() -->
-
-<!-- # PLOTTING -->
-<!-- Topt_plot <- Topt_df %>% -->
-<!--   ## Set up plot ## -->
-<!--   # color = sigmaH -->
-<!--   ggplot(aes(x = KH, colour = as.factor(sigmaH))) + -->
-<!--   # Topt curves: -->
-<!--   geom_path(aes(y = median), lwd = 1) + -->
-<!--   # # Add dotted lines showing 89% HCI limits -->
-<!--   # geom_path(aes(y = lowHCI), linetype = "dashed") + -->
-<!--   # geom_path(aes(y = highHCI), linetype = "dashed") + -->
-<!--   # x-axis: log10 scale, no buffer space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(0.01, 2E4), -->
-<!--     breaks = 10^seq(-2, 4), -->
-<!--     labels = TeX(c( -->
-<!--       "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$" -->
-<!--     )) -->
-<!--   ) + -->
-<!--   # y-axis -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Thermal optimum "(degree * C)), -->
-<!--     expand = c(0.05, 0.05), -->
-<!--     limits = c(21,30.5), # mean: 21-31, median: 21-32 -->
-<!--     breaks = seq(21,32, by = 1) -->
-<!--   ) + -->
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
-<!--     values = c(met.brewer("VanGogh3", 4, direction = 1), "black"), -->
-<!--     # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"), -->
-<!--     breaks = c(1, 10, 100, Inf), -->
-<!--     labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
-<!--   ) + -->
-<!--   scale_fill_manual( -->
-<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
-<!--     values = c(met.brewer("VanGogh3", 4, direction = 1), "black"), -->
-<!--     # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"), -->
-<!--     breaks = c(1, 10, 100, Inf), -->
-<!--     labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
-<!--   ) + -->
-<!--   # faceting: -->
-<!--   facet_wrap(~system_ID, nrow = 2, labeller = labeller()) + -->
-<!--   # theme options: -->
-<!--   theme_minimal(16) + -->
-<!--   guides(color = guide_legend(override.aes = list(size = 4))) + -->
-<!--   theme( -->
-<!--     legend.position = "bottom", -->
-<!--     legend.margin = margin(), -->
-<!--     legend.direction = "vertical", -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     legend.text = element_text( -->
-<!--       size = 10, -->
-<!--       hjust = 0 -->
-<!--     ), -->
-<!--     legend.justification = "left", -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- Topt_plot <- shift_legend(Topt_plot) -->
-<!-- ``` -->
-
-<!-- ```{r fig-S3_Topt_plots, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'} -->
-
-<!-- # x-axis = vertebrate host biting tolerance -->
-<!-- # y-axis = thermal optimum -->
-<!-- # color = vertebrate host population density -->
-
-<!-- Topt_plot <- data.Topt %>%  -->
-<!--   # filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
-<!--   # Choose appropriate pop. dens. values and group -->
-<!--   filter(KH %in% 10^seq(0, 3)) %>% -->
-<!--   arrange(system_ID, KH, sigmaH, median) %>%  -->
-<!--   ## Set up plot ## -->
-<!--   # color = sigmaH -->
-<!--   ggplot(aes(x = sigmaH, colour = as.factor(KH))) + -->
-<!--   # Topt curves: -->
-<!--   geom_path(aes(y = mean), lwd = 1) + -->
-<!--   # # Dotted lines showing limits of 89% HCI -->
-<!--   # geom_path(aes(y = lowHCI),linetype = "dashed") + -->
-<!--   # geom_path(aes(y = highHCI),linetype = "dashed") + -->
-<!--   # white lines breaking up finite/infinite sigmaH values: -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 0.95 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .9, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 1.05 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .9, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 1.15 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .9, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   # x-axis: Use a log10-scale with no buffer space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(0.5, 150), -->
-<!--     breaks = sigmaH_breaks, -->
-<!--     labels = sigmaH_labels -->
-<!--   ) + -->
-<!--   # y-axis -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Thermal optimum "(degree * C)), -->
-<!--     expand = c(0.05, 0.05), -->
-<!--     limits = c(21,31), # mean: 21-31, median: 21-32 -->
-<!--     breaks = seq(21,32, by = 1) -->
-<!--   ) + -->
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "Vertebrate host population\ndensity (ind/ha)", -->
-<!--     values = met.brewer("Hokusai3", 4, -->
-<!--                         # option = "plasma" -->
-<!--     )) + -->
-<!--   scale_fill_manual( -->
-<!--     name = "Vertebrate host population\ndensity (ind/ha)", -->
-<!--     values = met.brewer("Hokusai3", 4, -->
-<!--                         # option = "plasma" -->
-<!--     )) + -->
-<!--   # faceting: -->
-<!--   facet_wrap(~system_ID, -->
-<!--              scales = "free", -->
-<!--              nrow = 2, -->
-<!--              labeller = labeller()  ) + -->
-<!--   # theme options: -->
-<!--   theme_minimal(16) + -->
-<!--   guides(color = guide_legend(override.aes = list(size = 4))) + -->
-<!--   theme( -->
-<!--     legend.position = "bottom", -->
-<!--     legend.margin = margin(), -->
-<!--     legend.direction = "vertical", -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     legend.text = element_text( -->
-<!--       size = 10, -->
-<!--       hjust = 0 -->
-<!--     ), -->
-<!--     legend.justification = "left", -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- Topt_plot <- shift_legend(Topt_plot) -->
-<!-- ``` -->
-
-<!-- ```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'} -->
-<!-- # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider. -->
-
-<!-- #   x    = biting tolerance (with a point at infinity) -->
-<!-- #   y    = vertebrate host population density -->
-<!-- # colour = CTmin -->
-<!-- # Facets = systems -->
-
-<!-- CTmin_df <- data.CT %>% -->
-<!--   filter(variable == "CTmin") %>%  -->
-<!--   filter(is.finite(mean)) %>% -->
-<!--   mutate(sigmaH_proxy = sigmaH) %>%  -->
-<!--   # Arrange along the plotting variables -->
-<!--   arrange(system_ID, KH, sigmaH_proxy, mean) %>%  -->
-<!--   ungroup() -->
-
-<!-- # add many third proxy sigmaH points at infinity to make the values easier to see there -->
-<!-- temp <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.25 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.15 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.05 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.3 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.2 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.1 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(infinite_divide, infinite_skew)) -->
-<!--   )) -->
-
-<!-- CTmin_df <- add_row(CTmin_df, temp) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp2) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp3) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp4) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp5) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp6) -->
-<!-- CTmin_df <- add_row(CTmin_df, temp7) %>% -->
-<!--   arrange(sigmaH_proxy) %>% -->
-<!--   distinct() -->
-
-<!-- CTmin_heat_plots <- CTmin_df %>% -->
-<!--   ## Set up plot ## -->
-<!--   # x = biting tolerance (with a point at infinity), -->
-<!--   # y = vertebrate host population density, -->
-<!--   # color = width of parasite thermal mean_CTwidth -->
-<!--   ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) + -->
-
-<!--   # CTmin for FINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(CTmin_df, sigmaH_proxy < 100) -->
-<!--   ) + -->
-
-<!--   # CTmin for INFINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(CTmin_df, is.infinite(sigmaH)) -->
-<!--   ) + -->
-
-<!--   # x-axis: log10-scale with no buffer space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(0.05, 1E4), -->
-<!--     breaks = 10^seq(-1, 4, 1), -->
-<!--     labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$")) -->
-<!--   ) + -->
-<!--   # y-axis: log10-scale y axis, with no buffer space -->
-<!--   scale_y_log10( -->
-<!--     name = TeX("Biting tolerance (bites per host per day)"), -->
-<!--     expand = c(0, 0), -->
-<!--     breaks = sigmaH_breaks, -->
-<!--     labels = sigmaH_labels -->
-<!--   ) + -->
-<!--   # color: -->
-<!--   scale_fill_viridis_d( -->
-<!--     name = "Mean critical thermal minimum (°C)", -->
-<!--     option = "plasma" -->
-<!--   ) + -->
-<!--   # faceting: -->
-<!--   facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) + -->
-<!--   # legend: -->
-<!--   guides(fill = guide_coloursteps( -->
-<!--     title.position = "top", title.hjust = 0.5, -->
-<!--     barwidth = unit(10, "cm"), -->
-<!--     show.limits = TRUE -->
-<!--   )) + -->
-<!--   # theme options: -->
-<!--   theme_minimal(16) + -->
-<!--   theme( -->
-<!--     legend.box = "horizontal", -->
-<!--     legend.position = "bottom", -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     legend.direction = "horizontal", -->
-<!--     legend.justification = "left", -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- CTmin_heat_plots <- shift_legend(CTmin_heat_plots) -->
-<!-- ``` -->
-
-<!-- ```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'} -->
-
-<!-- # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider. -->
-
-<!-- #   x    = biting tolerance (with a point at infinity) -->
-<!-- #   y    = vertebrate host population density -->
-<!-- # colour = CTmax -->
-<!-- # Facets = systems -->
-
-<!-- CTmax_df <- read_rds("results/CT_vals.rds") %>% -->
-<!--   filter(variable == "CTmax") %>%  -->
-<!--   filter(is.finite(mean)) %>% -->
-<!--   mutate(sigmaH_proxy = sigmaH) %>%  -->
-<!--   # Arrange along the plotting variables -->
-<!--   arrange(system_ID, KH, sigmaH_proxy, mean) %>%  -->
-<!--   ungroup() -->
-
-<!-- # add many third proxy sigmaH points at infinity to make the values easier to see there -->
-<!-- temp <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.25 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.15 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.05 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.3 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.2 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(1.1 * infinite_divide, infinite_skew)) -->
-<!--   )) -->
-<!-- temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, -->
-<!--                                mean(c(infinite_divide, infinite_skew)) -->
-<!--   )) -->
-
-<!-- CTmax_df <- add_row(CTmax_df, temp) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp2) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp3) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp4) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp5) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp6) -->
-<!-- CTmax_df <- add_row(CTmax_df, temp7) %>% -->
-<!--   arrange(sigmaH_proxy) %>% -->
-<!--   distinct() -->
-
-<!-- min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median))) -->
-<!-- max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median))) -->
-<!-- CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1) -->
-
-<!-- CTmax_heat_plots <- CTmax_df %>% -->
-<!--   ## Set up plot ## -->
-<!--   # x = biting tolerance (with a point at infinity), -->
-<!--   # y = vertebrate host population density, -->
-<!--   # color = CTmax -->
-<!--   ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) + -->
-<!--   # CTmax for FINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(CTmax_df, sigmaH_proxy < 100) -->
-<!--   ) + -->
-
-<!--   # CTmax for INFINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(CTmax_df, is.infinite(sigmaH)) -->
-<!--   ) + -->
-<!--   # x-axis: log10-scale with no buffer space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(0.05, 1E4), -->
-<!--     breaks = 10^seq(-1, 4, 1), -->
-<!--     labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$")) -->
-<!--   ) + -->
-<!--   # y-axis: log10-scale y axis, with no buffer space -->
-<!--   scale_y_log10( -->
-<!--     name = TeX("Biting tolerance (bites per host per day)"), -->
-<!--     expand = c(0, 0), -->
-<!--     breaks = sigmaH_breaks, -->
-<!--     labels = sigmaH_labels -->
-<!--   ) + -->
-<!--   # color: -->
-<!--   scale_fill_viridis_d( -->
-<!--     name = "Mean critical thermal maximum (°C)", -->
-<!--     option = "plasma" -->
-<!--   ) + -->
-<!--   # faceting: -->
-<!--   facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) + -->
-<!--   # legend: -->
-<!--   guides(fill = guide_coloursteps( -->
-<!--     title.position = "top", title.hjust = 0.5, -->
-<!--     barwidth = unit(10, "cm"), -->
-<!--     show.limits = TRUE -->
-<!--   )) + -->
-<!--   # theme options: -->
-<!--   theme_minimal(16) + -->
-<!--   theme( -->
-<!--     legend.box = "horizontal", -->
-<!--     legend.position = "bottom", -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     legend.direction = "horizontal", -->
-<!--     legend.justification = "left", -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- CTmax_heat_plots <- shift_legend(CTmax_heat_plots) -->
-<!-- ``` -->
-
-<!-- ```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'} -->
-<!-- # x-axis = vertebrate host population density -->
-<!-- # y-axis = Temperature -->
-<!-- # linetype = biting tolerance -->
-<!-- # colour = CT_min (blue), CT_max (red) -->
-
-<!-- CTRange_df <- ThermPathChars %>% -->
-<!--   # Arrange along the plotting variables -->
-<!--   select(system_label, sigmaH, KH, CTmax, CTmin) %>% -->
-<!--   # Choose a few sigmaH values to plot, including Inf -->
-<!--   filter(sigmaH %in% c(10, 50, Inf)) %>% -->
-<!--   group_by(KH) %>% -->
-<!--   # Arrange along the plotting variables -->
-<!--   arrange(system_label, KH, sigmaH, CTmax, CTmin) %>% -->
-<!--   ungroup() %>% -->
-<!--   melt(id = c("system_label", "KH", "sigmaH")) %>% -->
-<!--   arrange(KH, sigmaH) -->
-
-<!-- CTRange_plots <- CTRange_df %>% -->
-<!--   ## Set up plot ## -->
-<!--   # x-axis = population density, y-axis = temperature, -->
-<!--   # color = thermal extrema, linetype = sigmaH -->
-<!--   ggplot(aes( -->
-<!--     x = KH, y = value, -->
-<!--     linetype = as.factor(sigmaH), color = variable -->
-<!--   )) + -->
-
-<!--   # Mosquito thermal tolerance range lines -->
-<!--   geom_hline( -->
-<!--     data = MosqThermRange_df, -->
-<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-<!--   geom_hline( -->
-<!--     data = MosqThermRange_df, -->
-<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-
-<!--   # Curves showing CTmin and CTmax -->
-<!--   geom_path( -->
-<!--     data = filter(CTRange_df, variable == "CTmin"), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-<!--   geom_path( -->
-<!--     data = filter(CTRange_df, variable == "CTmax"), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-
-<!--   # x-axis: log10-scale with no buffer space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host population density (ind/ha)"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(1E-2, 1E5), -->
-<!--     breaks = 10^seq(-1, 4), -->
-<!--     labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$")) -->
-<!--   ) + -->
-<!--   # y-axis: small buffer space -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Temperature "(degree * C)), -->
-<!--     expand = c(0.05, 0.05), -->
-<!--     limits = range(CTRange_df$value, na.rm = TRUE), -->
-<!--     breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]), -->
-<!--                  floor(range(CTRange_df$value, na.rm = TRUE)[2]), -->
-<!--                  by = 2 -->
-<!--     ) -->
-<!--   ) + -->
-<!--   # linetype: -->
-<!--   scale_linetype_manual( -->
-<!--     name = "Vertebrate host biting tolerance\n(bites per host per day)", -->
-<!--     values = c("solid", "longdash", "dotted"), -->
-<!--     breaks = c(10, 50, Inf), -->
-<!--     labels = unname(c("10 (Chitnis)", "50 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)"))) -->
-<!--   ) + -->
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "Thermal extrema", -->
-<!--     breaks = c("CTmax", "CTmin", "VTTR"), -->
-<!--     labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"), -->
-<!--     values = c("red", "blue", "grey"), -->
-<!--     guide = guide_legend(keyheight = unit(40, "cm")) -->
-<!--   ) + -->
-
-<!--   # faceting: -->
-<!--   facet_wrap(~system_label, -->
-<!--              scales = "free", -->
-<!--              nrow = 2, -->
-<!--              labeller = labeller() -->
-<!--   ) + -->
-
-<!--   # legend: -->
-<!--   guides( -->
-<!--     color = guide_legend( -->
-<!--       override.aes = list(size = 4), -->
-<!--       order = 1 -->
-<!--     ), -->
-<!--     linetype = guide_legend( -->
-<!--       keywidth = 4, -->
-<!--       order = 2 -->
-<!--     ), -->
-<!--   ) + -->
-
-<!--   # theme options: -->
-<!--   theme_minimal_hgrid(11) + -->
-<!--   theme( -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0 -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- shift_legend(CTRange_plots) -->
-<!-- ``` -->
-
-<!-- ```{r fig-S7_CH_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CH_Range} Critical community sizes as a function of temperature and biting tolerance.'} -->
-
-<!-- # x = vertebrate host population density -->
-<!-- # y = Temperature -->
-<!-- # linetype = vertebrate host biting tolerance (needs to vary from "zero to infinity") -->
-<!-- # curves: -->
-<!-- #   CH_min - blue -->
-<!-- #   CH_max - red -->
-<!-- #   VTTR - black -->
-
-<!-- # build data frame for plotting -->
-<!-- CHRange_df <- AllOutputs %>% -->
-<!--   ungroup() %>% -->
-<!--   # Arrange along the plotting variables -->
-<!--   select(system_label, Temperature, sigmaH, CHmax, CHmin) %>% -->
-<!--   filter(sigmaH %in% c(10, 50, 100)) %>% -->
-<!--   filter(is.finite(CHmax)) %>% -->
-<!--   filter(CHmin > 0) %>% -->
-<!--   distinct() %>% -->
-<!--   # Arrange along the plotting variables -->
-<!--   arrange(system_label, Temperature, sigmaH, CHmax, CHmin) %>% -->
-<!--   melt(id = c("system_label", "Temperature", "sigmaH")) %>% -->
-<!--   arrange(Temperature, sigmaH) -->
-
-<!-- CHRange_plots <- CHRange_df %>% -->
-<!--   ## Set up plot ## -->
-<!--   # x = threshold values, y = temperature, -->
-<!--   # color = threshold type, line type = sigmaH -->
-<!--   ggplot(aes( -->
-<!--     x = value, y = Temperature, -->
-<!--     color = variable, linetype = as.factor(sigmaH) -->
-<!--   )) + -->
-
-<!--   # mosquito thermal tolerance range curves: -->
-<!--   geom_hline( -->
-<!--     data = MosqThermRange_df, -->
-<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-<!--   geom_hline( -->
-<!--     data = MosqThermRange_df, -->
-<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-
-<!--   # CH threshold curves: -->
-<!--   geom_path( -->
-<!--     data = filter(CHRange_df, variable == "CHmin" & is.finite(sigmaH)), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-<!--   geom_path( -->
-<!--     data = filter(CHRange_df, variable == "CHmax"), -->
-<!--     lwd = 1 -->
-<!--   ) + -->
-
-<!--   # x-axis: log10-scaled with no buffer-space -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host population density"), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(0.01, 2E5), -->
-<!--     breaks = 10^seq(-2, 5), -->
-<!--     labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$", "$10^5$")) -->
-<!--   ) + -->
-<!--   # y-axis: -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Temperature "(degree * C)), -->
-<!--     expand = c(0.05, 0.05), -->
-<!--     limits = range(CHRange_df$Temperature), -->
-<!--     breaks = seq(floor(range(CHRange_df$Temperature)[1]), -->
-<!--                  floor(range(CHRange_df$Temperature)[2]), -->
-<!--                  by = 2 -->
-<!--     ) -->
-<!--   ) + -->
-<!--   # linetype: -->
-<!--   scale_linetype_manual( -->
-<!--     name = "Biting tolerance\n(bites per host per day)", -->
-<!--     values = c("solid", "longdash", "dotdash"), -->
-<!--     breaks = c(10, 50, 100) -->
-<!--   ) + -->
-
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "Threshold type", -->
-<!--     values = c("red", "blue", "grey"), -->
-<!--     breaks = c("CHmax", "CHmin", "VTTR"), -->
-<!--     labels = c("Maximum community size", "Minimum community size", "Mosquito thermal niche") -->
-<!--   ) + -->
-
-<!--   # faceting: -->
-<!--   facet_wrap(~system_label, scales = "free", nrow = 2) + -->
-
-<!--   # legend: -->
-<!--   guides( -->
-<!--     color = guide_legend( -->
-<!--       override.aes = list(size = 4), -->
-<!--       order = 1 -->
-<!--     ), -->
-<!--     linetype = guide_legend( -->
-<!--       keywidth = 4, -->
-<!--       order = 2 -->
-<!--     ), -->
-<!--   ) + -->
-<!--   # theme options: -->
-<!--   theme_minimal_vgrid(11) + -->
-<!--   theme( -->
-<!--     legend.box = "vertical", -->
-<!--     legend.position = "bottom", -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.text = ggtext::element_markdown(), -->
-<!--     legend.title = element_text(size = 11), -->
-<!--     legend.direction = "vertical", -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 11, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot -->
-<!-- shift_legend(CHRange_plots) -->
-<!-- ``` -->
+# Supplementary Figures
+
+```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
+# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
+
+# !!! [] get enough values of R0 across sigmaH and KH to do a heatmap (21 each?)
+
+# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
+# y = Temperature
+# color = R0
+# curves:
+#   R0 = 1 contour (black curve)
+#   Topt (red curve)
+
+# Facets:
+# Rows = levels of vertebrate host population density
+# Columns = two MBPT systems
+# Total = 6 plots
+
+## Set up plot data frame
+# We re-create the output data frame so that we can vary sigmaH correctly.
+# We also drop the resolution of KH down to just three values
+# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"
+
+## Configure data frame for plotting
+R0_df <- data.R0 %>%
+  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
+  rename(R0 = median) %>%
+  # Consider only 3 values of KH (on a log10-scale)
+  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
+  # Choose a limited range of sigmaH values
+  filter(sigmaH > 10^0.5) %>%
+  # Group by plotting variables
+  group_by(system_ID, KH, sigmaH) %>%
+  # Calculate Topt (which.max requires grouping)
+  mutate(Topt = `Temperature`[which.max(R0)]) %>%
+  as_tibble() %>%
+  arrange(system_ID, sigmaH, Temperature)
+
+## Add a "point at infinity" for sigmaH
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^3 + 2500
+
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+
+R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 3)
+
+# Get the largest value of log10(sigmaH)
+max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
+  select(sigmaH) %>%
+  max() %>%
+  log10()
+
+# # add a second proxy sigmaH point at infinity to make the values easier to see there
+# temp <- filter(R0_df, is.infinite(sigmaH)) %>%
+#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
+# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
+# R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
+#                                              sigmaH, infinite_skew
+# ))
+# R0_df <- add_row(R0_df, temp) %>% distinct()
+
+## Compute mosquito thermal tolerance range (minimum and maximum)
+temp_MosqThermRange_df <- MosqThermRange_df %>%
+  select(system_label, CTmin_V0, CTmax_V0)
+
+## PLOTTING ##
+
+## Options
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+# Labels for facet rows
+R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
+mylabels <- as_labeller(c(
+  `0.1` = "0.1 vertebrate hosts / ha",
+  `1` = "1 vertebrate host / ha",
+  `10` = "10 vertebrate hosts / ha"
+))
+
+# Breaks used to decide fill for the heat map
+fill_breaks <- c(1, seq(5, 20, by = 5), Inf)
+
+# Define colors for heat map so that values of R0>1 go from yellow to red
+my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))
+
+## PLOT ##
+R0_plot <- R0_df %>%
+  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
+  # Mosquito thermal tolerance range lines
+  geom_hline(
+    data = temp_MosqThermRange_df,
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  geom_hline(
+    data = temp_MosqThermRange_df,
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  # R0 contours for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
+    breaks = fill_breaks
+  ) +
+  # R0 contours for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
+    breaks = fill_breaks
+  ) +
+  # R0 = 1 contour:
+  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
+  # Topt curve:
+  geom_line(
+    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
+    mapping = aes(
+      x = sigmaH_proxy,
+      y = Topt,
+      colour = "Topt"
+    ),
+    lwd = 1,
+    linetype = 1
+  ) +
+  # white lines breaking up finite/infinite sigmaH values
+  geom_vline(
+    aes(xintercept = 0.85 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.2 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  # x-axis:
+  scale_x_log10(
+    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels,
+    expand = c(0, 0)
+  ) +
+  # y-axis:
+  scale_y_continuous(
+    name = expression("Temperature "(degree * C)),
+    expand = c(0, 0),
+    limits = c(14, 36),
+    breaks = seq(10, 36, by = 2)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "",
+    labels = c(
+      "R0=1" = unname(TeX("$R_0=1$")),
+      "Topt" = "Transmission\nthermal\noptimum",
+      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
+    ),
+    values = c("black", "purple", "grey"),
+    guide = guide_legend(
+      order = 1,
+      keyheight = unit(2, "cm"),
+      override.aes = list(size = 6)
+    )
+  ) +
+  # fill:
+  scale_fill_manual(
+    name = TeX("$R_0$"),
+    values = my.cols,
+    guide = guide_colorsteps(
+      order = 2,
+      breaks = fill_breaks,
+      barheight = unit(8, "cm")
+    )
+  ) +
+  # faceting:
+  facet_rep_grid(
+    rows = vars(system_label),
+    cols = vars(KH),
+    scales = "free_y",
+    labeller = labeller(.cols = mylabels),
+    repeat.tick.labels = "left"
+  ) +
+  # theme options:
+  theme_minimal_hgrid(11) +
+  theme(
+    axis.line = element_line(),
+    panel.spacing = unit(1, "lines"),
+    legend.text = element_text(size = 11),
+    legend.text.align = 0,
+    strip.text = ggtext::element_markdown(
+      size = 8,
+      hjust = 0
+    )
+  )
+
+# Plot it
+R0_plot
+```
+
+```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
+Topt_df <- data.Topt %>%
+  pivot_wider(id_cols = c("system_label", "Model", "sigmaH", "KH"),
+              names_from = variable,
+              values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%
+  rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
+         highHCI = highHCI_Topt) %>%
+  # Arrange along the plotting variables
+  arrange(system_label, KH, median, sigmaH) %>%
+  ungroup()
+
+# PLOTTING
+Topt_plot <- Topt_df %>%
+  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
+  ## Set up plot ##
+  # color = sigmaH
+  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
+  # Topt curves:
+  geom_path(aes(y = median), lwd = 1) +
+  # x-axis: log10 scale, no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.01, 2E4),
+    breaks = 10^seq(-2, 4),
+    labels = TeX(c(
+      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
+    ))
+  ) +
+  # y-axis
+  scale_y_continuous(
+    name = expression("Thermal optimum "(degree * C)),
+    expand = c(0,0), # c(0.05, 0.05),
+    limits = c(21,30.5), # mean: 21-31, median: 21-32
+    breaks = seq(21,32, by = 1)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
+    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  scale_fill_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
+    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  # faceting:
+  facet_wrap(~system_label, nrow = 2, labeller = labeller()) +
+  # theme options:
+  theme_minimal(16) +
+  guides(color = guide_legend(override.aes = list(size = 4))) +
+  theme(
+    legend.position = "bottom",
+    legend.margin = margin(),
+    legend.direction = "vertical",
+    legend.title = element_text(size = 10),
+    legend.text = element_text(
+      size = 10,
+      hjust = 0
+    ),
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(Topt_plot)
+```
+
+```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}
+
+# x-axis = vertebrate host biting tolerance
+# y-axis = thermal optimum
+# color = vertebrate host population density
+
+infinite_skew <- 4500 # 10000
+
+Topt_df <- Topt_df %>% 
+  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
+                               sigmaH,
+                               infinite_skew))
+Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
+
+sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15*infinite_divide, infinite_skew)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+Topt_plot <- Topt_df %>%
+  # Choose appropriate pop. dens. values and group
+  filter(KH %in% 10^seq(0, 3)) %>%
+  arrange(system_label, KH, sigmaH, median) %>%
+  ## Set up plot ##
+  # color = sigmaH
+  ggplot(aes(x = sigmaH_proxy, colour = as.factor(KH))) +
+  # Topt curves:
+  geom_path(aes(y = median), lwd = 1) +
+  # white lines breaking up finite/infinite sigmaH values:
+  geom_vline(
+    aes(xintercept = 1.05 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.15 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.25 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  # x-axis: Use a log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    # limits = c(0.5, 150),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # y-axis
+  scale_y_continuous(
+    name = expression("Thermal optimum "(degree * C)),
+    expand = c(0.05, 0.05),
+    limits = c(21,31), # mean: 21-31, median: 21-32
+    breaks = seq(21,32, by = 1)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    values = met.brewer("Hokusai3", 4)) +
+  scale_fill_manual(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    values = met.brewer("Hokusai3", 4)) +
+  # faceting:
+  facet_wrap(~system_label,
+             scales = "free",
+             nrow = 2,
+             labeller = labeller()  ) +
+  # theme options:
+  theme_minimal(16) +
+  guides(color = guide_legend(override.aes = list(size = 4))) +
+  theme(
+    legend.position = "bottom",
+    legend.margin = margin(),
+    legend.direction = "vertical",
+    legend.title = element_text(size = 10),
+    legend.text = element_text(
+      size = 10,
+      hjust = 0
+    ),
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(Topt_plot)
+```
+
+```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'}
+# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
+
+#   x    = biting tolerance (with a point at infinity)
+#   y    = vertebrate host population density
+# colour = CTmin
+# Facets = systems
+
+CTmin_df <- data.CT %>%
+  filter(variable == "CTmin") %>%
+  filter(is.finite(median)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, KH, sigmaH_proxy, median) %>%
+  ungroup()
+
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(CTmin_df, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+
+CTmin_df <- inf_skew_func(CTmin_df, infinite_skew, infinite_divide, 8)
+
+# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+CTmin_heat_plots <- CTmin_df %>%
+  ## Set up plot ##
+  # x = biting tolerance (with a point at infinity),
+  # y = vertebrate host population density,
+  # color = width of parasite thermal mean_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
+  # CTmin for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(CTmin_df, sigmaH_proxy < 100)
+  ) +
+  # CTmin for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(CTmin_df, is.infinite(sigmaH))
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E4),
+    breaks = 10^seq(-1, 4, 1),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: log10-scale y axis, with no buffer space
+  scale_y_log10(
+    name = TeX("Biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # color:
+  scale_fill_viridis_d(
+    name = "Median critical thermal minimum (°C)",
+    option = "plasma"
+  ) +
+  # faceting:
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
+  # legend:
+  guides(fill = guide_coloursteps(
+    title.position = "top", title.hjust = 0.5,
+    barwidth = unit(10, "cm"),
+    show.limits = TRUE
+  )) +
+  # theme options:
+  theme_minimal(16) +
+  theme(
+    legend.box = "horizontal",
+    legend.position = "bottom",
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.direction = "horizontal",
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(CTmin_heat_plots)
+```
+
+```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'}
+
+# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
+
+#   x    = biting tolerance (with a point at infinity)
+#   y    = vertebrate host population density
+# colour = CTmax
+# Facets = systems
+
+CTmax_df <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller() %>% 
+  filter(variable == "CTmax") %>%
+  filter(is.finite(median)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, KH, sigmaH_proxy, median) %>%
+  ungroup()
+
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(CTmax_df, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+
+CTmax_df <- inf_skew_func(CTmax_df, infinite_skew, infinite_divide, 8)
+
+# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median)))
+max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median)))
+CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1)
+
+CTmax_heat_plots <- CTmax_df %>%
+  ## Set up plot ##
+  # x = biting tolerance (with a point at infinity),
+  # y = vertebrate host population density,
+  # color = CTmax
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
+  # CTmax for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(CTmax_df, sigmaH_proxy < 100)
+  ) +
+
+  # CTmax for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(CTmax_df, is.infinite(sigmaH))
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E4),
+    breaks = 10^seq(-1, 4, 1),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: log10-scale y axis, with no buffer space
+  scale_y_log10(
+    name = TeX("Biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # color:
+  scale_fill_viridis_d(
+    name = "Median critical thermal maximum (°C)",
+    option = "plasma"
+  ) +
+  # faceting:
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
+  # legend:
+  guides(fill = guide_coloursteps(
+    title.position = "top", title.hjust = 0.5,
+    barwidth = unit(10, "cm"),
+    show.limits = TRUE
+  )) +
+  # theme options:
+  theme_minimal(16) +
+  theme(
+    legend.box = "horizontal",
+    legend.position = "bottom",
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.direction = "horizontal",
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(CTmax_heat_plots)
+```
+
+```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'}
+# x-axis = vertebrate host population density
+# y-axis = Temperature
+# linetype = biting tolerance
+# colour = CT_min (blue), CT_max (red)
+
+CTRange_df <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller() %>% 
+  # Arrange along the plotting variables
+  select(system_label, sigmaH, KH, variable, value = median) %>%
+  # Choose a few sigmaH values to plot, including Inf
+  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
+  filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 101)]) %>% 
+  pivot_wider(id_cols = c("system_label", "sigmaH", "KH"), 
+              names_from = variable, values_from = value) %>% 
+  group_by(system_label, KH, sigmaH) %>%
+  mutate(CTwidth = max(CTmax - CTmin, 0)) %>% 
+  filter(CTwidth > 0.05) %>%
+  # Arrange along the plotting variables
+  arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
+  ungroup() %>%
+  melt(id = c("system_label", "KH", "sigmaH")) %>%
+  arrange(KH, sigmaH)
+
+CTRange_plots <- CTRange_df %>%
+  ## Set up plot ##
+  # x-axis = population density, y-axis = temperature,
+  # color = thermal extrema, linetype = sigmaH
+  ggplot(
+    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
+    ) +
+  # Mosquito thermal tolerance range lines
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  # Curves showing CTmin and CTmax
+  geom_line(
+    data = filter(CTRange_df, variable == "CTmin"),
+    lwd = 1
+  ) +
+  geom_line(
+    data = filter(CTRange_df, variable == "CTmax"),
+    lwd = 1
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(1E-2, 1E5),
+    breaks = 10^seq(-1, 4),
+    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: small buffer space
+  scale_y_continuous(
+    name = expression("Temperature "(degree * C)),
+    expand = c(0.05, 0.05),
+    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
+    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
+                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
+                 by = 2)
+  ) +
+  # linetype:
+  scale_linetype_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c("solid", "dashed", "longdash", "dotted"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Thermal extrema",
+    breaks = c("CTmax", "CTmin", "VTTR"),
+    labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"),
+    values = c("red", "blue", "grey"),
+    guide = guide_legend(keyheight = unit(40, "cm"))
+  ) +
+  # faceting:
+  facet_wrap(~system_label,scales = "free",nrow = 2,labeller = labeller()) +
+  # legend:
+  guides(
+    color = guide_legend(override.aes = list(size = 4), order = 1),
+    linetype = guide_legend(keywidth = 4, order = 2),
+  ) +
+  # theme options:
+  theme_minimal_hgrid(11) +
+  theme(
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 11,
+      hjust = 0
+    )
+  )
+
+# Plot
+shift_legend(CTRange_plots)
+```
 
@@
 
-```{r fig-SX_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum, critical thermal maximum, and thermal optimum vary with vertebrate host availability.'}
+```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum, critical thermal maximum, and thermal optimum vary with vertebrate host availability.'}
 all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  ))
+  pathosystem_labeller()
 
@@
 
-```{r fig-SX_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
 R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  ))
+  pathosystem_labeller()
 
@@
 
-```{r fig-SX_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+```{r fig-S9_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
 ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  ))
+  pathosystem_labeller()
 
@@
 ```
-```{r fig-SX_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
 Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
+  pathosystem_labeller() %>% 
   filter(!is.na(rel_HPD_width)) %>%

### 2023-06-05 manuscript-figures.Rmd
increase resolution of R0 values

--- 2023-06-03 manuscript-figures.Rmd
@@
 
-# R0 as a function of temperature, seperate curves across values of KH and sigmaH
+# R0 as a function of temperature, separate curves across values of KH and sigmaH
 
@@
   select(-variable) %>%
-  # normalize variables to have a maximum of 1
+  # normalize median of R0 distribution to have a maximum of one
   group_by(system_ID, Model, sigmaH, KH) %>%
-  # mutate(mean_norm = mean / max(mean)) %>%
   mutate(median_norm = median / max(median)) %>%
-  # mutate(highHCI_norm = highHCI / max(median)) %>%
-  # mutate(lowHCI_norm = lowHCI / max(median)) %>%
   arrange(system_ID, sigmaH, KH, Temperature, median_norm)
@@
   ) +
-  # # 89% HCI of R0 TPC curves
-  # geom_ribbon(
-  #   data = filter(data.R0_norm, sigmaH == 100),
-  #   aes(ymin = lowHCI_norm, ymax = highHCI_norm, fill = KH),
-  #   alpha = 0.1
-  # ) +
   # x-axis:
   scale_x_continuous(
-    name = "Temperature (C)",
+    name = "Temperature (°C)",
     expand = c(0, 0),
@@
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
+  pathosystem_labeller() %>% 
   distinct() %>%
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
+infinite_skew <- 10^2.35
 # Used to create a gap dividing finite and infinite sigmaH
@@
 Toptalt_df <- inf_skew_func(Toptalt_df, infinite_skew, infinite_divide, 8)
-
-# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
 
@@
   ) +
-  # geom_contour(data = data.R0_norm,
-  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
   # x-axis: log10-scale with no buffer space
@@
 # Plot
-Toptalt_plots <- shift_legend(Toptalt_plots)
+shift_legend(Toptalt_plots)
 ```
@@
   ungroup() %>%
-  mutate(system_label = case_when(
-    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
-    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
-    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
-    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
-    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
-  )) %>%
+  pathosystem_labeller() %>% 
   filter(variable == "CTwidth") %>%
-  # filter(sigmaH < 10^2.2) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
@@
 # Plot
-CTWidth_heat_plots <- shift_legend(CTWidth_heat_plots)
+shift_legend(CTWidth_heat_plots)
 ```
 
-<!-- # Supplementary Figures -->
-
-<!-- ```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'} -->
-<!-- # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density. -->
-
-<!-- # x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity") -->
-<!-- # y = Temperature -->
-<!-- # color = R0 -->
-<!-- # curves: -->
-<!-- #   R0 = 1 contour (black curve) -->
-<!-- #   Topt (red curve) -->
-
-<!-- # Facets: -->
-<!-- # Rows = levels of vertebrate host population density -->
-<!-- # Columns = two MBPT systems -->
-<!-- # Total = 6 plots -->
-
-<!-- ## Set up plot data frame -->
-<!-- # We re-create the output data frame so that we can vary sigmaH correctly. -->
-<!-- # We also drop the resolution of KH down to just three values -->
-<!-- # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald" -->
-
-<!-- ## Configure data frame for plotting -->
-<!-- R0_df <- data.R0 %>% -->
-<!--   select(system_ID, system_label, Temperature, sigmaH, KH, median) %>% -->
-<!--   rename(R0 = median) %>%  -->
-<!--   # Consider only 3 values of KH (on a log10-scale) -->
-<!--   filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1 -->
-<!--   # Choose a limited range of sigmaH values -->
-<!--   filter(sigmaH > 10^0.5) %>% -->
-<!--   # Group by plotting variables -->
-<!--   group_by(system_ID, KH, sigmaH) %>% -->
-<!--   # Calculate Topt (which.max requires grouping) -->
-<!--   mutate(Topt = `Temperature`[which.max(R0)]) %>% -->
-<!--   as_tibble() %>% -->
-<!--   arrange(system_ID, sigmaH, Temperature) -->
-
-<!-- ## Add a "point at infinity" for sigmaH -->
-<!-- # Value of sigmaH to replace 'Inf' with for plotting -->
-<!-- infinite_skew <- 10^3 + 2500 -->
-
-<!-- # Get the largest value of log10(sigmaH) -->
-<!-- max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>% -->
-<!--   select(sigmaH) %>% -->
-<!--   max() %>% -->
-<!--   log10() -->
-
-<!-- # Used to create a gap dividing finite and infinite sigmaH -->
-<!-- infinite_divide <- 10^mean(c(3, log10(infinite_skew))) -->
-
-<!-- # add a second proxy sigmaH point at infinity to make the values easier to see there -->
-<!-- temp <- filter(R0_df, is.infinite(sigmaH)) %>% -->
-<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide)) -->
-<!-- # Create a proxy sigmaH variable that replaces Inf with infinite_skew -->
-<!-- R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH), -->
-<!--                                              sigmaH, infinite_skew -->
-<!-- )) -->
-<!-- R0_df <- add_row(R0_df, temp) %>% distinct() -->
-
-<!-- ## Compute mosquito thermal tolerance range (minimum and maximum) -->
-<!-- temp_MosqThermRange_df <- MosqThermRange_df %>% -->
-<!--   select(system_label, CTmin_V0, CTmax_V0) -->
-
-<!-- ## PLOTTING ## -->
-
-<!-- ## Options -->
-<!-- # Define sigmaH tick breaks and labels -->
-<!-- sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew) -->
-<!-- sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$")) -->
-
-<!-- # Labels for facet rows -->
-<!-- R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10)) -->
-<!-- mylabels <- as_labeller(c( -->
-<!--   `0.1` = "0.1 vertebrate hosts / ha", -->
-<!--   `1` = "1 vertebrate host / ha", -->
-<!--   `10` = "10 vertebrate hosts / ha" -->
-<!-- )) -->
-
-<!-- # Breaks used to decide fill for the heat map -->
-<!-- fill_breaks <- c(1, seq(5, 20, by = 5), Inf) -->
-
-<!-- # Define colors for heat map so that values of R0>1 go from yellow to red -->
-<!-- my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd")))) -->
-
-<!-- ## PLOT ## -->
-<!-- R0_plot <- R0_df %>% -->
-<!--   ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) + -->
-
-<!--   # Mosquito thermal tolerance range lines -->
-<!--   geom_hline( -->
-<!--     data = temp_MosqThermRange_df, -->
-<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-<!--   geom_hline( -->
-<!--     data = temp_MosqThermRange_df, -->
-<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
-<!--     lwd = 1.275 -->
-<!--   ) + -->
-
-<!--   # R0 contours for FINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98), -->
-<!--     breaks = fill_breaks -->
-<!--   ) + -->
-
-<!--   # R0 contours for INFINITE sigmaH: -->
-<!--   geom_contour_filled( -->
-<!--     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02), -->
-<!--     breaks = fill_breaks -->
-<!--   ) + -->
-
-<!--   # R0 = 1 contour: -->
-<!--   geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) + -->
-
-<!--   # Topt curve: -->
-<!--   geom_line( -->
-<!--     # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one -->
-<!--     mapping = aes( -->
-<!--       x = sigmaH_proxy, -->
-<!--       y = Topt, -->
-<!--       colour = "Topt" -->
-<!--     ), -->
-<!--     lwd = 1, -->
-<!--     linetype = 1 -->
-<!--   ) + -->
-
-<!--   # white lines breaking up finite/infinite sigmaH values -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 0.85 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-<!--   geom_vline( -->
-<!--     aes(xintercept = 1.2 * infinite_divide), -->
-<!--     colour = "white", -->
-<!--     lwd = .8, -->
-<!--     show.legend = FALSE -->
-<!--   ) + -->
-
-<!--   # x-axis: -->
-<!--   scale_x_log10( -->
-<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
-<!--     breaks = sigmaH_breaks, -->
-<!--     labels = sigmaH_labels, -->
-<!--     expand = c(0, 0) -->
-<!--   ) + -->
-
-<!--   # y-axis: -->
-<!--   scale_y_continuous( -->
-<!--     name = expression("Temperature "(degree * C)), -->
-<!--     expand = c(0, 0), -->
-<!--     limits = c(14, 36), -->
-<!--     breaks = seq(10, 36, by = 2) -->
-<!--   ) + -->
-
-<!--   # color: -->
-<!--   scale_colour_manual( -->
-<!--     name = "", -->
-<!--     labels = c( -->
-<!--       "R0=1" = unname(TeX("$R_0=1$")), -->
-<!--       "Topt" = "Transmission\nthermal\noptimum", -->
-<!--       "VTTR" = "Mosquito\nthermal\ntolerance\nlimit" -->
-<!--     ), -->
-<!--     values = c("black", "purple", "grey"), -->
-<!--     guide = guide_legend( -->
-<!--       order = 1, -->
-<!--       keyheight = unit(2, "cm"), -->
-<!--       override.aes = list(size = 6) -->
-<!--     ) -->
-<!--   ) + -->
-
-<!--   # fill: -->
-<!--   scale_fill_manual( -->
-<!--     name = TeX("$R_0$"), -->
-<!--     values = my.cols, -->
-<!--     guide = guide_colorsteps( -->
-<!--       order = 2, -->
-<!--       breaks = fill_breaks, -->
-<!--       barheight = unit(8, "cm") -->
-<!--     ) -->
-<!--   ) + -->
-
-<!--   # faceting: -->
-<!--   facet_rep_grid( -->
-<!--     rows = vars(system_label), -->
-<!--     cols = vars(KH), -->
-<!--     scales = "free_y", -->
-<!--     labeller = labeller(.cols = mylabels), -->
-<!--     repeat.tick.labels = "left" -->
-<!--   ) + -->
-
-<!--   # theme options: -->
-<!--   theme_minimal_hgrid(11) + -->
-<!--   theme( -->
-<!--     axis.line = element_line(), -->
-<!--     panel.spacing = unit(1, "lines"), -->
-<!--     legend.text = element_text(size = 11), -->
-<!--     legend.text.align = 0, -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 8, -->
-<!--       hjust = 0 -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- # Plot it -->
-<!-- R0_plot -->
-<!-- ``` -->
+# Supplementary Figures
+
+```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
+# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
+
+# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
+# y = Temperature
+# color = R0
+# curves:
+#   R0 = 1 contour (black curve)
+#   Topt (red curve)
+
+# Facets:
+# Rows = levels of vertebrate host population density
+# Columns = two MBPT systems
+# Total = 6 plots
+
+## Set up plot data frame
+# We re-create the output data frame so that we can vary sigmaH correctly.
+# We also drop the resolution of KH down to just three values
+# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"
+
+## Configure data frame for plotting
+R0_df <- data.R0 %>%
+  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
+  rename(R0 = median) %>%
+  # Consider only 3 values of KH (on a log10-scale)
+  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
+  # Choose a limited range of sigmaH values
+  filter(sigmaH > 10^0.5) %>%
+  # Group by plotting variables
+  group_by(system_ID, KH, sigmaH) %>%
+  # Calculate Topt (which.max requires grouping)
+  mutate(Topt = `Temperature`[which.max(R0)]) %>%
+  as_tibble() %>%
+  arrange(system_ID, sigmaH, Temperature)
+
+## Add a "point at infinity" for sigmaH
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^3 + 2500
+
+# Get the largest value of log10(sigmaH)
+max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
+  select(sigmaH) %>%
+  max() %>%
+  log10()
+
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+
+# add a second proxy sigmaH point at infinity to make the values easier to see there
+temp <- filter(R0_df, is.infinite(sigmaH)) %>%
+  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
+# Create a proxy sigmaH variable that replaces Inf with infinite_skew
+R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
+                                             sigmaH, infinite_skew
+))
+R0_df <- add_row(R0_df, temp) %>% distinct()
+
+## Compute mosquito thermal tolerance range (minimum and maximum)
+temp_MosqThermRange_df <- MosqThermRange_df %>%
+  select(system_label, CTmin_V0, CTmax_V0)
+
+## PLOTTING ##
+
+## Options
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+# Labels for facet rows
+R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
+mylabels <- as_labeller(c(
+  `0.1` = "0.1 vertebrate hosts / ha",
+  `1` = "1 vertebrate host / ha",
+  `10` = "10 vertebrate hosts / ha"
+))
+
+# Breaks used to decide fill for the heat map
+fill_breaks <- c(1, seq(5, 20, by = 5), Inf)
+
+# Define colors for heat map so that values of R0>1 go from yellow to red
+my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))
+
+## PLOT ##
+R0_plot <- R0_df %>%
+  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
+  # Mosquito thermal tolerance range lines
+  geom_hline(
+    data = temp_MosqThermRange_df,
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  geom_hline(
+    data = temp_MosqThermRange_df,
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  # R0 contours for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
+    breaks = fill_breaks
+  ) +
+  # R0 contours for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
+    breaks = fill_breaks
+  ) +
+  # R0 = 1 contour:
+  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
+  # Topt curve:
+  geom_line(
+    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
+    mapping = aes(
+      x = sigmaH_proxy,
+      y = Topt,
+      colour = "Topt"
+    ),
+    lwd = 1,
+    linetype = 1
+  ) +
+
+  # white lines breaking up finite/infinite sigmaH values
+  geom_vline(
+    aes(xintercept = 0.85 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.2 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  # x-axis:
+  scale_x_log10(
+    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels,
+    expand = c(0, 0)
+  ) +
+  # y-axis:
+  scale_y_continuous(
+    name = expression("Temperature "(degree * C)),
+    expand = c(0, 0),
+    limits = c(14, 36),
+    breaks = seq(10, 36, by = 2)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "",
+    labels = c(
+      "R0=1" = unname(TeX("$R_0=1$")),
+      "Topt" = "Transmission\nthermal\noptimum",
+      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
+    ),
+    values = c("black", "purple", "grey"),
+    guide = guide_legend(
+      order = 1,
+      keyheight = unit(2, "cm"),
+      override.aes = list(size = 6)
+    )
+  ) +
+  # fill:
+  scale_fill_manual(
+    name = TeX("$R_0$"),
+    values = my.cols,
+    guide = guide_colorsteps(
+      order = 2,
+      breaks = fill_breaks,
+      barheight = unit(8, "cm")
+    )
+  ) +
+  # faceting:
+  facet_rep_grid(
+    rows = vars(system_label),
+    cols = vars(KH),
+    scales = "free_y",
+    labeller = labeller(.cols = mylabels),
+    repeat.tick.labels = "left"
+  ) +
+  # theme options:
+  theme_minimal_hgrid(11) +
+  theme(
+    axis.line = element_line(),
+    panel.spacing = unit(1, "lines"),
+    legend.text = element_text(size = 11),
+    legend.text.align = 0,
+    strip.text = ggtext::element_markdown(
+      size = 8,
+      hjust = 0
+    )
+  )
+
+# Plot it
+R0_plot
+```
 

### 2023-06-05 code/get-outputs.R

@@ -47,7 +47,8 @@ samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
 sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
 
-data.Vec <- filter(data.Vec, sample_num %in% sample_inds)
+data.Vec <- read_rds("results/VecTPC_vals.rds") %>% 
+  filter(sample_num %in% sample_inds)
 
 
 # 1) Define accessory functions -------------------------------------------
@@ -239,8 +240,10 @@ if (!exists("cluster")) {
 }
 
 # Set up host trait data frame (for future visualization)
-data.R0 <- data.Host %>%
-  filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>% 
+data.R0 <- as.data.frame(data.Host) %>%
+  # filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>%
+  filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf,
+                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 21)])) %>% 
   filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)])
 
 # Slice host trait data
@@ -261,11 +264,12 @@ for (system_name in unique(data.Vec$system_ID)) {
     sigmaHslice_num <- 1
     for (index_sigmaH in sigmaH_slices) {
       print(paste0("sigmaH slice number ", sigmaHslice_num, " out of ", length(sigmaH_slices)))
-      R0.df <- data.R0 %>%
+      temp_df <- data.R0 %>%
         filter(sigmaH %in% index_sigmaH,
                KH %in% index_KH) %>%
-        R0_TPC_func(., system_name) %>%
-        rbind(R0.df)
+        R0_TPC_func(., system_name)
+        
+      R0.df <- rbind(temp_df, R0.df)
       sigmaHslice_num <- sigmaHslice_num  + 1
     }
     KHslice_num <- KHslice_num +1

### 2023-06-05 manuscript-figures.Rmd

--- 2023-06-05 manuscript-figures.Rmd
@@
   ) +
-  # # 89% HCI of R0 TPC curves
-  # geom_ribbon(
-  #   data = filter(data.R0_norm, sigmaH == 100),
-  #   aes(ymin = lowHCI_norm, ymax = highHCI_norm, fill = KH),
-  #   alpha = 0.1
-  # ) +
   # x-axis:
@@
   ) +
-  # geom_contour(data = data.R0_norm,
-  #              aes(y = sigmaH, z = median, colour = "R0=1"), breaks = c(1), size = 1) +
   # x-axis: log10-scale with no buffer space
@@
   filter(variable == "CTwidth") %>%
-  # filter(sigmaH < 10^2.2) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
@@
 # Plot
-CTWidth_heat_plots <- shift_legend(CTWidth_heat_plots)
+shift_legend(CTWidth_heat_plots)
 ```
@@
 # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
-
-# !!! [] get enough values of R0 across sigmaH and KH to do a heatmap (21 each?)
 
@@
   log10()
-
-# # add a second proxy sigmaH point at infinity to make the values easier to see there
-# temp <- filter(R0_df, is.infinite(sigmaH)) %>%
-#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
-# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
-# R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
-#                                              sigmaH, infinite_skew
-# ))
-# R0_df <- add_row(R0_df, temp) %>% distinct()
 
@@
 
-```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+```{r fig-SX_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+
+# !!! [] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
@@
 
-```{r fig-S9_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+```{r fig-SX_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+
+# !!! [] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
@@
 ```
-```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+```{r fig-SX_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+# !!! [] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
+
 Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%

### 2023-06-07 manuscript-figures.Rmd
clean up sensitivity figures

--- 2023-06-05 manuscript-figures.Rmd
@@
 data.CT <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller()
+
+# Sensitivity data for critical thermal extrema
+CT.HPD <- read_rds("results/CT_HPD_sens.rds") %>% 
+  ungroup() %>%
   pathosystem_labeller()
@@
 The range of temperatures is restricted to values where the immature development rate is positive.
-For traits that do not involve a parasite, *Aedes aegypti* with DENV and *Ae.
-aegypti* with ZIKV curves overlap.'}
+For traits that do not involve a parasite, \\textit{Aedes aegypti} with DENV and \\textit{Ae.
+aegypti} with ZIKV curves overlap.'}
 ## Set up plot dataframe
@@
   # theme options:
-  theme_minimal_vgrid(11) +
+  theme_minimal_vgrid() +
   theme(
@@
     legend.justification = "center",
-    axis.title.x = element_text(hjust = 0.2),
+    axis.title.x = element_text(hjust = 0.5),
     strip.text = element_text(
@@
   # theme options:
-  theme_minimal_vgrid(16) +
+  theme_minimal_vgrid() +
   theme(
@@
   # theme options:
-  theme_minimal(16) +
+  theme_minimal() +
   theme(
@@
   # theme options:
-  theme_minimal_hgrid(11) +
+  theme_minimal_hgrid() +
   theme(
@@
   # theme options:
-  theme_minimal(16) +
+  theme_minimal() +
   guides(color = guide_legend(override.aes = list(size = 4))) +
@@
 
+# !!! [] decrease length of color bar
+
 #   x    = biting tolerance (with a point at infinity)
@@
 
+# !!! [] decrease length of color bar (the length used in Topt plot might be good)
+
 # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
@@
   ) +
-
   # CTmax for INFINITE sigmaH:
@@
 
-test_plot <- Topt0_df %>%
-  ggplot(aes(x = Temperature, y = proxy_0)) +
-  geom_point() +
-  facet_wrap(~system_ID, scales = "free")
-test_plot
+# test_plot <- Topt0_df %>%
+#   ggplot(aes(x = Temperature, y = proxy_0)) +
+#   geom_point() +
+#   facet_wrap(~system_ID, scales = "free")
+# test_plot
 
@@
   facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid(16) +
+  theme_minimal_grid() +
   theme(
@@
 ```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+
+# !!! [] just compare "low host availability (sigmaH = 50, KH = 1 or 10)" and 
+#        "high host availability (sigmaH = Inf, KH = 100)" scenarios
+
 R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
@@
   scale_fill_discrete(
-    name = "Focal parameter",
-    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    name = "Focal trait",
+    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
     labels = c(
-      "Vector competence", "Pr(larval survival)",
-      "Parasite development rate", "Mortality rate",
-      "Immature development rate", "Max. biting rate",
-      "Eggs per female per day"
-    )
+      "Adult lifespan", "Biting frequency", "Eggs per female per day",
+      "Immature development rate", "Prob. of immature survival",
+      "Prob. of surviving EIP", "Vector competence")
   ) +
@@
   ) +
-  theme_minimal_hgrid(16) +
+  theme_minimal_hgrid() +
   theme(
@@
 ```{r fig-S9_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+
+# !!! [] just compare "low host availability (sigmaH = 50, KH = 1 or 10)" and 
+#        "high host availability (sigmaH = Inf, KH = 100)" scenarios
+
 ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
@@
 ```
-```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimmum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
 Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
@@
   facet_wrap(~system_label, scales = "free") +
-  theme_minimal_hgrid(16) +
+  theme_minimal_hgrid() +
   theme(
@@
 ```
+
+```{r fig-S11_CTmin_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the critical thermal minimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+
+plot.CTmin.rel.sens <- CT.HPD %>%
+  filter(variable == "CTmin") %>% 
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal trait",
+    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+    labels = c(
+      "Adult lifespan", "Biting frequency", "Eggs per female per day",
+      "Immature development rate", "Prob. of immature survival",
+      "Prob. of surviving EIP", "Vector competence")
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
+  ) +
+  facet_grid(cols = vars(system_label),
+             rows = vars(sigmaH), 
+             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
+                                                      default = label_parsed)),
+             scales = "free") +
+  theme_minimal_hgrid() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.CTmin.rel.sens
+```
+
+```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+
+plot.CTmax.rel.sens <- CT.HPD %>%
+  filter(variable == "CTmax") %>% 
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal trait",
+    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+    labels = c(
+      "Adult lifespan", "Biting frequency", "Eggs per female per day",
+      "Immature development rate", "Prob. of immature survival",
+      "Prob. of surviving EIP", "Vector competence")
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
+  ) +
+  facet_grid(cols = vars(system_label),
+             rows = vars(sigmaH), 
+             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
+                                                      default = label_parsed)),
+             scales = "free") +
+  theme_minimal_hgrid() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.CTmax.rel.sens
+```
+
+```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+
+plot.CTwidth.rel.sens <- CT.HPD %>%
+  filter(variable == "CTwidth") %>% 
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal trait",
+    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+    labels = c(
+      "Adult lifespan", "Biting frequency", "Eggs per female per day",
+      "Immature development rate", "Prob. of immature survival",
+      "Prob. of surviving EIP", "Vector competence")
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
+  ) +
+  facet_grid(cols = vars(system_label),
+             rows = vars(sigmaH), 
+             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
+                                                      default = label_parsed)),
+             scales = "free") +
+  theme_minimal_hgrid() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 11,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+plot.CTwidth.rel.sens
+```

### 2023-06-07 code/sensitivity.R

@@ -891,7 +891,7 @@ plot.Topt.rel.sens
 
 # Calculate the width of the 95% HPD for the full posterior of Topt across vertebrate host abundance
 
-sigmaH_vec <- c(50, Inf)
+sigmaH_vec <- c(10, 50, Inf)
 KH_vec <- 10^seq(-2,5)
 
 data.CTHPD <- dplyr::filter(data.Host, 
@@ -1389,6 +1389,57 @@ plot.CTmax.rel.sens <- CT.HPD %>%
   )
 plot.CTmax.rel.sens
 
+plot.CTwidth.rel.sens <- CT.HPD %>%
+  ungroup() %>% 
+  filter(variable == "CTwidth") %>% 
+  mutate(system_label = case_when(
+    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
+    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
+    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
+    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
+    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
+  )) %>%
+  filter(!is.na(rel_HPD_width)) %>% 
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>% 
+  mutate(sens_total = sum(rel_HPD_width)) %>% 
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
+  arrange(sens_rel) %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_discrete(
+    name = "Focal parameter",
+    breaks = c("betaV", "deltaL", "etaV", "muV", "rhoL", "sigmaV", "sigmaV_f"),
+    labels =  c("Vector competence", "Pr(larval survival)", 
+                "Parasite development rate", "Mortality rate", 
+                "Immature development rate", "Max. biting rate", 
+                "Eggs per female per day")
+  )  +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
[…]

### 2023-06-07 manuscript-figures.Rmd
adjust figure legends

@@
 
+# Label functions:
+appender_sigmaH <- function(string) {
+  unname(TeX(paste("$\\sigma_H = $", string)))
+}
+appender_KH <- function(string) {
+  unname(TeX(paste("$K_H = $", string)))
+}
+
 # Helper function: place legends in empty facets of plot grids
@@
 data.CT <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller()
+
+# Sensitivity data for R0
+R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>% 
+  ungroup() %>%
+  pathosystem_labeller()
+
+# Sensitivity data for Topt
+Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>% 
+  ungroup() %>%
   pathosystem_labeller()
@@
 #        "high host availability (sigmaH = Inf, KH = 100)" scenarios
-
-R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
-  ungroup() %>%
-  pathosystem_labeller()
-
-# Label functions:
-appender_sigmaH <- function(string) {
-  unname(TeX(paste("$\\sigma_H = $", string)))
-}
-appender_KH <- function(string) {
-  unname(TeX(paste("$K_H = $", string)))
-}
+# !!! [] put legend at bottom of plot
+# !!! [] change factor/levels for focal_var so that they show up in the same 
+#        order as in the legend
 
@@
   scale_fill_discrete(
-    name = "Focal trait",
+    name = "Focal trait:",
     breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
@@
     legend.text = element_text(size = 10),
+    legend.position = "bottom",
     axis.title.x = element_text(hjust = 0.5),

### 2023-06-07 code/sensitivity.R
update CT HPD values

@@ -950,8 +950,8 @@ for (index_KH in unique(data.CTHPD$KH)) {
 }
 
 # Save Topt highest posterior density data
-# write_rds(full.CT.HPD, "results/full_CT_HPD.rds")
-full.CT.HPD <- read_rds("results/full_CT_HPD.rds")
+write_rds(full.CT.HPD, "results/full_CT_HPD.rds")
+# full.CT.HPD <- read_rds("results/full_CT_HPD.rds")
 
 # # Diagnostic plot
 # test.plot <- full.CT.HPD %>%
@@ -1067,8 +1067,8 @@ for (var_name in temp_vars) {
 
 
 # Save CT relative highest posterior density data
-# write_rds(CT.HPD, "results/CT_HPD_sens.rds", compress = 'gz')
-CT.HPD <- read_rds("results/CT_HPD_sens.rds")
+write_rds(CT.HPD, "results/CT_HPD_sens.rds", compress = 'gz')
+# CT.HPD <- read_rds("results/CT_HPD_sens.rds")
 
 ## Plot Topt uncertainty 
 var_name_table <- list(

### 2023-06-07 manuscript-figures.Rmd
update R0 values

--- 2023-06-05 manuscript-figures.Rmd
@@
   # Consider only 3 values of KH (on a log10-scale)
-  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
+  # filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
   # Choose a limited range of sigmaH values

### 2023-06-07 code/get-outputs.R

@@ -243,8 +243,9 @@ if (!exists("cluster")) {
 data.R0 <- as.data.frame(data.Host) %>%
   # filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>%
   filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf,
-                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 21)])) %>% 
-  filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)])
+                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 21)])) %>%
+  filter(KH %in% c(10^seq(-2,5) ,
+                   unique(KH)[seq(1, length(unique(KH)), length.out = 21)]))
 
 # Slice host trait data
 sigmaH_slices <- slice(unique(data.R0$sigmaH), 2)
@@ -279,6 +280,8 @@ for (system_name in unique(data.Vec$system_ID)) {
 
 # Save data
 proper_dim <- dim(data.R0)[1] * length(unique(data.Vec$system_ID)) * length(unique(data.Vec$Temperature))
+
+(dim(R0.df)[1] == proper_dim)
 
 if (exists("R0.df") & dim(R0.df)[1] == proper_dim)
 {write_rds(R0.df, "results/R0_vals.rds", compress = "gz")

### 2023-06-07 manuscript-figures.Rmd

--- 2023-06-07 manuscript-figures.Rmd
@@
 ```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+# !!! [] be sure to use a consistent list of mosquito life history traits:
+#         - adult lifespan (1/mu_V)
+#         - biting frequency (sigma_V)
+#         - eggs per female per day (sigma_V * f)
+#         - immature development rate
+#         - Pr(larval survival) (deltaL)
+#         - Pr(surviving EIP) (theta_V)
+#         - vector competence (beta_V)
 Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%

### 2023-06-08 manuscript-figures.Rmd
fix up figure S1

@@
 R0_df <- data.R0 %>%
-  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
-  rename(R0 = median) %>%
+  select(system_ID, system_label, Temperature, sigmaH, KH, median, mean) %>%
+  rename(R0 = mean) %>%
   # Consider only 3 values of KH (on a log10-scale)
-  # filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
+  filter(KH %in% c(.1, 1, 10)) %>% 
   # Choose a limited range of sigmaH values
-  filter(sigmaH > 10^0.5) %>%
+  # filter(sigmaH > 10^0.5) %>%
   # Group by plotting variables
@@
 R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 3)
-
-# Get the largest value of log10(sigmaH)
-max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
-  select(sigmaH) %>%
-  max() %>%
-  log10()
-
-## Compute mosquito thermal tolerance range (minimum and maximum)
-temp_MosqThermRange_df <- MosqThermRange_df %>%
-  select(system_label, CTmin_V0, CTmax_V0)
 
@@
   geom_hline(
-    data = temp_MosqThermRange_df,
+    data = MosqThermRange_df,
     aes(yintercept = CTmin_V0, colour = "VTTR"),
@@
   geom_hline(
-    data = temp_MosqThermRange_df,
+    data = MosqThermRange_df,
     aes(yintercept = CTmax_V0, colour = "VTTR"),
@@
     expand = c(0, 0),
-    limits = c(14, 36),
+    limits = c(16, 35),
     breaks = seq(10, 36, by = 2)
@@
   facet_rep_grid(
-    rows = vars(system_label),
-    cols = vars(KH),
-    scales = "free_y",
-    labeller = labeller(.cols = mylabels),
+    rows = vars(KH),
+    cols = vars(system_label),
+    labeller = labeller(.rows = mylabels),
     repeat.tick.labels = "left"

### 2023-06-08 code/get-outputs.R

@@ -243,9 +243,9 @@ if (!exists("cluster")) {
 data.R0 <- as.data.frame(data.Host) %>%
   # filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>%
   filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf,
-                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 21)])) %>%
+                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 101)])) %>%
   filter(KH %in% c(10^seq(-2,5) ,
-                   unique(KH)[seq(1, length(unique(KH)), length.out = 21)]))
+                   unique(KH)[seq(1, length(unique(KH)), length.out = 101)]))
 
 # Slice host trait data
 sigmaH_slices <- slice(unique(data.R0$sigmaH), 2)

### 2023-06-08 manuscript-figures.Rmd
update sensitivity
- need to redo R0 sensitivity with updated values after push/pull

@@
 # !!! [] needs to be updated to include 1e-1, 1e0, 1e1
+data.R0_TPCs <- read_ds("results/R0_TPC_vals.rds") %>%
+  pathosystem_labeller()
+
 data.R0 <- read_rds("results/R0_vals.rds") %>%
@@
 #   - colour = value of KH. place it on a color scale in the bottom right corner
-newKH_vals <- unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]
-
-data.R0_norm <- data.R0 %>%
-  filter(KH %in% newKH_vals) %>%
+# newKH_vals <- unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]
+
+data.R0_norm <- data.R0_TPCs %>%
+  # filter(KH %in% newKH_vals) %>%
   filter(variable == "R0") %>%

### 2023-06-08 code/get-outputs.R

@@ -43,11 +43,12 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
 
 thin_size <- 300
 
+data.Vec <- read_rds("results/VecTPC_vals.rds")
 samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
 sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
 
-data.Vec <- read_rds("results/VecTPC_vals.rds") %>% 
+data.Vec <- data.Vec%>% 
   filter(sample_num %in% sample_inds)
 
 
@@ -230,6 +231,62 @@ CT_heat_func <- function(in_df, system_name) {
   return(out_df)
 }
 
+# 1) Set *host* parameters --------------------------------
+
+## Set resolution for host trait variation
+# Host density vector: Number of values to include to consider for vertebrate host density
+KH_vec_length <- 300 # full = 300, thin = 20
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 300 # full = 300, thin = 20
+
+
+## Host life history & behavioral traits
+# Host recruitment rate:
+# upper estimate from range for Primate traits: (0.001150685, 0.009624300)
+lambdaH_baseline <- .005
+
+# Host mortality rate:
+# estimate from range for Primate traits: lifespan (8.6, 60) years
+# muH_vec <- 1 / (365 * c(1, 25))
+muH_baseline <- 1 / (365 * 20)
+
+# Host maximum biting tolerance (mosquitoes bites per day)
+sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
+  c(1, 10, 20, 50, 100, 1000, Inf) %>%
+  unique() %>% sort()
+sigmaH_baseline <- 100
+
+# Host carrying capacity
+KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length) %>%
+  c(10^seq(-2,5)) %>%
+  unique() %>% sort()
+
+## Host-related pathogen parameters
+# Probability of becoming infected after bite from infectious mosquito
+# operates as a scaling parameter
+# betaH_vec <- c(.25, .75)
+betaH_baseline <- 1
+
+# Host recovery rate
+# plausible estimate for infectious period = (2-14 days)
+gammaH_vec <- 1 / c(5, 14)
+gammaH_baseline <- 1 / 5
+
[…]

### 2023-06-08 code/main-analysis.R

@@ -78,6 +78,7 @@ KH_vec_length <- 300 # full = 300, thin = 20
 # Biting tolerance vector: Number of values to consider for biting tolerance
 sigmaH_vec_length <- 300 # full = 300, thin = 20
 
+data.Host <- read_rds("results/Host_vals.rds")
 
 # data.in.params <- read_rds("data/clean/parameter_TPCs.rds")
 # data.in.params <- read_rds("data/clean/parameter_TPCs_thin.rds") # !!! thin

### 2023-06-08 code/sensitivity.R

@@ -54,6 +54,12 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                   lowHCI = c(), highHCI = c(), mean = c(), median = c())
 
 # Load needed datasets
+
+# Host trait dataset
+data.Host <- read_rds("results/Host_vals.rds")
+# Vector trait dataset
+data.Vec <- read_rds("results/VecTPC_vals.rds")
+
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
 # Topt data
@@ -89,15 +95,22 @@ appender_KH <- function(string) {
 ###* Mean traits data frame ----
 
 # Get mean values of uncertain traits
-
-data.Vec <- read_rds("results/VecTPC_vals.rds")
-
 mean.Vec <- data.Vec %>% 
   select(-c(KL, mosquito_species, pathogen, muL, etaL)) %>% 
   pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
   group_by(system_ID, Temperature, variable) %>% 
   summarise(mean = mean(value)) %>% 
   pivot_wider(names_from = "variable", values_from = "mean") %>% 
+  mutate(etaL = rhoL / (deltaL + eps)) %>%
+  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
+  mutate(muL = etaL - rhoL)
+
+median.Vec <- data.Vec %>% 
+  select(-c(KL, mosquito_species, pathogen, muL, etaL)) %>% 
+  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
+  group_by(system_ID, Temperature, variable) %>% 
+  summarise(median = median(value)) %>% 
+  pivot_wider(names_from = "variable", values_from = "median") %>% 
   mutate(etaL = rhoL / (deltaL + eps)) %>%
   # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
   mutate(muL = etaL - rhoL)
@@ -148,8 +161,8 @@ full.R0.HPD <- expand_grid(data.R0HPD,
   mutate(norm_HPD_width = HPD_width / max(HPD_width))
 
 # Save R0 highest posterior density data
-# write_rds(full.R0.HPD, "results/full_R0_HPD.rds")
[…]

### 2023-06-08 code/sensitivity.R
lil fixes

@@ -739,6 +739,12 @@ for (var_name in temp_vars) {
   }
 }
 
+Topt.HPD <- Topt.HPD %>% 
+  ungroup() %>% 
+  distinct() %>% 
+  filter(!is.na(HPD_width))
+
+
 # Save Topt relative highest posterior density data
 write_rds(Topt.HPD, "results/Topt_HPD_sens.rds")
 # Topt.HPD <- read_rds("results/Topt_HPD_sens.rds")
@@ -1208,7 +1214,7 @@ plot.CTmin.rel.sens <- CT.HPD %>%
     system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
     system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
   )) %>%
-  # filter(!is.na(rel_HPD_width)) %>% 
+  filter(!is.na(rel_HPD_width)) %>% 
   # For each KH value, sum up all sensitivity values to get total sensitivity
   group_by(system_ID, sigmaH, KH) %>% 
   mutate(sens_total = sum(rel_HPD_width)) %>% 

### 2023-06-08 code/get-outputs.R
fix up merge

@@ -43,6 +43,7 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
 
 thin_size <- 300
 
+
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
@@ -281,11 +282,11 @@ data.Host <- expand_grid(
   sigmaH = sigmaH_vec,
   # Infection-related parameters
   gammaH = gammaH_baseline,
-  betaH = betaH_baseline
-) %>% as.data.frame() %>%
+  betaH = betaH_baseline) %>%
+  as.data.frame() %>%
   mutate(Model = ifelse(is.infinite(sigmaH), "Ross-Macdonald model", "Chitnis model"))
 
-write_rds(data.Host, "results/Host_vals.rds")
+
 
 # 2) Calculate R0 TPCs -----------------------------------------
 
@@ -299,10 +300,10 @@ if (!exists("cluster")) {
 # Set up host trait data frame (for future visualization)
 data.R0 <- as.data.frame(data.Host) %>%
   # filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf)) %>%
-  filter(sigmaH %in% c(1e-1, 1, 10, 100, Inf,
-                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 101)])) %>%
+  filter(sigmaH %in% c(10^seq(-1,2), Inf,
+                       unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 51)])) %>%
   filter(KH %in% c(10^seq(-2,5) ,
-                   unique(KH)[seq(1, length(unique(KH)), length.out = 101)]))
+                   unique(KH)[seq(1, length(unique(KH)), length.out = 51)]))
 
 # Slice host trait data
 sigmaH_slices <- slice(unique(data.R0$sigmaH), 2)
@@ -347,13 +348,17 @@ proper_dim <- dim(data.R0)[1] * length(unique(data.Vec$system_ID)) * length(uniq
 
 (dim(R0.df)[1] == proper_dim)
 
-if (exists("R0.df") & dim(R0.df)[1] == proper_dim)
-{write_rds(R0.df, "results/R0_vals.rds", compress = "gz")
-} else {
-  warning("No file written. R0.df either empty or not complete.")
-}
+R0_TPCs.df <- R0.df %>% 
[…]

### 2023-06-08 code/get-outputs.R
test

@@ -288,6 +288,7 @@ data.Host <- expand_grid(
 
 
 
+
 # 2) Calculate R0 TPCs -----------------------------------------
 
 # Set up parallel

### 2023-06-09 manuscript-figures.Rmd
lil fixes
use high res Topt values for R0 heatmaps

@@
 # !!! [] needs to be updated to include 1e-1, 1e0, 1e1
-data.R0_TPCs <- read_ds("results/R0_TPC_vals.rds") %>%
+data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
   pathosystem_labeller()
@@
 # Compute *mosquito* thermal tolerance range (minimum and maximum)
-MosqThermRange_df <- median.Vec %>%
+MosqThermRange_df <- mean.Vec %>%
   pathosystem_labeller() %>%
@@
 
+Topt_for_R0_df <- data.Topt %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, sigmaH, KH, median) %>%
+  mutate(sigmaH_proxy = sigmaH)
+Topt_for_R0_df <- inf_skew_func(Topt_for_R0_df, infinite_skew, infinite_divide, 8)
+
 ## PLOTTING ##
@@
 R0_plot <- R0_df %>%
-  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
+  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
   # Mosquito thermal tolerance range lines
@@
     data = MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    mapping = aes(yintercept = CTmin_V0, colour = "VTTR"),
     lwd = 1.275
@@
     data = MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    mapping = aes(yintercept = CTmax_V0, colour = "VTTR"),
     lwd = 1.275
@@
     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
+    mapping = aes(z = R0),
     breaks = fill_breaks
@@
     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
+    mapping = aes(z = R0),
     breaks = fill_breaks
@@
   # R0 = 1 contour:
-  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
+  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
   # Topt curve:
-  geom_line(
-    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
+  geom_path(
+    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)),
     mapping = aes(
       x = sigmaH_proxy,
-      y = Topt,
+      y = median,
       colour = "Topt"
@@
   # theme options:
-  theme_minimal_hgrid() +
+  theme_minimal_hgrid(11) +
   theme(

### 2023-06-09 manuscript-figures.Rmd
fix up CTmin/max heatmap plots

@@
                              TeX("(c) Eggs per female per day: $\\sigma_V f$"),
-                             TeX("(d) Immature development rate: $\\rho_L$"),
+                             TeX("(d) Immature development rate: $\\rho_L$ (day$^{-1}$)"),
                              TeX("(e) Prob. of immature survival: $\\delta_L$"),
@@
     limits = c(10, 40),
-    breaks = seq(10, 40, 2)
+    # breaks = seq(10, 40, 2)
   ) +
@@
 data.R0_norm <- data.R0_TPCs %>%
-  # filter(KH %in% newKH_vals) %>%
+  filter(KH %in% unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]) %>%
   filter(variable == "R0") %>%
@@
   guides(fill = guide_coloursteps(
-    title.position = "top", title.hjust = 0,
-    barwidth = unit(7, "cm"),
+        title.position = "top", 
+        title.hjust = 0.5,
+        barwidth = 12,
         show.limits = TRUE
@@
   guides(fill = guide_coloursteps(
-    title.position = "top", title.hjust = 0.5,
-    barwidth = unit(5, "cm"),
+    title.position = "top", 
+    title.hjust = 0.5,
+    barwidth = 12,#unit(5, "cm"),
     show.limits = TRUE
@@
   # faceting:
-  facet_rep_grid(
+  facet_grid(
     rows = vars(KH),
@@
     labeller = labeller(.rows = mylabels),
-    repeat.tick.labels = "left"
+    # repeat.tick.labels = "left"
   ) +
@@
 ```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'}
-# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
-
-# !!! [] decrease length of color bar
-
 #   x    = biting tolerance (with a point at infinity)
 #   y    = vertebrate host population density
-# colour = CTmin
+# colour = parasite critical thermal minimum (CTmin)
 # Facets = systems
+
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
 
@@
   filter(variable == "CTmin") %>%
-  filter(is.finite(median)) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
@@
   arrange(system_ID, KH, sigmaH_proxy, median) %>%
-  ungroup()
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-max_sigmaH <- max(filter(CTmin_df, is.finite(sigmaH))$sigmaH)
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+  ungroup() %>% 
+  # Assign a value for cases where R0<1 for all temperatures
+  mutate(median_proxy = ifelse(is.finite(median), median, 100))
 
@@
 
-# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
-
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+maxCTmin <- ceiling(max(filter(CTmin_df, is.finite(median))$median))
+
+CTmin_breaks <- c(seq(14,35, by = 2), 101)
 
 CTmin_heat_plots <- CTmin_df %>%
+  select(-median) %>% 
   ## Set up plot ##
@@
   # y = vertebrate host population density,
-  # color = width of parasite thermal mean_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
+  # color = width of parasite thermal median_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
   # CTmin for FINITE sigmaH:
   geom_contour_filled(
-    data = filter(CTmin_df, sigmaH_proxy < 100)
+    data = filter(CTmin_df, 
+                  sigmaH_proxy < 10^2.2),
+    breaks = CTmin_breaks
     ) +
@@
   geom_contour_filled(
-    data = filter(CTmin_df, is.infinite(sigmaH))
+    data = filter(CTmin_df,
+                  sigmaH_proxy > 10^2.4,
+                  sigmaH_proxy < infinite_divide),
+    breaks = CTmin_breaks
     ) +
@@
   ) +
-  # color:
-  scale_fill_viridis_d(
-    name = "Median critical thermal minimum (°C)",
-    option = "plasma"
+  # fill:
+    scale_fill_manual(
+    name = "Critical thermal minimum (°C)",
+    values = c(viridis(9), "grey", "grey"),
+    labels = ~ ifelse(.x < maxCTmin, .x, 'n/a')
   ) +
@@
   guides(fill = guide_coloursteps(
-    title.position = "top", title.hjust = 0.5,
-    barwidth = unit(10, "cm"),
+    title.position = "top",
+    title.hjust = 0.5,
+    barwidth = unit(7, "cm"),
     show.limits = TRUE
@@
 
-# !!! [] decrease length of color bar (the length used in Topt plot might be good)
-
-# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
-
 #   x    = biting tolerance (with a point at infinity)
 #   y    = vertebrate host population density
-# colour = CTmax
+# colour = parasite critical thermal maximum (CTmax)
 # Facets = systems
 
-CTmax_df <- read_rds("results/CT_vals.rds") %>%
-  pathosystem_labeller() %>%
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+CTmax_df <- data.CT %>%
   filter(variable == "CTmax") %>%
-  filter(is.finite(median)) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
@@
   arrange(system_ID, KH, sigmaH_proxy, median) %>%
-  ungroup()
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-max_sigmaH <- max(filter(CTmax_df, is.finite(sigmaH))$sigmaH)
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35 # 10^log10(max_sigmaH*1.5) # 1.1*max_sigmaH #10^2 + 80
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+  ungroup() %>% 
+  # Assign a value for cases where R0<1 for all temperatures
+  mutate(median_proxy = ifelse(is.finite(median), median, -100))
 
@@
 
-# infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
-
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median)))
-max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median)))
-CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1)
+minCTmax <- floor(min(filter(CTmax_df, is.finite(median))$median))
+
+CTmax_breaks <- c(-101, seq(21,35, by = 2))
 
 CTmax_heat_plots <- CTmax_df %>%
+  select(-median) %>% 
   ## Set up plot ##
@@
   # y = vertebrate host population density,
-  # color = CTmax
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
-  # CTmax for FINITE sigmaH:
+  # color = width of parasite thermal median_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
+  # CTmin for FINITE sigmaH:
   geom_contour_filled(
-    data = filter(CTmax_df, sigmaH_proxy < 100)
-  ) +
-  # CTmax for INFINITE sigmaH:
+    data = filter(CTmax_df, 
+                  sigmaH_proxy < 10^2.2),
+    breaks = CTmax_breaks
+    ) +
+  # CTmin for INFINITE sigmaH:
   geom_contour_filled(
-    data = filter(CTmax_df, is.infinite(sigmaH))
+    data = filter(CTmax_df,
+                  sigmaH_proxy > 10^2.4,
+                  sigmaH_proxy < infinite_divide),
+    breaks = CTmax_breaks
     ) +
@@
   ) +
-  # color:
-  scale_fill_viridis_d(
-    name = "Median critical thermal maximum (°C)",
-    option = "plasma"
+  # fill:
+    scale_fill_manual(
+    name = "Critical thermal maximum (°C)",
+    values = c("grey", viridis(9)),
+    labels = ~ ifelse(.x < minCTmax-1, 'n/a', .x)
   ) +

### 2023-06-09 manuscript-figures.Rmd
add "half" violin plots to show CT distributions
- need to get rid of old code for previous figures

@@
 library(lemon)
+library(see) # for half-violin plots
 library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure
@@
     title.hjust = 0.5,
-    barwidth = unit(7, "cm"),
+    barwidth = 12,
     show.limits = TRUE
@@
 plot.densities_violin_inline <- ggplot() +
-  geom_violin(
-    data = filter(all.density.df, variable == "Thermal optimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
-  ) +
-  geom_violin(
-    data = filter(all.density.df, variable == "Critical thermal minimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
-  ) +
-  geom_violin(
-    data = filter(all.density.df, variable == "Critical thermal maximum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
-  ) +
-  scale_x_continuous(
+  # CT min 
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal minimum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 1
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal minimum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 1,
+    flip = TRUE
+  ) +
+  # CT max 
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal maximum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 1
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal maximum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 1,
+    flip = TRUE
+  ) +
+  # Thermal optima
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Thermal optimum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 1
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Thermal optimum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 1,
+    flip = TRUE
+  ) +
+  scale_x_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_y_continuous(
     name = "Temperature (°C)",
     expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
   ) +
@@
     )
-  )
+  ) +
+  coord_flip()
 shift_legend(plot.densities_violin_inline)
-
-### Option 2: inline box and whisker plots ----
-plot.densities_boxwhisker_inline <- ggplot() +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Thermal optimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
-  ) +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Critical thermal minimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
-  ) +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Critical thermal maximum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = "",
-    breaks = c("CTmin", "Topt", "CTmax"),
-    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_boxwhisker_inline)
-
-### Option 3: stacked violin plots ----
-plot.densities_violin_stacked <- ggplot() +
-  geom_violin(
-    data = all.density.df,
-    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = ""
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_violin_stacked)
-
-### Option 4: stacked box and whisker plots ----
-plot.densities_boxwhisker_stacked <- ggplot() +
-  geom_boxplot(
-    data = all.density.df,
-    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = ""
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_boxwhisker_stacked)
 ```
+
+<!-- ### Option 2: inline box and whisker plots ---- -->
+<!-- plot.densities_boxwhisker_inline <- ggplot() + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Thermal optimum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt") -->
+<!--   ) + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Critical thermal minimum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"), -->
+<!--   ) + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Critical thermal maximum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"), -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "", -->
+<!--     breaks = c("CTmin", "Topt", "CTmax"), -->
+<!--     labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum") -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_boxwhisker_inline) -->
+
+<!-- ### Option 3: stacked violin plots ---- -->
+<!-- plot.densities_violin_stacked <- ggplot() + -->
+<!--   geom_violin( -->
+<!--     data = all.density.df, -->
+<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "" -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_violin_stacked) -->
+
+<!-- ### Option 4: stacked box and whisker plots ---- -->
+<!-- plot.densities_boxwhisker_stacked <- ggplot() + -->
+<!--   geom_boxplot( -->
+<!--     data = all.density.df, -->
+<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "" -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 11, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_boxwhisker_stacked) -->
+<!-- ``` -->
 

### 2023-06-14 manuscript-figures.Rmd
minor fixes to figures

--- 2023-06-09 manuscript-figures.Rmd
@@
 # Set theme
-theme_set(theme_minimal(11))
+theme_set(theme_minimal(10))
 
@@
   # y-axis:
-  scale_y_continuous(expand = c(0.05, 0)) +
+  scale_y_continuous(
+    breaks = seq(10, 40, by = 5), 
+    expand = c(0.05, 0)) +
   # color:
@@
   # theme options:
-  theme_minimal_vgrid() +
+  theme_minimal_vgrid(10) +
   theme(
@@
     legend.justification = "center",
-    axis.title.x = element_text(hjust = 0.5),
+    axis.title.x = element_text(hjust = 0),
     strip.text = element_text(
@@
 data.R0_norm <- data.R0_TPCs %>%
-  filter(KH %in% unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]) %>%
+  # filter(KH %in% unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]) %>%
   filter(variable == "R0") %>%
@@
     strip.text = ggtext::element_markdown(
-      size = 11,
+      size = 10,
       hjust = 0,
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^3 + 2500
+infinite_skew <- 10^3 + 3500
 
@@
   `10` = "10 vertebrate hosts / ha"
+))
+
+R0_heatmap_labels <- as_labeller(c(
+        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti*  \nand  DENV",
+      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti*  \nand  ZIKV",
+      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand  DENV",
+      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae*  \nand  *P. falciparum*",
+      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV" 
 ))
@@
     cols = vars(system_label),
-    labeller = labeller(.rows = mylabels),
+    labeller = labeller(.rows = mylabels,
+                        .cols = R0_heatmap_labels),
     # repeat.tick.labels = "left"
@@
     panel.spacing = unit(1, "lines"),
-    legend.text = element_text(size = 11),
+    legend.text = element_text(size = 10),
     legend.text.align = 0,
     strip.text = ggtext::element_markdown(
-      size = 8,
-      hjust = 0
+      size = 7,
+      hjust = 0.5
     )
@@
 
-```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}
+```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}
 
@@
     strip.text = ggtext::element_markdown(
-      size = 11,
+      size = 10,
       hjust = 0
@@
 
-### Option 1: inline violin plots ----
+# half-violin plots
 plot.densities_violin_inline <- ggplot() +
-  geom_violin(
-    data = filter(all.density.df, variable == "Thermal optimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
-  ) +
-  geom_violin(
-    data = filter(all.density.df, variable == "Critical thermal minimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
-  ) +
-  geom_violin(
-    data = filter(all.density.df, variable == "Critical thermal maximum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
-  ) +
-  scale_x_continuous(
+  # CT min 
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal minimum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal minimum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  # CT max 
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal maximum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Critical thermal maximum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  # Thermal optima
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Thermal optimum",
+                  sigmaH == 100),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(all.density.df, variable == "Thermal optimum",
+                  sigmaH == Inf),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  scale_x_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_y_continuous(
     name = "Temperature (°C)",
     expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
   ) +
@@
   ) +
-  facet_wrap(~system_label, labeller = labeller()) +
+  facet_wrap(~system_label, labeller = labeller(), scales = "free") +
   theme_minimal_grid() +
@@
     )
-  )
+  ) +
+  coord_flip()
 shift_legend(plot.densities_violin_inline)
-
-### Option 2: inline box and whisker plots ----
-plot.densities_boxwhisker_inline <- ggplot() +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Thermal optimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
-  ) +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Critical thermal minimum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
-  ) +
-  geom_boxplot(
-    data = filter(all.density.df, variable == "Critical thermal maximum"),
-    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = "",
-    breaks = c("CTmin", "Topt", "CTmax"),
-    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_boxwhisker_inline)
-
-### Option 3: stacked violin plots ----
-plot.densities_violin_stacked <- ggplot() +
-  geom_violin(
-    data = all.density.df,
-    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = ""
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_violin_stacked)
-
-### Option 4: stacked box and whisker plots ----
-plot.densities_boxwhisker_stacked <- ggplot() +
-  geom_boxplot(
-    data = all.density.df,
-    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
-  ) +
-  scale_x_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_y_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = ""
-  ) +
-  facet_wrap(~system_label, labeller = labeller()) +
-  theme_minimal_grid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 11,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.densities_boxwhisker_stacked)
 ```
+
+<!-- ### Option 2: inline box and whisker plots ---- -->
+<!-- plot.densities_boxwhisker_inline <- ggplot() + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Thermal optimum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt") -->
+<!--   ) + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Critical thermal minimum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"), -->
+<!--   ) + -->
+<!--   geom_boxplot( -->
+<!--     data = filter(all.density.df, variable == "Critical thermal maximum"), -->
+<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"), -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "", -->
+<!--     breaks = c("CTmin", "Topt", "CTmax"), -->
+<!--     labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum") -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 10, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_boxwhisker_inline) -->
+
+<!-- ### Option 3: stacked violin plots ---- -->
+<!-- plot.densities_violin_stacked <- ggplot() + -->
+<!--   geom_violin( -->
+<!--     data = all.density.df, -->
+<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "" -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 10, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_violin_stacked) -->
+
+<!-- ### Option 4: stacked box and whisker plots ---- -->
+<!-- plot.densities_boxwhisker_stacked <- ggplot() + -->
+<!--   geom_boxplot( -->
+<!--     data = all.density.df, -->
+<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
+<!--   ) + -->
+<!--   scale_x_continuous( -->
+<!--     name = "Temperature (°C)", -->
+<!--     expand = c(0, 0) -->
+<!--   ) + -->
+<!--   scale_y_discrete( -->
+<!--     name = "Vertebrate host population density (ind/ha)" -->
+<!--   ) + -->
+<!--   scale_linetype( -->
+<!--     name = "Biting tolerance\n(bites per host per day)" -->
+<!--   ) + -->
+<!--   scale_fill_discrete( -->
+<!--     name = "" -->
+<!--   ) + -->
+<!--   facet_wrap(~system_label, labeller = labeller()) + -->
+<!--   theme_minimal_grid() + -->
+<!--   theme( -->
+<!--     legend.margin = margin(0, 0, 0, 0), -->
+<!--     legend.title = element_text(size = 10), -->
+<!--     axis.title.x = element_text(hjust = 0.5), -->
+<!--     strip.text = ggtext::element_markdown( -->
+<!--       size = 10, -->
+<!--       hjust = 0, -->
+<!--       padding = margin(0, 0, 0, 0), -->
+<!--       margin = margin(1, 1, 1, 1) -->
+<!--     ) -->
+<!--   ) -->
+<!-- shift_legend(plot.densities_boxwhisker_stacked) -->
+<!-- ``` -->
 
@@
     strip.text.x = ggtext::element_markdown(
-      size = 11,
+      size = 10,
       hjust = 0,

### 2023-06-15 manuscript-figures.Rmd
small fixes to figures

@@
 data.R0_norm <- data.R0_TPCs %>%
-  # filter(KH %in% unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]) %>%
+  filter(KH %in% unique(data.R0_TPCs$KH)[seq(1, length(unique(data.R0_TPCs$KH)), length.out = 21)]) %>%
   filter(variable == "R0") %>%
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^3 + 3500
+infinite_skew <- 10^4
 
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
+infinite_divide <- 10^3.5
 
@@
     legend.text.align = 0,
-    strip.text = ggtext::element_markdown(
+    strip.text.y = ggtext::element_markdown(
       size = 7,
-      hjust = 0.5
-    )
+      hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 7,
+      hjust = 0),
+    panel.spacing = unit(2, "pt")
     )
@@
 Topt_df <- data.Topt %>%
+  filter(KH < 10^4 + 1) %>% 
   pivot_wider(id_cols = c("system_label", "Model", "sigmaH", "KH"),
@@
     expand = c(0, 0),
-    limits = c(0.01, 2E4),
-    breaks = 10^seq(-2, 4),
-    labels = TeX(c(
-      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
-    ))
+    # limits = c(0.5, 150),
+    breaks = c(10^c(seq(-1, 4, by = 1))),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
     ) +
@@
 sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15*infinite_divide, infinite_skew)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))
 
@@
     name = expression("Thermal optimum "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = c(21,31), # mean: 21-31, median: 21-32
+    expand = c(0,0), # c(0.05, 0.05),
+    limits = c(21,30), # mean: 21-31, median: 21-32
     breaks = seq(21,32, by = 1)
@@
 
-# !!! [] just compare "low host availability (sigmaH = 50, KH = 1 or 10)" and
-#        "high host availability (sigmaH = Inf, KH = 100)" scenarios
-# !!! [] put legend at bottom of plot
 # !!! [] change factor/levels for focal_var so that they show up in the same
 #        order as in the legend
+# !!! [] figure out what's going on with the "color" bars occuring at low temperatures for plots (a) (b) and (e)
 
@@
 plot.R0.rel.sens <- R0.HPD %>%
-  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
-  filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
+  # filter(!(KH == 100 & sigmaH == Inf)) %>%
   filter(rel_HPD_width != 0) %>%
@@
   scale_x_continuous(
-    limits = Temp_range_for_plot,
+    # limits = Temp_range_for_plot,
     expand = c(0, 0)
@@
     ),
-    scales = "free_y"
-  ) +
-  theme_minimal_hgrid() +
+    scales = "free"
+  ) +
+  theme_minimal() +
   theme(
@@
   )
+
+# shift_legend(plot.R0.rel.sens)
 plot.R0.rel.sens
-# shift_legend(plot.R0.rel.sens)
+
 ```
@@
 plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
-  filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
+  # filter(!(KH == 100 & sigmaH == Inf)) %>%
   filter(rel_HPD_width != 0) %>%
@@
       margin = margin(1, 1, 1, 1)
-    )
+    ),
+    panel.spacing.x = unit(2, "lines")
   )
@@
   filter(variable == "CTmin") %>%
+  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
 
-```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(variable == "CTmax") %>%
+  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
   filter(variable == "CTwidth") %>%
+  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%

### 2023-06-16 manuscript-figures.Rmd
update sensitivity values & plots

@@
 library(viridis)
-library(RColorBrewer)
-library(MetBrewer)
+library(RColorBrewer) # for colorblind friendly color palettes
+library(MetBrewer) # for colorblind friendly color palettes
+library(cols4all) # for colorblind friendly color palettes
 library(here)
@@
   ungroup() %>%
-  pathosystem_labeller()
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  ))
+
+ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
+  ungroup() %>%
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  ))
 
@@
   ungroup() %>%
-  pathosystem_labeller()
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  ))
 
@@
   # y-axis:
-  scale_y_continuous(
-    breaks = seq(10, 40, by = 5), 
-    expand = c(0.05, 0)) +
+  scale_y_continuous(expand = c(0.05, 0)) +
   # color:
@@
     axis.line = element_line(),
-    panel.spacing = unit(1, "lines"),
     legend.text = element_text(size = 10),
@@
   ungroup() %>%
-  pathosystem_labeller()
+  pathosystem_labeller() %>% 
+  filter(KH > 0.01)
 
@@
   ) +
-  facet_wrap(~system_label, labeller = labeller(), scales = "free") +
+  facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
   theme_minimal_grid() +
@@
 
-<!-- ### Option 2: inline box and whisker plots ---- -->
-<!-- plot.densities_boxwhisker_inline <- ggplot() + -->
-<!--   geom_boxplot( -->
-<!--     data = filter(all.density.df, variable == "Thermal optimum"), -->
-<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt") -->
-<!--   ) + -->
-<!--   geom_boxplot( -->
-<!--     data = filter(all.density.df, variable == "Critical thermal minimum"), -->
-<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"), -->
-<!--   ) + -->
-<!--   geom_boxplot( -->
-<!--     data = filter(all.density.df, variable == "Critical thermal maximum"), -->
-<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"), -->
-<!--   ) + -->
-<!--   scale_x_continuous( -->
-<!--     name = "Temperature (°C)", -->
-<!--     expand = c(0, 0) -->
-<!--   ) + -->
-<!--   scale_y_discrete( -->
-<!--     name = "Vertebrate host population density (ind/ha)" -->
-<!--   ) + -->
-<!--   scale_linetype( -->
-<!--     name = "Biting tolerance\n(bites per host per day)" -->
-<!--   ) + -->
-<!--   scale_fill_discrete( -->
-<!--     name = "", -->
-<!--     breaks = c("CTmin", "Topt", "CTmax"), -->
-<!--     labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum") -->
-<!--   ) + -->
-<!--   facet_wrap(~system_label, labeller = labeller()) + -->
-<!--   theme_minimal_grid() + -->
-<!--   theme( -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 10, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-<!-- shift_legend(plot.densities_boxwhisker_inline) -->
-
-<!-- ### Option 3: stacked violin plots ---- -->
-<!-- plot.densities_violin_stacked <- ggplot() + -->
-<!--   geom_violin( -->
-<!--     data = all.density.df, -->
-<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
-<!--   ) + -->
-<!--   scale_x_continuous( -->
-<!--     name = "Temperature (°C)", -->
-<!--     expand = c(0, 0) -->
-<!--   ) + -->
-<!--   scale_y_discrete( -->
-<!--     name = "Vertebrate host population density (ind/ha)" -->
-<!--   ) + -->
-<!--   scale_linetype( -->
-<!--     name = "Biting tolerance\n(bites per host per day)" -->
-<!--   ) + -->
-<!--   scale_fill_discrete( -->
-<!--     name = "" -->
-<!--   ) + -->
-<!--   facet_wrap(~system_label, labeller = labeller()) + -->
-<!--   theme_minimal_grid() + -->
-<!--   theme( -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 10, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-<!-- shift_legend(plot.densities_violin_stacked) -->
-
-<!-- ### Option 4: stacked box and whisker plots ---- -->
-<!-- plot.densities_boxwhisker_stacked <- ggplot() + -->
-<!--   geom_boxplot( -->
-<!--     data = all.density.df, -->
-<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
-<!--   ) + -->
-<!--   scale_x_continuous( -->
-<!--     name = "Temperature (°C)", -->
-<!--     expand = c(0, 0) -->
-<!--   ) + -->
-<!--   scale_y_discrete( -->
-<!--     name = "Vertebrate host population density (ind/ha)" -->
-<!--   ) + -->
-<!--   scale_linetype( -->
-<!--     name = "Biting tolerance\n(bites per host per day)" -->
-<!--   ) + -->
-<!--   scale_fill_discrete( -->
-<!--     name = "" -->
-<!--   ) + -->
-<!--   facet_wrap(~system_label, labeller = labeller()) + -->
-<!--   theme_minimal_grid() + -->
-<!--   theme( -->
-<!--     legend.margin = margin(0, 0, 0, 0), -->
-<!--     legend.title = element_text(size = 10), -->
-<!--     axis.title.x = element_text(hjust = 0.5), -->
-<!--     strip.text = ggtext::element_markdown( -->
-<!--       size = 10, -->
-<!--       hjust = 0, -->
-<!--       padding = margin(0, 0, 0, 0), -->
-<!--       margin = margin(1, 1, 1, 1) -->
-<!--     ) -->
-<!--   ) -->
-<!-- shift_legend(plot.densities_boxwhisker_stacked) -->
-<!-- ``` -->
-
 ```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
@@
   dplyr::filter(rel_HPD_width > eps) %>%
-  select(Temperature) %>%
+  dplyr::select(Temperature) %>%
   range()
@@
 plot.R0.rel.sens <- R0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
+  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
@@
   arrange(sens_rel) %>%
+  arrange(focal_var) %>% 
   # Make a stacked plot, colored by parameter
@@
   geom_area() +
-  scale_fill_discrete(
+  scale_fill_manual(
     name = "Focal trait:",
-    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-    labels = c(
-      "Adult lifespan", "Biting frequency", "Eggs per female per day",
-      "Immature development rate", "Prob. of immature survival",
-      "Prob. of surviving EIP", "Vector competence")
+    values = rev(c4a("misc.okabe", 7))
   ) +
@@
 
-ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
-  ungroup() %>%
-  pathosystem_labeller()
-
 ## Plot R0 uncertainty
@@
 
-var_name_table <- list(
-  betaV = c(TeX("$\\beta_V$")),
-  deltaL = c(TeX("$\\delta_L$")),
-  etaV = c(TeX("$\\eta_V$")),
-  muV = c(TeX("$\\mu_V$")),
-  rhoL = c(TeX("$\\rho_L$")),
-  sigmaV = c(TeX("$\\sigma_V$")),
-  sigmaV_f = c(TeX("$\\sigma_v f$"))
-)
-
 plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
+  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
@@
   geom_area() +
-  scale_fill_discrete(
-    name = "Focal trait",
-    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-    labels = c(
-      "Adult lifespan", "Biting frequency", "Eggs per female per day",
-      "Immature development rate", "Prob. of immature survival",
-      "Prob. of surviving EIP", "Vector competence")
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
   ) +
   scale_x_continuous(
-    limits = Temp_range_for_plot,
+    # limits = Temp_range_for_plot,
     expand = c(0, 0)
@@
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $dR_0/dT$ HPD width"))
+    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
   ) +
@@
   )
+
+# shift_legend(plot.R0.rel.sens)
 plot.ddTR0.rel.sens
+
 ```
+
 ```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
@@
 #         - vector competence (beta_V)
-Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
+Topt.HPD <- Topt.HPD %>% 
   ungroup() %>%
@@
   geom_area() +
-  scale_fill_discrete(
-    name = "Focal trait",
-    breaks = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-    labels = c(
-      "Adult lifespan", "Biting frequency", "Eggs per female per day",
-      "Immature development rate", "Prob. of immature survival",
-      "Prob. of surviving EIP", "Vector competence")
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
   ) +
@@
     ),
-    panel.spacing.x = unit(2, "lines")
+    panel.spacing.x = unit(1, "lines")
   )
@@
   filter(variable == "CTmin") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
+  filter(sigmaH %in% c(100, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
   filter(variable == "CTmax") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
+  filter(sigmaH %in% c(100, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
 
-```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(variable == "CTwidth") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
+  filter(sigmaH %in% c(100, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
   # For each KH value, sum up all sensitivity values to get total sensitivity
-  group_by(system_ID, sigmaH, KH) %>%
+  group_by(system_ID, sigmaH, KH) %>%W
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each sensitivity value by the total sensitiviWty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%

### 2023-06-16 code/sensitivity.R

@@ -128,8 +128,8 @@ median.Vec <- data.Vec %>%
 
 # Calculate the width of the 95% HPD for the full posterior of R0 across temperatures
 
-sigmaH_vec <- c(50, Inf)#unique(data.Host$sigmaH)
-KH_vec <- 10^seq(-2,5)
+sigmaH_vec <- c(100, Inf)#unique(data.Host$sigmaH)
+KH_vec <- 10^seq(-2,4)
 
 data.R0HPD <- dplyr::filter(data.Host,
                             sigmaH %in% sigmaH_vec,
@@ -164,33 +164,33 @@ full.R0.HPD <- expand_grid(data.R0HPD,
 write_rds(full.R0.HPD, "results/full_R0_HPD.rds")
 # full.R0.HPD <- read_rds("results/full_R0_HPD.rds")
 
-# R0 HPD diagnostic plot
-R0.HPD.plot <- full.R0.HPD %>%
-  # dplyr::filter(KH %in% c(1,100)) %>%
-  arrange(system_ID, sigmaH) %>% 
-  # dplyr::filter(is.finite(sigmaH)) %>%
-  ggplot(aes(x = Temperature, y = norm_HPD_width, color = as.factor(KH))) +
-  geom_path(lwd = 1) +
-  scale_color_viridis_d(
-    name = "Vertebrate host population\ndensity (ind/ha)",
-    breaks = 10^seq(-2, 4),
-    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
-    limits = 10^seq(-2, 4)
-  ) +
-  scale_y_continuous(name = "Normalized HPD width") +
-  facet_grid(rows = vars(system_ID), cols =vars(sigmaH),
-             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
-                                                      default = label_parsed),
-                                 KH = as_labeller(appender_KH, 
-                                                  default = label_parsed)),
-             scales = "free") +
-  theme_minimal(16)
-R0.HPD.plot
-
-# Save full R0 highest posterior density data
-ggsave("figures/results/R0_HPD.svg", 
-       plot = R0.HPD.plot,
-       width = 16, height = 9)
+# # R0 HPD diagnostic plot
+# R0.HPD.plot <- full.R0.HPD %>%
+#   # dplyr::filter(KH %in% c(1,100)) %>%
[…]

### 2023-06-16 manuscript-figures.Rmd
final(?) figure edits

@@
   # Choose a limited range of sigmaH values
-  # filter(sigmaH > 10^0.5) %>%
+  filter(sigmaH < 10^2.275 | is.infinite(sigmaH)) %>%
   # Group by plotting variables
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^4
+infinite_skew <- 10^2.75
 
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^3.5
-
-R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 3)
+infinite_divide <- 10^2.4
+
+R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 8)
 
@@
 # Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+sigmaH_breaks_heatmap <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, infinite_skew)
+sigmaH_labels_heatmap <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
 
@@
     data = MosqThermRange_df,
-    mapping = aes(yintercept = CTmin_V0, colour = "VTTR"),
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
     lwd = 1.275
@@
     data = MosqThermRange_df,
-    mapping = aes(yintercept = CTmax_V0, colour = "VTTR"),
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
     lwd = 1.275
@@
   geom_path(
-    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)),
+    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
     mapping = aes(
@@
     name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels,
+    breaks = sigmaH_breaks_heatmap,
+    labels = sigmaH_labels_heatmap,
     expand = c(0, 0)
@@
 
-# !!! [] be sure to use a consistent list of mosquito life history traits:
-#         - adult lifespan (1/mu_V)
-#         - biting frequency (sigma_V)
-#         - eggs per female per day (sigma_V * f)
-#         - immature development rate
-#         - Pr(larval survival) (deltaL)
-#         - Pr(surviving EIP) (theta_V)
-#         - vector competence (beta_V)
 Topt.HPD <- Topt.HPD %>% 
@@
   # For each KH value, sum up all sensitivity values to get total sensitivity
-  group_by(system_ID, sigmaH, KH) %>%W
+  group_by(system_ID, sigmaH, KH) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%

### 2023-06-16 code/sensitivity.R

@@ -864,11 +864,13 @@ plot.Topt.rel.sens
 # Calculate the width of the 95% HPD for the full posterior of Topt across vertebrate host abundance
 
 sigmaH_vec <- c(10, 100, Inf)
-KH_vec <- 10^seq(-2,4)
+KH_vec <- 10^seq(-2, 4, length.out = 601)
 
-data.CTHPD <- dplyr::filter(data.Host, 
-                            sigmaH %in% sigmaH_vec,
-                            KH < 1e4) #%>% 
+data.CTHPD <- dplyr::filter(data.Host, sigmaH %in% sigmaH_vec) %>% 
+  select(-KH) %>% 
+  full_join(as_tibble(list(KH = KH_vec)), by = character()) %>% 
+  distinct()
+
 #dplyr::filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 11)])
 
 full.CT.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),

### 2023-06-16 manuscript-figures.Rmd
fix some figure labels

--- 2023-06-15 manuscript-figures.Rmd
@@
 data.R0_norm <- data.R0_TPCs %>%
-  filter(KH %in% unique(data.R0_TPCs$KH)[seq(1, length(unique(data.R0_TPCs$KH)), length.out = 21)]) %>%
+  # filter(KH %in% unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]) %>%
   filter(variable == "R0") %>%
@@
 # Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^4
+infinite_skew <- 10^3 + 3500
 
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^3.5
+infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
 
@@
     legend.text.align = 0,
-    strip.text.y = ggtext::element_markdown(
+    strip.text = ggtext::element_markdown(
       size = 7,
-      hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 7,
-      hjust = 0),
-    panel.spacing = unit(2, "pt")
+      hjust = 0.5
+    )
   )
@@
 Topt_df <- data.Topt %>%
-  filter(KH < 10^4 + 1) %>% 
   pivot_wider(id_cols = c("system_label", "Model", "sigmaH", "KH"),
@@
     expand = c(0, 0),
-    # limits = c(0.5, 150),
-    breaks = c(10^c(seq(-1, 4, by = 1))),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+    limits = c(0.01, 2E4),
+    breaks = 10^seq(-2, 4),
+    labels = TeX(c(
+      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
+    ))
   ) +
@@
 sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15*infinite_divide, infinite_skew)
-sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
 
@@
     name = expression("Thermal optimum "(degree * C)),
-    expand = c(0,0), # c(0.05, 0.05),
-    limits = c(21,30), # mean: 21-31, median: 21-32
+    expand = c(0.05, 0.05),
+    limits = c(21,31), # mean: 21-31, median: 21-32
     breaks = seq(21,32, by = 1)
@@
 
+# !!! [] just compare "low host availability (sigmaH = 50, KH = 1 or 10)" and
+#        "high host availability (sigmaH = Inf, KH = 100)" scenarios
+# !!! [] put legend at bottom of plot
 # !!! [] change factor/levels for focal_var so that they show up in the same
 #        order as in the legend
-# !!! [] figure out what's going on with the "color" bars occuring at low temperatures for plots (a) (b) and (e)
 
@@
 
+sens_labels <- as_labeller(c(
+        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
+      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
+      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus* and  \nDENV",
+      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
+      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV" 
+))
+
 plot.R0.rel.sens <- R0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
-  # filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
+  filter(!(KH == 100 & sigmaH == Inf)) %>%
   filter(rel_HPD_width != 0) %>%
@@
   scale_x_continuous(
-    # limits = Temp_range_for_plot,
+    limits = Temp_range_for_plot,
     expand = c(0, 0)
@@
     labeller = labeller(
-      system_label = label_wrap_gen(width = 10),
+      system_label = sens_labels,
       sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
@@
     ),
-    scales = "free"
-  ) +
-  theme_minimal() +
+    scales = "free_y"
+  ) +
+    facet_grid(
+    rows = vars(KH),
+    cols = vars(system_label),
+    labeller = labeller(.rows = mylabels,
+                        .cols = R0_heatmap_labels),
+    # repeat.tick.labels = "left"
+  ) +
+  theme_minimal_hgrid() +
   theme(
@@
   )
-
+plot.R0.rel.sens
 # shift_legend(plot.R0.rel.sens)
-plot.R0.rel.sens
-
 ```
@@
 plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(50, Inf)) %>%
-  # filter(!(KH == 100 & sigmaH == Inf)) %>%
+  filter(KH %in% c(1, 100) & sigmaH %in% c(50, Inf)) %>%
+  filter(!(KH == 100 & sigmaH == Inf)) %>%
   filter(rel_HPD_width != 0) %>%
@@
       margin = margin(1, 1, 1, 1)
-    ),
-    panel.spacing.x = unit(2, "lines")
+    )
   )
@@
   filter(variable == "CTmin") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
 
-```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(variable == "CTmax") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%
@@
   filter(variable == "CTwidth") %>%
-  filter(sigmaH %in% c(10, Inf)) %>% 
   filter(!is.na(rel_HPD_width)) %>%

### 2023-06-16 manuscript-figures.Rmd

--- 2023-06-16 manuscript-figures.Rmd
@@
 
+sens_labels <- as_labeller(c(
+        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
+      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
+      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus* and  \nDENV",
+      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
+      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
+))
+
 plot.R0.rel.sens <- R0.HPD %>%
@@
   ) +
-  theme_minimal() +
+    facet_grid(
+    rows = vars(KH),
+    cols = vars(system_label),
+    labeller = labeller(.rows = mylabels,
+                        .cols = R0_heatmap_labels),
+    # repeat.tick.labels = "left"
+  ) +
+  theme_minimal_hgrid() +
   theme(

### 2023-06-16 manuscript-figures.Rmd
increase resolution of sensitivity analysis

--- 2023-06-16 manuscript-figures.Rmd
@@
 
+sens_labels <- as_labeller(c(
+        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
+      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
+      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand DENV",
+      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
+      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
+))
+
 plot.R0.rel.sens <- R0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
+  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
@@
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
+    name = unname(TeX("Relative contribution to $ddTR_0$ HPD width"))
   ) +
@@
   facet_wrap(~system_label, scales = "free") +
-  theme_minimal_hgrid() +
+  theme_minimal() +
   theme(
@@
       margin = margin(1, 1, 1, 1)
-    ),
-    panel.spacing.x = unit(1, "lines")
+    )
   )
@@
 
-plot.CTmin.rel.sens <- CT.HPD %>%
+CTmin_df <- CT.HPD %>%
   filter(variable == "CTmin") %>%
-  filter(sigmaH %in% c(100, Inf)) %>% 
+  filter(sigmaH %in% c(10, Inf)) %>%
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) #%>%
+
+  # Make a stacked plot, colored by parameter
+plot.CTmin.rel.sens <- CTmin_df %>% 
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
+  ) +
+  facet_grid(
+    cols = vars(system_label),
+    rows = vars(sigmaH),
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    legend.position = "bottom",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    ),
+    panel.spacing.x = unit(2, "lines")
+  )
+plot.CTmin.rel.sens
+```
+
+```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+
+plot.CTmax.rel.sens <- CT.HPD %>%
+  filter(variable == "CTmax") %>%
+  filter(sigmaH %in% c(10, Inf)) %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
     expand = c(0, 0),
-    limits = c(0.05, 1E3),
     breaks = 10^seq(-2, 4, 1),
@@
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
-  ) +
-  facet_grid(cols = vars(system_label),
+    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
+  ) +
+  facet_grid(
+    cols = vars(system_label),
     rows = vars(sigmaH),
-             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
-                                                      default = label_parsed)),
-             scales = "free") +
-  theme_minimal_hgrid() +
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  theme_minimal() +
   theme(
@@
     ),
-    panel.spacing.x = unit(1, "lines")
-  )
-plot.CTmin.rel.sens
+    panel.spacing.x = unit(2, "lines")
+  )
+plot.CTmax.rel.sens
 ```
 
-```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
-
-plot.CTmax.rel.sens <- CT.HPD %>%
-  filter(variable == "CTmax") %>%
-  filter(sigmaH %in% c(100, Inf)) %>% 
+```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+
+plot.CTwidth.rel.sens <- CT.HPD %>%
+  filter(variable == "CTwidth") %>%
+  filter(sigmaH %in% c(10, Inf)) %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each sensitivity value by the total sensitiviWty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%
@@
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
-  ) +
-  facet_grid(cols = vars(system_label),
+    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
+  ) +
+  facet_grid(
+    cols = vars(system_label),
     rows = vars(sigmaH),
-             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
-                                                      default = label_parsed)),
-             scales = "free") +
-  theme_minimal_hgrid() +
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  theme_minimal() +
   theme(
@@
     ),
-    panel.spacing.x = unit(1, "lines")
-  )
-plot.CTmax.rel.sens
-```
-
-```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
-
-plot.CTwidth.rel.sens <- CT.HPD %>%
-  filter(variable == "CTwidth") %>%
-  filter(sigmaH %in% c(100, Inf)) %>% 
-  filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity
-  group_by(system_ID, sigmaH, KH) %>%
-  mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitiviWty
-  mutate(sens_rel = rel_HPD_width / sens_total) %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
-  geom_area() +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.05, 1E3),
-    breaks = 10^seq(-2, 4, 1),
-    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  scale_y_continuous(
-    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
-  ) +
-  facet_grid(cols = vars(system_label),
-             rows = vars(sigmaH),
-             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
-                                                      default = label_parsed)),
-             scales = "free") +
-  theme_minimal_hgrid() +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
-    legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    ),
-    panel.spacing.x = unit(1, "lines")
+    panel.spacing.x = unit(2, "lines")
   )

### 2023-06-16 code/sensitivity.R

@@ -128,7 +128,7 @@ median.Vec <- data.Vec %>%
 
 # Calculate the width of the 95% HPD for the full posterior of R0 across temperatures
 
-sigmaH_vec <- c(100, Inf)#unique(data.Host$sigmaH)
+sigmaH_vec <- c(10, 100, Inf)#unique(data.Host$sigmaH)
 KH_vec <- 10^seq(-2,4)
 
 data.R0HPD <- dplyr::filter(data.Host,
@@ -917,7 +917,7 @@ for (index_KH in unique(data.CTHPD$KH)) {
     summarise(
       HPD_low = hdi(value, credMass = 0.95)[1],
       HPD_high = hdi(value, credMass = 0.95)[2],
-      HPD_width = HPD_high-HPD_low,
+      HPD_width = max(eps, HPD_high-HPD_low),
       .groups = "keep"
     ) %>% 
     rbind(full.CT.HPD)
@@ -1022,7 +1022,7 @@ for (var_name in temp_vars) {
       summarise(
         HPD_low = hdi(value, credMass = 0.95)[1],
         HPD_high = hdi(value, credMass = 0.95)[2],
-        HPD_width = HPD_high-HPD_low,
+        HPD_width = max(eps, HPD_high-HPD_low),
         .groups = "keep"
       ) %>% 
       select(system_ID, sigmaH, KH, variable, HPD_width) %>% 

### 2023-06-16 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 appender_sigmaH <- function(string) {
-  unname(TeX(paste("$\\sigma_H = $", string)))
+  ifelse(string == "Inf", 
+         unname(TeX(paste("$\\sigma_H = \\infty$"))),
+         unname(TeX(paste("$\\sigma_H = $", string))))
 }
@@
 }
+
+sens_labels <- as_labeller(c(
+        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
+      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
+      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand DENV",
+      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
+      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
+))
 
@@
       "Topt" = "Transmission\nthermal\noptimum",
-      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
+      "VTTR" = "Mosquito\npopulation\nthermal\nniche"
     ),
@@
     breaks = c("CTmax", "CTmin", "VTTR"),
-    labels = c("Critical maximum", "Critical minimum", "Mosquito thermal\ntolerance range"),
+    labels = c("Critical maximum", "Critical minimum", "Mosquito population\nthermal niche"),
     values = c("red", "blue", "grey"),
@@
   range()
-
-sens_labels <- as_labeller(c(
-        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
-      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
-      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand DENV",
-      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
-      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
-))
 
@@
       system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      KH = as_labeller(appender_KH, default = label_parsed)
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
     ),
@@
   ungroup() %>%
+  distinct() %>% 
+  filter(!is.na(HPD_width)) %>% 
   pathosystem_labeller() %>%
@@
   # ) +
-  facet_wrap(~system_label, scales = "free") +
+  facet_wrap(~system_label) +
   theme_minimal() +
@@
   filter(variable == "CTmin") %>%
-  filter(sigmaH %in% c(10, Inf)) %>%
+  filter(sigmaH %in% c(100, Inf)) %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
       sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
-    ),
-    scales = "free"
+    )
   ) +
@@
     strip.text.x = ggtext::element_markdown(
-      size = 10,
+      size = 8,
       hjust = 0,
@@
   filter(variable == "CTmax") %>%
-  filter(sigmaH %in% c(10, Inf)) %>%
+  filter(sigmaH %in% c(100, Inf)) %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
   filter(variable == "CTwidth") %>%
-  filter(sigmaH %in% c(10, Inf)) %>%
+  filter(sigmaH %in% c(100, Inf)) %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
       system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
-    ),
-    scales = "free"
+      sigmaH = as_labeller(
+        appender_sigmaH, default = label_parsed)
+    )
   ) +

### 2023-06-16 code/sensitivity.R
update Topt values using more TPC samples

@@ -58,7 +58,7 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
 # Host trait dataset
 data.Host <- read_rds("results/Host_vals.rds")
 # Vector trait dataset
-data.Vec <- read_rds("results/VecTPC_vals.rds")
+# data.Vec <- read_rds("results/VecTPC_vals.rds")
 
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
@@ -738,7 +738,7 @@ for (var_name in temp_vars) {
       mutate(focal_var = var_name) %>% 
       group_by(system_ID, sigmaH, KH, focal_var) %>% 
       # d) Normalize HPD width by the full HPD width when all parameters are allowed to vary
-      mutate(rel_HPD_width = ifelse(full_HPD_width %in% c(0,eps), 0, HPD_width / full_HPD_width))
+      mutate(rel_HPD_width = ifelse(full_HPD_width < 1.1 * eps, 0, HPD_width / full_HPD_width))
     
     Topt.HPD <- rbind(Topt.HPD, temp_df)
   }
@@ -1034,7 +1034,7 @@ for (var_name in temp_vars) {
       mutate(focal_var = var_name) %>% 
       group_by(system_ID, sigmaH, KH, focal_var) %>% 
       # d) Normalize HPD width by the full HPD width when all parameters are allowed to vary
-      mutate(rel_HPD_width = ifelse(full_HPD_width %in% c(0,eps), 0, HPD_width / full_HPD_width))
+      mutate(rel_HPD_width = ifelse(full_HPD_width < 1.1 * eps, 0, HPD_width / full_HPD_width))
     
     CT.HPD <- rbind(CT.HPD, temp_df)
   }

### 2023-06-16 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
 host_density_range <- c(1E-1, 1E2)
-host_fixed_value <- 50
+host_fixed_value <- 10
 host_density_vec <- sort(c(seq(host_density_range[1], host_density_range[2],
@@
 vector_density_range <- c(0, 1E3)
-vector_fixed_value <- 500
+vector_fixed_value <- 1000
 vector_density_vec <- sort(c(seq(vector_density_range[1], vector_density_range[2],
@@
 
-host_annoyance_threshold <- 50
+host_annoyance_threshold <- 100
 sigma_H <- host_annoyance_threshold
@@
   # x-axis:
-  scale_x_continuous(
+  scale_x_log10(
     name = "",
@@
   # x-axis:
-  scale_x_continuous(
+  scale_x_log10(
     name = "Mosquito population density",
@@
   # x-axis:
-  scale_x_continuous(
+  scale_x_log10(
     name = "Host population density",

### 2023-06-16 manuscript-figures.Rmd
try to salvage sensitivity analysis...

@@
 host_fixed_value <- 10
-host_density_vec <- sort(c(seq(host_density_range[1], host_density_range[2],
+host_density_vec <- sort(c(10^seq(log10(host_density_range[1]), 
+                                  log10(host_density_range[2]),
                                   length.out = resolution
@@
 
-vector_density_range <- c(0, 1E3)
+vector_density_range <- c(1, 1E3)
 vector_fixed_value <- 1000
-vector_density_vec <- sort(c(seq(vector_density_range[1], vector_density_range[2],
+vector_density_vec <- sort(c(10^seq(log10(vector_density_range[1]), 
+                                    log10(vector_density_range[2]),
                                     length.out = resolution
@@
   geom_path(size = 1) +
-  geom_blank(aes(y = y_max)) +
+  # geom_blank(aes(y = y_max)) +
   # plot labels
@@
     expand = c(0, 0),
-    limits = c(0, NA)
+    # limits = c(0, NA)
   )
@@
     expand = c(0, 0),
-    limits = c(0, NA)
+    # limits = c(0, NA)
   ) +

### 2023-06-16 code/sensitivity.R

@@ -859,6 +859,163 @@ plot.Topt.rel.sens <- Topt.HPD %>%
   )
 plot.Topt.rel.sens
 
+# 5*) dTopt dKH uncertainty -------------------------------------------------------
+
+# Calculate the width of the 95% HPD for the full posterior of Topt across vertebrate host abundance
+
+# !!! [] re-run: make sure KH values have high enough resolution
+
+data.dToptdKH.HPD <- dplyr::filter(data.Host, 
+                              sigmaH == 100) #,
+# KH < 1e3) #%>% 
+# dplyr::filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 31)])
+
+full.dToptdKH.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
+                        sigmaH = c(), KH = c(), 
+                        HPD_low = c(), HPD_high = c(), HPD_width = c())
+
+for (index_KH in unique(data.dToptdKH.HPD$KH)) {
+  temp_df <- expand_grid(dplyr::filter(data.dToptdKH.HPD, KH == index_KH), 
+                         data.Vec) %>%
+    data.table::data.table() %>%
+    mutate(RV = ifelse(is.infinite(sigmaH),
+                       sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
+                       sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
+    mutate(bV = ifelse(is.infinite(sigmaH),
+                       sigmaV, # Ross-Macdonald model
+                       sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
+    mutate(RH = ifelse(V0 == 0,
+                       0,
+                       bV * betaV * V0 * exp(-1 / (lf * etaV)) / (KH * (gammaH + muH) + eps))) %>%
+    # Basic reproduction number
+    mutate(R0 = sqrt(RV*RH)) %>%
+    # dplyr::filter to maximum value of R0
+    dplyr::filter(R0>0) %>% 
+    select(system_ID, sample_num, sigmaH, KH, Temperature, R0) %>% 
+    group_by(system_ID, sample_num, sigmaH, KH) %>%
+    dplyr::filter(R0 == max(R0)) %>%
+    distinct() %>% 
[…]

### 2023-06-16 manuscript-figures.Rmd
clean up contact plot

--- 2023-06-16 manuscript-figures.Rmd
@@
 ## Set up density ranges
-host_density_range <- c(1E-1, 1E2)
+host_density_range <- c(1E0, 1E3)
 host_fixed_value <- 10
-host_density_vec <- sort(c(seq(host_density_range[1], host_density_range[2],
+host_density_vec <- sort(c(10^seq(log10(host_density_range[1]), 
+                                  log10(host_density_range[2]),
                                   length.out = resolution
@@
 
-vector_density_range <- c(0, 1E3)
+vector_density_range <- c(1E0, 1E3)
 vector_fixed_value <- 1000
-vector_density_vec <- sort(c(seq(vector_density_range[1], vector_density_range[2],
+vector_density_vec <- sort(c(10^seq(log10(vector_density_range[1]), 
+                                    log10(vector_density_range[2]),
                                     length.out = resolution
@@
            `Host population density` == host_fixed_value) %>%
-  filter(`Bites per host per day` < 1E3) %>%
+  # filter(`Bites per host per day` < 1E3) %>%
   select(-sigma_V, -sigma_H, -model) %>%

### 2023-06-16 code/sensitivity.R
try to get dTopt dKH working

@@ -860,6 +860,165 @@ plot.Topt.rel.sens <- Topt.HPD %>%
   )
 plot.Topt.rel.sens
 
+# 5*) dTopt dKH uncertainty -------------------------------------------------------
+
+# Calculate the width of the 95% HPD for the full posterior of Topt across vertebrate host abundance
+
+# !!! [] re-run: make sure KH values have high enough resolution
+
+KH_vec <- unique(data.Host$KH)[seq(1, length(unique(data.Host$KH)), length.out = 5)]
+
+data.dToptdKH.HPD <- dplyr::filter(data.Host, 
+                                   sigmaH == 100,
+                                   KH %in% KH_vec)
+
+full.dToptdKH.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
+                            sigmaH = c(), KH = c(), 
+                            HPD_low = c(), HPD_high = c(), HPD_width = c())
+
+for (index_KH in unique(data.dToptdKH.HPD$KH)) {
+  temp_df <- expand_grid(dplyr::filter(data.dToptdKH.HPD, KH == index_KH), 
+                         data.Vec) %>%
+    data.table::data.table() %>%
+    mutate(RV = ifelse(is.infinite(sigmaH),
+                       sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
+                       sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
+    mutate(bV = ifelse(is.infinite(sigmaH),
+                       sigmaV, # Ross-Macdonald model
+                       sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
+    mutate(RH = ifelse(V0 == 0,
+                       0,
+                       bV * betaV * V0 * exp(-1 / (lf * etaV)) / (KH * (gammaH + muH) + eps))) %>%
+    # Basic reproduction number
+    mutate(R0 = sqrt(RV*RH)) %>%
+    # dplyr::filter to maximum value of R0
+    dplyr::filter(R0>0) %>% 
+    select(system_ID, sample_num, sigmaH, KH, Temperature, R0) %>% 
+    group_by(system_ID, sample_num, sigmaH, KH) %>%
+    dplyr::filter(R0 == max(R0)) %>%
+    distinct() %>% 
[…]

### 2023-06-16 code/sensitivity.R
add possible parallelization of dToptdKH calculations

@@ -607,7 +607,7 @@ plot.ddTR0.rel.sens
 
 data.ToptHPD <- dplyr::filter(data.Host, 
                               sigmaH %in% c(10, 100)) #,
-                              # KH < 1e3) #%>% 
+# KH < 1e3) #%>% 
 # dplyr::filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 31)])
 
 full.Topt.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
@@ -862,9 +862,7 @@ plot.Topt.rel.sens
 
 # 5*) dTopt dKH uncertainty -------------------------------------------------------
 
-# Calculate the width of the 95% HPD for the full posterior of Topt across vertebrate host abundance
-
-# !!! [] re-run: make sure KH values have high enough resolution
+# Calculate the width of the 95% HPD for the full posterior of dTopt/dKH across vertebrate host abundance
 
 KH_vec <- unique(data.Host$KH)[seq(1, length(unique(data.Host$KH)), length.out = 5)]
 
@@ -876,42 +874,38 @@ full.dToptdKH.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                             sigmaH = c(), KH = c(), 
                             HPD_low = c(), HPD_high = c(), HPD_width = c())
 
-for (index_KH in unique(data.dToptdKH.HPD$KH)) {
-  temp_df <- expand_grid(dplyr::filter(data.dToptdKH.HPD, KH == index_KH), 
-                         data.Vec) %>%
-    data.table::data.table() %>%
-    mutate(RV = ifelse(is.infinite(sigmaH),
-                       sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
-                       sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
-    mutate(bV = ifelse(is.infinite(sigmaH),
-                       sigmaV, # Ross-Macdonald model
-                       sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
-    mutate(RH = ifelse(V0 == 0,
-                       0,
[…]

### 2023-06-16 code/sensitivity.R
Update sensitivity.R

@@ -864,64 +864,122 @@ plot.Topt.rel.sens
 
 # Calculate the width of the 95% HPD for the full posterior of dTopt/dKH across vertebrate host abundance
 
-KH_vec <- unique(data.Host$KH)[seq(1, length(unique(data.Host$KH)), length.out = 5)]
+KH_length <- 301
+KH_vec <- sort(c(10^-1.02, 10^3.02,
+                 10^seq(-1, 3, length.out = KH_length)))
+sigmaH_vec <- 100
 
-data.dToptdKH.HPD <- dplyr::filter(data.Host, 
-                                   sigmaH == 100,
-                                   KH %in% KH_vec)
+
+data.dToptdKH.HPD <- dplyr::filter(data.Host, sigmaH == sigmaH_vec) %>% 
+  select(-KH) %>% 
+  full_join(as_tibble(list(KH = KH_vec)), by = character()) %>% 
+  distinct()
 
 full.dToptdKH.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                             sigmaH = c(), KH = c(), 
                             HPD_low = c(), HPD_high = c(), HPD_width = c())
 
-temp_df <- expand_grid(data.dToptdKH.HPD, 
-                       data.Vec) %>%
-  data.table::data.table() %>%
-  mutate(RV = ifelse(is.infinite(sigmaH),
-                     sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
-                     sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
-  mutate(bV = ifelse(is.infinite(sigmaH),
-                     sigmaV, # Ross-Macdonald model
-                     sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
-  mutate(RH = ifelse(V0 == 0,
-                     0,
-                     bV * betaV * V0 * exp(-1 / (lf * etaV)) / (KH * (gammaH + muH) + eps))) %>%
-  # Basic reproduction number
-  mutate(R0 = sqrt(RV*RH)) %>%
-  # dplyr::filter to maximum value of R0
-  dplyr::filter(R0>0) %>% 
-  select(system_ID, sample_num, sigmaH, KH, Temperature, R0) %>% 
[…]

### 2023-06-16 code/sensitivity.R
dToptdKH

@@ -58,7 +58,7 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
 # Host trait dataset
 data.Host <- read_rds("results/Host_vals.rds")
 # Vector trait dataset
-# data.Vec <- read_rds("results/VecTPC_vals.rds")
+data.Vec <- read_rds("results/VecTPC_vals.rds")
 
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
@@ -607,7 +607,7 @@ plot.ddTR0.rel.sens
 
 data.ToptHPD <- dplyr::filter(data.Host, 
                               sigmaH %in% c(10, 100)) #,
-                              # KH < 1e3) #%>% 
+# KH < 1e3) #%>% 
 # dplyr::filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 31)])
 
 full.Topt.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
@@ -866,19 +866,26 @@ plot.Topt.rel.sens
 
 # !!! [] re-run: make sure KH values have high enough resolution
 
-KH_vec <- unique(data.Host$KH)[seq(1, length(unique(data.Host$KH)), length.out = 5)]
+KH_length <- 601
+KH_vec <- sort(c(10^-1.02, 10^3.02,
+            10^seq(-1, 3, length.out = KH_length)))
+sigmaH_vec <- 100
 
-data.dToptdKH.HPD <- dplyr::filter(data.Host, 
-                                   sigmaH == 100,
-                                   KH %in% KH_vec)
+
+data.dToptdKH.HPD <- dplyr::filter(data.Host, sigmaH == sigmaH_vec) %>% 
+  select(-KH) %>% 
+  full_join(as_tibble(list(KH = KH_vec)), by = character()) %>% 
+  distinct()
 
 full.dToptdKH.HPD <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                             sigmaH = c(), KH = c(), 
                             HPD_low = c(), HPD_high = c(), HPD_width = c())
 
-for (index_KH in unique(data.dToptdKH.HPD$KH)) {
-  temp_df <- expand_grid(dplyr::filter(data.dToptdKH.HPD, KH == index_KH), 
[…]

### 2023-06-17 manuscript-figures.Rmd
R0 derivatives

@@
     mutate(focal_var = factor(focal_var,
-                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                            labels = c(
@@
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
-  filter(rel_HPD_width != 0) %>%
+  # filter(rel_HPD_width != 0) %>%
   # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
@@
     cols = vars(system_label),
-    rows = vars(KH, sigmaH),
+    rows = vars(sigmaH),
     labeller = labeller(
@@
 plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
+  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
-  filter(rel_HPD_width != 0) %>%
+  # filter(rel_HPD_width != 0) %>%
   # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
@@
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $ddTR_0$ HPD width"))
+    name = unname(TeX("Relative contribution to $dR_0 / dT$ HPD width"))
   ) +
@@
     cols = vars(system_label),
-    rows = vars(KH, sigmaH),
+    rows = vars(sigmaH),
     labeller = labeller(
       system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      KH = as_labeller(appender_KH, default = label_parsed)
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
     ),
@@
 
-Topt.HPD <- Topt.HPD %>%
+# !!! mention the value of sigmaH
+
+plot.Topt.rel.sens <- Topt.HPD %>% 
   ungroup() %>%
   distinct() %>% 
+  filter(sigmaH == 100) %>% 
   filter(!is.na(HPD_width)) %>% 
@@
   # Divide each sensitivity value by the total sensitivity
-  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
-# arrange(sens_rel)
-
-# !!! mention the value of sigmaH
-
-plot.Topt.rel.sens <- Topt.HPD %>%
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
   # Make a stacked plot, colored by parameter
@@
   ) +
-  # scale_y_continuous(
-  #   limits = c(0,1)
-  # ) +
   facet_wrap(~system_label) +
@@
 shift_legend(plot.Topt.rel.sens)
+```
+
+```{r fig-S10_2_dToptdKH_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_sens.rds") %>%
+  ungroup() %>%
+  distinct() %>% 
+  filter(!is.na(HPD_width)) %>% 
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  )) %>% 
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all sensitivity values to get total sensitivity
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each sensitivity value by the total sensitivity
+  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
+# arrange(sens_rel)
+
+# !!! mention the value of sigmaH
+
+plot.dToptdKH.rel.sens <- dToptdKH.HPD %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    # limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $ dT_{opt}/dK_H$ HPD width"))
+  ) +
+  facet_wrap(~system_label) +
+  theme_minimal() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.dToptdKH.rel.sens)
 ```

### 2023-06-17 code/get-outputs.R

@@ -317,7 +317,7 @@ gc()
 
 # Collect R0 TPC data across systems and host trait values
 for (system_name in unique(data.Vec$system_ID)) {
-  print(paste0("Topt vals: ", system_name))
+  print(paste0("R0 vals: ", system_name))
   KHslice_num <- 1
   pb <- progress_bar$new(
     format = ":spin :system progress = :percent [:bar] :elapsedfull | eta: :eta",
@@ -334,7 +334,7 @@ for (system_name in unique(data.Vec$system_ID)) {
         filter(sigmaH %in% index_sigmaH,
                KH %in% index_KH) %>%
         R0_TPC_func(., system_name)
-        
+      
       R0.df <- rbind(temp_df, R0.df)
       sigmaHslice_num <- sigmaHslice_num  + 1
     }
@@ -359,9 +359,121 @@ R0_heat.df <- R0.df %>%
   filter(KH %in% c(0.1, 1, 10, 100))
 write_rds(R0_heat.df, "results/R0_vals.rds", compress = "gz")
 
-# !!! [] filter down R0.df to get it under 100 MB
 
-# 3) Calculate Topt -------------------------------------------------------
+# 3) Calculate R0 derivatives ---------------------------------------------
+
+# Set up parallel
+if (!exists("cluster")) {
+  cluster_size <- min(21, parallel::detectCores() - 2)
+  cluster <- new_cluster(cluster_size)
+  cluster_library(cluster, c("dplyr", "tidyr"))
+}
+
+# Set up host trait data frame (for future visualization)
+data.dR0dk <- data.Host %>%
+  filter(sigmaH %in% c(100, Inf)) #%>%
+  # filter(sigmaH %in% c(10^seq(-1,2), Inf,
+  #                      unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 51)])) %>%
+  # filter(KH %in% c(10^seq(-2,5)))
+# filter(KH %in% c(10^seq(-2,5) ,
+#                  unique(KH)[seq(1, length(unique(KH)), length.out = 51)]))
+
+# Slice host trait data
+sigmaH_slices <- slice(unique(data.dR0dk$sigmaH), 2)
+KH_slices <- slice(unique(data.dR0dk$KH), cluster_size)
+
+# Initialize R0 data frame
+dR0dvar.df <- init.df
+
+gc()
+
[…]

### 2023-06-17 code/sensitivity.R

@@ -40,10 +40,9 @@ library(svglite) #nec
 library(HDInterval)
 
 # Set up parallel
-if (!exists("cluster")) {
-  cluster_size <- min(21, parallel::detectCores() - 2)
-  cluster <- makeCluster(cluster_size) #new_cluster(cluster_size)
-  registerDoParallel(cluster)
+if (!exists("cl")) {
+  cl <- parallel::makeCluster(parallel::detectCores() - 2)
+  registerDoSNOW(cl)
   # cluster_library(cluster, c("dplyr", "tidyr"))
 }
 
@@ -59,14 +58,12 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
 # Host trait dataset
 data.Host <- read_rds("results/Host_vals.rds")
 # Vector trait dataset
-# data.Vec <- read_rds("results/VecTPC_vals.rds")
+data.Vec <- read_rds("results/VecTPC_vals.rds")
 
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
-# Topt data
-data.Topt <- read_rds("results/Topt_vals.rds")
-# Critical thermal extrema data
-data.CT <- read_rds("results/CT_vals.rds")
+
+
 
 
 # KH_vec_length <- 300 # full = 300, thin = 20
@@ -166,27 +163,27 @@ write_rds(full.R0.HPD, "results/full_R0_HPD.rds")
 # full.R0.HPD <- read_rds("results/full_R0_HPD.rds")
 
 # # R0 HPD diagnostic plot
-# R0.HPD.plot <- full.R0.HPD %>%
-#   # dplyr::filter(KH %in% c(1,100)) %>%
-#   arrange(system_ID, sigmaH) %>% 
-#   # dplyr::filter(is.finite(sigmaH)) %>%
-#   ggplot(aes(x = Temperature, y = norm_HPD_width, color = as.factor(KH))) +
-#   geom_path(lwd = 1) +
-#   scale_color_viridis_d(
-#     name = "Vertebrate host population\ndensity (ind/ha)",
-#     breaks = 10^seq(-2, 4),
-#     labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
-#     limits = 10^seq(-2, 4)
-#   ) +
-#   scale_y_continuous(name = "Normalized HPD width") +
[…]

### 2023-06-18 code/get-outputs.R
update all values

@@ -372,10 +372,11 @@ if (!exists("cluster")) {
 # Set up host trait data frame (for future visualization)
 data.dR0dk <- data.Host %>%
   filter(sigmaH %in% c(100, Inf)) %>%
+  filter(KH %in% 10^seq(-2,5))
   # filter(sigmaH %in% c(10^seq(-1,2), Inf,
   #                      unique(sigmaH)[seq(1, length(unique(sigmaH)), length.out = 51)])) %>%
   # filter(KH %in% c(10^seq(-2,5)))
-  filter(KH %in% c(10^seq(-2,5) ,unique(KH)[seq(1, length(unique(KH)), length.out = 201)]))
+  # filter(KH %in% c(10^seq(-2,5) ,unique(KH)[seq(1, length(unique(KH)), length.out = 201)]))
 
 R0_deriv_func <- function(in_df) {
   out_df <- in_df %>% # Pr(surviving the EIP)
@@ -466,6 +467,7 @@ pb$terminate()
 dR0dvar.df2 <- dR0dvar.df %>% 
   ungroup() %>% 
   filter(Temperature %in% unique(Temperature)[seq(1, length(unique(Temperature)), length.out = 500)])
+
 write_rds(dR0dvar.df2, "results/dR0dk_vals.rds", compress = "gz")
 
 # Save data

### 2023-06-18 code/sensitivity.R

@@ -261,8 +261,8 @@ for (var_name in temp_vars) {
 }
 
 # Save R0 relative highest posterior density data
-write_rds(R0.HPD, "results/R0_HPD_sens.rds")
-# R0.HPD <- read_rds("results/R0_HPD_sens.rds")
+write_rds(R0.HPD, "results/R0_HPD_unc.rds")
+# R0.HPD <- read_rds("results/R0_HPD_unc.rds")
 
 ## Plot R0 uncertainty 
 Temp_range_for_plot <- R0.HPD %>% 
@@ -493,8 +493,8 @@ for (var_name in temp_vars) {
 }
 
 # Save R0 relative highest posterior density data
-write_rds(ddTR0.HPD, "results/ddTR0_HPD_sens.rds")
-# ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds")
+write_rds(ddTR0.HPD, "results/ddTR0_HPD_unc.rds")
+# ddTR0.HPD <- read_rds("results/ddTR0_HPD_unc.rds")
 
 ## Plot R0 uncertainty 
 Temp_range_for_plot <- ddTR0.HPD %>% ungroup() %>% 
@@ -669,7 +669,7 @@ full.Topt.HPD <- foreach(index_KH = 1:KH_length,
 close(pb)
 
 # Save Topt highest posterior density data
-# write_rds(full.Topt.HPD, "results/full_Topt_HPD.rds")
+write_rds(full.Topt.HPD, "results/full_Topt_HPD.rds")
 # full.Topt.HPD <- read_rds("results/full_Topt_HPD.rds")
 
 # # Diagnostic plot
@@ -773,8 +773,8 @@ for (var_name in temp_vars) {
 }
 
 # Save Topt relative highest posterior density data
-# write_rds(Topt.HPD, "results/Topt_HPD_sens.rds")
-# Topt.HPD <- read_rds("results/Topt_HPD_sens.rds")
+write_rds(Topt.HPD, "results/Topt_HPD_unc.rds")
+# Topt.HPD <- read_rds("results/Topt_HPD_unc.rds")
 
 ## Plot Topt uncertainty 
 var_name_table <- list(
@@ -1024,8 +1024,8 @@ dToptdKH.HPD <- dToptdKH.HPD %>%
   distinct()
 
 # Save Topt relative highest posterior density data
[…]

### 2023-06-18 manuscript-figures.Rmd
add dR0dvar plot, rename sensitivity

--- 2023-06-16 manuscript-figures.Rmd
@@
   pathosystem_labeller()
-
-# Sensitivity data for R0
-R0.HPD <- read_rds("results/R0_HPD_sens.rds") %>%
+# Local sensitivity of R0 to mosquito traits
+data.dR0dvar <- read_rds("results/dR0dk_vals.rds") %>% 
+  ungroup() %>% 
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  ))
+
+# Uncertainty data for R0
+R0.HPD <- read_rds("results/R0_HPD_unc.rds") %>%
   ungroup() %>%
@@
 
-ddTR0.HPD <- read_rds("results/ddTR0_HPD_sens.rds") %>%
+ddTR0.HPD <- read_rds("results/ddTR0_HPD_unc.rds") %>%
   ungroup() %>%
@@
 
-# Sensitivity data for Topt
-Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
+# Uncertainty data for Topt
+Topt.HPD <- read_rds("results/Topt_HPD_unc.rds") %>%
   ungroup() %>%
@@
 
-# Sensitivity data for critical thermal extrema
-CT.HPD <- read_rds("results/CT_HPD_sens.rds") %>%
+# Uncertainty data for critical thermal extrema
+CT.HPD <- read_rds("results/CT_HPD_unc.rds") %>%
   ungroup() %>%
@@
 
-```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_sens} The sensitivity of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
+```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc} The uncertainty of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
 
@@
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
-  filter(rel_HPD_width != 0) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  # filter(rel_HPD_width != 0) %>%
+  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
   group_by(system_ID, sigmaH, KH, Temperature) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each uncertainty value by the total uncertainty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%
@@
 
-```{r fig-S9_ddTR0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_sens} The sensitivity of the distribution of the derivative of $\\mathcal{R}_0$ with respect to temperature to mosquito life history traits.'}
+```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
+
+# !!! [] change factor/levels for focal_var so that they show up in the same
+#        order as in the legend
+# !!! [] figure out what's going on with the "color" bars occuring at low temperatures for plots (a) (b) and (e)
+
+KH_vals <- c(1)
+
+dR0dk.df <- data.dR0dvar %>%
+  filter(KH %in% KH_vals,
+         sigmaH %in% c(100, Inf)) %>%
+  # filter(median > 0) %>%
+  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>% 
+              filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) ) %>% 
+  filter(median_R0 > 0) %>%
+  mutate(abs_median = abs(median)) %>% 
+  mutate(sign_median = sign(median)) %>% 
+  filter(sign_median != 0, !is.na(sign_median)) %>% 
+  # filter(!(focal_var %in% c("Immature development rate", "Prob. of immature survival", "Eggs per female per day", "Vector competence", "Adult lifespan"))) %>% 
+  arrange(sign_median) %>% 
+  arrange(Temperature)
+
+plot.dR0dk <- dR0dk.df  %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = abs_median, color = focal_var, linetype = (as.factor(sign_median)))) +
+  geom_line(lwd = 1) +
+  scale_color_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_continuous(
+    # limits = Temp_range_for_plot,
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Local sensitivity of $R_0$")),
+    limits = 10^c(-4, 3),
+    breaks = 10^(seq(-4,3)), 
+    labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
+    trans = 'log10',
+    expand = c(0,0)
+  ) +
+  scale_linetype_manual(
+    name = "Sign of sensitivity:",
+    values = c(1,3),
+    breaks = c(1,-1),
+    labels = c("Positive", "Negative")
+  ) +
+  facet_rep_grid(
+    cols = vars(system_label),
+    rows = vars(KH, sigmaH),
+    labeller = labeller(
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  guides(linetype = guide_legend(
+    title.position = "left",
+    title.vjust = 0.5,
+    direction = "vertical")) +
+  theme_minimal_hgrid() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    legend.position = "bottom",
+    legend.justification = 0.5,
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# shift_legend(plot.R0.rel.sens)
+plot.dR0dk
+
+```
+
+```{r fig-S9_ddTR0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_unc} The uncertainty in the sensitivity of $\\mathcal{R}_0$ with respect to temperature.'}
 
@@
 plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
+  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
   # filter(!(KH == 100 & sigmaH == Inf)) %>%
-  filter(rel_HPD_width != 0) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
+  # filter(rel_HPD_width != 0) %>%
+  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
   group_by(system_ID, sigmaH, KH, Temperature) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each uncertainty value by the total uncertainty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%
@@
 
-```{r fig-S10_Topt_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
-
-Topt.HPD <- Topt.HPD %>%
+```{r fig-S10_Topt_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+# !!! mention the value of sigmaH
+
+plot.Topt.rel.sens <- Topt.HPD %>% 
   ungroup() %>%
   distinct() %>% 
+  filter(sigmaH == 100) %>% 
   filter(!is.na(HPD_width)) %>% 
@@
   filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity
+  # For each KH value, sum up all uncertainty values to get total uncertainty
   group_by(system_ID, sigmaH, KH) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
-  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
-# arrange(sens_rel)
-
-# !!! mention the value of sigmaH
-
-plot.Topt.rel.sens <- Topt.HPD %>%
+  # Divide each uncertainty value by the total uncertainty
+  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
   # Make a stacked plot, colored by parameter
@@
 
-```{r fig-S11_CTmin_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_sens} The sensitivity of the critical thermal minimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S10_2_dToptdKH_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty in the sensitivity of the thermal optimum to host availability as a function of vertebrate host population density when $\\sigma_H = 50$.'}
+
+dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_unc.rds") %>%
+  ungroup() %>%
+  distinct() %>% 
+  filter(!is.na(HPD_width)) %>% 
+  pathosystem_labeller() %>%
+    mutate(focal_var = factor(focal_var,
+                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                           labels = c(
+                             TeX("Adult lifespan"),
+                             TeX("Biting frequency"),
+                             TeX("Eggs per female per day"),
+                             TeX("Immature development rate"),
+                             TeX("Prob. of immature survival"),
+                             TeX("Prob. of surviving EIP"),
+                             TeX("Vector competence")
+                           )
+  )) %>% 
+  filter(!is.na(rel_HPD_width)) %>%
+  # For each KH value, sum up all uncertainty values to get total uncertainty
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(sens_total = sum(rel_HPD_width)) %>%
+  # Divide each uncertainty value by the total uncertainty
+  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
+# arrange(sens_rel)
+
+# !!! mention the value of sigmaH
+
+plot.dToptdKH.rel.sens <- dToptdKH.HPD %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  geom_area() +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    # limits = c(0.05, 1E3),
+    breaks = 10^seq(-2, 4, 1),
+    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Relative contribution to $ dT_{opt}/dK_H$ HPD width"))
+  ) +
+  facet_wrap(~system_label) +
+  theme_minimal() +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+shift_legend(plot.dToptdKH.rel.sens)
+```
+
+```{r fig-S11_CTmin_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_unc} The uncertainty of the critical thermal minimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity
+  # For each KH value, sum up all uncertainty values to get total uncertainty
   group_by(system_ID, sigmaH, KH) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each uncertainty value by the total uncertainty
   mutate(sens_rel = rel_HPD_width / sens_total) #%>%
@@
 
-```{r fig-S12_CTmax_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_sens} The sensitivity of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S12_CTmax_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_unc} The uncertainty of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity
+  # For each KH value, sum up all uncertainty values to get total uncertainty
   group_by(system_ID, sigmaH, KH) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitivity
+  # Divide each uncertainty value by the total uncertainty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%
@@
 
-```{r fig-S13_CTwidth_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_sens} The sensitivity of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
+```{r fig-S13_CTwidth_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_unc} The uncertainty of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
 
@@
   filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all sensitivity values to get total sensitivity
+  # For each KH value, sum up all uncertainty values to get total uncertainty
   group_by(system_ID, sigmaH, KH) %>%
   mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each sensitivity value by the total sensitiviWty
+  # Divide each uncertainty value by the total sensitiviWty
   mutate(sens_rel = rel_HPD_width / sens_total) %>%

### 2023-06-18 manuscript-figures.Rmd
Update manuscript-figures.Rmd

@@
   # theme options:
-  theme_minimal() +
+  theme_minimal(10) +
   theme(
@@
   # theme options:
-  theme_minimal_hgrid(11) +
+  theme_minimal_hgrid(10) +
   theme(
@@
   # theme options:
-  theme_minimal() +
+  theme_minimal(10) +
   guides(color = guide_legend(override.aes = list(size = 4))) +
@@
   # theme options:
-  theme_minimal_hgrid() +
+  theme_minimal_hgrid(10) +
   theme(
@@
   facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
-  theme_minimal_grid() +
+  theme_minimal_grid(10) +
   theme(
@@
   ) +
-  theme_minimal() +
+  theme_minimal(10) +
   theme(
@@
 
-```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
+```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
 
@@
     labeller = labeller(
+      system_label = sens_labels,
       sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
@@
     direction = "vertical")) +
-  theme_minimal_hgrid() +
+  theme_minimal_hgrid(10) +
   theme(
@@
     legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
+    legend.text = element_text(size = 8),
     legend.position = "bottom",
@@
   facet_wrap(~system_label) +
-  theme_minimal() +
+  theme_minimal(10) +
   theme(

### 2023-06-19 manuscript-figures.Rmd
clean up figures; revert CT HPD data

@@
     limits = c(10, 40),
-    # breaks = seq(10, 40, 2)
+    breaks = seq(10, 40, 2)
   ) +
@@
 
-infinite_skew <- 4500 # 10000
-
-Topt_df <- Topt_df %>%
+infinite_skew <- 10^3.7
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^3.35 # 10^log10(max_sigmaH*1)
+
+Topt_df <- data.Topt %>%
   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
@@
 
+```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
+
+KH_vals <- c(1)
+
+dR0dk.df <- data.dR0dvar %>%
+  filter(KH %in% KH_vals,
+         sigmaH %in% c(100, Inf)) %>%
+  # filter(median > 0) %>%
+  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>% 
+              filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) ) %>% 
+  filter(median_R0 > 0) %>%
+  mutate(abs_median = abs(median)) %>% 
+  mutate(sign_median = sign(median)) %>% 
+  filter(sign_median != 0, !is.na(sign_median)) %>%
+  # filter(!(focal_var %in% c("Immature development rate", "Prob. of immature survival", "Eggs per female per day", "Vector competence", "Adult lifespan"))) %>% 
+  arrange(sign_median) %>% 
+  arrange(Temperature)
+
+plot.dR0dk <- dR0dk.df  %>% 
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = abs_median, color = focal_var, linetype = (as.factor(sign_median)))) +
+  geom_line(lwd = 1) +
+  scale_color_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_continuous(
+    # limits = Temp_range_for_plot,
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    name = unname(TeX("Local sensitivity of $R_0$")),
+    limits = 10^c(-4, 3),
+    breaks = 10^(seq(-4,3)), 
+    labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
+    trans = 'log10',
+    expand = c(0,0)
+  ) +
+  scale_linetype_manual(
+    name = "Sign of sensitivity:",
+    values = c(1,3),
+    breaks = c(1,-1),
+    labels = c("Positive", "Negative")
+  ) +
+  facet_rep_grid(
+    cols = vars(system_label),
+    rows = vars(KH, sigmaH),
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  guides(linetype = guide_legend(
+    title.position = "left",
+    title.vjust = 0.5,
+    direction = "vertical")) +
+  theme_minimal_hgrid(10) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 8),
+    legend.position = "bottom",
+    legend.justification = 0.5,
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# shift_legend(plot.R0.rel.sens)
+plot.dR0dk
+
+```
+
 ```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc} The uncertainty of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
@@
 plot.R0.rel.sens
-
-```
-
-```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
-
-# !!! [] change factor/levels for focal_var so that they show up in the same
-#        order as in the legend
-# !!! [] figure out what's going on with the "color" bars occuring at low temperatures for plots (a) (b) and (e)
-
-KH_vals <- c(1)
-
-dR0dk.df <- data.dR0dvar %>%
-  filter(KH %in% KH_vals,
-         sigmaH %in% c(100, Inf)) %>%
-  # filter(median > 0) %>%
-  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>% 
-              filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) ) %>% 
-  filter(median_R0 > 0) %>%
-  mutate(abs_median = abs(median)) %>% 
-  mutate(sign_median = sign(median)) %>% 
-  filter(sign_median != 0, !is.na(sign_median)) %>% 
-  # filter(!(focal_var %in% c("Immature development rate", "Prob. of immature survival", "Eggs per female per day", "Vector competence", "Adult lifespan"))) %>% 
-  arrange(sign_median) %>% 
-  arrange(Temperature)
-
-plot.dR0dk <- dR0dk.df  %>% 
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = abs_median, color = focal_var, linetype = (as.factor(sign_median)))) +
-  geom_line(lwd = 1) +
-  scale_color_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_continuous(
-    # limits = Temp_range_for_plot,
-    expand = c(0, 0)
-  ) +
-  scale_y_continuous(
-    name = unname(TeX("Local sensitivity of $R_0$")),
-    limits = 10^c(-4, 3),
-    breaks = 10^(seq(-4,3)), 
-    labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
-    trans = 'log10',
-    expand = c(0,0)
-  ) +
-  scale_linetype_manual(
-    name = "Sign of sensitivity:",
-    values = c(1,3),
-    breaks = c(1,-1),
-    labels = c("Positive", "Negative")
-  ) +
-  facet_rep_grid(
-    cols = vars(system_label),
-    rows = vars(KH, sigmaH),
-    labeller = labeller(
-      system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      KH = as_labeller(appender_KH, default = label_parsed)
-    ),
-    scales = "free"
-  ) +
-  guides(linetype = guide_legend(
-    title.position = "left",
-    title.vjust = 0.5,
-    direction = "vertical")) +
-  theme_minimal_hgrid(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 8),
-    legend.position = "bottom",
-    legend.justification = 0.5,
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# shift_legend(plot.R0.rel.sens)
-plot.dR0dk
 

### 2023-06-27 manuscript-figures.Rmd
commit for publication
- major cleaning of old files and unnecessary comments

@@
 
-# !!! [] make sure all plots have font size set at 11 max, unless necessary
-
 # Set theme
@@
     unname(TeX(paste("$\\sigma_H = \\infty$"))),
-         unname(TeX(paste("$\\sigma_H = $", string))))
+    unname(TeX(paste("$\\sigma_H = $", string)))
+  )
 }
@@
 
-# Load required data ----
-
-# !!! [] make sure all data is getting loaded here
-
-eps <- .Machine$double.eps
-
-# Vector trait TPC data
-data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
-  #
-  pathosystem_labeller()
-# R0 data
-# !!! [] needs to be updated to include 1e-1, 1e0, 1e1
-data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
-  pathosystem_labeller()
-
-data.R0 <- read_rds("results/R0_vals.rds") %>%
-  pathosystem_labeller()
-# Topt data
-data.Topt <- read_rds("results/Topt_vals.rds") %>%
-  pathosystem_labeller()
-# Critical thermal extrema data
-data.CT <- read_rds("results/CT_vals.rds") %>%
-  pathosystem_labeller()
-# Local sensitivity of R0 to mosquito traits
-data.dR0dvar <- read_rds("results/dR0dk_vals.rds") %>% 
-  ungroup() %>% 
-  pathosystem_labeller() %>%
+# Helper function: apply nice labels for focal variables
+focalvar_labeller <- function(df) {
+  df <- df %>%
+    mutate(focal_var = ifelse(focal_var == "muV", "lf", focal_var)) %>%
     mutate(focal_var = factor(focal_var,
@@
     ))
+}
+
+# Load required data ----
+
+eps <- .Machine$double.eps
+
+# Vector trait TPC data
+data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
+  pathosystem_labeller()
+
+# R0 data
+data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
+  pathosystem_labeller()
+
+data.R0 <- read_rds("results/R0_vals.rds") %>%
+  pathosystem_labeller()
+
+# Topt data
+data.Topt <- read_rds("results/Topt_vals.rds") %>%
+  pathosystem_labeller()
+
+# Critical thermal extrema data
+data.CT <- read_rds("results/CT_vals.rds") %>%
+  pathosystem_labeller()
+
+# Local sensitivity of R0 to mosquito traits
+data.dR0dvar <- read_rds("results/dR0dk_vals.rds") %>%
+  ungroup() %>%
+  pathosystem_labeller() %>%
+  focalvar_labeller()
+
+# Densities of CTmin/max and Topt
+all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%
+  ungroup() %>%
+  pathosystem_labeller() %>%
+  filter(KH > 0.01)
 
@@
   pathosystem_labeller() %>%
-    mutate(focal_var = factor(focal_var,
-                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-                           labels = c(
-                             TeX("Adult lifespan"),
-                             TeX("Biting frequency"),
-                             TeX("Eggs per female per day"),
-                             TeX("Immature development rate"),
-                             TeX("Prob. of immature survival"),
-                             TeX("Prob. of surviving EIP"),
-                             TeX("Vector competence")
-                           )
-  ))
-
+  focalvar_labeller()
+
+# Uncertainty data for the derivative of R0 wrt temperature
 ddTR0.HPD <- read_rds("results/ddTR0_HPD_unc.rds") %>%
@@
   pathosystem_labeller() %>%
-    mutate(focal_var = factor(focal_var,
-                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-                           labels = c(
-                             TeX("Adult lifespan"),
-                             TeX("Biting frequency"),
-                             TeX("Eggs per female per day"),
-                             TeX("Immature development rate"),
-                             TeX("Prob. of immature survival"),
-                             TeX("Prob. of surviving EIP"),
-                             TeX("Vector competence")
-                           )
-  ))
+  focalvar_labeller()
 
@@
   pathosystem_labeller() %>%
-    mutate(focal_var = factor(focal_var,
-                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-                           labels = c(
-                             TeX("Adult lifespan"),
-                             TeX("Biting frequency"),
-                             TeX("Eggs per female per day"),
-                             TeX("Immature development rate"),
-                             TeX("Prob. of immature survival"),
-                             TeX("Prob. of surviving EIP"),
-                             TeX("Vector competence")
-                           )
-  ))
+  focalvar_labeller()
 
@@
   pathosystem_labeller() %>%
-    mutate(focal_var = factor(focal_var,
-                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-                           labels = c(
-                             TeX("Adult lifespan"),
-                             TeX("Biting frequency"),
-                             TeX("Eggs per female per day"),
-                             TeX("Immature development rate"),
-                             TeX("Prob. of immature survival"),
-                             TeX("Prob. of surviving EIP"),
-                             TeX("Vector competence")
-                           )
-  ))
+  focalvar_labeller()
+
+# Derivative of Topt with respect to host pop. density
+dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_unc.rds") %>%
+  ungroup() %>%
+  distinct() %>%
+  filter(!is.na(HPD_width)) %>%
+  pathosystem_labeller() %>%
+  focalvar_labeller()
 
@@
   ))
+
 # Median values (this one is used more frequently)
@@
   mutate(etaL = rhoL / (deltaL + eps)) %>%
-  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
   mutate(muL = etaL - rhoL) %>%
@@
 
-```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}
+```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Chitnis dynamic contact rate and the standard Ross-Macdonald contact rate models.
+In the left columns, mosquito population is held constant while in the right columns host population density is held constant.
+Upper panel: In the Ross-Macdonald model, the mosquito biting rate is constant with respect to both host and mosquito population density (a and b, blue lines) while in the Chitnis model mosquito biting increases with host population density (a, red curve) and decreases with mosquito population density (b, red curve).
+Lower panels: The relationships between the number of bites that a host receives per day and host and mosquito densities diverge at low host population densities (c) and, to a lesser extent, at high mosquito densities (d).
+For plots (a) and (c), mosquito population density is fixed at 1000 individuals per km2.
+For plots (b) and (d), host population density is fixed at 10 individuals per square kilometer.
+Maximum mosquito biting rate is 0.45 bites per mosquito per day and maximum host biting rate is 100 bites per host per day.
+Mosquito and host population densities are plotted on a logarithmic scale.
+'}
 # resolution setting
@@
     `Host population density` == host_fixed_value) %>%
-  # filter(`Bites per host per day` < 1E3) %>%
   select(-sigma_V, -sigma_H, -model) %>%
@@
     name = "Bites per mosquito per day",
-    expand = c(0, 0),
-    # limits = c(0, NA)
+    expand = c(0, 0)
   )
@@
 
-```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model.
-The range of temperatures is restricted to values where the immature development rate is positive.
-For traits that do not involve a parasite, \\textit{Aedes aegypti} with DENV and \\textit{Ae.
-aegypti} with ZIKV curves overlap.'}
+```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model.
+Curves are shown in color for each of the five systems we considered.
+Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive).
+Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d).
+Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7.
+The \\textit{Aedes aegypti} and DENV and \\textit{Ae.
+aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al.
+(2018)).
+All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020.
+Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions.
+A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
 ## Set up plot dataframe
@@
   select(Temperature, system_ID, sigmaV, sigmaV_f, rhoL, lf, deltaL, P_EIP, betaV) %>%
-  # select(Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP) %>%
   # Turn all columns except Temperature and system_ID into variables
@@
 
-```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}
-# Plot R0 vs. temperature curves. One plot for each pathosysten
-# One curve for Ross-Macdonald and a few illustrative examples for Chitnis
-
-# x-axes = temperature
-# y-axes = R0 (normalized so that max(R0) = 1)
-# plots = one for each mosquito+pathogen combination, "system_ID"
-# curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
-# curves  = Chitnis dynamic R0,
-#   - colour = value of KH. place it on a color scale in the bottom right corner
-
-# R0 as a function of temperature, separate curves across values of KH and sigmaH
-
+```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} $\\mathcal{R}_0$ as a function of temperature has the usual properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.
+The shape of the $\\mathcal{R}_0$ TPC depends on vertebrate host availability and the mosquito-parasite system.
+The shape of the thermal response of $\\mathcal{R}_0$ derived from the Ross-Macdonald model (dotted black curves) is independent of vertebrate host population density while those derived from the Chitnis dynamic model are dependent on vertebrate host population density (solid lines in color).
+Shown here are the median values of $\\mathcal{R}_0$ with respect to the mosquito trait TPC posterior distributions.
+$\\mathcal{R}_0$ is normalized by dividing by its maximum value in each system, for the given value of biting tolerance and vertebrate host population density.
+Vertebrate host population density is varied on a log$_{10}$ scale.'}
 # Plot R0 vs. temperature curves. One plot for each system
@@
 
-```{r fig-5_Topt, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
+```{r fig-5_Topt, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{\\mathrm{opt}}$, may be sensitive to vertebrate host population density and biting tolerance.
+Here, $T_{\\mathrm{opt}}$ is plotted as a function of vertebrate host population density and biting tolerance for each of the five systems.
+In the Ross-Macdonald model, where biting tolerance is assumed to be infinite, $T_{\\mathrm{opt}}$ is independent of vertebrate host population density (upper bars in plots).
+But when biting tolerance is limited, $T_{\\mathrm{opt}}$ can vary as much as 5\textdegree C (d).
+$T_{\\mathrm{opt}}$ may increase (d) or decrease (a, b, c, e) as vertebrate host population density or biting tolerance is increased.
+Shown here are the median values of $T_{\\mathrm{opt}}$ with respect to the mosquito trait TPC posterior distributions.
+Both biting tolerance and vertebrate host population density are varied on a $\\log_{10}$ scale.
+$\\mathcal{R}_0$ is greater than one in the region contained within the black $\\mathcal{R}_0=1$ curve.
+All remaining parameters are given in Table 1 and Figure 3.
+'}
 # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
@@
 # Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7 # 10^log10(max_sigmaH*1)
+infinite_divide <- 10^2.7
 
@@
   # Topt for INFINITE sigmaH:
-  # take median of median to hide variation from artifacts of uncertainty
   geom_contour_filled(
@@
   ) +
-  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
+  # # R0 = 1 contour: use where CTwidth = 0 (i.e. where R0<1 at any temperature)
   geom_contour(
@@
   ) +
-
   # fill:
@@
 
-```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
+```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal niche, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.
+As vertebrate host population density approaches an upper threshold, the width of the parasite population thermal niche shrinks to zero.
+At low levels of biting tolerance, there is also a lower threshold to vertebrate host population density.
+Shown here are the median values of $\\textrm{CT}_{\\textrm{width}}$ with respect to the mosquito trait TPC posterior distributions.
+Vertebrate host population density and biting tolerance are both plotted on $\\log_{10}$ scales.
+Biting tolerance is varied from one to one thousand bites per day, with an additional point at infinity to illustrate the case where biting tolerance is unlimited (the Ross-Macdonald model).
+Both biting tolerance and vertebrate host population density are varied on a $\\log_{10}$ scale.
+All remaining parameters are given in Table 1 and Figure 3.'}
 # Shows how the parasite thermal niche (temperatures between CT_min and CT_max)
@@
     title.hjust = 0.5,
-    barwidth = 12,#unit(5, "cm"),
+    barwidth = 12, # unit(5, "cm"),
     show.limits = TRUE
@@
 
-```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
+```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
+The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
+and \\textit{P.
+falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
+Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+All remaining parameters are given in Table 1 and Figure 3.'}
 # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
@@
     cols = vars(system_label),
-    labeller = labeller(.rows = mylabels,
-                        .cols = R0_heatmap_labels),
+    labeller = labeller(
+      .rows = mylabels,
+      .cols = R0_heatmap_labels
+    ),
     # repeat.tick.labels = "left"
@@
       size = 7,
-      hjust = 0.5),
+      hjust = 0.5
+    ),
     strip.text.x = ggtext::element_markdown(
       size = 7,
-      hjust = 0),
+      hjust = 0
+    ),
     panel.spacing = unit(2, "pt")
@@
 
-```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
+```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
+The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
+and \\textit{P.
+falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
+Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+All remaining parameters are given in Table 1 and Figure 3.'}
 Topt_df <- data.Topt %>%
   filter(KH < 10^4 + 1) %>%
-  pivot_wider(id_cols = c("system_label", "Model", "sigmaH", "KH"),
+  pivot_wider(
+    id_cols = c("system_label", "Model", "sigmaH", "KH"),
     names_from = variable,
-              values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%
-  rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
-         highHCI = highHCI_Topt) %>%
+    values_from = c("mean", "median", "lowHCI", "highHCI")
+  ) %>%
+  rename(
+    mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
+    highHCI = highHCI_Topt
+  ) %>%
   # Arrange along the plotting variables
@@
     expand = c(0, 0),
-    # limits = c(0.5, 150),
     breaks = c(10^c(seq(-1, 4, by = 1))),
@@
     name = expression("Thermal optimum "(degree * C)),
-    expand = c(0,0), # c(0.05, 0.05),
-    limits = c(21,30.5), # mean: 21-31, median: 21-32
-    breaks = seq(21,32, by = 1)
+    expand = c(0, 0),
+    limits = c(21, 30.5),
+    breaks = seq(21, 32, by = 1)
   ) +
@@
     values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
-    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
     breaks = c(1, 10, 100, Inf),
@@
 
-```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}
-
+```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance.
+At low host population densities, there may be warmer (a, b, c, e) or cooler (d) thermal optima when biting tolerance is low compared to when it is high.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host biting tolerance is varied on a $\\log_{10}$ scale with a break to indicate values of $\\mathcal{R}_0$ when biting tolerance is unlimited.
+'}
 # x-axis = vertebrate host biting tolerance
@@
     sigmaH,
-                               infinite_skew))
+    infinite_skew
+  ))
 Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
 
-sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15*infinite_divide, infinite_skew)
+sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15 * infinite_divide, infinite_skew)
 sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))
@@
     name = expression("Thermal optimum "(degree * C)),
-    expand = c(0,0), # c(0.05, 0.05),
-    limits = c(21,30), # mean: 21-31, median: 21-32
-    breaks = seq(21,32, by = 1)
+    expand = c(0, 0), # c(0.05, 0.05),
+    limits = c(21, 30), # mean: 21-31, median: 21-32
+    breaks = seq(21, 32, by = 1)
   ) +
@@
     name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 4)) +
+    values = met.brewer("Hokusai3", 4)
+  ) +
   scale_fill_manual(
     name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 4)) +
+    values = met.brewer("Hokusai3", 4)
+  ) +
   # faceting:
@@
     nrow = 2,
-             labeller = labeller()  ) +
+    labeller = labeller()
+  ) +
   # theme options:
@@
 
-```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} Critical thermal minimum as a function of vertebrate host availability.'}
+```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
+In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal minimum with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+'}
 #   x    = biting tolerance (with a point at infinity)
@@
 
-CTmin_breaks <- c(seq(14,35, by = 2), 101)
+CTmin_breaks <- c(seq(14, 35, by = 2), 101)
 
@@
   geom_contour_filled(
-    data = filter(CTmin_df,
-                  sigmaH_proxy < 10^2.2),
+    data = filter(
+      CTmin_df,
+      sigmaH_proxy < 10^2.2
+    ),
     breaks = CTmin_breaks
@@
   geom_contour_filled(
-    data = filter(CTmin_df,
+    data = filter(
+      CTmin_df,
       sigmaH_proxy > 10^2.4,
-                  sigmaH_proxy < infinite_divide),
+      sigmaH_proxy < infinite_divide
+    ),
     breaks = CTmin_breaks
@@
     values = c(viridis(9), "grey", "grey"),
-    labels = ~ ifelse(.x < maxCTmin, .x, 'n/a')
+    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
   ) +
@@
 
-```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} Critical thermal maximum as a function of vertebrate host availability.'}
-
+```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
+In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal maximum with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+'}
 #   x    = biting tolerance (with a point at infinity)
@@
 
-CTmax_breaks <- c(-101, seq(21,35, by = 2))
+CTmax_breaks <- c(-101, seq(21, 35, by = 2))
 
@@
   geom_contour_filled(
-    data = filter(CTmax_df,
-                  sigmaH_proxy < 10^2.2),
+    data = filter(
+      CTmax_df,
+      sigmaH_proxy < 10^2.2
+    ),
     breaks = CTmax_breaks
@@
   geom_contour_filled(
-    data = filter(CTmax_df,
+    data = filter(
+      CTmax_df,
       sigmaH_proxy > 10^2.4,
-                  sigmaH_proxy < infinite_divide),
+      sigmaH_proxy < infinite_divide
+    ),
     breaks = CTmax_breaks
@@
     values = c("grey", viridis(9)),
-    labels = ~ ifelse(.x < minCTmax-1, 'n/a', .x)
+    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
   ) +
@@
 
-```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} Parasite thermal niche as a function of vertebrate host population density and biting tolerance.'}
+```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves).
+Transmission is sustained ($\\mathcal{R}_0$>1) in the regions enclosed by the red and blue curves.
+$\\textrm{CT}_{\\min}$ is a convex function of vertebrate host population density while $\\textrm{CT}_{\\max}$ is concave.
+The points where the red and blue curves touch indicate thresholds of vertebrate host population density beyond which parasite population persistence is no longer possible at any temperature (i.e.
+$\\mathcal{R}_0$(T)<1) (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal minimum, maximum, and mosquito thermal tolerance niche with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+All remaining parameters are given in Table 1 and Figure 2.'}
 # x-axis = vertebrate host population density
@@
 
-CTRange_df <- read_rds("results/CT_vals.rds") %>%
-  pathosystem_labeller() %>%
+CTRange_df <- data.CT %>%
   # Arrange along the plotting variables
@@
   filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 101)]) %>%
-  pivot_wider(id_cols = c("system_label", "sigmaH", "KH"),
-              names_from = variable, values_from = value) %>%
+  pivot_wider(
+    id_cols = c("system_label", "sigmaH", "KH"),
+    names_from = variable, values_from = value
+  ) %>%
   group_by(system_label, KH, sigmaH) %>%
@@
       floor(range(CTRange_df$value, na.rm = TRUE)[2]),
-                 by = 2)
+      by = 2
+    )
   ) +
@@
   # faceting:
-  facet_wrap(~system_label,scales = "free",nrow = 2,labeller = labeller()) +
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
   # legend:
@@
 
-# test_plot <- Topt0_df %>%
-#   ggplot(aes(x = Temperature, y = proxy_0)) +
-#   geom_point() +
-#   facet_wrap(~system_ID, scales = "free")
-# test_plot
-
 Topt0_base_estimates <- Topt0_df %>%
@@
   rename(Topt_0 = Temperature)
-# check with above: Topt_0 matches with Topt when sigmaH*KH is minimized
-# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
 
@@
   distinct()
-# Calculate Topt_RM
-# filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>%
-# rename(Topt_RM = Temperature)
-# check with above: Topt_RM matches with Topt when sigmaH*KH is maximized
-# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)
 
@@
   mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
-
-# Investigating Topt_RM and Topt_0 further
-
-test_df <- median.Vec %>%
-  mutate(muV = 1 / (lf + eps)) %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(sigmaVV0 = sigmaV * V0) %>%
-  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
-  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0
-  filter(is.finite(proxy_0)) %>%
-  select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0)
 ```
 
-```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum, critical thermal maximum, and thermal optimum vary with vertebrate host availability.'}
-all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%
-  ungroup() %>%
-  pathosystem_labeller() %>%
-  filter(KH > 0.01)
-
+```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability.
+Distributions for the limited biting tolerance case (solid lines) and unlimited biting tolerance case (dashed lines) are shown above and below the vertebrate host population density levels, respectively.
+As vertebrate host population density is increased, the distributions become approximately equal, with the critical thermal minimum and maximum converging to each other at sufficiently high population densities.
+The \\textit{An.
+gambiae} and \\textit{P.
+falciparum} system shows the most drastic differences between the limited and unlimited biting tolerance cases at low vertebrate host population density levels.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
 # half-violin plots
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Critical thermal minimum",
-                  sigmaH == 100),
+    data = filter(
+      all.density.df, variable == "Critical thermal minimum",
+      sigmaH == 100
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Critical thermal minimum",
-                  sigmaH == Inf),
+    data = filter(
+      all.density.df, variable == "Critical thermal minimum",
+      sigmaH == Inf
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Critical thermal maximum",
-                  sigmaH == 100),
+    data = filter(
+      all.density.df, variable == "Critical thermal maximum",
+      sigmaH == 100
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Critical thermal maximum",
-                  sigmaH == Inf),
+    data = filter(
+      all.density.df, variable == "Critical thermal maximum",
+      sigmaH == Inf
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Thermal optimum",
-                  sigmaH == 100),
+    data = filter(
+      all.density.df, variable == "Thermal optimum",
+      sigmaH == 100
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
@@
   geom_violinhalf(
-    data = filter(all.density.df, variable == "Thermal optimum",
-                  sigmaH == Inf),
+    data = filter(
+      all.density.df, variable == "Thermal optimum",
+      sigmaH == Inf
+    ),
     aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
@@
 
-```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The uncertainty in the local sensitivity of $\\mathcal{R}_0$ with respect to mosquito life history traits.'}
-
+```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
+Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
+Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
+Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
+'}
 KH_vals <- c(1)
@@
 dR0dk.df <- data.dR0dvar %>%
-  filter(KH %in% KH_vals,
-         sigmaH %in% c(100, Inf)) %>%
-  # filter(median > 0) %>%
+  filter(
+    KH %in% KH_vals,
+    sigmaH %in% c(100, Inf)
+  ) %>%
   right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-              filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) ) %>% 
+    filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
   filter(median_R0 > 0) %>%
@@
   filter(sign_median != 0, !is.na(sign_median)) %>%
-  # filter(!(focal_var %in% c("Immature development rate", "Prob. of immature survival", "Eggs per female per day", "Vector competence", "Adult lifespan"))) %>% 
   arrange(sign_median) %>%
@@
   ) +
-  scale_x_continuous(
-    # limits = Temp_range_for_plot,
-    expand = c(0, 0)
-  ) +
+  scale_x_continuous(expand = c(0, 0)) +
   scale_y_continuous(
@@
     limits = 10^c(-4, 3),
-    breaks = 10^(seq(-4,3)), 
+    breaks = 10^(seq(-4, 3)),
     labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
-    trans = 'log10',
-    expand = c(0,0)
+    trans = "log10",
+    expand = c(0, 0)
   ) +
@@
     name = "Sign of sensitivity:",
-    values = c(1,3),
-    breaks = c(1,-1),
+    values = c(1, 3),
+    breaks = c(1, -1),
     labels = c("Positive", "Negative")
@@
     title.vjust = 0.5,
-    direction = "vertical")) +
+    direction = "vertical"
+  )) +
   theme_minimal_hgrid(10) +
@@
 
-# shift_legend(plot.R0.rel.sens)
 plot.dR0dk
-
 ```
 
-```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc} The uncertainty of the distribution of $\\mathcal{R}_0$ to mosquito life history traits.'}
-
-# !!! [] change factor/levels for focal_var so that they show up in the same
-#        order as in the legend
-# !!! [] figure out what's going on with the "color" bars occuring at low temperatures for plots (a) (b) and (e)
-
+```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc}  The uncertainty of $\\mathcal{R}_0$ to mosquito traits across temperatures as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$ when vertebrate host population density is set to one individual per hectare.
+Temperatures are restricted to those at which $\\mathcal{R}_0$ is positive for the given system.
+At the cool end of the thermal niche, variation in $\\mathcal{R}_0$ is mostly driven by the probability of surviving the extrinsic incubation period, except in the case of (d) \\textit{An.
+gambiae} and \\textit{P.
+falciparum}.
+As temperature is increased, the influence of adult mosquito lifespan also increases to eventually become the most influential parameter for all systems except (e) \\textit{Cx.
+quinquefasciatus} and WNV.'}
 Temp_range_for_plot <- R0.HPD %>%
@@
   filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
-  # filter(!(KH == 100 & sigmaH == Inf)) %>%
-  # filter(rel_HPD_width != 0) %>%
   # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
@@
 
-# shift_legend(plot.R0.rel.sens)
 plot.R0.rel.sens
-
 ```
@@
 ```{r fig-S9_ddTR0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_unc} The uncertainty in the sensitivity of $\\mathcal{R}_0$ with respect to temperature.'}
-
-# !!! [] just compare "low host availability (sigmaH = 50, KH = 1 or 10)" and
-#        "high host availability (sigmaH = Inf, KH = 100)" scenarios
-
 ## Plot R0 uncertainty
@@
 
-# shift_legend(plot.R0.rel.sens)
 plot.ddTR0.rel.sens
-
 ```
 
-```{r fig-S10_Topt_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}
-
-# !!! mention the value of sigmaH
-
+```{r fig-S10_Topt_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty of $T_{\\textrm{opt}}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width when $\\sigma_H$ is 100 bites per vertebrate host per day.
+At high levels of vertebrate host population density, the effect of vertebrate host traits diminishes and the relative sensitivities of $T_{\\textrm{opt}}$ to mosquito traits stabilize.
+Generally, adult lifespan is an influential parameter and, to lesser extents, vector competence and the probability of surviving the extrinsic incubation period (EIP).
+Eggs per female per day tends to be most important when vertebrate host population density is low, though this not the case for (e) \\textit{Cx.
+quinquefasciatus} and WNV.Immature development rate and the probability of immature survival are never very influential parameters.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
 plot.Topt.rel.sens <- Topt.HPD %>%
@@
 
-```{r fig-S10_2_dToptdKH_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty in the sensitivity of the thermal optimum to host availability as a function of vertebrate host population density when $\\sigma_H = 50$.'}
-
-dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_unc.rds") %>%
-  ungroup() %>%
-  distinct() %>% 
-  filter(!is.na(HPD_width)) %>% 
-  pathosystem_labeller() %>%
-    mutate(focal_var = factor(focal_var,
-                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
-                           labels = c(
-                             TeX("Adult lifespan"),
-                             TeX("Biting frequency"),
-                             TeX("Eggs per female per day"),
-                             TeX("Immature development rate"),
-                             TeX("Prob. of immature survival"),
-                             TeX("Prob. of surviving EIP"),
-                             TeX("Vector competence")
-                           )
-  )) %>% 
+```{r fig-S10_2_dToptdKH_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc2} The uncertainty in the sensitivity of the thermal optimum to host availability as a function of vertebrate host population density when $\\sigma_H = 100$.'}
+dToptdKH.HPD <- dToptdKH.HPD %>%
   filter(!is.na(rel_HPD_width)) %>%
@@
   # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
-# arrange(sens_rel)
-
-# !!! mention the value of sigmaH
+  mutate(sens_rel = rel_HPD_width / sens_total)
 
@@
     expand = c(0, 0),
-    # limits = c(0.05, 1E3),
     breaks = 10^seq(-2, 4, 1),
@@
 
-```{r fig-S11_CTmin_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_unc} The uncertainty of the critical thermal minimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
-
+```{r fig-S11_CTmin_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_unc} The uncertainty of $\\textrm{CT}_{\\min}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$.
+Sensitivities are only plotted when $\\textrm{CT}_{\\min}$ exists for the given value of vertebrate host population density.
+Generally, eggs per female per day and the probability of surviving the EIP are the most influential parameters.
+$\\textrm{CT}_{\\min}$ is sensitive to vector competence across the full range of vertebrate host population densities for systems (b) and (e) but, in systems (a), (c), and (d), only when population density is high.
+Immature development rate and the probability of immature survival are not very influential parameters and $\\textrm{CT}_{\\min}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
 CTmin_df <- CT.HPD %>%
@@
   # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total) #%>%
+  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
 
@@
 
-```{r fig-S12_CTmax_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_unc} The uncertainty of the critical thermal maximum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
-
+```{r fig-S12_CTmax_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_unc} The uncertainty of $\\textrm{CT}_{\\max}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$.
+Sensitivities are only plotted when $\\textrm{CT}_{\\max}$ exists for the given value of vertebrate host population density.
+Generally, adult mosquito life span is the most influential parameter.
+At low vertebrate host population densities, $\\textrm{CT}_{\\max}$ is sensitive to eggs per female per day in systems (c) and (e).
+$\\textrm{CT}_{\\max}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high.
+The influence of other parameters increases at high levels of vertebrate host population density.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
 plot.CTmax.rel.sens <- CT.HPD %>%
@@
 
-```{r fig-S13_CTwidth_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_unc} The uncertainty of the thermal niche width to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$ and $\\sigma_H=\\infty$.'}
-
+```{r fig-S13_CTwidth_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_unc}  The uncertainty of $\\textrm{CT}_{\\textrm{width}}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$.
+Sensitivities are only plotted when $\\textrm{CT}_{\\textrm{width}}$exists for the given value of vertebrate host population density.
+Generally, adult mosquito life span, eggs per female per day, and the probability of surviving the EIP are the most influential parameters, though $\\textrm{CT}_{\\textrm{width}}$ is not sensitive the probability of surviving the EIP in system (d).
+$\\textrm{CT}_{\\textrm{width}}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
 plot.CTwidth.rel.sens <- CT.HPD %>%
@@
       sigmaH = as_labeller(
-        appender_sigmaH, default = label_parsed)
+        appender_sigmaH,
+        default = label_parsed
+      )
     )

### 2023-06-27 code/DEBUG_TPCs.R

@@ -1,16 +1,0 @@
-
-data_df <- filter(data.in.TPC, mosquito_species == mosquito_in, trait.name == trait_in)
-plot(data_df$T, data_df$trait)
-
-# sample_index = sample(300,1)
-for (sample_index in 1:dim(temp_sample)[1]) {
-(c = filter(temp_sample, sample_num == sample_index)$c)
-(T0 = filter(temp_sample, sample_num == sample_index)$T0)
-(Tm = filter(temp_sample, sample_num == sample_index)$Tm)
-
-test_func <- Quadratic(c,T0,Tm)
-
-
-
-lines(seq(0,50, by = 0.1), test_func(seq(0,50, by = 0.1)))
-}

### 2023-06-27 code/Shocket_2018/R0Calculation_AppendixCalcs_Final.R

@@ -1,261 +1,0 @@
-##### Marta Shocket, Stanford University
-##### Updated April 2018
-
-##### Purpose: Process trait thermal response output from JAGS to calculate R0(T) for RRV model - Appendix calculations
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) Calculate pEA(T), M(T), and R0(T)
-##           3) Specify other helper function
-##           4) Calculate quantiles, get optima, etc.
-##           5) Appendix Figures S5, S6, and S9
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("")
-
-##### Load JAGS output - fits from uniform priors
-load("jagsout_GCD_Cann.Rdata")
-load("jagsout_EFD_Cann.Rdata")
-load("jagsout_pRH_Cann.Rdata")
-load("jagsout_nLR_Cann.Rdata")
-load("jagsout_pLA_Cann.Rdata")
-load("jagsout_MDR_Cann.Rdata")
-load("jagsout_ls_Cann.Rdata")
-load("jagsout_bc_RRV_Ovig.Rdata")
-load("jagsout_PDR_RRV_Ovig.Rdata")
-
-##### Load JAGS output - fits from data-informed priors
-load("jagsout_GCD_Cann_inf.Rdata")
-load("jagsout_EFD_Cann_inf.Rdata")
-load("jagsout_pLA_Cann_inf.Rdata")
-load("jagsout_MDR_Cann_inf.Rdata")
-load("jagsout_ls_Cann_inf.Rdata")
-load("jagsout_PDR_RRV_inf.Rdata")
-
-##### Load JAGS output - fits from alternate vector and virus species
-load("jagsout_PDR_MVE_Cann_inf.Rdata")
-load("jagsout_MDR_Ocam_inf.Rdata")
-load("jagsout_pLA_Ocam_inf.Rdata")
-load("jagsout_MDR_Anot_inf.Rdata")
-load("jagsout_pLA_Anot_inf.Rdata")
-
-#####  Pull out the derived/predicted values for main RRV models:
-GCD.preds <- GCD.Cann.out$BUGSoutput$sims.list$z.trait.mu.pred
[…]

### 2023-06-27 code/Shocket_2018/R0Calculation_Final.R

@@ -1,226 +1,0 @@
-##### Marta Shocket, Stanford University
-##### Updated April 2018
-
-##### Purpose: Process trait thermal response output from JAGS to calculate R0(T) for RRV model - main text calculations
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) Calculate pEA(T), M(T), and R0(T)
-##           3) Specify other helper functions
-##           4) Calculate quantiles, get optima, etc.
-##           5) Manuscript Figure 3
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Dropbox/Research Mordecai Lab/VBD Temp Project/RRV/Fitting Traits")
-
-##### Load JAGS output - fits from uniform priors
-load("jagsout_pRH_Cann.Rdata")
-load("jagsout_nLR_Cann.Rdata")
-load("jagsout_bc_RRV_Ovig.Rdata")
-load("jagsout_PDR_RRV_Ovig.Rdata")
-
-##### Load JAGS output - data-informed fits
-load("jagsout_GCD_Cann_inf.Rdata")
-load("jagsout_EFD_Cann_inf.Rdata")
-load("jagsout_pLA_Cann_inf.Rdata")
-load("jagsout_MDR_Cann_inf.Rdata")
-load("jagsout_ls_Cann_inf.Rdata")
-load("jagsout_PDR_RRV_inf.Rdata")
-
-#####  Pull out the derived/predicted values:
-GCD.preds.inf <- GCD.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-EFD.preds.inf <- EFD.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-pRH.preds <- pRH.Cann.out$BUGSoutput$sims.list$z.trait.mu.pred # no data-informed fit
-nLR.preds <- nLR.Cann.out$BUGSoutput$sims.list$z.trait.mu.pred # no data-informed fit
-pLA.preds.inf <- pLA.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-MDR.preds.inf <- MDR.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-ls.preds.inf <- ls.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
[…]

### 2023-06-27 code/Shocket_2018/R0_Seasonality_Final.R

@@ -1,154 +1,0 @@
-##### Marta Shocket, Stanford University
-##### Updated April 2018
-
-##### Purposes: 1) Calculate R0 as a function of temperature for monthly mean temperatures from example cities across Australia
-##              2) Calculate R0 as a function of temperature for nationwide, population-weighted monthly mean temperature and 
-##                 compare to data of average monthly RRV cases
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) Calculate R0(T) seasonality for 15 largest urban areas in Australia
-##           3) Calculate R0(T) seasonality nationwide (weighted by population)
-##           4) Manuscript Figures 5 and 6
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("")
-
-# Get R0 function
-R0.quantiles <- read.csv("R0Quantiles.csv")
-R0.med <- R0.quantiles$R0_full_inf_median
-
-# Get data frame of monthly avg temps for all cities
-city.temps.df <- read.csv("RRVCitiesmean_Transposed_Rounded.csv")
-
-# Get RRV human case data
-# Data from: https://cameronwebb.wordpress.com/2014/04/09/why-is-mosquito-borne-disease-risk-greater-in-autumn/
-# "Average monthly notifications of Ross River virus across Australia between 1992-2013 (National Notifiable Diseases Surveillance System)"
-rrv.cases <- read.csv("MonthlyAvgRRVCases.csv")
-
-# Temp list
-Temp.xs <- seq(5, 45, 0.2)
-N.Temp.xs <-length(Temp.xs)
-Temp.xs.ch <- as.character(Temp.xs) # which() isn't working for numbers, so convert to characters
-
-
-#######
-##### 2. Calculate R0(T) seasonality for 15 largest urban areas in Australia
-#######
-
-# Create output dataframe for R0(T) calcs
-city.R0s <- data.frame(matrix(nrow = 12, ncol = 15))
[…]

### 2023-06-27 code/Shocket_2018/SensitivityAnalysis_Final.R

@@ -1,335 +1,0 @@
-## Marta Shocket, Stanford University
-## Updated April 2018
-##
-## Purpose: Perform sensitivity analysis to determine which mosquito and parasite traits driver the
-##          thermal response of R0.
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) Deriviative and helper functions
-##           3) Calculate trait means across temp
-##           4) Sensitivity Analysis #1 - partial derivitatives
-##           4) Sensitivity Analysis #2 - holding single parameters constant
-##           5) Appendix Figure S7
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("")
-
-# Load libraties
-library(mosaic)
-
-##### Load JAGS output (informative fits when available)
-load("jagsout_pRH_Cann.Rdata")
-load("jagsout_nLR_Cann.Rdata")
-load("jagsout_bc_RRV_Ovig.Rdata")
-load("jagsout_GCD_Cann_inf.Rdata")
-load("jagsout_EFD_Cann_inf.Rdata")
-load("jagsout_pLA_Cann_inf.Rdata")
-load("jagsout_MDR_Cann_inf.Rdata")
-load("jagsout_ls_Cann_inf.Rdata")
-load("jagsout_PDR_RRV_inf.Rdata")
-
-#####  Pull out the derived/predicted values:
-GCD.preds.inf <- GCD.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-EFD.preds.inf <- EFD.Cann.out.inf$BUGSoutput$sims.list$z.trait.mu.pred
-pRH.preds <- pRH.Cann.out$BUGSoutput$sims.list$z.trait.mu.pred # no informative fit
[…]

### 2023-06-27 code/Shocket_2018/TraitFits_DataInformedPriors_Final.R

@@ -1,499 +1,0 @@
-## Marta Shocket, Stanford University
-## Updated April 2018
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for mosquito and pathogen traits for RRV model
-##            with informative priors fit from other mosquito data
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit Cx. annulirostris trait thermal responses with data-informed priors
-##           5) Plot Manuscript Figure 2
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-
-# Load Data
-data.RRV <- read.csv("data/raw/Shocket_2018/RRVTraitData.csv") # Data from database for most traits (except below)
-data.surv.proc <- read.csv("McDonaldSurvivalDataExpanded_ForJAGS.csv") # Processed survival data from McDonald 1980
-data.EFD.proc <- read.csv("McDonaldEFDDataExpanded_ForJAGS.csv") # Processed fecundity data from McDonald 1980
-
-#### EFD mean calcs for plotting
-data.EFD.20 <- subset(data.EFD.proc, T == 20)
-data.EFD.25 <- subset(data.EFD.proc, T == 25)
-data.EFD.30 <- subset(data.EFD.proc, T == 30)
-EFD.means <- data.frame(T = c(20, 25, 30), mean = c(mean(data.EFD.20$trait), mean(data.EFD.25$trait), mean(data.EFD.30$trait)), 
-                        SE = c(sd(data.EFD.20$trait)/sqrt(nrow(data.EFD.20)), sd(data.EFD.25$trait)/sqrt(nrow(data.EFD.25)), sd(data.EFD.30$trait)/sqrt(nrow(data.EFD.30))))
-
-#### Lifespan mean calcs for plotting
-data.surv.20 <- subset(data.surv.proc, T == 20)
[…]

### 2023-06-27 code/Shocket_2018/TraitFits_OtherSpecies_Final.R

@@ -1,519 +1,0 @@
-## Marta Shocket, Stanford University
-## Updated April 2018
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for mosquito and pathogen traits for RRV model
-##            from alternate vector and virus species
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit trait responses for alternate vector and virus species with uniform and data-informed priors
-##           5) Plot Appendix Figures S2, S3, and S4
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Dropbox/Research Mordecai Lab/VBD Temp Project/RRV/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-
-# Load Data for fitting traits
-data.RRV <- read.csv("RRVTraitData.csv") # Data from database for all mosquito traits, RRV, and MVE
-
-##### Subset data
-data.pLA.Anot <- subset(data.RRV, trait.name == "pEA" & host.code == "Anot")
-data.MDR.Anot <- subset(data.RRV, trait.name == "1/MDR" & host.code == "Anot")
-data.pLA.Ocam <- subset(data.RRV, trait.name == "pEA" & host.code == "Ocam")
-data.MDR.Ocam <- subset(data.RRV, trait.name == "1/MDR" & host.code == "Ocam")
-data.bc.MVE <- subset(data.RRV, trait.name == "bc" & paras.code == "MVE")
-data.PDR.MVE <- subset(data.RRV, trait.name == "EIP" & paras.code == "MVE")
-
-# Load saved prior fits (gamma dists fit to parameter posteriors)
-load("PriorFitsList.Rdata")
-pEA.prior.gamma.fits  <- as.data.frame(prior.fits.list[4])
[…]

### 2023-06-27 code/Shocket_2018/TraitFits_PriorFits_Final.R

@@ -1,412 +1,0 @@
-##### Marta Shocket, Stanford University
-##### Updated April 2018
-
-##### Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for mosquito and pathogen traits 
-##             to be used as priors for RRV model
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit trait thermal reponses to data
-##           5) Fit gamma distributions & save prior hyperparameters
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-library('MASS')
-
-# Load trait data for priors
-data.prior <- read.csv("RRVPriorData.csv")
-
-# Subset data
-data.a.prior <- subset(data.prior, trait.name == "a")
-data.EFD.prior <- subset(data.prior, trait.name == "EFD")
-data.PDR.prior <- subset(data.prior, trait.name == "PDR")
-data.pEA.prior <- subset(data.prior, trait.name == "pEA")
-data.MDR.prior <- subset(data.prior, trait.name == "MDR")
-
-# Lifespan data needs to be formatted
-data.ls1.prior <- subset(data.prior, trait.name == "1/mu")
-data.ls2.prior <- subset(data.prior, trait.name == "mu")
-data.ls2.prior$trait <- 1/data.ls2.prior$trait # Convert Yang et al. data to lifespan not mu
-data.ls.prior <- rbind(data.ls1.prior, data.ls2.prior) # combine the two data lifespan sets
-
-
-##########
-###### 2. JAGS Models
-##########
-
-############## Quadratic Model with uniform priors
-
-sink("quad.txt")
-cat("
-    model{
-    
-    ## Priors
-    cf.q ~ dunif(0, 1)
-    cf.T0 ~ dunif(0, 24)
[…]

### 2023-06-27 code/Shocket_2020/6V_R0Calculation_inf.R

@@ -1,624 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use trait thermal response posterior distributions from JAGS to calculate R0(T)
-##
-## Contents: 1) Set-up, load packages, get data, etc.
-##           2) Specify functions to calculate mean & quantiles, define R0
-##           3) Calculate R0
-##           4) Plots comparing alternate model specifications (Figure S22)
-##           5) Specify functions for Figure 7
-##           6) Main text R0 Figure 7
-##           7) Histogram Figure S21
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-##########
-###### 6. Main text R0 Figure 7 Histogram Figure S21
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-##### Load JAGS output
-load("jagsout_a_Cpip_inf.Rdata")
-load("jagsout_a_Cqui_inf.Rdata")
-load("jagsout_a_Ctar_inf.Rdata")
-load("jagsout_a_Cmel_inf.Rdata")
-
-load("jagsout_bc_CpipWNV_inf.Rdata")
-load("jagsout_c_CpipWNV_inf.Rdata")
-load("jagsout_b_CtarWNV_inf.Rdata")
-load("jagsout_bc_CuniWNV_inf.Rdata")
-load("jagsout_bc_CtarWEEV_inf.Rdata")
-load("jagsout_c_CtarWEEV_inf.Rdata")
-load("jagsout_b_CtarWEEV_inf.Rdata")
-load("jagsout_c_CtarSLEV_inf.Rdata")
-load("jagsout_b_CtarSLEV_inf.Rdata")
-load("jagsout_bc_AtriEEEV_inf.Rdata")
-load("jagsout_bc_AtaeRVFV_inf.Rdata")
-load("jagsout_c_CpipSINV_inf.Rdata")
[…]

### 2023-06-27 code/Shocket_2020/CombinedTraitsPlot.R

@@ -1,730 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Plot trait thermal responses for many Culex and Aedes species
-##
-
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-
-##########
-###### Make list of trait averages
-##########
-
-TraitAvgList <- list(Cpip.pLA.avg, Cqui.pLA.avg, Ctar.pLA.avg,
-                     Cpip.MDR.avg, Cqui.MDR.avg, Ctar.MDR.avg,
-                     Cpip.a.avg, Cqui.a.avg, data.a.Ctar,
-                     data.EFGC.Cpip, Cqui.ER.avg,
-                     Cpip.lf.avg, Cqui.lf.avg, Ctar.lf.avg,
-                     CpipWNV.PDR.avg, CtarWEEV.PDR.avg,
-                     CpipWNV.c.avg, CpipWNV.bc.avg, CtarWNV.b.avg, CuniWNV.bc.avg, 
-                     CtarWEEV.c.avg, CtarWEEV.b.avg, CtarWEEV.bc.avg, CtarSLEV.c.avg, CtarSLEV.b.avg, 
-                     CpipSINV.c.avg, AtaeSINV.c.avg, AtaeRVFV.bc.avg, AtriEEEV.bc.avg,
-                     Atri.pLA.avg, Atae.lf.avg,
-                     Cpip.pO.avg, Cqui.pO.avg,
-                     Cthe.EV.avg, Avex.EV.avg)
-save(TraitAvgList, file = "TraitAvgList.RSave")
-
-
-##########
-###### Figures of mosquito traits
-##########
-
-# Load/subset data, saved fits, and parameters for plotting
-
-Temp.xs <- seq(1, 45, 0.1)
-N.Temp.xs <-length(Temp.xs)
-
-# Load averaged trait data
-load("TraitAvgList.RSave")
[…]

### 2023-06-27 code/Shocket_2020/SensitivityAnalysis.R

@@ -1,1964 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Perform sensitivity analysis to determine which mosquito and parasite traits drive the
-##          thermal response of R0.
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) Deriviative and helper functions
-##           3) Calculate trait means across temp
-##           4) Sensitivity Analysis #1 - partial derivitatives
-##           5) Sensitivity Analysis #2 - holding single parameters constant
-##           6) Uncertainty Analysis
-##           7) Appendix Figures S2-S11
-
-
-#** For each model four panels: sensitivity analysis #1, #2, uncertainty, and then R0 with 95% CIs
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties
-library(mosaic)
-
-##### Load JAGS output
-load("jagsout_a_Cpip_inf.Rdata")
-load("jagsout_a_Cqui_inf.Rdata")
-load("jagsout_a_Ctar_inf.Rdata")
-load("jagsout_a_Cmel_inf.Rdata")
-
-load("jagsout_bc_CpipWNV_inf.Rdata")
-load("jagsout_c_CpipWNV_inf.Rdata")
-load("jagsout_b_CtarWNV_inf.Rdata")
-load("jagsout_bc_CuniWNV_inf.Rdata")
-load("jagsout_bc_CtarWEEV_inf.Rdata")
-load("jagsout_c_CtarWEEV_inf.Rdata")
-load("jagsout_b_CtarWEEV_inf.Rdata")
-load("jagsout_c_CtarSLEV_inf.Rdata")
-load("jagsout_b_CtarSLEV_inf.Rdata")
-load("jagsout_bc_AtriEEEV_inf.Rdata")
[…]

### 2023-06-27 code/Shocket_2020/TraitFits_EFD.R

@@ -1,781 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for fecundity related traits for many Culex and Aedes species
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit EFD thermal responses with uniform priors
-##           5) Fit EFD thermal responses for priors
-##           6) Fit gamma distributions to EFD prior thermal responses
-##           7) Fit EFD thermal responses with data-informed priors
-##           8) Calculate treatment averages for plotting
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-library('MASS')
-
-# Load Data
-data.E <- read.csv("TraitData_EFD.csv")
-
-# Subset Data by trait
-data.EFOC.Cpip <- subset(data.E, Trait.Name == "EFOC")
-data.EPR <- subset(data.E, Trait.Name == "EPR")
-data.pO <- subset(data.E, Trait.Name == "pO")
-
-# Subset Data
-data.EPR.Cqui <- subset(data.EPR, host.code == "Cqui")
-data.EPR.Cmol <- subset(data.EPR, host.code == "Cmol")
-data.EPR.Cpal <- subset(data.EPR, host.code == "Cpal")
-data.EPR.Ador <- subset(data.EPR, host.code == "Ador")
-
-# Subset Data
-data.pO.Cpip <- subset(data.pO, host.code == "Cpip")
-data.pO.Cqui <- subset(data.pO, host.code == "Cqui")
-data.pO.Cmol <- subset(data.pO, host.code == "Cmol")
[…]

### 2023-06-27 code/Shocket_2020/TraitFits_EV.R

@@ -1,583 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for egg viability for many Culex and Aedes species
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit EV thermal responses with uniform priors
-##           5) Fit EV thermal responses for priors
-##           6) Fit gamma distributions to EV prior thermal responses
-##           7) Fit EV thermal responses with data-informed priors
-##           8) Calculate treatment averages for plotting
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-library('MASS')
-
-# Load Data
-data.EV <- read.csv("TraitData_EV.csv") # Data from database for most traits (except below)
-unique(data.EV$host.code)
-
-# Subset Data
-data.EV.Cpip <- subset(data.EV, host.code == "Cpip")
-data.EV.Cqui <- subset(data.EV, host.code == "Cqui")
-data.EV.Cthe <- subset(data.EV, host.code == "Cthe")
-data.EV.Cmol <- subset(data.EV, host.code == "Cmol")
-data.EV.Avex <- subset(data.EV, host.code == "Avex")
-data.EV.Ador <- subset(data.EV, host.code == "Ador")
-data.EV.Anig <- subset(data.EV, host.code == "Anig")
-
-par(mfrow = c(1,1), mar = c(4.5, 4.5, 1, 1))
-plot(trait ~ T, xlim = c(5, 45), data = data.EV, ylab = "EV for Cx. mosquitoes", xlab = "Temperature")
-points(trait ~ T, data = data.EV.Cpip, col = "grey")
[…]

### 2023-06-27 code/Shocket_2020/TraitFits_PDR.R

@@ -1,1190 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for parasite development rate (PDR) for six temperature arboviruses
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit PDR thermal responses with uniform priors
-##           5) Fit PDR thermal responses for priors
-##           6) Fit gamma distributions to PDR prior thermal responses
-##           7) Fit PDR thermal responses with data-informed priors
-##           8) Calculate Treatment averages for plotting
-##           9) Plot preliminary figures
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-
-# Load Data
-data.PDR <- read.csv("TraitData_PDR.csv") # Data from database for most traits (except below)
-unique(data.PDR$joint.code)
-
-# Subset Data
-data.PDR.CpipWNV <- subset(data.PDR, joint.code == "CpipWNV")
-data.PDR.CtarWNV <- subset(data.PDR, joint.code == "CtarWNV")
-data.PDR.CquiWNV <- subset(data.PDR, joint.code == "CquiWNV")
-data.PDR.CuniWNV <- subset(data.PDR, joint.code == "CuniWNV")
-
-data.PDR.CtarWEEV <- subset(data.PDR, joint.code == "CtarWEEV")
-data.PDR.CtarSLEV <- subset(data.PDR, joint.code == "CtarSLEV")
-
-data.PDR.AtaeSINV <- subset(data.PDR, joint.code == "AtaeSINV")
[…]

### 2023-06-27 code/Shocket_2020/TraitFits_a.R

@@ -1,692 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for biting rate (a) for many Culex and Aedes species
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit a thermal responses with uniform priors
-##           5) Fit a thermal responses for priors
-##           6) Fit gamma distributions to a prior thermal responses
-##           7) Fit a thermal responses with data-informed priors
-##           8) Calculate treatment averages for plotting
-##           9) Plot preliminary figures
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-library('MASS')
-
-# Load Data - NOTE: these data are in GCD (gonotrophic cycle duration) format
-data.a <- read.csv("TraitData_a.csv")
-
-# Subset Data
-data.a.Cpip <- subset(data.a, host.code == "Cpip") 
-data.a.Cqui <- subset(data.a, host.code == "Cqui")
-data.a.Ctar <- subset(data.a, host.code == "Ctar")
-data.a.Cpal <- subset(data.a, host.code == "Cpal")
-data.a.Cmel <- subset(data.a, host.code == "Cmel") # This data was added later, not included in priors for other species
-
-# Plot Data
-par(mfrow = c(1,1))
-plot(trait ~ T, xlim = c(5, 45), ylim = c(0,0.5), data = data.a, ylab = "a for Cx. mosquitoes", xlab = "Temperature")
-points(1/trait ~ T, data = data.a.Cpip, col = "grey")
[…]

### 2023-06-27 code/Shocket_2020/TraitFits_bc.R

@@ -1,1766 +1,0 @@
-## Marta Shocket, Stanford University / UCLA, marta.shocket@gmail.com
-## Started Jan 2018, Updated August 2020
-##
-## Purpose: Use Bayesian Inference (JAGS) to fit temperature-dependent functions for vector competence tarits (bc, b, c) for six arboviruses in many Culex and Aedes species
-##
-## Contents: 1) Set-up,load packages, get data, etc.
-##           2) JAGS models
-##           3) Shared settings for all models
-##           4) Fit bc thermal responses with uniform priors
-##           5) Fit bc thermal responses for priors
-##           6) Fit gamma distributions to bc prior thermal responses
-##           7) Fit bc thermal responses with data-informed priors
-##           8) Calculate treatment averages for plotting
-
-
-##########
-###### 1. Set up workspace, load packages, get data, etc.
-##########
-
-# Set working directory
-setwd("~/Fitting Traits")
-
-# Load libraties for fitting traits
-library('R2jags')
-library('mcmcplots')
-
-# Load Data
-data.bc <- read.csv("TraitData_bc.csv") # Data from database for most traits (except below)
-unique(data.bc$joint.code)
-
-# Subset Data
-data.c.CpipWNV <- subset(data.bc, joint.code == "CpipWNV" & trait.name == "c")
-data.bc.CpipWNV <- subset(data.bc, joint.code == "CpipWNV" & trait.name == "bc")
-
-data.b.CtarWNV <- subset(data.bc, joint.code == "CtarWNV" & trait.name == "b")
-data.bc.CuniWNV <- subset(data.bc, joint.code == "CuniWNV")
-
-data.bc.CtarWEEV <- subset(data.bc, joint.code == "CtarWEEV" & trait.name == "bc")
-data.c.CtarWEEV <- subset(data.bc, joint.code == "CtarWEEV" & trait.name == "c")
[…]

### 2023-06-27 code/TEMP_R0_uncertainty.R

@@ -1,815 +1,0 @@
-## Title: Prior distributions of mosquito thermal traits #######################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Compute prior distributions for thermal trait parameters and provide
-##          functions for sampling from these distributions
-##
-## Contents: 1) Set-up, load in necessary packages and data-sets
-##           2) Instantiate data frame incorporating all axes of variation
-##           3) Transform thermal trait parameters into model parameters
-##           4) Calculate R0 across all thermal trait parameter samples
-##           5) Create visualizations of R0 distributions
-##           6) Functions to sample from thermal trait parameter distributions
-##
-##
-## Inputs:  data - data/clean/ThermalTraitSamples.csv
-##
-##
-##          code - code/Mordecai2017/mcmc_utils_all.R
-##                 code/Mordecai2017/temp_functions_all.R
-##
-## Outputs: functions:
-##          data:
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized February 2023
-## _____________________________________________________________________________
-
-# 1) Set-up,load packages, get data, etc. ----
-
-### Load Libraries ----
-library(tidyverse)
-
-# Helper function to thin vectors
-res_reduce <- function(df, new_length) {
-  old_length <- length(unique(df))
-  if (old_length < new_length) {
-    warning("new_length is larger than old length. Vector will be unchanged")
-    new_length <- old_length
-  }
-  ret <- unique(df)[seq(1, length(unique(df)), length.out = new_length)]
-}
-
-### Load in data and functions ----
-# Load samples of thermal trait parameters
-samples.All <- read.csv("data/clean/ThermalTraitSamples.csv") %>% 
-  # thin samples for analyses
-  filter(sample_num %in% res_reduce(sample_num, 300))
-
-# Load functions from Mordecai et al., 2017
-# This file contains tools for analysis and visualization.
[…]

### 2023-06-27 code/TEMPmeanTPCs.R

@@ -1,238 +1,0 @@
-## Title: Transform TPC traits into model parameters #######################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Transform trait values, which we have fit TPCs to from data, in 
-##          order to use in model analyses
-##
-## Contents: 0) Set-up, load in necessary packages and data-sets
-##           1) Define accessory functions
-##           2) Create TPCs and deal with missing data
-##           3) Create parameters data frame
-##           4) Save parameters data frame
-##           *) Diagnostics and visualizations
-##
-##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: data - data/clean/parameter_TPCs.rds
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-# _______________________________________________________________________________
-
-# 0) Set-up, load in necessary packages and data-sets ---------------------
-
-# Load Libraries
-library(tidyverse)
-library(reshape2)
-
-# 1) Define accessory functions -------------------------------------------
-# Define TPC functions
-# Briere function
-Briere <- function(q, Tmin, Tmax) {
-  function(t) {
-    pmax(q * t * (t - Tmin) * (Tmax - t)^(1 / 2), 0, na.rm = TRUE)
-  }
-}
-# Quadratic function
-Quadratic <- function(q, Tmin, Tmax) {
-  function(t) {
-    pmax(-q * (t - Tmin) * (t - Tmax), 0, na.rm = TRUE)
-  }
-}
-# Linear
-Linear <- function(q, Tmax) {
-  function(t) {
-    pmax(q * (Tmax - t), 0, na.RM = FALSE)
-  }
-}
-
-# Function: designate proper thermal response function # !!! This should go somewhere else
-# - output is a function of temperature
-get.thermal.response <- function(data_in, Temperature) {
-  parms <- dplyr::select(data_in, c, T0, Tm)
-  function_type <- dplyr::select(data_in, func)
-  
-  temp_function <- case_when(
-    function_type == "Briere" ~ Briere(parms$c, parms$T0, parms$Tm),
[…]

### 2023-06-27 code/Tesla_2018/GLMM_TempAnalysis.R

@@ -1,205 +1,0 @@
-# Metadata:
-
-#Mosquito_ID = unique identifier per mosquito
-#Replicate: 1, 2 = biological replicate
-#Batch: Mosquito cohort - we ignore this as this is mostly captured by variation across replicates
-#Day: 3, 6, 9, 12, 15, 18, 21 - days post infection mosquitoes were destructively sampled for virus
-#Temperature: 16, 20, 24, 28, 32, 34, 36, 38 C
-#Infected: 0 = no, 1 = yes (positive bodies = 1)
-#Disseminated: 0 = no, 1 = yes (positive head and legs = 1)
-#Infectious = 0 = no, 1 = yes (positive saliva = 1)
-
-#We are interested in the probability of infection, dissemination, and infectiousness out of all 
-#mosquitoes exposed and the probability of infectiousness out of all of those mosquitoes successfully 
-#infected.
-
-##############################
-# PRODUCTS
-
-# 2 charts to copy from R Graphics Device
-
-# 4 "best model" tables, one fore each response variable:
-#	BEST_Infected
-#	BEST_Disseminated
-#	BEST_Infectious
-#	BEST_Efficiency
-
-
-# load packages, run the installs, if needed
-library(readxl)	#install.packages("readxl")
-library(lme4)	#install.packages("lme4")
-library(MuMIn)	#install.packages("MuMIn")
-
-antilogit <- function(x) { exp(x) / (1 + exp(x) ) }
-
-############################################
-#load data, center and scale continuous variables
-
-setwd("C:/Users/Courtney Murdock/Documents/Dropbox/Research/Research/Papers&Posters&Talks/Tenure/Zika_NSFRAPID/Aim 2/ProcRoySoc/Dryad")
-dat <- read_excel("InfectionData.xlsx")
-dat$Tfactor <- as.factor(dat$Temperature)
-dat$Dfactor <- as.factor(dat$Day)
-dat$Tscale <- scale(dat$Temperature)
-dat$Dscale <- scale(dat$Day)
-
-summary(dat) # by-column summaries of variables
-str(dat)	# structure of the data in each column
-
-#infected only datafile
[…]

### 2023-06-27 code/Tesla_2018/Informative_ZIKV_IndividualParameterFitCode.R

@@ -1,277 +1,0 @@
-### This file will process the temperature data and create the individual parameter 
-### samples for all the traits that are included in the DENV R0 model. 
-
-wd = "C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Tesla_2018"
-
-## Loading the required packages and supplementary code for sampling and analysis.
-library(IDPmisc)
-library('rjags')
-library('MASS')
-
-# This file contains tools for analysis and visualization.
-source("C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Tesla_2018/mcmc_utils_all.R")
-
-# This file contains the thermal response functions and their derivatives.
-source("C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Tesla_2018/temp_functions_all.R")
-
-
-# Load posterior distributions of traits previously fit for Aedes aegypti and DENV
-load(paste(wd, "LifespanFits_2016-03-30-informative.Rsave", sep = "/"))
-
-load(paste(wd, "Informative_Aegypti_DENV_ParameterFits_2016-03-30.Rsave", sep = "/"))
-
-# Fit gamma distributions of priors for each previous trait from which we want to derive priors
-
-gamma.fits.PDR = apply(PDR.samps, 2, function(df) fitdistr(df, "gamma")$estimate)
-
-lf.samps.pos = lf.DENV.samps[,c(1:4,6)]
-lf.samps.pos$qd <- -lf.samps.pos$qd
-gamma.fits.lf = apply(lf.samps.pos, 2, function(df) fitdistr(df, "gamma")$estimate)
-
-# the previous work fit b and c separately
-# Since c has a broader distribution, use it for a prior
-gamma.fits.c = apply(c.samps, 2, function(df) fitdistr(df, "gamma")$estimate)
-
-# Creating a small constant to keep denominators from being zero.
-ec<-0.000001 
-
-## Loading the data
-data.all <- read.csv(
-  "C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/data/raw/Tesla_2018/zikv_traits.csv", header=TRUE)
-head(data.all)
-str(data.all)
-
-## Now the code will choose all the temperature sensitive traits and fit either a
-## Briere or Quadratic model to it using MCMC sampling.
[…]

### 2023-06-27 code/Tesla_2018/ZIKV_IndividualParameterFitCode.R

@@ -1,327 +1,0 @@
-### This file will process the temperature data and create the individual parameter 
-### samples for all the traits that are included in the DENV R0 model. 
-
-
-## Loading the required packages and supplementary code for sampling and analysis.
-library(IDPmisc)
-library('rjags')
-
-# This file contains tools for analysis and visualization.
-source("mcmc_utils_all.R") 
-
-# This file contains the thermal response functions
-source("temp_functions_all.R") 
-
-# Creating a small constant to keep denominators from being zero.
-ec<-0.000001 
-
-## Loading the data
-data.all <- read.csv("zikv_traits.csv", header=TRUE)
-head(data.all)
-str(data.all)
-
-## Now the code will choose all the temperature sensitive traits and fit either a
-## Briere or Quadratic model to it using MCMC sampling.
-# Specifing the parameters that control the MCMC (these will be used throughout the code). 
-
-n.chains <- 5
-n.adapt <- 5000
-n.samps <- 5000
-
-priors1<-list()
-priors1$names<-c( "T0", "Tm", "c","tau")
-priors1$fun<-c( "uniform", "uniform", "gamma","gamma")
-priors1$hyper<-matrix(NA, ncol=4, nrow=3)
-priors1$hyper[,1]<-c(0, 24, NA)
-priors1$hyper[,2]<-c(25, 45, NA)
-priors1$hyper[,3]<-c(1, 10, NA)
-priors1$hyper[,4]<-c(0.0001, 0.0001, NA)
-
-
-###########################################
-## The next trait we'll be choosing is the vector competence, b*c.
-## Due to the data that was collected it will be necessary
-## to decompose it into its two parts, b and c.
-
-# Choose b, the probability a human will be bitten and infected by
-# an infectious mosquito (ie. transmission).
-
-data <- data.all[ which(data.all$trait.name=="bc"),]
-
-# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
-# the data.
-
-plot(trait ~ T, data = data)
-
-# Given the data we've chosen to use the Quadratic function. 
-
-jags <- jags.model('C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Mordecai_2017/jags-quad-neg.bug',
-                   data = list('Y' = data$trait, 'T' = data$T, 'N'= length(data$T)),
[…]

### 2023-06-27 code/Tesla_2018/ZIKV_R0_plotting.R

@@ -1,341 +1,0 @@
-# Plotting ZIKV temperature-dependent traits and R0
-
-library(IDPmisc)
-library(rjags)
-library(RColorBrewer)
-
-
-# This file contains tools for analysis and visualization.
-source("mcmc_utils_all.R") 
-
-# This file contains the thermal response functions
-source("temp_functions_all.R") 
-
-# Load posterior distributions of traits previously fit for Aedes aegypti and DENV
-load("Informative_Aegypti_DENV_ParameterFits_2016-03-30.Rsave")
-# remove the vector competence and EIR fits since we'll use the new ones
-remove(b.samps, c.samps, PDR.samps)
-
-# Next, load the new ZIKV fits to overwrite the old ones for lf.samps, PDR.samps, and b.samps
-load("zikv_trait_fits_uninformative.Rsave")
-
-# Load the pre-calculated posterior distributions of R0 and traits
-load("ZIKV_model_outputs-uninformative.Rsave")
-
-# Temperature sequence
-temp = seq(5,45,by=0.1)
-t<-length(temp)
-
-# Length of samples, assuming they're all the same length
-n = dim(b.samps)[1]
-n.samps = nrow(b.samps)
-
-
-# Thinned samples
-thinned<-seq(1, n, by = 5)
-lthin = length(thinned)
-# thinned.mu<-seq(1, n.mu, length = lthin)
-
-# Creating a small constant to keep denominators from being zero.
-ec<-1/24
-
-##################################
-## Calculate the posterior distribution of each parameter and R0 vs. T
-## Creating the function encoding the value of R0 as a function of the parameters
-## Unlike in previous formulations, our b.samps fit includes bc (probability of infectiousness given exposure)
-
-myR0<-function(a, b, PDR, MDR, EFD, e2a, lf){
-  mu = 1/(lf + ec)
-  ((a^2*b*(EFD*e2a*MDR/(mu)^2)*exp((-mu/(PDR+ec))))/(mu))^0.5
-}
-
[…]

### 2023-06-27 code/Tesla_2018/mcmc_utils_all.R

@@ -1,267 +1,0 @@
-## This file contains utility functions for manipulating mcmc samps,
-## and calculating/plotting predictions
-
-library(IDPmisc)
-library('rjags')
-
-## first some functions to put the mcmc samples into a properly
-## labeled data frame, depending on the functional form
-
-# Added by Daniel W, for the linear, columns = inter, slope, sigma
-make.linear.samps<-function(coda.samps, nchains=2, samp.lims=c(151, 5000), sig=TRUE){
-  n.inter<-slope<-sigma<-NULL
-  l1<-samp.lims[1]
-  l2<-samp.lims[2]
-  for(i in 1:nchains){
-    n.inter<-c(n.inter, coda.samps[[i]][l1:l2,1])
-    slope<-c(slope, coda.samps[[i]][l1:l2,2])
-    if(sig) sigma<-c(sigma, coda.samps[[i]][l1:l2,3])
-  }
-  if(sig){
-    samps<-data.frame(matrix(c(n.inter, slope, sigma), ncol=3, byrow=FALSE))
-    names(samps)<-c("n.inter", "slope", "sigma")
-  }
-  else{
-    samps<-data.frame(matrix(c(n.inter, slope), ncol=2, byrow=FALSE))
-    names(samps)<-c("n.inter", "slope", "sigma")
-    
-  }
-  return(samps)
-}
-
-make.nlinear.samps<-function(coda.samps, nchains=2, samp.lims=c(151, 5000), sig=TRUE){
-  inter<-n.slope<-sigma<-NULL
-  l1<-samp.lims[1]
-  l2<-samp.lims[2]
-  for(i in 1:nchains){
-    inter<-c(inter, coda.samps[[i]][l1:l2,1])
-    n.slope<-c(n.slope, coda.samps[[i]][l1:l2,2])
-    if(sig) sigma<-c(sigma, coda.samps[[i]][l1:l2,3])
-  }
-  if(sig){
-    samps<-data.frame(matrix(c(inter, n.slope, sigma), ncol=3, byrow=FALSE))
-    names(samps)<-c("inter", "n.slope", "sigma")
-  }
-  else{
-    samps<-data.frame(matrix(c(inter, n.slope), ncol=2, byrow=FALSE))
-    names(samps)<-c("inter", "n.slope", "sigma")
-    
-  }
-  return(samps)
-}
[…]

### 2023-06-27 code/Tesla_2018/temp_functions_all.R

@@ -1,127 +1,0 @@
-# temp_functions_all.R
-AIC.c<-function(myfit){##, ndata){
-  k<-(length(coef(myfit))+1)
-  lLfit<-logLik(myfit)
-  
-  n<-attr(lLfit, "nobs")
-  cort<-2*k*(k+1)/(n-k-1)
-
-  AICc <- -2*lLfit + 2*k + cort
-
-  return(AICc)
-
-}
-
-linear<-function(T, inter, slope){
-  x = inter+slope*T
-  x[which(x<0)] <- 0
-  x
-}
-
-linear.trunc<-function(T, inter, slope){
-  x = inter+slope*T
-  x[which(x>1)] <- 1
-  x[which(x<0)] <- 0
-  x
-}
-
-
-quad.trunc<-function(T, T0, Tm, qd){
-  1*((qd*(T-T0)*(T-Tm))>1) + (qd*(T-T0)*(T-Tm)*(T<=Tm)*(T>=T0))*((qd*(T-T0)*(T-Tm))<1)
-}
-
-briere<-function(t, c, Tm, T0){
-  b=c()
-  for (i in 1:length(t))
-  {
-    if(t[i]>T0 && t[i]<Tm){  b[i]<-(c*t[i]*(t[i]-T0)*sqrt(Tm-t[i]))  }
-    else {b[i]<-0}
-  }
-  b
-}
-
-briere.trunc<-function(t, c, Tm, T0){
-  b=c()
-  for (i in 1:length(t))
-  {
-    if(t[i]>T0 && t[i]<Tm){  b[i]<-(c*t[i]*(t[i]-T0)*sqrt(Tm-t[i]))  }
-    else {b[i]<-0}
-  }
-  b[which(b>1)]<-1
-  b
-}
-
-
-
-d_briere<-function(t, c, Tm, T0){
-  b=c()
-  for (i in 1:length(t))
-  {
-    if (t[i]>T0 && t[i]<Tm)  {b[i]<-(c*(-5*(t[i]^2) + 3*t[i]*T0 + 4*t[i]*Tm - 2*T0*Tm)/(2*sqrt(Tm-t[i]))
-    )}
-    else {b[i]<-0}
-  }
-  b
-}
-
-d_briere_trunc<-function(t, c, Tm, T0){
-  b=c()
-  for (i in 1:length(t))
-  {
[…]

### 2023-06-27 code/Villena_2021/ConsistencyAnalysis.R

@@ -1,300 +1,0 @@
-######################################################
-## Code to reproduce the consistency analysis 
-## requires datafile "data/Prevalence_Pfalciparum.csv"
-## code by Oswaldo C. Villena, Leah R. Johnson
-## 11 January 2022
-######################################################
-
-## Example to validate the model for An. gambiae/P. falciparum 
-## First load the necessary R packages and files for the computation and
-## visualization 
-library("statmod")
-library("visreg")
-library("dplyr")
-library("sjPlot")
-library("texreg")
-library("coefplot")
-
-## Load data
-dat1<-read.csv("data/Prevalence_Pfalciparum.csv", header=TRUE)
-
-## select data >= 1990
-datf<-dat1[dat1$year_start>=1990,]
-
-## Select covariates of interest
-
-dat2 <- datf[,c(2,4,5,12,13,14,15,17,18,19)]
-summary(dat2)
-
-## Remove NA's 
-
-ww<- which(!is.na(dat2$GDP_adjusted))
-dat2<- dat2[ww,]
-
-ww<- which(!is.na(dat2$lGDP))
-dat2<- dat2[ww,]
-
-
-## Select data only for Africa
-dat2$AFR <- dat2$continent=="Africa"
-
-
-## We consider a few combinations of S(T) measures and population
-dat2$R0G0.lpop<-dat2$STGZ*log(dat2$pop_den)
-dat2$R0G0.lgdp<- dat2$STGZ*log(dat2$GDP_adjusted)
-dat2$lR0G0.pop<-log((dat2$STGZ*dat2$pop_den)+1)
-dat2$lR0G0.gdp<- log((dat2$STGZ*dat2$GDP_adjusted)+1)
-
-##Check correlation
-vary<- c(2,3,7:15)
-pairs(dat2[,vary])
-
-## Models for the Presence/Absence Data
-## 1 lpop_den only
-reg1<-glm(pa ~ lpop_den*AFR - AFR, family=binomial, data=dat2)
-summary(reg1)
-
-## 2 lGDP only
-reg2<-glm(pa ~ lGDP*AFR - AFR, family=binomial, data=dat2)
-summary(reg2)
-
-## 3 ROGO only
-reg3<-glm(pa ~ STGZ*AFR - AFR, family=binomial, data=dat2)
-summary(reg3)
-
-## 4 socio factors only
[…]

### 2023-06-27 code/Villena_2021/SuitabilityMetricCalcs.R

@@ -1,169 +1,0 @@
-###################################################################
-## Code to reproduce the estimation of the suitability metric S(T)
-## requires datafile "Angamb_Pfalc_samps.Rsave"
-## code by Oswaldo C. Villena, Leah R. Johnson
-## 11 January 2022
-###################################################################
-
-
-##Example to calculate the  S(T) for An. gambiae/P. falciparum
-## First load the necessary R packages and files for the computation and
-## visualization 
-library(matrixStats)
-library(Hmisc)
-
-
-## First, we identify the files where the posterior samples for each
-## component of R0 are saved.
-
-post<- load("data/Angamb_Pfalc_samps.Rsave") ## Rdata file from previous step
-
-
-## Next we set up the temperatures over which we will be evaluating S(T)
-## as well as the thinning interval for the samples.
-
-temp = seq(5,45,by=0.1)	##temperature sequence
-
-t<-length(temp)  ## length of temperature
-
-n = dim(a.sampsgampf)[1]    	## length of samples
-
-thinned<-seq(1, n, by=20)  ## thinned samples
-
-lthin<-length(thinned)  ## number of thinned samples
-
-ec<-0.000001  ## small constant used to keep denominators from being numerically zero
-
-
-## Function encoding the value of S(T) as a function of the parameters
-myST <-function(a, PDR, MDR, efd, pea, bc, mu){
-  ((a^2*bc*(efd*pea*MDR/mu^2)*exp(-mu/(PDR+ec)))/(mu+ec))^0.5
-}
-
-## The following code runs through the samples and calculates the
-## posterior trajectories (i.e. as a function of temperatures) of each
-## component and of S(T), and sets up a matrix to store them (each
-## column is a trajectory)
-
[…]

### 2023-06-27 code/Villena_2021/TPC_Traits.R

@@ -1,145 +1,0 @@
-###################################################################
-## Code to reproduce the estimation of the thermal performance curves (TPC)
-## requires datafile "data/traits.csv"
-## code by Oswaldo C. Villena, Leah R. Johnson
-## 11 January 2022
-###################################################################
-
-
-## First load the necessary R packages and files for the computation and
-## visualization
-library('rjags')
-library('MASS')
-
-
-## Next load data
-data.all<-read.csv("data/traits.csv", header=TRUE)
-
-## Select the trait of interest. Here we showed as an example MDR for An. gambiae
-data<-data.all[which(data.all$trait.name=="bc.succ"), 2:9]
-plot(data$T, data$trait/100) ## visualize your data
-
-
-## specify the parameters that control the MCMC
-n.chains<-5
-n.adapt<-10000
-n.samps<-20000
-n.burn<- 10000
-
-
-##Choose the appropiate model for the specific trait 
-
-##Briere model (MDR, PDR, a)
-
-jags_briere.bug <- "model {
-
-for (i in 1:N) {
-Y[i] ~ dnorm(mu[i], tau)T(0,)
-mu.temp[i] <- c*T[i]*(T[i]-T0)*sqrt((Tm-T[i])*(Tm>T[i]))
-mu[i] <- 0*(mu.temp[i]<0) + mu.temp[i]*(mu.temp[i]>0)
-
-}
-
-c ~ dgamma(1,10)
-Tm ~ dunif(25,45)
-T0  ~ dunif(0, 24)
-sigma<-1/tau
-tau ~ dgamma(0.0001, 0.0001)
-
-}"
-
-
-## Concave down quadratic model (PEA, EFD, bc)
-
-jags_quad.bug <- "model {
-
-for (i in 1:N) {
-Y[i] ~ dnorm(mu[i], tau)T(0,)
-mu[i] <- -qd*(T[i]-T0)*(T[i]-Tm)*((T[i]>T0))*((T[i]<Tm))
-}
-
-Tm  ~ dunif(25,45)
-T0 ~ dunif(0,24)
-qd  ~ dgamma(1,1)
-sigma<-1/tau
-tau ~ dgamma(0.0001, 0.0001)
-
-}"
-
-
-## Concave up quadratic model (mu)
-
-jags_quad.bug <- "model {
-
-for (i in 1:N) {
[…]

### 2023-06-27 code/create-figures.R

@@ -1,993 +1,0 @@
-## Title: Generate figures for "Thermal optima" manuscript ########################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Create figures used in the manuscript
-##
-## Contents: 0) Load in necessary packages, functions, settings
-##           1) Build vector trait data frame
-##           2) Build all traits and model outputs data frame
-##           3) Build thermal characteristics data frame
-##
-##
-## Settings:  Options for reducing the resolution of variables for memory
-##            allocation and figure plotting purposes
-##
-## Inputs:  data - results/AllThermChar_thin.rds
-##                 data/clean/AllOutputs_thin.rds
-##
-## Outputs: (in ./figures)
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-# _______________________________________________________________________________
-
-
-# 0) Load libraries and data sets. Define helper functions ----------------
-
-# Load libraries
-library(tidyverse)
-library(latex2exp) # nec
-library(viridis) # nec
-library(cowplot) # nec
-library(modeest)
-library(MetBrewer) #nec
-library(svglite) #nec
-
-# Load in data sets
-data.CT <- read_rds("results/CT_vals.rds")
-data.R0 <- read_rds("results/R0_vals.rds")
-data.Topt <- read_rds("results/Topt_vals.rds")
-data.Topt.restrict <- read_rds("results/Topt_alt_vals.rds")
-
-# Helper function to place legends in empty facets of plot grids
-# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
-shift_legend <- function(p) {
-  pnls <- cowplot::plot_to_gtable(p) %>%
-    gtable::gtable_filter("panel") %>%
-    with(setNames(grobs, layout$name)) %>%
-    purrr::keep(~ identical(.x, zeroGrob()))
-  
-  if (length(pnls) == 0) {return(p)} #stop("No empty facets in the plot")
-  
[…]

### 2023-06-27 code/data-cleaning.R

@@ -19,7 +19,6 @@
 ##          A table explaining how traits are transformed into the ones used in
 ##          analyses
 ##
-## Outputs: data - data/clean/ThermalTraitData.rds
 ##
 ## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
 ## Initialized February 2023
@@ -27,7 +26,6 @@
 
 # 0) Set-up, load in necessary packages and data-sets ---------------------
 library(tidyverse)
-
 
 # 1) Load in all data sets ------------------------------------------------
 
@@ -69,7 +67,6 @@ data.Mordecai2017.Aegypti <- read.csv("data/raw/Mordecai_2017/aegyptiDENVmodelTe
     ref == "McLean_et_al_1974_CanJMicobiol" ~ "DENV",
     ref == "Watts_et_al_1987_AJTMH" ~ "DENV"
   ), NA)) %>% 
-  # mutate(pathogen = ifelse(trait.name %in% c("b", "c", "PDR"), "DENV", NA)) %>%
   dplyr::select(-c("trait2", "trait2.name"))
 
 data.Mordecai2017.Albopictus <- read.csv("data/raw/Mordecai_2017/albopictusCHIKVmodelTempData_2016-03-26.csv", header = TRUE) %>%
@@ -84,7 +81,6 @@ data.Mordecai2017.Albopictus <- read.csv("data/raw/Mordecai_2017/albopictusCHIKV
     ref == "Westbrook_Thesis_2010" ~ "CHIKV",
     ref == "Xiao_et_al_2014_Arch Virol" ~ "DENV"
   ), NA)) %>% 
-  # mutate(pathogen = ifelse(trait.name %in% c("b", "c", "PDR"), "CHIKV", NA)) %>%
   dplyr::select(-c("trait2", "trait2.name"))
 
 data.Mordecai2017.AedesSpp <- read.csv("data/raw/Mordecai_2017/Aedes_prior_data.csv", header = TRUE) %>%
@@ -273,15 +269,15 @@ data.Villena2022 <- read.csv("data/raw/Villena_2022/traits.csv", header = TRUE) 
   dplyr::select(trait.name, T, trait, mosquito_species, pathogen, lead_author, year) 
 
 # Following Villena 2022, use An. arabiensis and An. Pseudopunctipennis data for Anopheles gambiae biting rate
-data.Villena2021 <- data.Villena2021 %>% 
[…]

### 2023-06-27 code/deprecated/Bayoh2001-lifespan-analysis.R

@@ -1,141 +1,0 @@
-## Title: Fitting lifespan data from Mordecai 2013 ###############################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Estimate mortality rate from data provided in Bayoh 2001, following 
-##          process outlined in Mordecai et al., 2013
-##
-## Contents: 1) Set-up, load in necessary packages and data-sets
-##           2) Load in and clean data as necessary
-##           3) Filter data to values prescribed in Mordecai 2013 supplement
-##           4) Fit exponential survival curves
-##           5) Get estimates of mu and translate to lifespan
-##           6) Output data in correct format for further processing (to data_cleaning.R)
-##
-##
-## Inputs:  data/raw/Mordecai_2013/survival_data.csv
-##
-##
-## Outputs: data - data/clean/Bayoh2001_mortality.csv
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-
-
-
-# 1) Set-up load in necessary packages ----
-require(tidyverse)
-require(stringr)
-
-# 2) Load in and clean data as necessary ----
-###* Using data from (Bayoh 2001).
-mortality.data <- read.csv("data/raw/Mordecai_2013/survival_data.csv", header = TRUE) %>%
-  # change columns to be: day, temperature (T), and proportion alive (prop.alive)
-  pivot_longer(cols = X5.C:X40.C, names_to = "T", values_to = "prop.alive") %>% 
-  rename(day = D) %>% 
-  mutate(T = readr::parse_number(T)) %>% 
-  relocate(T, .before = day) %>%
-  arrange(T, day)
-
-
-# 3) Filter data to values prescribed in Mordecai 2013 supplement ----
-
-###* Find the final day where the population proportion exceeded 1%.
-# Get the first day at which zero living mosquitoes were reported
-first_zero <- mortality.data %>%
-  group_by(T) %>%
-  filter(prop.alive == 0) %>%
-  summarize(first.zero = min(day)) %>%
-  # population was persisted through the entire experiment at 20C
-  add_row(T = 20, first.zero = Inf)
-
-# Get the last day the proportion alive exceeded 0.1%
-cutoff_days <- mortality.data %>%
-  # Ignore days after the first zero was reported
-  right_join(first_zero) %>%
[…]

### 2023-06-27 code/deprecated/OLDthermal-trait-priors.R

@@ -1,302 +1,0 @@
-## Title: Prior distributions of mosquito thermal traits #######################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Compute prior distributions for thermal trait parameters and provide
-##          functions for sampling from these distributions
-##
-## Contents: 1) Set-up, load in necessary packages and data-sets
-##           2) Define accessory functions
-##           3) Calculate prior distributions of thermal trait parameters from data
-##           4) Save thermal trait parameter distributions
-##           5) Functions to sample from thermal trait parameter distributions
-##
-##
-## Inputs:  data - data/raw/aegyptiDENVmodelTempData_2016-03-30.csv
-##                 data/raw/albopictusCHIKVmodelTempData_2016-03-26.csv
-##                 data/clean/trait_table.csv
-##                 data/clean/gamma_fits.csv
-##
-##          code - code/Mordecai2017/mcmc_utils_all.R
-##                 code/Mordecai2017/temp_functions_all.R
-##
-## Outputs: functions:
-##          data - data/clean/ThermalTraitSamples.csv
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized February 2023
-## Modified from original code provided in the following articles:
-# * Mordecai, E. A., J. M. Caldwell, M. K. Grossman, C. A. Lippi, L. R. Johnson, M. Neira, J. R. Rohr, S. J. Ryan, V. Savage, M. S. Shocket, R. Sippy, A. M. Stewart Ibarra, M. B. Thomas, and O. Villena. 2019. Thermal biology of mosquito-borne disease. Ecology letters 22:1690–1708.
-# * Mordecai, E. A., J. M. Cohen, M. V. Evans, P. Gudapati, L. R. Johnson, C. A. Lippi, K. Miazgowicz, C. C. Murdock, J. R. Rohr, S. J. Ryan, V. Savage, M. S. Shocket, A. Stewart Ibarra, M. B. Thomas, and D. P. Weikel. 2017. Detecting the impact of temperature on transmission of Zika, dengue, and chikungunya using mechanistic models. PLoS neglected tropical diseases 11:e0005568.
[…]

### 2023-06-27 code/deprecated/TEMP_TPC_diagnostics.R

@@ -1,202 +1,0 @@
-source("code/get-thermal-trait-priors.R")
-data_in <- data.in
-
-distinct_combos <- distinct(data_in, trait.name, system_ID)
-
-
-n.chains <-2 # 5
-n.adapt <- 100 # 5000
-n.samps <- 100 # 5000
-
-
-samples <- tibble(
-  trait = as.character(),
-  system_ID = as.character(),
-  T0 = as.double(),
-  Tm = as.double(),
-  c = as.double(), # !!! note that we're using c as a generic parameter for Briere or Quadratic
-  sample_num = as.double(),
-  func = as.character()
-)
-
-for (sample_num in 1:dim(distinct_combos)[1]) {
-  print(paste0("System # ", sample_num, "--------------------------------------------------------"))
-  system_sample <- distinct_combos$system_ID[sample_num]
-  trait_in <- distinct_combos$trait.name[sample_num]
-
-  mosquito_in <- filter(data.in, system_ID == system_sample) %>%
-    dplyr::select(mosquito_species) %>%
-    unique() %>%
-    as.character()
-  pathogen_in <- filter(data.in, system_ID == system_sample) %>%
-    dplyr::select(pathogen) %>%
-    unique() %>%
-    as.character()
-
-
-  temp_sample <- thermtrait.prior.sample(data.in, trait_in, mosquito_in, pathogen_in,
-    n.chains, n.adapt, n.samps,
-    old_informative = FALSE
-  )
-
-  temp_sample <- temp_sample %>%
-    mutate(
-      trait = trait_in,
-      system_ID = system_sample
-    )
-  samples <- rbind(samples, temp_sample)
-  
-}
-
-
-# Save samples for now
-# write_csv(samples, "data/clean/temp_samples.csv")
-
-# -------------------------------------------------------------------------
-
-
-# samples <- read_csv("data/clean/temp_samples.csv")
-
-library(reshape2)
-library(cowplot)
-
-# 2) Histograms of parameter distributions of thermal traits ----
-plot_df <- samples %>%
-  dplyr::select(-func) %>%
-  mutate(temp_diff = Tm - T0) %>%
-  mutate(logc = log(c)) %>%
-  melt(id = c("system_ID", "trait", "sample_num")) #%>%
-  # filter(system_ID %in% c(
-  #   "Aedes aegypti / DENV", "Aedes aegypti / none",
[…]

### 2023-06-27 code/deprecated/get-outputs.R

@@ -1,139 +1,0 @@
-## Title: Analysis code for "Thermal optima" manuscript ########################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Build data frames for: 1) vector traits, 2) all traits and model
-##          outputs, and 3) thermal characteristics of transmission
-##
-## Contents: 0) Load in necessary packages, functions, settings
-##           1) Build vector trait data frame
-##           2) Build all traits and model outputs data frame
-##           3) Build thermal characteristics data frame
-##
-##
-## Settings:  Options for reducing the resolution of variables for memory
-##            allocation and figure plotting purposes
-##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: (in ./results)
-##          1) VectorTraits.csv - vector trait data frame
-##          2) AllOutputs.csv - all traits and model outputs data frame
-##          3) ThermalCharacteristics.csv - thermal characteristics data frame
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-# _______________________________________________________________________________
-
-
-# 0) Load in necessary packages, functions, settings ----------------------
-# Packages
-library(tidyverse)
-
-# Functions for computing transmission measures
-source("code/output-functions.R")
-
-# 1) Calculate outputs ----------------------------------------------------
-
-## Combine all parameter combinations into a large table
-AllOutputs_df <- data.in.analysis %>%
-  # Name the model (just in case this is handier than referring to sigmaH)
-  mutate(Model = ifelse(is.infinite(sigmaH), "Ross-Macdonald model", "Chitnis model")) %>%
-  ## Compute outputs ##
-  # Vector lifespan !!! do this in an earlier dataset instead
-  # mutate(test = sigmaV_f * deltaL * lf)
-  
-  # Vector abundance
-  mutate(V0 = compute.V0(.)) %>%
-  # Basic reproduction number
-  mutate(R0 = sqrt(compute.RH(.) * compute.RV(.))) %>%
-  # If any R0 = NA, replace it with R0 = 0
-  # (we only get R0=NA when V0<0, i.e. when mosquito recruitment is less than mortality)
-  replace_na(list(R0 = 0)) %>%
[…]

### 2023-06-27 code/deprecated/make_hyperparams_table.R

@@ -1,19 +1,0 @@
-load("code/Mordecai2017/aedes_prior_gamma_fits.Rsave")
-
-library(reshape2)
-library(tidyverse)
-
-trait_names <- c("a", "b", "c", "e2a", "EFD", "lf", "MDR", "PDR", "TFD")
-
-hyperparams_df <- data.frame(trait = "a", melt(gamma.fits.a), multiplier = 0.1) %>%
-  rbind(data.frame(trait = "b", melt(gamma.fits.b), multiplier = 0.5)) %>%
-  rbind(data.frame(trait = "c", melt(gamma.fits.c), multiplier = 0.5)) %>%
-  rbind(data.frame(trait = "e2a", melt(gamma.fits.e2a), multiplier = 0.1)) %>%
-  rbind(data.frame(trait = "EFD", melt(gamma.fits.EFD), multiplier = 0.1)) %>%
-  rbind(data.frame(trait = "lf", melt(gamma.fits.lf), multiplier = 0.01)) %>%
-  rbind(data.frame(trait = "MDR", melt(gamma.fits.MDR), multiplier = 0.1)) %>%
-  rbind(data.frame(trait = "PDR", melt(gamma.fits.PDR), multiplier = 0.5)) %>%
-  rbind(data.frame(trait = "TFD", melt(gamma.fits.TFD), multiplier = 0.1)) %>%
-  rbind(data.frame(trait = "lf", melt(gamma.fits.lf), multiplier = 0.01))
-
-write_csv(hyperparams_df, "data/clean/gamma_fits.csv")

### 2023-06-27 code/deprecated/prelim_viz.R

@@ -1,424 +1,0 @@
-## Title: Visualization of thermal traits ######################################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Produce visualizations of thermal trait distributions for a sanity check
-##
-## Contents: 1) Set-up, load in necessary packages and data-sets
-##           2) Histograms of parameter distributions of thermal traits
-##           3) Plots of thermal trait functions with 89% HCI
-##           4)
-##
-##
-## Inputs:  data - data/clean/gamma_fits.csv
-##
-##          code - code/Mordecai2017/mcmc_utils_all.R
-##                 code/Mordecai2017/temp_functions_all.R
-##
-## Outputs: functions:
-##          data - data/clean/ThermalTraitSamples.csv
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized February 2023
-
-# 1) Set-up, load in necessary packages and data-sets ----
-### Load Libraries ----
-library(tidyverse)
-library(reshape2)
-library(cowplot)
-library(latex2exp) # nec
-library(viridis) # nec
-
-### Load in data and functions ----
-# Load samples of thermal trait parameters
-samples.All <- read.csv("data/clean/ThermalTraitSamples.csv")
-
-# Load functions from Mordecai et al., 2017
-# This file contains tools for analysis and visualization.
-source("code/Mordecai2017/mcmc_utils_all.R")
-
-# This file contains the thermal response functions and their derivatives.
-source("code/Mordecai2017/temp_functions_all.R")
-
-# This file contains functions to compute model outputs like R0 and sensitivities
-source("code/output-functions.R")
-
-# 2) Histograms of parameter distributions of thermal traits ----
-plot_df <- samples.All %>%
-  dplyr::select(-func) %>% 
-  melt(id = c("Species", "trait", "sample_num"))
-
-###* Figure: thermal trait parameter posterior distributions ----
-parm_hists <- plot_df %>%
[…]

### 2023-06-27 code/deprecated/survival_analysis_Mordecai2013.R

@@ -1,65 +1,0 @@
-library(tidyverse)
-
-# Treat survival data separately.
-# - Use data from the first day of the experiment, one day before reaching 0.01
-#   threshold to three days after the threshold, giving 6 data points
-# - Use the exponent(?) of the constant mortality function as an independent 
-#   observation of mortality at each temperature
-survival.Mordecai2013 <- read.csv("data/raw/Mordecai_2013/survival_data.csv", header = TRUE) %>%
-  pivot_longer(cols = X5.C:X40.C, names_to = "T", values_to = "prop.alive") %>% 
-  rename(day = D) %>% 
-  mutate(T = readr::parse_number(T)) %>% 
-  # replace NAs (beyond the first five days) with 0's
-  mutate(prop.alive = ifelse(day > 5 & is.na(prop.alive), 0, prop.alive))
-
-# !!! add in days prior to experiment, so that Gompertz fit is non-singular. This is not justified.
-fake_data <- expand.grid(day = seq(-20,0), T = unique(survival.Mordecai2013$T), prop.alive = 1)
-
-survival.Mordecai2013 <- rbind(survival.Mordecai2013, fake_data) %>% 
-  arrange(day)
-
-# Gompertz function
-Gompertz <- function(x, k, lag){
-  ymax <- 1
-  y0 <- 0
-  result <- y0 + (ymax -y0)*exp(-exp(k*(lag-x)/(ymax-y0) + 1) )
-  # result <- pmin(1, result)
-  return(result)
-}
-
-survival_fit.df <- tibble(T = numeric(), y0 = numeric(), ymax = numeric(), 
-                          k = numeric(), lag = numeric())
-# had to remove extreme high and low temperatures because fit is singular 
-for (TT in unique(survival.Mordecai2013$T)) {
-  df <- filter(survival.Mordecai2013, T == TT)
-  # Fit Gompertz curves to the data
-  Gomp_fit <- nls(1-prop.alive ~ Gompertz(day, k, lag),
-                  data = df,
-                  start = list(k = 0.1, lag = 0))
-  Gomp_coefs <- coef(Gomp_fit)
-  
-  survival_fit.df <- add_row(survival_fit.df, T = TT, k = Gomp_coefs["k"], 
-                             lag = Gomp_coefs["lag"])
-}
-
[…]

### 2023-06-27 code/get-CT-vals.R

@@ -1,221 +1,0 @@
-# 0) Set-up, load in necessary packages and data-sets ---------------------
-
-# Load Libraries
-library(tidyverse)
-library(reshape2)
-library(multidplyr)
-library(foreach)
-library(doParallel)
-library(progress)
-
-# 1) Define accessory functions -------------------------------------------
-
-eps <- .Machine$double.eps
-
-# Function: Slice data to optimize usage of parallel processing and memory
-slice<-function(x,n) {
-  N<-length(x);
-  lapply(seq(1,N,n),function(i) x[i:min(i+n-1,N)])
-}
-
-# Function: evaluate CTmin, CTmax, CTwidth and their means, medians, and highest
-#           prob. intervals across samples
-CT_heat_func <- function(in_df, system_name) {
-  out_df <- in_df %>%
-    expand_grid(filter(data.Vec, system_ID == system_name)) %>%
-    data.table::data.table() %>%
-    mutate(RV = ifelse(is.infinite(sigmaH),
-                       sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald
-                       sigmaH * sigmaV * betaH * KH / ((1 / (lf + eps)) * (sigmaH * KH + sigmaV * V0)))) %>%
-    mutate(bV = ifelse(is.infinite(sigmaH),
-                       sigmaV, # Ross-Macdonald model
-                       sigmaV * sigmaH * KH / (sigmaH * KH + sigmaV * V0 + eps))) %>%
-    mutate(RH = ifelse(V0 == 0,
-                       0,
-                       bV * betaV * V0 * exp(-1 / (lf * etaV)) / (KH * (gammaH + muH) + eps))) %>%
-    # Basic reproduction number
-    mutate(R0 = sqrt(RV*RH)) %>%
-    # Filter to maximum value of R0
-    group_by(system_ID, sample_num, sigmaH, KH) %>%
-    filter(R0 > 1) 
-  
-  # If R0 < 1 across all temperatures, report the following:
-  #  CTmin = Inf, CTmax = -Inf, CTwidth = 0
-  if (dim(out_df)[1] == 0) {
-    out_df <- expand_grid(select(in_df, sigmaH, KH, Model),
-                          system_ID = system_name,
-                          variable = c("CTmax", "CTmin", "CTwidth")) %>%
-      distinct() %>%
-      mutate(mean = case_when(
-        variable == "CTmax" ~ -Inf,
-        variable == "CTmin" ~ Inf,
-        variable == "CTwidth" ~ 0
[…]

### 2023-06-27 code/get-mosquito-traits.R

@@ -1,253 +1,0 @@
-## Kyle Dahlin, University of Georgia, kydahlin@gmail.com
-## Initialized September 2021
-##
-## Title: Mosquito trait functions #############################################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Functions for determining mosquito traits as parameters for the
-##          transmission model. Traits may vary by mosquito species, pathogen
-##          of interest, and temperature.
-##
-## Contents: 1) Set-up, load in necessary packages and data-sets
-##           2) Define accessory functions
-##           3) Build parameter table-generating function for mosquito-pathogen pairs
-##
-##
-## Inputs:  (currently not implemented but code can be modified to take
-##           different values for temperature)
-##        temp_seq: a sequence of temperature values at which to evaluate
-##          mosquito-pathogen traits
-##
-##
-## Outputs: MosquitoThermalResponse.csv
-##          a table of vector+pathogen traits with columns of
-##          Species (= mosquito species), Pathogen (= name of pathogen),
-##          Temperature (in Celsius) and all mosquito-pathogen traits:
-##          maximum biting frequency (sigma_V), fecundity (f),
-##          probability of egg survival to adulthood (delta_L),
-##          immature mosquito development rate (rho_L), and adult mosquito
-##          mortality rate (mu_V)
-
-# 1) Set-up,load packages, get data, etc.#######################################
-
-### Load Libraries ----
-library(tidyverse)
-
-### Get data ----
-
-# Read in mosquito-specific traits
-MosqThermParms <- read_csv("./data/MosquitoThermalParameters.csv",
-  col_types = cols()
-)
-
-
-# Define mosquito species names and codes:
-sp_names <- c(
-  "Aedes aegypti", "Aedes albopictus", "Culex quinquefasciatus",
-  "Anopheles spp."
-)
-sp_code <- c("AE", "AL", "CQ", "AN")
-names(sp_names) <- sp_code
-
-# Define pathogen names
-path_names <- c("DENV", "ZIKV", "WNV", "P.fal.")
-
-# Define mosquito-pathogen pairs
[…]

### 2023-06-27 code/get-outputs.R

@@ -14,10 +14,6 @@
 ##           *) Diagnostics and visualizations
 ##
 ##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: data - data/clean/parameter_TPCs.rds
-##
 ## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
 ## Initialized March 2023
 # _______________________________________________________________________________
@@ -39,12 +35,11 @@ init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
                   sigmaH = c(), KH = c(), variable = c(),
                   lowHCI = c(), highHCI = c(), mean = c(), median = c())
 
-# Thin out the vector data set as necessary
 
-thin_size <- 300
-
-
+# Load in vector trait data
 data.Vec <- read_rds("results/VecTPC_vals.rds")
+# Thin out the vector trait data samples
+thin_size <- 500
 samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
 sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
@@ -52,11 +47,13 @@ sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
 data.Vec <- data.Vec%>% 
   filter(sample_num %in% sample_inds)
 
+# Load in host trait data
+data.Host <- read_rds("results/Host_vals.rds")
 
 # 1) Define accessory functions -------------------------------------------
 
 # Function: Slice data to optimize usage of parallel processing and memory
-slice<-function(x,n) {
+slice_func<-function(x,n) {
   N<-length(x);
   lapply(seq(1,N,n),function(i) x[i:min(i+n-1,N)])
 }
@@ -120,53 +117,13 @@ Topt_heat_func <- function(in_df, system_name) {
     ungroup() %>%
     pivot_longer(cols = Topt, names_to = "variable", values_to = "value") %>%
     group_by(system_ID, Model, sigmaH, KH, variable) %>%
-    # partition(cluster) %>%
     summarise(
       lowHCI = quantile(value, 0.055),
       highHCI = quantile(value, 0.945),
       mean = mean(value),
       median = median(value),
       .groups = "keep"
-    ) #%>%
[…]

### 2023-06-27 code/get-thermal-trait-priors.R

@@ -53,7 +53,6 @@ source("code/Mordecai_2017/temp_functions_all.R")
 ### * Load in data ----
 # Trait data
 data.in <- data.in.TPC
-# data.in <- read_csv("data/clean/data_for_TPC_fitting.csv") # !!! remove this later so this can interact with the main-analysis.R script
 
 # 1) Define accessory functions -------------------------------------------
 
@@ -341,8 +340,6 @@ get.prior_hyperparams <- function(in_data, TPC_function, variable_names,
   # Initialize the hyperparameter list
   hypers <- NULL
   
-  # inits_list <- list(T0 = 5, Tm = 31, c = 0.00007)
-  
   # get samples from trait TPC parameter distributions
   temp_samples <- run.jags(
     in_data, TPC_function, variable_names,
@@ -500,19 +497,17 @@ distinct_combos <- data_in %>%
   filter(system_ID != "Culex spp. / WNV" | trait.name != "MDR") %>%
   filter(system_ID != "Culex spp. / WNV" | trait.name != "PDR")
 
-
 samples <- tibble(
   trait = as.character(),
   system_ID = as.character(),
   T0 = as.double(),
   Tm = as.double(),
-  c = as.double(), # !!! note that we're using c as a generic parameter for Briere or Quadratic
+  c = as.double(), # note that we're using c as a generic parameter for Briere or Quadratic
   sample_num = as.double(),
   func = as.character()
 )
 
 # Go through all trait/system combinations to generate TPC parameter posterior samples
-# system.time(
 for (system_index in 1:dim(distinct_combos)[1]) {
   # Pull system information
   system_sample <- distinct_combos$system_ID[system_index]
@@ -557,8 +552,6 @@ distinct_samples <- data.in.transform %>%
   distinct(system_ID, trait)
 
 print(distinct_samples)
-# 3) Save trait TPC parameter posterior distribution samples --------------
-
 
 
 # *) Diagnostics & visualizations -----------------------------------------
@@ -659,7 +652,7 @@ if (plot_bool) {
     summarise(mean_val = mean(Trait_val), .groups = "keep") %>%
     unique()
   
-  # get edges of 89% HCI of samples # !!! not calculated correctly?
+  # get edges of 89% HCI of samples
   quantsTPC_df <- TPC_df %>%
     group_by(system_ID, trait, Temperature) %>%
     mutate(lowHCI_val = quantile(Trait_val, 0.055)) %>%

### 2023-06-27 code/host-traits.R

@@ -1,0 +1,61 @@
+## Title: Vertebrate host traits and parameters #######################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Record and save host traits for use in analyses
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+# _______________________________________________________________________________
+
+## Set resolution for host trait variation
+# Host density vector: Number of values to include to consider for vertebrate host density
+KH_vec_length <- 300
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 300
+
+## Host life history & behavioral traits
+# Host recruitment rate:
+# upper estimate from range for Primate traits: (0.001150685, 0.009624300)
+lambdaH_baseline <- .005
+
+# Host mortality rate:
+# estimate from range for Primate traits: lifespan (8.6, 60) years
+muH_baseline <- 1 / (365 * 20)
+
+# Host maximum biting tolerance (mosquitoes bites per day)
+sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
+  c(1, 10, 20, 50, 100, 1000, Inf) %>%
+  unique() %>% sort()
+sigmaH_baseline <- 100
+
+# Host carrying capacity
+KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length) %>%
+  c(10^seq(-2,5)) %>%
+  unique() %>% sort()
+
+## Host-related pathogen parameters
+# Probability of becoming infected after bite from infectious mosquito
+# operates as a scaling parameter
+betaH_baseline <- 1
+
+# Host recovery rate
+# plausible estimate for infectious period = (5-14 days)
+gammaH_vec <- 1 / c(5, 14)
+gammaH_baseline <- 1 / 5
+
+data.Host <- expand_grid(
+  # Life-history parameters
+  lambdaH = lambdaH_baseline,
+  muH = muH_baseline,
+  KH = KH_vec,
+  sigmaH = sigmaH_vec,
+  # Infection-related parameters
+  gammaH = gammaH_baseline,
+  betaH = betaH_baseline) %>%
+  as.data.frame() %>%
+  mutate(Model = ifelse(is.infinite(sigmaH), "Ross-Macdonald model", "Chitnis model"))
+
+# Save host traits
+write_rds(data.Host, "results/Host_vals.rds")

### 2023-06-27 code/main-analysis.R

@@ -1,106 +1,0 @@
-## Title: Mosquito Thermal Trait Data processing ###############################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Conduct all parts of the analysis
-##
-## Contents: 0) Set-up, load in necessary packages and data-sets
-##           1) Load empirical trait data
-##           2) Fit trait thermal performance curves to trait data
-##           3) Translate traits into model parameters
-##           4) Build data set incorporating all axes of variation
-##           5) Calculate model outputs
-##           6) Illustrate model outputs (might be done separately)
-##           7) Conduct sensitivity analysis
-##
-##
-## Inputs:
-##
-##
-## Outputs:
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-
-
-# 0) Set-up, load in necessary packages and data-sets ---------------------
-library(tidyverse)
-
-set.seed(512)
-
-# 1) Load empirical trait data --------------------------------------------
-
-# # Run this to produce dataset from raw data
-# source("code/data-cleaning.R")
-
-# # Run this to load pre-processed dataset
-# # load dataset for fitting trait TPCs
-data.in.TPC <- read_rds("data/clean/data_for_TPC_fitting.rds")
-
-# 2) Fit trait thermal performance curves to trait data -------------------
-
-# Set parameters for MCMC
-n.chains <- 5 # 3 # 5
-n.adapt <- 5000 # 100 # 5000
-n.samps <- 5000 # 1000 # 5000
-
-# Do you want to look at diagnostic plots?
-plot_bool <- TRUE
-
-# # Run this to generate samples of trait TPC parameters from informed posterior distributions
-source("code/get-thermal-trait-priors.R")
-
-# write_rds(data.in.transform, "data/clean/TPC_param_samples.rds")
-
-# # Run this to load pre-processed data set
-data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
-
-# 3) Translate traits into model parameters -------------------------------
-
-# Define temperature range of study
-Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
-
-# Thin sample size
-thin_size <- 1000 # full = 1000, thin = 100
-
-plot_bool = FALSE
-source("code/trait-transform.R")
-
-# write_rds(data.in.params, "data/clean/parameter_TPCs.rds", compress = "gz")
[…]

### 2023-06-27 code/output-functions.R

@@ -1,118 +1,0 @@
-## For questions, contact Kyle Dahlin, kydahlin@gmail.com
-## Initialized Oct 2020
-##
-## Title: Functions for getting model outputs like R0 #############
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Provide functions for evaluating several model properties and equilibrium values
-##
-## Contents: A set of functions listed below
-##
-##          compute.RH: Evaluates the host type reproduction number
-##
-##          compute.RV: Evaluates the mosquito type reproduction number
-##
-##          compute.R0: Evaluates the basic reproduction number (actually just sqrt(RH*RV))
-##
-##          compute.CHmin: Evaluates the critical minimum host density for pathogen persistence
-##
-##          compute.CHmax: Evaluates the critical maximum host density for pathogen persistence
-
-
-# Helper function: Reduces resolution of a vector by sub-sampling to length new_length
-res_reduce <- function(df, new_length) {
-  old_length <- length(unique(df))
-  if (old_length < new_length) {
-    warning("new_length is larger than old length. Vector will be unchanged")
-    new_length <- old_length
-  }
-  ret <- unique(df)[seq(1, length(unique(df)), length.out = new_length)]
-}
-
-## 1) Functions for computing outputs ##########################################
-
-### Equilibrium total vector population-----------------------------------------
-compute.V0 <- function(input) {
-  with(input, {
-    eps <- .Machine$double.eps
-    # if(is.null(lf)) {lf = 1 / (muV + eps)}
-    temp <- sigmaV_f * deltaL
-    # check if net reproduction rate exceeds mortality rate
-    temp_bool <- temp > (1 / lf)
-    ifelse(temp_bool,
-           V0 <- KL * rhoL * lf * (1 - 1 / (lf * temp + eps)) ,
-           V0 <- 0 # if mortality exceeds reproduction, set to zero
-    )
-  })
-}
-
-### Host-to-mosquito reproduction number----------------------------------------
-compute.RH <- function(input) {
-  with(input, {
-    eps <- .Machine$double.eps
-    # Derive intermediate quantities
-    bV <- ifelse(is.infinite(sigmaH),
[…]

### 2023-06-27 code/sensitivity.R

@@ -14,10 +14,6 @@
 ##           *) Diagnostics and visualizations
 ##
 ##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: data - data/clean/parameter_TPCs.rds
-##
 ## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
 ## Initialized March 2023
 # _______________________________________________________________________________
@@ -29,8 +25,7 @@ library(tidyverse)
 library(reshape2)
 library(multidplyr)
 library(foreach)
-# library(doParallel)
-library(doSNOW)
+library(doParallel)
 library(progress)
 library(latex2exp) # nec
 library(viridis) # nec
@@ -43,7 +38,6 @@ library(HDInterval)
 if (!exists("cl")) {
   cl <- parallel::makeCluster(parallel::detectCores() - 2)
   registerDoSNOW(cl)
-  # cluster_library(cluster, c("dplyr", "tidyr"))
 }
 
 eps <- .Machine$double.eps
@@ -61,22 +55,12 @@ data.Host <- read_rds("results/Host_vals.rds")
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 
 # R0 data
-data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
-
-
-
-
-# KH_vec_length <- 300 # full = 300, thin = 20
-# 
-# # Biting tolerance vector: Number of values to consider for biting tolerance
-# sigmaH_vec_length <- 300 # full = 300, thin = 20
-# 
-# source("code/trait-variation.R")
+data.R0 <- read_rds("results/R0_vals.rds")
 
 # 1) Define accessory functions -------------------------------------------
 
 # Function: Slice data to optimize usage of parallel processing and memory
-slice<-function(x,n) {
+slice_func<-function(x,n) {
   N<-length(x);
   lapply(seq(1,N,n),function(i) x[i:min(i+n-1,N)])
 }
@@ -87,12 +71,9 @@ appender_sigmaH <- function(string) {
 appender_KH <- function(string) {
   unname(TeX(paste("$K_H = $", string)))}
 
+# 2) Set up mosquito trait data frames ----------------------------------------
 
[…]

### 2023-06-27 code/trait-transform.R

@@ -13,10 +13,6 @@
 ##           *) Diagnostics and visualizations
 ##
 ##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: data - data/clean/parameter_TPCs.rds
-##
 ## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
 ## Initialized March 2023
 # _______________________________________________________________________________
@@ -48,7 +44,7 @@ Linear <- function(q, Tmax) {
   }
 }
 
-# Function: designate proper thermal response function # !!! This should go somewhere else
+# Function: designate proper thermal response function
 # - output is a function of temperature
 get.thermal.response <- function(data_in, Temperature) {
   parms <- dplyr::select(data_in, c, T0, Tm)
@@ -62,7 +58,6 @@ get.thermal.response <- function(data_in, Temperature) {
   
   out <- temp_function(Temperature)
 }
-
 
 # 2) Create TPCs and deal with missing data ----
 
@@ -87,7 +82,6 @@ TPC_df <- data.in.transform %>%
   # i.e. putting together reproductive traits to estimate eggs per female per day (EFD)
   mutate(e2a = case_when(
     !(is.na(e2a)) ~ e2a,
-    # !(is.na(pRH * nLR * pLA)) ~ pRH * nLR * pLA,
     !(is.na(EV * pLA)) ~ EV * pLA
   )) %>% 
   mutate(EFD = case_when(
@@ -121,23 +115,6 @@ combined_df <- left_join(Infection_df, noInfection_df)%>%
   ) %>% 
   relocate(system_ID, mosquito_species, pathogen, Temperature, sample_num)
 
-
-# # Check what data we're missing (we'll go back and use substitutes for these)
-# missing_traits_df <- combined_df %>% 
-#   pivot_longer(cols = bc:MDR) %>% 
-#   dplyr::filter(is.na(value)) %>% 
-#   dplyr::select(-c(sample_num, Temperature)) %>% 
-#   filter(system_ID %in% c(
-#     "Aedes aegypti / DENV", "Aedes aegypti / none",
-#     "Aedes aegypti / ZIKV", "Aedes aegypti / none",
-#     "Aedes albopictus / DENV", "Aedes albopictus / none",
-#     "Culex quinquefasciatus / WNV", "Culex quinquefasciatus / none",
-#     "Anopheles gambiae / Plasmodium falciparum",
-#     "Anopheles gambiae / none"
-#   )) %>% 
-#   unique()
[…]

### 2023-06-27 code/trait-variation.R

@@ -1,96 +1,0 @@
-## Title: Transform TPC traits into model parameters #######################
-##
-## Project: Global zoonoses - spillover of mosquito-borne pathogens
-##
-## Purpose: Transform trait values, which we have fit TPCs to from data, in
-##          order to use in model analyses
-##
-## Contents: 0) Set-up, load in necessary packages and data-sets
-##           1) Set *host* parameters
-##           2) Set non-TPC *mosquito* parameters
-##           *) Diagnostics and visualizations
-##
-##
-## Inputs:  data - data/clean/trait_transforms.rds
-##
-## Outputs: data - data/clean/parameter_TPCs.rds
-##
-## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
-## Initialized March 2023
-# _______________________________________________________________________________
-
-# 0) Set-up, load in necessary packages and data-sets ---------------------
-
-# Load Libraries
-library(tidyverse)
-library(reshape2)
-library(multidplyr)
-library(foreach)
-library(doParallel)
-library(progress)
-
-
-# 1) Set *host* parameters --------------------------------
-
-## Host life history & behavioral traits
-# Host recruitment rate:
-# upper estimate from range for Primate traits: (0.001150685, 0.009624300)
-lambdaH_baseline <- .005
-
-# Host mortality rate:
-# estimate from range for Primate traits: lifespan (8.6, 60) years
-# muH_vec <- 1 / (365 * c(1, 25))
-muH_baseline <- 1 / (365 * 20)
-
-# Host maximum biting tolerance (mosquitoes bites per day)
-sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
-  c(1, 10, 20, 50, 100, 1000, Inf) %>%
-  unique() %>% sort()
-sigmaH_baseline <- 100
-
-# Host carrying capacity
-KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length) %>%
-  c(10^seq(-2,5)) %>%
-  unique() %>% sort()
-
-## Host-related pathogen parameters
-# Probability of becoming infected after bite from infectious mosquito
-# operates as a scaling parameter
-# betaH_vec <- c(.25, .75)
-betaH_baseline <- 1
-
-# Host recovery rate
-# plausible estimate for infectious period = (2-14 days)
-gammaH_vec <- 1 / c(5, 14)
-gammaH_baseline <- 1 / 5
-
[…]

### 2023-06-27 code/vector-traits.R

@@ -1,0 +1,69 @@
+## Title: Mosquito Thermal Trait Data processing ###############################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Conduct all parts of the analysis
+##
+## Contents: 0) Set-up, load in necessary packages and data-sets
+##           1) Load empirical trait data
+##           2) Fit trait thermal performance curves to trait data
+##           3) Translate traits into model parameters
+##           4) Build data set incorporating all axes of variation
+##           5) Calculate model outputs
+##           6) Illustrate model outputs (might be done separately)
+##           7) Conduct sensitivity analysis
+##
+##
+## Inputs:
+##
+##
+## Outputs:
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+library(tidyverse)
+
+# 1) Load empirical trait data --------------------------------------------
+
+# # Run this to produce workable dataset from raw data for the first time
+# plot_bool <- FALSE # decide whether you'd like to generate a diagnostic plot
+# source("code/data-cleaning.R")
+
+# # Alternatively, run this to load pre-processed dataset
+# # load dataset for fitting trait TPCs
+# data.in.TPC <- read_rds("data/clean/data_for_TPC_fitting.rds")
+
+# 2) Fit trait thermal performance curves to trait data -------------------
+
+# # Run this to generate samples of trait TPC parameters from informed posterior distributions for the first time
+# # Set parameters for MCMC
+# n.chains <- 5
+# n.adapt <- 5000
+# n.samps <- 5000
+# # Do you want to look at diagnostic plots?
+# plot_bool <- FALSE
+# # source("code/get-thermal-trait-priors.R")
+# # write_rds(data.in.transform, "results/TPC_param_samples.rds")
+
+# Alternatively, run this to load pre-processed data set
+data.in.transform <- read_rds("results/TPC_param_samples.rds")
+
+# 3) Translate traits into model parameters -------------------------------
+
+# Define temperature range of study
+Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
+
+# Thin sample size
+thin_size <- 500 # full = 1000, thin = 100
+
+plot_bool = FALSE
+source("code/trait-transform.R")
+
[…]

### 2023-06-27 figures/klowden_lea_79_figure.R

@@ -1,32 +1,0 @@
-library(tidyverse)
-library(cowplot)
-
-defense_df <- tibble(
-  Species = c("Aedes triseriatus", "Aedes aegypti", "Aedes sollicitans",
-              "Aedes taeniorhynchus", "Anopheles crucians","Aedes triseriatus", "Aedes aegypti", "Aedes sollicitans",
-              "Aedes taeniorhynchus", "Anopheles crucians"),
-  restrained = c(1,1,1,1,1,0,0,0,0,0),
-  fed_percent = c(.86,1,.67,1,NA,.1,.01,.02,.04,.06),
-  n = c(83,117,164,20,0,240,122,1252,796,32)
-) %>%
-  mutate(estimate_fed = floor(n*fed_percent)) %>% 
-  group_by(Species, restrained) %>% 
-  rowwise() %>% 
-  mutate(low_CI = ifelse(!is.na(fed_percent), 
-                         binom.test(estimate_fed, n, p = 0.5, conf.level = 0.95)$conf.int[1],
-                         NA)) %>% 
-  mutate(high_CI = ifelse(!is.na(fed_percent), 
-                         binom.test(estimate_fed, n, p = 0.5, conf.level = 0.95)$conf.int[2],
-                         NA)) %>% 
-  mutate(restrained = ifelse(restrained, "Restrained", "Unrestrained"))
-
-
-defense_plot <- defense_df %>% 
-  ggplot(aes(x = restrained, y = fed_percent, fill = Species)) +
-  geom_boxplot(aes(ymin = low_CI, lower = low_CI, middle = fed_percent, upper = high_CI, ymax = high_CI),
-               stat = "identity",
-               outlier.shape = NA) +
-  scale_x_discrete(name = "") +
-  scale_y_continuous(name = "Proportion of mosquitoes fed") +
-  ggtitle("Across species, mosquito feeding success is significantly higher when hosts are restrained (Klowden & Lea 1979)") +
-  theme_minimal_hgrid(16) 

### 2023-10-02 manuscript-figures.Rmd
re-do sensitivity analysis
also reduce resolution for host traits

@@
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = abs_median, color = focal_var, linetype = (as.factor(sign_median)))) +
+  ggplot(aes(x = Temperature, y = median, color = focal_var, linetype = (as.factor(sign_median)))) +
   geom_line(lwd = 1) +
@@
     name = unname(TeX("Local sensitivity of $R_0$")),
-    limits = 10^c(-4, 3),
-    breaks = 10^(seq(-4, 3)),
-    labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
-    trans = "log10",
+    # limits = c(-2,2),
+    # limits = 10^c(-4, 3),
+    # breaks = 10^(seq(-4, 3)),
+    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
+    # trans = "log10",
     expand = c(0, 0)

### 2023-10-02 code/get-outputs.R

@@ -189,14 +189,15 @@ CT_heat_func <- function(in_df, system_name) {
 
 # Function: Evaluate local derivatives of R0 with respect to mosquito traits
 R0_deriv_func <- function(in_df) {
-  out_df <- in_df %>% # Pr(surviving the EIP)
-    mutate(thetaV = exp(-1 / (lf * etaV + eps))) %>% 
-    # Host constant
-    mutate(C = betaH / (KH * (gammaH + muH))) %>% 
-    # Biting rate term
-    mutate(K = ifelse(is.infinite(sigmaH), 1, sigmaH * KH / (sigmaH * KH + sigmaV * V0))) %>% 
-    # Basic reproduction number
-    mutate(R0 = K * sqrt(C * sigmaV^2 * V0 * betaV * thetaV * lf)) %>% 
+  out_df <- in_df %>% 
+    # # Pr(surviving the EIP)
+    # mutate(thetaV = exp(-1 / (lf * etaV + eps))) %>% 
+    # # Host constant
+    # mutate(C = betaH / (KH * (gammaH + muH))) %>% 
+    # # Biting rate term
+    # mutate(K = ifelse(is.infinite(sigmaH), 1, sigmaH * KH / (sigmaH * KH + sigmaV * V0))) %>% 
+    # # Basic reproduction number
+    # mutate(R0 = K * sqrt(C * sigmaV^2 * V0 * betaV * thetaV * lf)) %>% 
     # Derivative of biting rate term wrt vector abundance
     mutate(dKdV0 = -sigmaV * K^2 / (sigmaH * KH)) %>% 
     # Derivative of vector abundance wrt variable
@@ -208,7 +209,7 @@ R0_deriv_func <- function(in_df) {
       TRUE ~ 0
     )) %>% 
     # Derivative of R0 wrt variable
-    mutate(dR0dk = (C / (2 * R0 + eps)) * case_when(
+    mutate(dR0dpar = (C / (2 * R0 + eps)) * case_when(
       focal_var == "lf" ~ sigmaV^2 * betaV * K * thetaV * (2 * dKdV0 * dV0dvar * V0 * lf + dV0dvar * K * lf + K * V0 * lf / (etaV * (lf^2) + eps) + K * V0),
       focal_var == "sigmaV" ~ 2 * V0 * betaV * thetaV * lf * K * sigmaV * (K + sigmaV * dKdV0 * dV0dvar),
[…]

### 2023-10-02 code/host-traits.R

@@ -10,10 +10,10 @@
 
 ## Set resolution for host trait variation
 # Host density vector: Number of values to include to consider for vertebrate host density
-KH_vec_length <- 300
+KH_vec_length <- 100
 
 # Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 300
+sigmaH_vec_length <- 100
 
 ## Host life history & behavioral traits
 # Host recruitment rate:
@@ -31,7 +31,7 @@ sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
 sigmaH_baseline <- 100
 
 # Host carrying capacity
-KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length) %>%
+KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length - 6) %>%
   c(10^seq(-2,5)) %>%
   unique() %>% sort()
 

### 2023-10-02 code/get-outputs.R
fix sensitivity analysis calculations

@@ -31,9 +31,10 @@ library(progress)
 eps <- .Machine$double.eps
 
 # Initialize a data frame to save our analyses
-init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
-                  sigmaH = c(), KH = c(), variable = c(),
-                  lowHCI = c(), highHCI = c(), mean = c(), median = c())
+init.df <- tibble(system_ID = character(), Temperature = double(), 
+                  Model = character(), sigmaH = double(), KH = double(), 
+                  variable = character(), lowHCI = double(), highHCI = double(),
+                  mean = double(), median = double())
 
 
 # Load in vector trait data
@@ -44,7 +45,7 @@ samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
 sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
 
-data.Vec <- data.Vec%>% 
+data.Vec <- data.Vec %>% 
   filter(sample_num %in% sample_inds)
 
 # Load in host trait data
@@ -109,19 +110,18 @@ Topt_heat_func <- function(in_df, system_name) {
     # Basic reproduction number
     mutate(R0 = sqrt(RV*RH)) %>%
     # Filter to maximum value of R0
-    group_by(system_ID, sample_num, sigmaH, KH) %>%
+    group_by(system_ID, sigmaH, KH, sample_num) %>%
     filter(R0 == max(R0)) %>%
     # Get temperature at which R0 is maximized
     rename(Topt = Temperature) %>%
-    dplyr::select(system_ID, sample_num, Model, sigmaH, KH, Topt) %>%
+    dplyr::select(system_ID, Model, sigmaH, KH, Topt, sample_num) %>%
     ungroup() %>%
-    pivot_longer(cols = Topt, names_to = "variable", values_to = "value") %>%
-    group_by(system_ID, Model, sigmaH, KH, variable) %>%
+    group_by(system_ID, Model, sigmaH, KH, Topt) %>%
     summarise(
-      lowHCI = quantile(value, 0.055),
-      highHCI = quantile(value, 0.945),
-      mean = mean(value),
-      median = median(value),
+      lowHCI = quantile(Topt, 0.055),
+      highHCI = quantile(Topt, 0.945),
+      mean = mean(Topt),
+      median = median(Topt),
       .groups = "keep"
     )
 }
[…]

### 2023-10-02 code/host-traits.R

@@ -10,10 +10,10 @@
 
 ## Set resolution for host trait variation
 # Host density vector: Number of values to include to consider for vertebrate host density
-KH_vec_length <- 100
+KH_vec_length <- 300
 
 # Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 100
+sigmaH_vec_length <- 300
 
 ## Host life history & behavioral traits
 # Host recruitment rate:

### 2023-10-02 code/host-traits.R
re-calculate sensitivity values

@@ -8,6 +8,8 @@
 ## Initialized March 2023
 # _______________________________________________________________________________
 
+library(tidyverse)
+
 ## Set resolution for host trait variation
 # Host density vector: Number of values to include to consider for vertebrate host density
 KH_vec_length <- 300

### 2023-10-02 manuscript-figures.Rmd
indicate where CTwidth = 0 in CTmin/max plots

@@
 CTmin_df <- data.CT %>%
-  filter(variable == "CTmin") %>%
+  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
+  pivot_wider(names_from = variable, values_from = median) %>% 
+  # If CTwidth is essentially zero, set CTmin to Inf indicating R0 < 1
+  mutate(CTmin = if_else(CTwidth < eps, Inf, CTmin)) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
   # Arrange along the plotting variables
-  arrange(system_ID, KH, sigmaH_proxy, median) %>%
+  arrange(system_ID, KH, sigmaH_proxy, CTmin) %>%
   ungroup() %>%
   # Assign a value for cases where R0<1 for all temperatures
-  mutate(median_proxy = ifelse(is.finite(median), median, 100))
+  mutate(CTmin = ifelse(is.finite(CTmin), CTmin, 100))
 
@@
 
-maxCTmin <- ceiling(max(filter(CTmin_df, is.finite(median))$median))
+maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))
 
@@
 CTmin_heat_plots <- CTmin_df %>%
-  select(-median) %>%
   ## Set up plot ##
@@
   # color = width of parasite thermal median_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmin)) +
   # CTmin for FINITE sigmaH:
@@
 CTmax_df <- data.CT %>%
-  filter(variable == "CTmax") %>%
+  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
+  pivot_wider(names_from = variable, values_from = median) %>% 
+  # If CTwidth is essentially zero, set CTmax to -Inf indicating R0 < 1
+  mutate(CTmax = if_else(CTwidth < eps, Inf, CTmax)) %>%
   mutate(sigmaH_proxy = sigmaH) %>%
   # Arrange along the plotting variables
-  arrange(system_ID, KH, sigmaH_proxy, median) %>%
+  arrange(system_ID, KH, sigmaH_proxy, CTmax) %>%
   ungroup() %>%
   # Assign a value for cases where R0<1 for all temperatures
-  mutate(median_proxy = ifelse(is.finite(median), median, -100))
+  mutate(CTmax = ifelse(is.finite(CTmax), CTmax, -100))
 
@@
 
-minCTmax <- floor(min(filter(CTmax_df, is.finite(median))$median))
+minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))
 
@@
 CTmax_heat_plots <- CTmax_df %>%
-  select(-median) %>%
   ## Set up plot ##
@@
   # color = width of parasite thermal median_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmax)) +
   # CTmin for FINITE sigmaH:

### 2023-11-27 manuscript-figures.Rmd
Save references from which data was obtained

@@
 library(see) # for half-violin plots
-library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure
+library(zplyr) #devtools::install_github("burchill/zplyr") from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contdact comparison figure
 

### 2023-12-07 manuscript-figures.Rmd
remake sensitivity plot
following Mordecai 2013 Fig. 3(a)

@@
   df <- df %>%
-    mutate(focal_var = ifelse(focal_var == "muV", "lf", focal_var)) %>%
     mutate(focal_var = factor(focal_var,
-                              levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
+                              levels = c("total", "muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                               labels = c(
-                                TeX("Adult lifespan"),
+                                TeX("Overall"),
+                                TeX("Adult mortality rate"),
                                 TeX("Biting frequency"),
@@
                                 TeX("Prob. of immature survival"),
-                                TeX("Prob. of surviving EIP"),
+                                TeX("Parasite development rate"),
                                 TeX("Vector competence")
@@
 
+temp_lims <- data.dR0dvar %>% 
+  filter(focal_var == "Adult mortality rate") %>% 
+  filter(!is.na(median)) %>% 
+  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
+  filter(median_R0 > 0) %>%
+  group_by(system_ID) %>% 
+  summarise(min_Temp = min(Temperature),
+            max_Temp = max(Temperature))
+
+val_lims <- tibble(sigmaH = c(100, Inf), 
+                   min_median = c(-90, -0.05), 
+                   max_median = c(5, 0.5))
+
 dR0dk.df <- data.dR0dvar %>%
@@
                filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
-  filter(median_R0 > 0) %>%
+  right_join(temp_lims) %>% 
+  group_by(system_ID) %>% 
+  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
+  ungroup() %>% 
+  right_join(val_lims) %>% 
+  group_by(sigmaH) %>% 
+  filter(median > min_median, median < max_median) %>% 
+  # filter(median_R0 > 0) %>%
   mutate(abs_median = abs(median)) %>%
+  # filter(abs_median < 1e10) %>%
   mutate(sign_median = sign(median)) %>%
@@
 plot.dR0dk <- dR0dk.df %>%
+  # filter(focal_var %in% c("Adult mortality rate")) %>%
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = median, color = focal_var, linetype = (as.factor(sign_median)))) +
+  ggplot(aes(x = Temperature, y = median, color = focal_var, 
+             # linetype = (as.factor(sign_median))
+             )) +
   geom_line(lwd = 1) +
@@
     name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
+    values = rev(c(c4a("misc.okabe", 7), "black"))
   ) +
@@
     name = unname(TeX("Local sensitivity of $R_0$")),
-    # limits = c(-2,2),
-    # limits = 10^c(-4, 3),
-    # breaks = 10^(seq(-4, 3)),
-    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
+    # limits = c(-1, 1),
+    # limits = 10^c(-4, 4),
+    # breaks = 10^(seq(-4, 4)),
+    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
     # trans = "log10",

### 2023-12-07 code/get-outputs.R

@@ -189,37 +189,66 @@ CT_heat_func <- function(in_df, system_name) {
 
 # Function: Evaluate local derivatives of R0 with respect to mosquito traits
 R0_deriv_func <- function(in_df) {
-  out_df <- in_df %>% 
-    # # Pr(surviving the EIP)
-    # mutate(thetaV = exp(-1 / (lf * etaV + eps))) %>% 
-    # # Host constant
-    # mutate(C = betaH / (KH * (gammaH + muH))) %>% 
-    # # Biting rate term
-    # mutate(K = ifelse(is.infinite(sigmaH), 1, sigmaH * KH / (sigmaH * KH + sigmaV * V0))) %>% 
-    # # Basic reproduction number
-    # mutate(R0 = K * sqrt(C * sigmaV^2 * V0 * betaV * thetaV * lf)) %>% 
-    # Derivative of biting rate term wrt vector abundance
-    mutate(dKdV0 = -sigmaV * K^2 / (sigmaH * KH)) %>% 
-    # Derivative of vector abundance wrt variable
-    mutate(dV0dvar = case_when(
-      focal_var == "lf" ~ rhoL * KL,
-      focal_var == "sigmaV_f" ~ (rhoL * KL)/ ((sigmaV_f^2) * deltaL + eps),
-      focal_var == "deltaL" ~ (rhoL * KL)/ (sigmaV_f * (deltaL^2) + eps),
-      focal_var == "rhoL" ~ (KL * (1 - deltaL))/ (sigmaV_f * deltaL + eps),
-      TRUE ~ 0
-    )) %>% 
-    # Derivative of R0 wrt variable
-    mutate(dR0dpar = (C / (2 * R0 + eps)) * case_when(
-      focal_var == "lf" ~ sigmaV^2 * betaV * K * thetaV * (2 * dKdV0 * dV0dvar * V0 * lf + dV0dvar * K * lf + K * V0 * lf / (etaV * (lf^2) + eps) + K * V0),
-      focal_var == "sigmaV" ~ 2 * V0 * betaV * thetaV * lf * K * sigmaV * (K + sigmaV * dKdV0 * dV0dvar),
-      focal_var == "sigmaV_f" ~ sigmaV^2 * betaV * thetaV * lf * K * dV0dvar * (2 * dKdV0 * V0 + K),
-      focal_var == "deltaL" ~ sigmaV^2 * betaV * thetaV * lf * K * dV0dvar * (2 * dKdV0 * V0 + K),
[…]

### 2023-12-07 manuscript-figures.Rmd
update sensitivity figure

@@
 '}
-KH_vals <- c(1)
-
-temp_lims <- data.dR0dvar %>% 
-  filter(focal_var == "Adult mortality rate") %>% 
-  filter(!is.na(median)) %>% 
-  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
+KH_vals <- c(10)
+
+data.dR0dT <- data.dR0dvar %>% 
+  filter(KH %in% KH_vals)
+
+temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) %>%
   filter(median_R0 > 0) %>%
+  # filter(!is.na(median_R0)) %>%
   group_by(system_ID) %>% 
@@
 
-val_lims <- tibble(sigmaH = c(100, Inf), 
+val_lims <- tibble(sigmaH = unique(data.dR0dT$sigmaH), 
                    min_median = c(-90, -0.05), 
@@
 
-dR0dk.df <- data.dR0dvar %>%
+dR0dk.df <- data.dR0dT %>%
   filter(
     KH %in% KH_vals,
-    sigmaH %in% c(100, Inf)
+    sigmaH %in% unique(data.dR0dT$sigmaH)
   ) %>%
-  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
+  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
+  # Restrict to relevant temperatures (V0 and R0 > 0)
   right_join(temp_lims) %>% 
@@
   ungroup() %>% 
+  # Restrict plotted values (so all plots are visible)
   right_join(val_lims) %>% 
   group_by(sigmaH) %>% 
-  filter(median > min_median, median < max_median) %>% 
+  # filter(median > min_median, median < max_median) %>% 
+  ungroup() %>% 
   # filter(median_R0 > 0) %>%
   mutate(abs_median = abs(median)) %>%
-  # filter(abs_median < 1e10) %>%
+  # Normalize values to better tell which is most important
   mutate(sign_median = sign(median)) %>%
-  filter(sign_median != 0, !is.na(sign_median)) %>%
+  group_by(system_ID, sigmaH, KH) %>% 
+  mutate(median = ifelse(sign_median>0,
+                         sign_median * median / max(median, na.rm = TRUE),
+                         sign_median * median / min(median, na.rm = TRUE))) %>% 
+  # filter(sign_median != 0, !is.na(sign_median)) %>%
   arrange(sign_median) %>%
@@
 
+# R0 derivative dataframe
+R0deriv_df <- data.R0 %>% 
+  group_by(system_ID, Model, sigmaH, KH) %>% 
+  arrange(system_ID, Model, sigmaH, KH, Temperature) %>%
+  mutate(deriv = (mean - lag(mean)) / (Temperature - lag(Temperature)))
+
+test_plot <- R0deriv_df %>% 
+  filter(KH %in% c(1), sigmaH %in% c(100, Inf), median > 0) %>% 
+  ggplot(aes(x = Temperature, y = deriv)) +
+  geom_line() +
+  geom_hline(yintercept = 0) +
+  facet_rep_grid(
+    rows = vars(KH, sigmaH),
+    cols = vars(system_label),
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free"
+  ) 
+test_plot
+
+# NB: in order to produce an R0 TPC, overall derivative should go from positive to negative
 plot.dR0dk <- dR0dk.df %>%
-  # filter(focal_var %in% c("Adult mortality rate")) %>%
+  # filter(focal_var %in% c("Overall")) %>%
   # Make a stacked plot, colored by parameter
@@
   geom_line(lwd = 1) +
+  geom_hline(yintercept = 0) +
   scale_color_manual(
@@
     name = unname(TeX("Local sensitivity of $R_0$")),
-    # limits = c(-1, 1),
+    limits = c(-1, 1),
     # limits = 10^c(-4, 4),
@@
   facet_rep_grid(
+    rows = vars(KH, sigmaH),
     cols = vars(system_label),
-    rows = vars(KH, sigmaH),
     labeller = labeller(

### 2023-12-07 code/get-outputs.R

@@ -196,11 +196,11 @@ R0_deriv_func <- function(in_df) {
     out_df <- in_df %>% 
       # Derivative of V0 wrt focal variable
       mutate(V0_deriv = ifelse(V0 == 0, 0,case_when(
-        focal_var == "sigmaV" ~ rhoL * KL / (sigmaV_f * sigmaV * deltaL + eps),
-        focal_var == "sigmaV_f" ~ (rhoL * KL)/ ((sigmaV_f^2) * deltaL + eps),
+        focal_var == "sigmaV" ~ rhoL * KL / (sigmaV_f * deltaL * (sigmaV)^2 + eps),
+        focal_var == "sigmaV_f" ~ (rhoL * KL)/ (deltaL * (sigmaV_f^2) + eps),
         focal_var == "deltaL" ~ (rhoL * KL)/ (sigmaV_f * (deltaL^2) + eps),
         focal_var == "rhoL" ~ KL * ((1/(muV + eps)) - (1/(sigmaV_f + eps))),
-        focal_var == "muV" ~ - rhoL * KL / (muV^2 + eps),
+        focal_var == "muV" ~ -1 * rhoL * KL / (muV^2 + eps),
         TRUE ~ 0
       ))) %>% 
       # Derivative of R0 wrt focal variable
@@ -211,7 +211,9 @@ R0_deriv_func <- function(in_df) {
         focal_var == "deltaL" ~ 0.5 * V0_deriv / (V0 + eps),
         focal_var == "rhoL" ~ 0.5 * V0_deriv / (V0 + eps),
         focal_var == "etaV" ~ 0.5 * muV / (etaV^2 + eps),
-        focal_var == "muV" ~ ifelse(etaV>0,- 0.5 * ( (V0_deriv / (V0 + eps)) - (1/(etaV + eps)) - (1/(muV + eps))), 0),
+        focal_var == "muV" ~ ifelse(etaV>0, 
+                                    0.5 * ((V0_deriv / (V0 + eps)) - (1/(etaV + eps)) - (1/(muV + eps))),
+                                    0),
         TRUE ~ 0
       )) %>% 
       mutate(Temp_deriv = R0_deriv * dpardT)
@@ -220,31 +222,33 @@ R0_deriv_func <- function(in_df) {
   } else {
     out_df <- in_df %>% 
       # Derivative of V0 wrt focal variable
[…]

### 2023-12-10 manuscript-figures.Rmd
clean up code

--- 2023-12-07 manuscript-figures.Rmd
@@
 # Vector trait TPC data
+
+# Create data frame of TPCs
+
 data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
   pathosystem_labeller()
+
+thin_size <- 500
+num_samples <- length(unique(data.Vec$sample_num))
+sample_inds <- sample(1:num_samples, thin_size, replace = FALSE)
+
+data.Vec <- filter(data.Vec, sample_num %in% sample_inds)
 
@@
 Topt.HPD <- read_rds("results/Topt_HPD_unc.rds") %>%
+  mutate(focal_var = ifelse(focal_var == "lf", "muV", focal_var)) %>% 
   ungroup() %>%
@@
 
-```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
+```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
 Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
@@
 '}
-KH_vals <- c(1)
-
-temp_lims <- data.dR0dvar %>% 
-  filter(focal_var == "Adult mortality rate") %>% 
-  filter(!is.na(median)) %>% 
-  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
-  filter(median_R0 > 0) %>%
+KH_vals <- c(1, 100)
+
+data.dR0dT <- data.dR0dvar %>%
+  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH)))
+
+temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+  filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) %>%
+  filter(!is.na(median_R0), median_R0 > eps) %>%
   group_by(system_ID) %>% 
@@
   filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
+  filter(!is.na(median)) %>% 
   ungroup() %>% 
+  # Restrict plotted values (so all plots are visible)
   right_join(val_lims) %>% 
   group_by(sigmaH) %>% 
-  filter(median > min_median, median < max_median) %>% 
+  # filter(median > min_median, median < max_median) %>% 
+  ungroup() %>% 
   # filter(median_R0 > 0) %>%
   mutate(abs_median = abs(median)) %>%
-  # filter(abs_median < 1e10) %>%
+  # Normalize values to better tell which is most important
   mutate(sign_median = sign(median)) %>%
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(norm_median = ifelse(sign_median>0,
+                              sign_median * median / max(median, na.rm = TRUE),
+                              sign_median * median / min(median, na.rm = TRUE))) %>%
   filter(sign_median != 0, !is.na(sign_median)) %>%
@@
 
+# # R0 derivative dataframe
+# R0deriv_df <- data.R0 %>% 
+#   group_by(system_ID, Model, sigmaH, KH) %>% 
+#   arrange(system_ID, Model, sigmaH, KH, Temperature) %>%
+#   mutate(deriv = (mean - lag(mean)) / (Temperature - lag(Temperature)))
+
+# test_plot <- R0deriv_df %>% 
+#   filter(KH %in% c(1), sigmaH %in% c(100, Inf), median > 0) %>% 
+#   ggplot(aes(x = Temperature, y = deriv)) +
+#   geom_line() +
+#   geom_hline(yintercept = 0) +
+#   facet_rep_grid(
+#     rows = vars(KH, sigmaH),
+#     cols = vars(system_label),
+#     labeller = labeller(
+#       system_label = sens_labels,
+#       sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+#       KH = as_labeller(appender_KH, default = label_parsed)
+#     ),
+#     scales = "free"
+#   ) 
+# test_plot
+
+# NB: in order to produce an R0 TPC, overall derivative should go from positive to negative
 plot.dR0dk <- dR0dk.df %>%
-  # filter(focal_var %in% c("Adult mortality rate")) %>%
+  # filter(focal_var %in% c("Overall")) %>%
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = median, color = focal_var, 
+  ggplot(aes(x = Temperature, y = norm_median, color = focal_var, 
              # linetype = (as.factor(sign_median))
   )) +
-  geom_line(lwd = 1) +
+  geom_line(lwd = 0.5) +
+  geom_hline(yintercept = 0, lwd = 0.25) +
   scale_color_manual(
@@
   scale_y_continuous(
-    name = unname(TeX("Local sensitivity of $R_0$")),
+    name = unname(TeX("Normalized local sensitivity of $\\,R_0$ to temperature")),
     # limits = c(-1, 1),
@@
   ) +
-  scale_linetype_manual(
-    name = "Sign of sensitivity:",
-    values = c(1, 3),
-    breaks = c(1, -1),
-    labels = c("Positive", "Negative")
-  ) +
+  # scale_linetype_manual(
+  #   name = "Sign of sensitivity:",
+  #   values = c(1, 3),
+  #   breaks = c(1, -1),
+  #   labels = c("Positive", "Negative")
+  # ) +
   facet_rep_grid(
+    rows = vars(KH, sigmaH),
     cols = vars(system_label),
-    rows = vars(KH, sigmaH),
     labeller = labeller(
@@
 plot.dR0dk
+```
+
+```{r fig-S8_3_dR0dvar_comparison, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
+Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
+Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
+Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
+'}
+
+comp_dR0dk.df <- dR0dk.df %>%
+  # filter(sigmaH == 10) %>% 
+  filter(focal_var != "Overall") %>% 
+  group_by(system_ID, Temperature, sigmaH, KH) %>% 
+  mutate(abs_median = abs(median),
+         total_sens = sum(abs_median),
+         prop_sens = abs_median / total_sens) %>% 
+  arrange(system_label, Temperature, KH, sigmaH, focal_var) #%>% 
+# filter(focal_var %in% c("Parasite development rate", "Biting frequency"))
+# # mutate(median = abs(median)) %>% 
+# select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
+# pivot_wider(names_from = KH, values_from = prop_sens) %>% 
+# mutate(sens_comp = ifelse(`10` == 0 & `1` == 0,
+#                           0,
+#                           (`10` - `1`) / ((`10` + `1`)/2)))
+# mutate(sens_comp = (`10` - `1`) / `1`)
+
+plot.comp_dR0dk <- comp_dR0dk.df %>%
+  # filter(focal_var %in% c("Overall")) %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
+             # linetype = (as.factor(sign_median))
+  )) +
+  # geom_area() +
+  geom_line(lwd = 1) +
+  geom_hline(yintercept = 0, lwd = 0.25) +
+  scale_color_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(
+    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
+    # limits = c(-100, 100),
+    # limits = c(-0.2, 0.1),
+    # limits = 10^c(-4, 4),
+    # breaks = 10^(seq(-4, 4)),
+    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
+    # trans = "log10",
+    expand = c(0, 0)
+  ) +
+  # scale_linetype_manual(
+  #   name = "Sign of sensitivity:",
+  #   values = c(1, 3),
+  #   breaks = c(1, -1),
+  #   labels = c("Positive", "Negative")
+  # ) +
+  facet_rep_grid(
+    rows = vars(sigmaH, KH),
+    cols = vars(system_label),
+    labeller = labeller(
+      system_label = sens_labels,
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  guides(linetype = guide_legend(
+    title.position = "left",
+    title.vjust = 0.5,
+    direction = "vertical"
+  )) +
+  theme_minimal_hgrid(10) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 8),
+    legend.position = "bottom",
+    legend.justification = 0.5,
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+plot.comp_dR0dk
+```
+
+```{r fig-S8_4_dR0dvar_compzoom, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
+Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
+Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
+Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
+'}
+
+compzoom_dR0dk.df <- comp_dR0dk.df %>%
+  filter(sigmaH == 10) %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
+  pivot_wider(names_from = KH, values_from = prop_sens) %>%
+  mutate(abs_comp = abs(`1`) - abs(`100`))
+
+plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
+  # filter(focal_var %in% c("Parasite development rate", "Adult mortality rate", "Biting frequency")) %>%
+  # Make a stacked plot, colored by parameter
+  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
+             # linetype = (as.factor(sign_median))
+  )) +
+  # geom_area() +
+  # geom_smooth(se = FALSE) +
+  geom_line(lwd = 1) +
+  geom_hline(yintercept = 0, lwd = 0.25) +
+  scale_color_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(
+    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 10$ ")),
+    # limits = c(-100, 100),
+    # limits = c(-0.2, 0.1),
+    # limits = 10^c(-4, 4),
+    # breaks = 10^(seq(-4, 4)),
+    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
+    # trans = "log10",
+    expand = c(0, 0)
+  ) +
+  # scale_linetype_manual(
+  #   name = "Sign of sensitivity:",
+  #   values = c(1, 3),
+  #   breaks = c(1, -1),
+  #   labels = c("Positive", "Negative")
+  # ) +
+  facet_rep_grid(
+    rows = vars(sigmaH),
+    cols = vars(system_label),
+    labeller = labeller(
+      system_label = sens_labels,
+      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      # KH = as_labeller(appender_KH, default = label_parsed)
+    ),
+    scales = "free"
+  ) +
+  guides(linetype = guide_legend(
+    title.position = "left",
+    title.vjust = 0.5,
+    direction = "vertical"
+  )) +
+  theme_minimal_hgrid(10) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 8),
+    legend.position = "bottom",
+    legend.justification = 0.5,
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text.x = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+plot.compzoom_dR0dk
 ```

### 2023-12-10 code/data-cleaning.R

@@ -229,6 +229,15 @@ data.Anga_fecundity <- read.csv("data/raw/Anopheles_fecundity.csv", header = TRU
   mutate(pathogen = NA) %>% 
   dplyr::select(trait.name, T, trait, mosquito_species, pathogen, lead_author, year) 
 
+### * Anopheles lifespan death points ----
+# We lack data expressing temperatures at which Anopheles mosquitoes can never survive
+# This impedes our ability to properly fit TPCs for adult mortality rates
+# We add two additional data points setting lifespan to zero at 0C and 50C
+data.An_extreme <- tibble(trait.name = "lf", T = c(0,50), trait = c(0,0), 
+                          mosquito_species = "Anopheles spp.", pathogen = NA)%>%
+  mutate(lead_author = "Dahlin") %>%
+  mutate(year = "2023")
+
 ### * Villena 2022 ----
 data.Villena2022 <- read.csv("data/raw/Villena_2022/traits.csv", header = TRUE) %>%
   # make mosquito names consistent with other data
@@ -287,7 +296,7 @@ data.Villena2022 <- data.Villena2022 %>%
 # Combine all data frames
 data.All <- rbind(data.Mordecai2013, data.Mordecai2017, data.Shocket2018, 
                   data.Tesla2018, data.Shocket2020, data.Anga_fecundity, 
-                  data.Villena2022)
+                  data.Villena2022, data.An_extreme)
 
 # 3) Rename non-focal systems and combine synonymous traits -----------------
 
@@ -419,7 +428,7 @@ if (plot_bool) {
     "PDR" ~ "Parasite development rate"
   )
   
- data.Viz <- data.Viz %>% mutate(trait_label = factor(trait_label, levels = label_order))
+  data.Viz <- data.Viz %>% mutate(trait_label = factor(trait_label, levels = label_order))
   
   
   # show thermal response of all traits across all systems
@@ -435,19 +444,22 @@ if (plot_bool) {
     facet_wrap(~ trait_label, scales = "free") +
     theme_cowplot(16)
   
-
+  
   # show thermal response data for focal systems only
   select_trait_plots <- data.Viz %>% 
     filter(system_ID %in% c(#"Aedes aegypti / DENV", "Aedes aegypti / none", 
-                            # "Aedes aegypti / ZIKV", "Aedes aegypti / none",
-                            # "Aedes albopictus / DENV", "Aedes albopictus / none",
[…]

### 2023-12-10 code/get-outputs.R

@@ -40,7 +40,7 @@ init.df <- tibble(system_ID = character(), Temperature = double(),
 # Load in vector trait data
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 # Thin out the vector trait data samples
-thin_size <- 500
+thin_size <- 10
 samples <- unique(data.Vec$sample_num)
 num_samples <- length(samples)
 sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
@@ -116,7 +116,7 @@ Topt_heat_func <- function(in_df, system_name) {
     rename(Topt = Temperature) %>%
     dplyr::select(system_ID, Model, sigmaH, KH, Topt, sample_num) %>%
     ungroup() %>%
-    group_by(system_ID, Model, sigmaH, KH, Topt) %>%
+    group_by(system_ID, Model, sigmaH, KH) %>%
     summarise(
       lowHCI = quantile(Topt, 0.055),
       highHCI = quantile(Topt, 0.945),
@@ -191,68 +191,73 @@ CT_heat_func <- function(in_df, system_name) {
 R0_deriv_func <- function(in_df) {
   
   sigmaH_val <- unique(in_df$sigmaH)
-  # Infinite sigmaH case
-  if (is.infinite(sigmaH_val)) {
-    out_df <- in_df %>% 
-      # Derivative of V0 wrt focal variable
-      mutate(V0_deriv = ifelse(V0 == 0, 0,case_when(
-        focal_var == "sigmaV" ~ rhoL * KL / (sigmaV_f * deltaL * (sigmaV)^2 + eps),
-        focal_var == "sigmaV_f" ~ (rhoL * KL)/ (deltaL * (sigmaV_f^2) + eps),
-        focal_var == "deltaL" ~ (rhoL * KL)/ (sigmaV_f * (deltaL^2) + eps),
-        focal_var == "rhoL" ~ KL * ((1/(muV + eps)) - (1/(sigmaV_f + eps))),
-        focal_var == "muV" ~ -1 * rhoL * KL / (muV^2 + eps),
-        TRUE ~ 0
-      ))) %>% 
-      # Derivative of R0 wrt focal variable
-      mutate(R0_deriv = case_when(
-        focal_var == "sigmaV" ~ 0.5 * (sigmaV * V0_deriv + 2 * V0) / (sigmaV * V0 + eps),
-        focal_var == "betaV" ~ 0.5 / (betaV + eps),
[…]

### 2023-12-10 code/get-thermal-trait-priors.R

@@ -514,7 +514,7 @@ samples <- tibble(
 )
 
 # Go through all trait/system combinations to generate TPC parameter posterior samples
-for (system_index in 11:dim(distinct_combos)[1]) {
+for (system_index in 1:dim(distinct_combos)[1]) {
   # Pull system information
   system_sample <- distinct_combos$system_ID[system_index]
   trait_in <- distinct_combos$trait.name[system_index]

### 2023-12-10 code/sensitivity.R

@@ -242,6 +242,7 @@ full.ddTR0.HPD <- expand_grid(data.ddTR0HPD,
   mutate(R0 = sqrt(RV*RH)) %>%
   ungroup() %>% 
   arrange(system_ID, sample_num, sigmaH, KH, Temperature) %>% 
+  # Calculate temperature derivative of R0
   mutate(ddTR0 = (R0 - lag(R0)) / (Temperature - lag(Temperature))) %>% 
   select(system_ID, sample_num, sigmaH, KH, Temperature, ddTR0) %>% 
   group_by(system_ID, sigmaH, KH, Temperature) %>% 
@@ -298,6 +299,7 @@ for (var_name in temp_vars) {
     mutate(R0 = sqrt(RV*RH)) %>%
     ungroup() %>% 
     arrange(system_ID, sample_num, sigmaH, KH, Temperature) %>% 
+    # Calculate temperature derivative of R0
     mutate(ddTR0 = (R0 - lag(R0)) / (Temperature - lag(Temperature))) %>% 
     select(system_ID, sample_num, sigmaH, KH, Temperature, ddTR0) %>% 
     # c) Calculate the 95% HPD at each temperature
@@ -425,7 +427,7 @@ for (var_name in temp_vars) {
                      .combine = 'rbind') %dopar%  {
                        expand_grid(dplyr::filter(data.ToptHPD, 
                                                  KH %in% KH_vec[index_KH]), 
-                                           data.HPD.Vec) %>%  
+                                   data.HPD.Vec) %>%  
                          ungroup() %>% 
                          mutate(RV = ifelse(is.infinite(sigmaH),
                                             sigmaV * betaH / (1 / (lf + eps)), # Ross-Macdonald

### 2023-12-10 code/vector-traits.R

@@ -23,7 +23,7 @@ library(tidyverse)
 # 1) Load empirical trait data --------------------------------------------
 
 # # Run this to produce workable dataset from raw data for the first time
-# plot_bool <- FALSE # decide whether you'd like to generate a diagnostic plot
+plot_bool <- FALSE # decide whether you'd like to generate a diagnostic plot
 source("code/data-cleaning.R")
 
 # # Alternatively, run this to load pre-processed dataset
@@ -51,12 +51,12 @@ write_rds(data.in.transform, "results/TPC_param_samples.rds")
 Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
 
 # Thin sample size
-thin_size <- 500 # full = 1000, thin = 100
+thin_size <- 5000 # full = 1000, thin = 100
 
 plot_bool = FALSE
 source("code/trait-transform.R")
 
-write_rds(data.in.params, "results/VecTPC_vals", compress = "gz")
+write_rds(data.in.params, "results/VecTPC_vals.rds", compress = "gz")
 
 # remove work sets (these may be taking up a lot of memory)
 rm("combined_df", "Infection_df", "noInfection_df", "TPC_df", "data.in.transform")
